### 2019-07-29 concept_dev.tex
template for ConDev

\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

%SetFonts

%SetFonts

\title{Concept Dev for COMP study}
\author{Sitaram Devarakonda \& George Chacko}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle
\section{Motivation} Making discovery in a manner that would leverage existing resources and skills with focus on  the computer science field, which has experienced vigorous growth in the last twenty years. Citation analysis is a particular focus.

%\subsection{}
\end{document}

### 2019-08-02 concept_dev.tex
notes on progress so far

@@
 
-%\subsection{}
+\section{Data and Methods} The following sections describe the datasets and initial data exploration 
+\subsection{Year slices} Year slices were developed for all publications from 1996-2018.
+All publications of language 'English' and with at-least 2 references and complete publication data in Scopus are selected.
+Publications type include (article, conference paper, dissertation etc) and belong to subject area 'COMP'.
+%\vspace{-7mm}
+\begin{table}[ht]
+\caption{Summary of base Scopus Analytical data set. The number of unique publications, unique references, total references . } 
+\label{tab:summary_data}
+\centering
+\scalebox{0.7}{
+\begin{tabular}{|r  ccc |}
+  \hline
+Year & Unique Publications & Unique References  & Total References \\ 
+  \hline
+1996 & 30,740 & 184,617 & 318,700 \\ 
+1997 &37,166 & 228,464 & 386,627 \\
+1998 & 44,764 & 250,491 & 438,908 \\
+1999 & 40,434 & 237,175 & 413,681 \\
+2000 & 44,636 & 261,393 & 460,310 \\
+2001 & 62,000 & 343,937 & 619,330 \\
+2002 & 71,645 & 394,882 &722,278 \\
+2003 & 83,676 & 438,498 & 849,950 \\
+2004 & 82,914 & 482,475 & 915,997 \\
+2005 & 107,905 & 591,784 & 1,193,198 \\
+2006 & 139,379 & 713,924 & 1,531,101 \\
+2007 & 170,396 & 829,444 & 1,830,944 \\
+2008 & 204,084 & 1,000,790 & 2,226,980 \\
+2009 & 239,113 & 1,222,312 & 2,790,194 \\
+2010 & 254,763 & 1,374,471 & 3,164,912 \\
+2011 & 255,144 & 1,519,064 & 3,419,719 \\
+2012 & 170,364 & 1,374,757 & 2,785,900 \\
+2013 & 195,008 & 1,606,955 & 3,353,390 \\
+2014 & 264,968 & 1,863,488 & 4,260,613 \\
+2015 & 297,534 & 2,037,838 & 4,762,036 \\
+2016 & 305,372 & 2,217,138 & 5,140,149 \\
+2017 & 291,481 & 2,349,259 & 5,262,725 \\
+2018 & 316,495 & 2,623,449 & 6,009,386 \\
+ \hline
+\end{tabular}}
+\vspace{-1mm}%Put here to reduce too much white space after your table 
+\end{table}
+
+\subsection{Disciplinary Composition} One way to identify the growth and diversity of a field might be the subject areas of publications and how it changes over time .So We  calculated the disciplinary composition for all the publications and unique references from 1996-2018.
+These are calculated based on ASJC codes which are assigned by Scopus at journal level, i.e every publication in a journal or conference will have the same subject area.
+Journals or conferences can have multiple subject areas.
+Multidisciplinary journals such as Nature, Science, Proceedings of the National Academy of Sciences are classified as General which result in the loss of computer science articles published in those journals.
+Also there is a lot of ambiguity in journals/conferences with multiple ASJC codes.
+Following possibilities can be explored to overcome ambiguity:
+
+\begin{description}
+\item[$\bullet$ ] NSF follows a single subject area for journals which can be used for publication level classification.
+\item[$\bullet$ ] Ludo Waltman methodology for publication-level classification (uses direct citation)
+\item[$\bullet$ ] Kevin Boyack methodology 
+\item[$\bullet$ ] Using Scopus FPE to generate publication level classification
+\item[$\bullet$ ] Obtain top conferences/journals in COMP field and analyze their citation patterns. (Assuming they contain articles related to single discipline)
+\end{description}
+
+\subsection{Possible next steps(based on discussion)}  Analyze the citation patterns of top authors in the field and how it evolved over time.
+Selecting authors with at least 30 papers published might be a good place to start.
+Another experiment might be to approach the diversity of computer science from other disciplines.
+i.e studying the citation patterns of other disciplines and how computer science has been more inclusive over time.
 \end{document}

### 2019-08-15 concept_dev.tex
fleshed out the justification

@@
 
-\subsection{Disciplinary Composition} One way to identify the growth and diversity of a field might be the subject areas of publications and how it changes over time .So We  calculated the disciplinary composition for all the publications and unique references from 1996-2018.
-These are calculated based on ASJC codes which are assigned by Scopus at journal level, i.e every publication in a journal or conference will have the same subject area.
-Journals or conferences can have multiple subject areas.
-Multidisciplinary journals such as Nature, Science, Proceedings of the National Academy of Sciences are classified as General which result in the loss of computer science articles published in those journals.
-Also there is a lot of ambiguity in journals/conferences with multiple ASJC codes.
-Following possibilities can be explored to overcome ambiguity:
+\subsection{Disciplinary Composition} One way to identify the growth and diversity of a field is by considering the count and subject areas of scientific publications in it and how these change over time.
+In our study of the evolution of the field of computer science, we initially used the All Science Journal Classification (ASJC) codes assigned by Scopus to journals to crudely estimate publications and unique references from 1996-2018.
+Accordingly, we searched for articles or conference proceedings labelled computer science (COMP), one of the 27 major subject areas in the Scopus classification system.
+ICOMP itself comprises 13 minor subject areas such as Hardware and Architecture and Artificial Intelligence.
+A limitation of the ASJC system is that every publication inherits its journal or conference subject area(s), which is problematic for a field that has had broad influence and interactions on other fields.
+Further, multidisciplinary journals such as Nature, Science, Proceedings of the National Academy of Sciences are classified under General and computer science articles published in those journals would be overlooked.
+Thus, we followed an initial subsetting of Scopus using COMP and GENERAL with an article level clustering approach.
+:
 

### 2019-08-15 concept_dev.tex
updated base table with counts from Aug 15, 2019 regenerated data

@@
 %\vspace{-7mm}
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Thu Aug 15 14:13:47 2019
 \begin{table}[ht]
-\caption{Summary of base Scopus Analytical data set. The number of unique publications, unique references, total references . } 
+\caption{Summary of initial Scopus Analytical data set. The number of unique publications, unique references, total references . } 
 \label{tab:summary_data}
+\vspace{1mm}
 \centering
 \scalebox{0.7}{
-\begin{tabular}{|r  ccc |}
+\begin{tabular}{|r rrr r|}
   \hline
-Year & Unique Publications & Unique References  & Total References \\ 
+ & Year & Unique Publications & Unique References & Total References \\ 
   \hline
-1996 & 30,740 & 184,617 & 318,700 \\ 
-1997 &37,166 & 228,464 & 386,627 \\
-1998 & 44,764 & 250,491 & 438,908 \\
-1999 & 40,434 & 237,175 & 413,681 \\
-2000 & 44,636 & 261,393 & 460,310 \\
-2001 & 62,000 & 343,937 & 619,330 \\
-2002 & 71,645 & 394,882 &722,278 \\
-2003 & 83,676 & 438,498 & 849,950 \\
-2004 & 82,914 & 482,475 & 915,997 \\
-2005 & 107,905 & 591,784 & 1,193,198 \\
-2006 & 139,379 & 713,924 & 1,531,101 \\
-2007 & 170,396 & 829,444 & 1,830,944 \\
-2008 & 204,084 & 1,000,790 & 2,226,980 \\
-2009 & 239,113 & 1,222,312 & 2,790,194 \\
-2010 & 254,763 & 1,374,471 & 3,164,912 \\
-2011 & 255,144 & 1,519,064 & 3,419,719 \\
-2012 & 170,364 & 1,374,757 & 2,785,900 \\
-2013 & 195,008 & 1,606,955 & 3,353,390 \\
-2014 & 264,968 & 1,863,488 & 4,260,613 \\
-2015 & 297,534 & 2,037,838 & 4,762,036 \\
-2016 & 305,372 & 2,217,138 & 5,140,149 \\
-2017 & 291,481 & 2,349,259 & 5,262,725 \\
-2018 & 316,495 & 2,623,449 & 6,009,386 \\
+1 & 1996 & 30783 & 185816 & 320533 \\ 
+  2 & 1997 & 37284 & 230475 & 389779 \\ 
+  3 & 1998 & 45198 & 254160 & 445703 \\ 
+  4 & 1999 & 40776 & 241013 & 420839 \\ 
+  5 & 2000 & 45310 & 266764 & 471079 \\ 
+  6 & 2001 & 65168 & 357472 & 651196 \\ 
+  7 & 2002 & 75583 & 410290 & 761714 \\ 
+  8 & 2003 & 88701 & 458459 & 904755 \\ 
+  9 & 2004 & 88984 & 506063 & 980388 \\ 
+  10 & 2005 & 110741 & 609294 & 1247543 \\ 
+  11 & 2006 & 140729 & 731622 & 1579690 \\ 
+  12 & 2007 & 171357 & 845569 & 1879419 \\ 
+  13 & 2008 & 205852 & 1019330 & 2281452 \\ 
+  14 & 2009 & 239905 & 1239406 & 2841795 \\ 
+  15 & 2010 & 255254 & 1391036 & 3214371 \\ 
+  16 & 2011 & 255633 & 1534865 & 3464829 \\ 
+  17 & 2012 & 264011 & 1700862 & 3845051 \\ 
+  18 & 2013 & 261442 & 1866133 & 4199482 \\ 
+  19 & 2014 & 272711 & 2004406 & 4581855 \\ 
+  20 & 2015 & 309446 & 2220732 & 5202960 \\ 
+  21 & 2016 & 316430 & 2422531 & 5630283 \\ 
+  22 & 2017 & 308102 & 2622125 & 5918274 \\ 
+  23 & 2018 & 340221 & 3012740 & 6960056 \\ 
    \hline
 \end{tabular}}
-\vspace{-1mm}%Put here to reduce too much white space after your table 
+\vspace{-1mm}
 \end{table}

### 2019-09-25 concept_dev.tex
updated text

@@
 \maketitle
-\section{Motivation} Making discovery in a manner that would leverage existing resources and skills with focus on  the computer science field, which has experienced vigorous growth in the last twenty years.
-Citation analysis is a particular focus.
+\section{Motivation} The field of computer science has experienced vigorous growth in the last twenty years that has also impacted other fields.
+Citation analysis is the major avenue down which we choose to explore this growth and diversification.
 
-\section{Data and Methods} The following sections describe the datasets and initial data exploration 
+\section{Data and Methods} The following sections describe datasets and initial explorations.
 \subsection{Year slices} Year slices were developed for all publications from 1996-2018.
-All publications of language 'English' and with at-least 2 references and complete publication data in Scopus are selected.
+All publications of language `English', with at-least 2 references and a complete publication record in Scopus are selected.
 Publications type include (article, conference paper, dissertation etc) and belong to subject area 'COMP'.
@@
 \label{tab:summary_data}
-\vspace{1mm}
+\vspace{3 mm}
 \centering
@@
 \subsection{Disciplinary Composition} One way to identify the growth and diversity of a field is by considering the count and subject areas of scientific publications in it and how these change over time.
-In our study of the evolution of the field of computer science, we initially used the All Science Journal Classification (ASJC) codes assigned by Scopus to journals to crudely estimate publications and unique references from 1996-2018.
+In our study of the evolution of the field of computer science, we initially used the All Science Journal Classification (ASJC) codes in Scopus to journals to estimate relevant publications and their cited references from 1996-2018.
 Accordingly, we searched for articles or conference proceedings labelled computer science (COMP), one of the 27 major subject areas in the Scopus classification system.
-ICOMP itself comprises 13 minor subject areas such as Hardware and Architecture and Artificial Intelligence.
-A limitation of the ASJC system is that every publication inherits its journal or conference subject area(s), which is problematic for a field that has had broad influence and interactions on other fields.
-Further, multidisciplinary journals such as Nature, Science, Proceedings of the National Academy of Sciences are classified under General and computer science articles published in those journals would be overlooked.
-Thus, we followed an initial subsetting of Scopus using COMP and GENERAL with an article level clustering approach.
-:
+It should be noted that COMP itself comprises 13 minor subject areas such as Hardware and Architecture and Artificial Intelligence.
+A limitation of the ASJC system is that publications inherit ASJC codes code from those assigned to their parent journal or conferences.
+Further, multidisciplinary journals such as Nature, Science, Proceedings of the National Academy of Sciences are classified under General and computer science articles published in those journals could be overlooked.
+The extend of both false positives (publications that are not computer science but have COMP labels) and false negatives (publications that are computer science but do not have COMP labels) must, therefore, be considered when engaging in such studies.
+We chose to refine an initial subsetting of Scopus by restricting to COMP and GENERAL and then refining the results in through article level clustering using citations to form clusters.
+A second approach involves mining the dblp repository assuming that it contains a validated set of computer science publications from journals and conference proceedings.
+Publications so mined are matched to Scopus identifiers and further analyzed.
+
+\subsection{Possible next steps(based on discussion)}
+
+\begin{itemize}
+\item Expt 1: Use dblp as input to Scopus instead of Scopus\_COMP (super idea from Sitaram)
+\begin{enumerate}
+\item Match dblp titles to Scopus titles using (insert full text search syntax) using a stringent rankfilter cut off $> 0.99$ for matching to Scopus 
+\item Get cited references using Scopus ids from matched titles and construct an undirected citation graph
+\item Cluster with Graclus into 30 clusters
+\item Get Topics of Prominence (TOP) counts for articles in these clusters 
+\item Vary rankfilter cutoff
+\item Vary cluster number
+\end{enumerate}
+\end{itemize}
+
+Expt 2: Reduce Graclus and Leiden clusters to top tenth percentile of cited articles
+• Use total citations from Scopus for citation counts
+• Get TOP counts for these publications
+Expt 3: George will keep fiddling with Sitaram's previously generated data to extract insight.
 
@@
 
-\subsection{Possible next steps(based on discussion)}  Analyze the citation patterns of top authors in the field and how it evolved over time.
-Selecting authors with at least 30 papers published might be a good place to start.
-Another experiment might be to approach the diversity of computer science from other disciplines.
-i.e studying the citation patterns of other disciplines and how computer science has been more inclusive over time.
 \end{document}

### 2019-10-23 Scientometrics/comp.tex
scientometrics template

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Specialization in Computer Science%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
\subtitle{Article Level Clusters vs Journals\\ If so, write it here}

%\titlerunning{Short form of title}        % if too long for running head

\author{Sitaram Devarakonda         \and
        George Chacko %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{Sitaram Devarakonda \at
              Netelabs, NET ESolutions Corporation, McLean, VA \\
              %Tel.: +123-45-678910\\
              %Fax: +123-45-678910\\
              \email{sitaram@nete.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           George Chacko \at
              Netelabs, NET ESolutions Corporation, McLean, VA \\
              \email{netelabs@nete.com}
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
Computer science and its applications have experienced dramatic growth and diversification. Toward understanding its organization, we use computer science literature to identify clusters of documents and the extent of connectedness between them.

\keywords{Bibliometrics \and Clustering \and Knowledge Evolution \and Research Evaluation}
% \PACS{PACS code1 \and PACS code2 \and more}
\subclass{01A85 \and 01A90} %\and more}
\end{abstract}

\section{Introduction}
\label{intro}
Your text comes here. Separate text sections with
\section{Section title}
\label{sec:1}
Text with citations \cite{RefB} and \cite{RefJ}.
\subsection{Subsection title}
\label{sec:2}
as required. Don't forget to give each section
and subsection a unique label (see Sect.~\ref{sec:1}).
\paragraph{Paragraph headings} Use paragraph headings as needed.
\begin{equation}
a^2+b^2=c^2
\end{equation}

% For one-column wide figures use
\begin{figure}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics{example.eps}
% figure caption is below the figure
\caption{Please write your figure caption here}
\label{fig:1}       % Give a unique label
\end{figure}
%
% For two-column wide figures use
\begin{figure*}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[width=0.75\textwidth]{example.eps}
% figure caption is below the figure
\caption{Please write your figure caption here}
\label{fig:2}       % Give a unique label
\end{figure*}
%
% For tables use
\begin{table}
% table caption is above the table
\caption{Please write your table caption here}
\label{tab:1}       % Give a unique label
% For LaTeX tables use
\begin{tabular}{lll}
\hline\noalign{\smallskip}
first & second & third  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
number & number & number \\
number & number & number \\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

% Authors must disclose all relationships or interests that 
% could have direct or potential influence or impart bias on 
% the work: 
%
% \section*{Conflict of interest}
%
% The authors declare that they have no conflict of interest.

% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
%\bibliography{}   % name your BibTeX data base

% Non-BibTeX users please use
\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{RefJ}
% Format for Journal Reference
Author, Article title, Journal, Volume, page numbers (year)
% Format for books
\bibitem{RefB}
Author, Book title, page numbers. Publisher, place (year)
% etc
\end{thebibliography}

\end{document}
% end of file template.tex

### 2019-10-24 Scientometrics/comp.tex
update

@@
 
-\title{Specialization in Computer Science%\thanks{Grants or other notes
+\title{An Appreciation of Computer Science%\thanks{Grants or other notes
 %about the article that should go on the front page should be
@@
 \begin{abstract}
-Computer science and its applications have experienced dramatic growth and diversification.
-Toward understanding its organization, we use computer science literature to identify clusters of documents and the extent of connectedness between them.
+Computer science and its applications has experienced dramatic growth and diversification over the last twenty years.
+Toward understanding the nature of these changes, we analyze a cohort of the computer science literature using a historiographic approach that relies on citations.
+To escape the imprecise definitions encoded in journal-level groupings, we build article-level clusters.
+Mention structure and information flow.
+We compare two different clustering approaches and reconcile them with subject categories in the Scopus database.
 
@@
 \label{intro}
-Your text comes here. Separate text sections with
+
+Cite Alan Porter on expanding universe versus myopic focus.
+Cite Traag, Waltman, Lariviere papers.
+Peter Sjögårde and Per Ahlgren, Loet Leydesdorff, Caroline S.
+Wagner and Lutz Bornmann, Discontinuities in citation relations among journals: self-organized criticality as a model of scientific revolutions and change, Scientometrics, 10.1007/s11192-018-2734-6, 116, 1, (623-644), (2018).
+Antonio Perianes-Rodriguez and Javier Ruiz-Castillo, A comparison of the Web of Science and publication-level classification systems of science, Journal of Informetrics, 10.1016/j.joi.2016.10.007, 11, 1, (32-45), (2017).
+Qi Wang and Ludo Waltman, Large-scale analysis of the accuracy of the journal classification systems of Web of Science and Scopus, Journal of Informetrics, 10.1016/j.joi.2016.02.003, 10, 2, (347-364), (2016).
+Henry Small, Kevin W.
+Boyack and Richard Klavans, Identifying emerging topics in science and technology,
+Crossref
 \section{Section title}

### 2019-10-24 Scientometrics/comp.tex
update

@@
 Crossref
-\section{Section title}
+\section{Materials and Methods}
 \label{sec:1}
 Text with citations \cite{RefB} and \cite{RefJ}.
+
+\section{Results}
+\label{sec:2}
+
+Overall strategy:
+
+\begin{itemize}
+\item Spectral clustering
+\begin{enumerate}
+\item Subset Scopus by COMP
+\item Match COMP to dblp at high stringency -> reduced number of scps
+ \item Harvest cited refefences  from Scopus
+ \item Cluster articles by direct citation using Graclus to a number that meets simple optimality criteria and does not impose cognitive challenges
+ \item Reconcile cluster contents to journal classification for the purpose of referencing
+ \item Infer inter-cluster relationships using direct citations, co-citations, and bibliographic coupling
+\end{enumerate}
+\item Co-citation based clustering
+\begin{enumerate}
+\item Stratify by year after subsetting by COMP and restricting to article and cp only
+\item Apply fractional citation counting and identify highly-cited papers
+\item Calculate normalized co-citations
+\item Cluster by variable clustering method of Small
+\item Evaluate major co-cited pairs
+\end{enumerate}
+\end{itemize}
+
+Text with citations \cite{RefB} and \cite{RefJ}.
+
 \subsection{Subsection title}

### 2019-11-07 Scientometrics/comp.tex
m and methods

@@
 
-\title{An Appreciation of Computer Science%\thanks{Grants or other notes
+\title{Using Citation Data to Study Computer Science%\thanks{Grants or other notes
 %about the article that should go on the front page should be
@@
 }
-\subtitle{Article Level Clusters vs Journals\\ If so, write it here}
+\subtitle{Relationship With Other Fields}
 
@@
 \author{Sitaram Devarakonda  \and
-        George Chacko %etc.
-}
+        Dmitriy Korobskiy \and
+        Tandy Warnow \and
+        George Chacko }
 
@@
 
-\institute{Sitaram Devarakonda \at
+\institute{Sitaram Devarakonda,  \at
               Netelabs, NET ESolutions Corporation, McLean, VA \\
@@
 %             \emph{Present address:} of F. Author  %  if needed
+           \and
+	  Dmitriy Korobskiy \at
+              Netelabs, NET ESolutions Corporation, McLean, VA \\
+              \email{dk@nete.com}
+                  \and
+           Tandy Warnow \at
+              Dept of Computer Science, University of Iliinois Urbana-Champaign, Champaign IL \\
+              \email{warnow@illinois.edu}
                   \and
@@
 Computer science and its applications has experienced dramatic growth and diversification over the last twenty years.
-Toward understanding the nature of these changes, we analyze a cohort of the computer science literature using a historiographic approach that relies on citations.
-To escape the imprecise definitions encoded in journal-level groupings, we build article-level clusters.
-Mention structure and information flow.
-We compare two different clustering approaches and reconcile them with subject categories in the Scopus database.
+Towards understanding the nature of these changes, we analyze a cohort of the computer science literature using a historiographic approach.
+To understand the features of this cohort and the flow of information within its components, we construct article level clusters whose elements are linked by citations or co-citations, and reconcile them with subject categories in the Scopus database.
 
@@
 Crossref
+
+%%%%%%%%%%%%%%%
 \section{Materials and Methods}
+
+\emph{Data} The dblp computer science bibliography, dblp-2018-08-01.xml.gz, consisting of 7,079,994 records was downloaded from  `https://dblp.uni-trier.de/xml/`.
+Publications were parsed from the xml source file and loaded into a PostgreSQL database.
+These parsed records were then matched to Scopus identifiers using PostgreSQL's full text search feature applied to document titles.
+The process involves parsing Scopus document titles into tokens, reducing the tokens into lexemes and returning a ts\_vector which lists the lexemes together with their positions.
+The ts\_vector is then matched with DBLP document titles.
+A ts\_rank is returned based on the frequency of matching lexemes.
+Only records in dblp with DOIs (4,291,130) were considered and only matches with a rank of $>$ 0.99 were accepted.
+This procedure resulted in a dataset of 634,100 publications.
+Cited references for these were extracted from Scopus, resulting in a total of 3,960,503 nodes (publications and references) and 11,992,387 edges that represents citations of these references and publications within the dataset.
+This dataset was labelled \emph{comp}.\par \emph{Clustering by Direct Citation} Graclus software was downloaded from \\`http://www.cs.utexas.edu/users/dml/Software/graclus.html'.
+The \emph{comp} dataset was cast as an undirected graph and stored in a file with a header line indicating the number of nodes and edges.
+Graclus accepts the number of clusters required as a parameter, so we used 10,15, 20, 25, 30, 40, and 50 as this parameter and  \emph{comp} as input.
+Based on criteria articulated in the Louvain and Leiden clustering algorithms, we chose 20 clusters as the number of output clusters.
+\par \emph{Clustering by Co-Citation} To build clusters using co-citations, we slightly modified the approach of Small and Sweeney (1985) as follows.
+We first calculated the number of citations accumulated across Scopus for all 634,100 articles in \emph{comp}.
+After discarding those publications that had not been cited at all, we restricted further analysis to the those in the 90th percentile or higher resulting in a dataset of size 50,869.
+We then identified all publications in Scopus that cite the 50,869 previously selected papers from \emph{comp}.
+The cited references in these papers were restricted to those in the set of 50,869 highly cited papers previously identified.
+For each publication in turn, all possible reference pairs were generated.
+The frequency of these co-cited pairs was then computed across the dataset  and normalized using Salton's cosine formula.
+A total of 2,208,135 unique co-cited pairs were thus obtained.
+
+Variable level Clustering involves iteratively selecting the edges with highest normalized co-citation value and collecting
+all the nodes related to them and so forth. One issue faced is the accumulation of one giant cluster.
+
+To break them up we applied thresholds based on normalized co-citation values. In this experiment we started with 0.5 and progressively increased by 0.1
+until 0.9, then by 0.01 until 0.99. Any cluster larger than 200 is carried over to be clustered based on higher thresholds.
+
+After the completion of 1st round of clustering we had 6645 clusters with a total of 36024 nodes, losing 29.18 % nodes.
+Clusters with only 2 nodes were eliminated bringing down the total clusters to 3760
+
+To obtain target clusters of around 20 we did hierarchical clustering based on the above results. Inter-cluster relations were calculated for every
+cluster and the max edge value based on normalized co-citaion is selected.
+
+Based on max edge value two clusters which are merged into one. This process was applied for 9 times and we ended up with 12 clusters
+
+First round input no of clusters: 3760
+hierarchical\_clustering\_round,no\_of\_clusters
+no1,1757
+no2,853
+no3,419
+no4,208
+no5,103
+no6,51
+no7,25
+no8,12
+
+Message Sitaram
+
 \label{sec:1}
@@
 \item Match COMP to dblp at high stringency -> reduced number of scps
- \item Harvest cited refefences  from Scopus
+ \item Harvest cited references  from Scopus
  \item Cluster articles by direct citation using Graclus to a number that meets simple optimality criteria and does not impose cognitive challenges

### 2019-11-07 Scientometrics/comp.tex
m and methods

@@
 After discarding those publications that had not been cited at all, we restricted further analysis to the those in the 90th percentile or higher resulting in a dataset of size 50,869.
-We then identified all publications in Scopus that cite the 50,869 previously selected papers from \emph{comp}.
+We then identified 897,407 publications in Scopus that cite the 50,869 previously selected papers from \emph{comp}.
 The cited references in these papers were restricted to those in the set of 50,869 highly cited papers previously identified.
@@
 A total of 2,208,135 unique co-cited pairs were thus obtained.
+These data were represented in an edgelist where each node was a publication and the weighted edge between the pair was the normalized co-citation frequency.
+To build clusters we used Small and Sweeney's approach with an initial threshold of 0.5 (normalized co-citation frequency), a maximum cluster size of 200, and an increment of 0.1 where 0.5 $<=$ threshold $<=$ 0.9 after which the increment was reduced to 0.01 for 0.9 $<$ threshold $<$ 0.99.
+A final threshold of 0.999 was applied to the last large cluster.
 

### 2019-11-07 Scientometrics/comp.tex
materials and methods

--- 2019-11-07 Scientometrics/comp.tex
@@
 A total of 2,208,135 unique co-cited pairs were thus obtained.
-
-Variable level Clustering involves iteratively selecting the edges with highest normalized co-citation value and collecting
-all the nodes related to them and so forth. One issue faced is the accumulation of one giant cluster.
-
-To break them up we applied thresholds based on normalized co-citation values. In this experiment we started with 0.5 and progressively increased by 0.1
-until 0.9, then by 0.01 until 0.99. Any cluster larger than 200 is carried over to be clustered based on higher thresholds.
-
-After the completion of 1st round of clustering we had 6645 clusters with a total of 36024 nodes, losing 29.18 % nodes.
-Clusters with only 2 nodes were eliminated bringing down the total clusters to 3760
-
-To obtain target clusters of around 20 we did hierarchical clustering based on the above results. Inter-cluster relations were calculated for every
-cluster and the max edge value based on normalized co-citaion is selected.
-
-Based on max edge value two clusters which are merged into one. This process was applied for 9 times and we ended up with 12 clusters
+These data were represented in an edge list where each node was a publication and the weighted edge between the pair was the normalized co-citation frequency.
+Variable level clustering involves iteratively selecting the edges with the highest normalized co-citation value and extracting connected components from the graph.
+An issue faced is the generation of very large clusters by chaining through low edge weights.
+To address this, we used Small and Sweeney's variable clustering approach with initial parameters threshold ($t$) = 0.5 (median normalized co-citation frequency), increment $i = 0.1$, and maximum cluster size, $mcs = 200$.
+Thus, at start, all edges below the median normalized co-citation frequency are dissolved.
+Clusters were formed by assembling connected components from each co-cited pair beginning with the heaviest edge weight.
+Clusters below size 200 were retained and any cluster larger than 200 nodes is carried over to be clustered based on higher thresholds.
+The threshold, $t$, was then incremented by 0.1 and the process was repeated progressively increments of $t$ by 0.1 where $0.5 <= t <= 0.9$, after which $i$ was reduced to 0.01 for the range $0.9 <= t <= 0.99$.
+A final threshold value of $t$=0.999 was applied to the last remaining large cluster.
+All clusters generated thus, contained  less than 200 nodes.
+Using this approach, 6,645 clusters containing 36,024 nodes were generated.
+Clusters containing only 2 nodes were then discarded bringing down the total number of clusters to 3,760.
+Pairwise clustering was then performed on these clusters using max inter-cluster edge weights.
+After 9 rounds of pairwise clustering 12 clusters were generated.
 
@@
 hierarchical\_clustering\_round,no\_of\_clusters
-no1,1757
-no2,853
-no3,419
-no4,208
-no5,103
-no6,51
-no7,25
-no8,12
+no1, 1757
+no2, 853
+no3, 419
+no4, 208
+no5, 103
+no6, 51
+no7, 25
+no8, 12
 

### 2019-11-07 Scientometrics/comp.tex
update

@@
 Clusters below size 200 were retained and any cluster larger than 200 nodes is carried over to be clustered based on higher thresholds.
-The threshold, $t$, was then incremented by 0.1 and the process was repeated progressively increments of $t$ by 0.1 where $0.5 <= t <= 0.9$, after which $i$ was reduced to 0.01 for the range $0.9 <= t <= 0.99$.
-A final threshold value of $t$=0.999 was applied to the last remaining large cluster.
+The threshold, $t$, was then incremented by 0.1 and the process was repeated while progressively incrementing $t$.
 All clusters generated thus, contained  less than 200 nodes.
@@
 After 9 rounds of pairwise clustering 12 clusters were generated.
+{leftover\_text: by 0.1 where $0.5 <= t <= 0.9$, after which $i$ was reduced to 0.01 for the range $0.9 <= t <= 0.99$.
+A final threshold value of $t$=0.999 was applied to the last remaining large cluster.}
 

### 2019-11-08 Scientometrics/comp.tex
incremental M&M

--- 2019-11-07 Scientometrics/comp.tex
@@
 
-\emph{Data} The dblp computer science bibliography, dblp-2018-08-01.xml.gz, consisting of 7,079,994 records was downloaded from  `https://dblp.uni-trier.de/xml/`.
+\emph{Data} The dblp computer science bibliography consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz from  `https://dblp.uni-trier.de/xml/`.
 Publications were parsed from the xml source file and loaded into a PostgreSQL database.
@@
 For each publication in turn, all possible reference pairs were generated.
-The frequency of these co-cited pairs was then computed across the dataset  and normalized using Salton's cosine formula.
+The frequency of these co-cited pairs was then computed across the dataset  and normalized using Salton's cosine formula~\cite{salton_citation_1979}.
 A total of 2,208,135 unique co-cited pairs were thus obtained.
@@
 Variable level clustering involves iteratively selecting the edges with the highest normalized co-citation value and extracting connected components from the graph.
+\begin{figure}[ht]
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.3]{vlc.pdf}
+% figure caption is below the figure
+\caption{Schematic representation of variable clustering protocol modified from Small and Sweeney (1985).
+Three parameters are specified (i) a threshold or starting level based on a quantile of normalized co-citation frequency (ii) a level increment (iii) a maximum cluster size.
+Input data is a set of co-cited publications with edge-weight defined by normalized co-citation frequencies.
+Green clusters are within the max cluster size.
+At the initial threshold, $t1$, a single cluster below the maximum cluster size, $mcs$ (green), along with one large cluster above it (red) are generated.
+As the threshold is incremented to $t2$, additional clusters of acceptable size is generated.
+The cascade continues to completion, which is defined by all clusters being of size less than or equal to the $mcs$.
+In this schematic, five rounds are adequate.}
+\label{vlc_process}       % Give a unique label
+\end{figure}
+
 An issue faced is the generation of very large clusters by chaining through low edge weights.
-To address this, we used Small and Sweeney's variable clustering approach with initial parameters threshold ($t$) = 0.5 (median normalized co-citation frequency), increment $i = 0.1$, and maximum cluster size, $mcs = 200$.
+To address this, we used Small and Sweeney's variable clustering approach~\cite{small_clustering_1985} with initial parameters of threshold ($t$) = 0.5 (median normalized co-citation frequency), increment $i = 0.1$, and maximum cluster size, $mcs = 100$.
 Thus, at start, all edges below the median normalized co-citation frequency are dissolved.
 Clusters were formed by assembling connected components from each co-cited pair beginning with the heaviest edge weight.
-Clusters below size 200 were retained and any cluster larger than 200 nodes is carried over to be clustered based on higher thresholds.
-The threshold, $t$, was then incremented by 0.1 and the process was repeated progressively increments of $t$ by 0.1 where $0.5 <= t <= 0.9$, after which $i$ was reduced to 0.01 for the range $0.9 <= t <= 0.99$.
-A final threshold value of $t$=0.999 was applied to the last remaining large cluster.
-All clusters generated thus, contained  less than 200 nodes.
-Using this approach, 6,645 clusters containing 36,024 nodes were generated.
-Clusters containing only 2 nodes were then discarded bringing down the total number of clusters to 3,760.
-Pairwise clustering was then performed on these clusters using max inter-cluster edge weights.
-After 9 rounds of pairwise clustering 12 clusters were generated.
-
-First round input no of clusters: 3760
-hierarchical\_clustering\_round,no\_of\_clusters
-no1, 1757
-no2, 853
-no3, 419
-no4, 208
-no5, 103
-no6, 51
-no7, 25
-no8, 12
-
-Message Sitaram
+Clusters below size 100 were retained and any cluster larger than 200 nodes was carried over to the next round.
+The threshold, $t$, was then incremented by 0.1 and the process repeated while progressively incrementing $t$.
+We used a bi-phasic approach where in which $t$ ranged from 0.5-0.9, after which $i$ was reduced to 0.01 for the range $0.9 <= t <= 0.99$.
+A final threshold of $t$=0.999 was applied to break the single remaining large cluster.
+All clusters generated thus, contained  less than 100 nodes.
+Using this approach, 6,822 clusters containing 35,485 nodes were generated.
+Clusters containing only 2 nodes were then discarded bringing the total number of clusters down to 3,851.
+Pairwise clustering was then performed on these clusters to generate super-clusters.
+After 9 rounds of pairwise clustering, 12 clusters were generated resulting from agglomeration of the original 3,851 clusters
 
@@
 %\bibliographystyle{spbasic}      % basic style, author-year citations
-%\bibliographystyle{spmpsci}      % mathematics and physical sciences
+\bibliographystyle{spmpsci}      % mathematics and physical sciences
 %\bibliographystyle{spphys}       % APS-like style for physics
-%\bibliography{}   % name your BibTeX data base
+\bibliography{comp}   % name your BibTeX data base
 

### 2019-11-11 Scientometrics/comp.tex
updates

@@
 
-\title{Using Citation Data to Study Computer Science%\thanks{Grants or other notes
+\title{Citation Analysis of Computer Science%\thanks{Grants or other notes
 %about the article that should go on the front page should be
@@
 Towards understanding the nature of these changes, we analyze a cohort of the computer science literature using a historiographic approach.
-To understand the features of this cohort and the flow of information within its components, we construct article level clusters whose elements are linked by citations or co-citations, and reconcile them with subject categories in the Scopus database.
+For further insight on the features of this cohort and the flow of information within its components, we construct article level clusters whose elements are linked by citations or co-citations, and reconcile them with subject categories in the All Science Journal Classification.
 
-\keywords{Bibliometrics \and Clustering \and Knowledge Evolution \and Research Evaluation}
+\keywords{Bibliometrics \and Clustering \and Research Evaluation \and Computer Science}
 % \PACS{PACS code1 \and PACS code2 \and more}
 \subclass{01A85 \and 01A90} %\and more}
+
 \end{abstract}
@@
 
-Cite Alan Porter on expanding universe versus myopic focus.
-Cite Traag, Waltman, Lariviere papers.
-Peter Sjögårde and Per Ahlgren, Loet Leydesdorff, Caroline S.
-Wagner and Lutz Bornmann, Discontinuities in citation relations among journals: self-organized criticality as a model of scientific revolutions and change, Scientometrics, 10.1007/s11192-018-2734-6, 116, 1, (623-644), (2018).
-Antonio Perianes-Rodriguez and Javier Ruiz-Castillo, A comparison of the Web of Science and publication-level classification systems of science, Journal of Informetrics, 10.1016/j.joi.2016.10.007, 11, 1, (32-45), (2017).
-Qi Wang and Ludo Waltman, Large-scale analysis of the accuracy of the journal classification systems of Web of Science and Scopus, Journal of Informetrics, 10.1016/j.joi.2016.02.003, 10, 2, (347-364), (2016).
-Henry Small, Kevin W.
-Boyack and Richard Klavans, Identifying emerging topics in science and technology,
-Crossref
+%
+Computer science, and its applications, has experienced dramatic growth and diversification over the last twenty years.
+As noted in a 2017 US National Academies Report~\cite{nas_2017}, ``A wide range of jobs in virtually all sectors demand computing skills to an unprecedented extent.
+And every academic discipline finds itself incorporating computing into its research and educational mission".
+Additionally, the collective influence of the Internet of Things, `big' data, accessible cloud computing, and advances in artificial intelligence have also been postulated as a recent driver for the growth and evolution~\cite{siebel2019_digital}.
+
+In a historical study of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles), Salton and Bergmark described the global structure of computer science as consisting of three main subareas (i) theoretical foundations, e.g., theory of computation (ii) hardware and computer systems, e.g., architecture (iii) software, e.g, programming systems~\cite{salton_citation_1979}.
+Related areas discussed were  (a) mathematics of computing, e.g., numerical analysis (b) special software topics, e.g., operating systems (c) data management and database systems (d) methodologies valid for multiple applications, e.g., algebraic manipulation (e) computer applications, e.g., computer graphics (f) nontechnical aspects, e.g., computer education.
+In presenting their study, Salton and Bergmark made the key point that the scientific literature serves a rich source of information to study the structure and historical development of a field.
+
+The Computing Classification System (CCS), an ontology, published by the Association for Computing Machinery (ACM), last updated in 2012, consists of 13 top-level areas.
+https://dl.acm.org/ccs/ccs.cfm \emph{need to figure out to put this in BibTeX} that reflect a more current view of the field.
+However, given its considerable influence, a description of computer science, as it exists today, must also consider interactions with other fields.
+An easy way to map scientific publications, especially interdisciplinary articles or those from adjacent fields, to the CCS classification does not exist, however.
+Other classification systems exist such as the NSF\\
+\emph{https://www.nsf.gov/statistics/nsf13327/pdf/tabb1.pdf}, WoS \\ 
+\emph{https://bit.ly/2NBRqaH}, and the All Science Journal Classification (ASJC) developed and maintained by Scopus 
+\\ \emph{insert url} are based on journals that rely on assigning journal-level labels to articles.
+The limitations of journal-based annotations are well known~\emph{wang and waltman; lariviere paper} and efforts have been made to instead build article level clusters using citations or other criteria for assembly \emph{cite Boyack, Small, Waltman, etc,}.
+
+In this article, we attempt to provide new insights into computer science by matching records from two major data sources.
+(i) the dblp bibliography- a reference bibliography for computer science\emph{cite} (ii) the Scopus bibliography.
+which covers the physical science, life sciences, social sciences, and health sciences.
+Using direct citations and co-citations, we construct clusters of articles that are drawn from both journals and conference proceedings  and reconcile them with the All Science Journal Classification (ASJC) developed and maintained by Scopus.
+
+We observe that....[what do we observe?]
 
@@
 Publications were parsed from the xml source file and loaded into a PostgreSQL database.
-These parsed records were then matched to Scopus identifiers using PostgreSQL's full text search feature applied to document titles.
+The Scopus dataset of over 72,000,000 publications was previously parsed into a custom schema as part of the comnstruction of a larger data platform for research evaluation~\cite{Korobskiy_2019}.
+Records in the dblp dataset, were matched to Scopus identifiers using PostgreSQL's full text search feature applied to document titles.
 The process involves parsing Scopus document titles into tokens, reducing the tokens into lexemes and returning a ts\_vector which lists the lexemes together with their positions.
@@
 % For example, with the graphicx package use
-  \includegraphics[scale=0.3]{vlc.pdf}
+  \includegraphics[scale=0.2]{vlc.pdf}
 % figure caption is below the figure
@@
 
-An issue faced is the generation of very large clusters by chaining through low edge weights.
+An issue is the generation of very large clusters by chaining through low edge weights.
 To address this, we used Small and Sweeney's variable clustering approach~\cite{small_clustering_1985} with initial parameters of threshold ($t$) = 0.5 (median normalized co-citation frequency), increment $i = 0.1$, and maximum cluster size, $mcs = 100$.
@@
 
+Cite Alan Porter on expanding universe versus myopic focus.
+Cite Traag, Waltman, Lariviere papers.
+Peter Sjögårde and Per Ahlgren, Loet Leydesdorff, Caroline S.
+Wagner and Lutz Bornmann, Discontinuities in citation relations among journals: self-organized criticality as a model of scientific revolutions and change, Scientometrics, 10.1007/s11192-018-2734-6, 116, 1, (623-644), (2018).
+Antonio Perianes-Rodriguez and Javier Ruiz-Castillo, A comparison of the Web of Science and publication-level classification systems of science, Journal of Informetrics, 10.1016/j.joi.2016.10.007, 11, 1, (32-45), (2017).
+Qi Wang and Ludo Waltman, Large-scale analysis of the accuracy of the journal classification systems of Web of Science and Scopus, Journal of Informetrics, 10.1016/j.joi.2016.02.003, 10, 2, (347-364), (2016).
+Henry Small, Kevin W.
+Boyack and Richard Klavans, Identifying emerging topics in science and technology,
+Crossref
 Overall strategy:

### 2019-11-11 concept_dev.tex
generic update

@@
 \section{Data and Methods} The following sections describe datasets and initial explorations.
-\subsection{Year slices} Year slices were developed for all publications from 1996-2018.
+\subsection{Scopus Year slices} Year slices were developed for all publications from 1996-2018.
 All publications of language `English', with at-least 2 references and a complete publication record in Scopus are selected.
 Publications type include (article, conference paper, dissertation etc) and belong to subject area 'COMP'.
+\subsection{DBLP Data} Data from DBLP, for the years 1996-2018 were collected. A whole text matching approach (@dk) was used to match titles to Scopus identifiers. 
+\subsection{Clustering}
 %\vspace{-7mm}

### 2019-11-13 Scientometrics/comp.tex
update

@@
 stroke
-grestore
+grestorew
 \end{filecontents*}
@@
 \begin{abstract}
-Computer science and its applications has experienced dramatic growth and diversification over the last twenty years.
-Towards understanding the nature of these changes, we analyze a cohort of the computer science literature using a historiographic approach.
-For further insight on the features of this cohort and the flow of information within its components, we construct article level clusters whose elements are linked by citations or co-citations, and reconcile them with subject categories in the All Science Journal Classification.
+Computer science as a field has experienced dramatic growth and diversification over the last twenty years.
+Towards an improved understanding of the structure of the field, we analyze a cohort of the computer science literature using a historiographic approach.
+For further insight on the features of this cohort and the flow of information within its components, we construct article level clusters whose elements are linked by citations or co-citations, and reconcile them with subject categories in the All Science Journal Classification (Scopus).
+[abstract is feeble and needs to be rewritten]
 
@@
 And every academic discipline finds itself incorporating computing into its research and educational mission".
-Additionally, the collective influence of the Internet of Things, `big' data, accessible cloud computing, and advances in artificial intelligence have also been postulated as a recent driver for the growth and evolution~\cite{siebel2019_digital}.
+Additionally, the collective influence of the Internet of Things, `big' data, accessible cloud computing, and advances in artificial intelligence have been postulated as a recent driver for growth and evolution~\cite{siebel2019_digital}.
 
@@
 Related areas discussed were  (a) mathematics of computing, e.g., numerical analysis (b) special software topics, e.g., operating systems (c) data management and database systems (d) methodologies valid for multiple applications, e.g., algebraic manipulation (e) computer applications, e.g., computer graphics (f) nontechnical aspects, e.g., computer education.
-In presenting their study, Salton and Bergmark made the key point that the scientific literature serves a rich source of information to study the structure and historical development of a field.
+In presenting this work, Salton and Bergmark made the key point that the scientific literature serves a rich source of information to study the structure and historical development of a field and reference relevant work in bibliometrics.
 
-The Computing Classification System (CCS), an ontology, published by the Association for Computing Machinery (ACM), last updated in 2012, consists of 13 top-level areas.
+Progressing beyond the triad of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS) published by the Association for Computing Machinery (ACM) now consists of 13 top-level areas.
 https://dl.acm.org/ccs/ccs.cfm \emph{need to figure out to put this in BibTeX} that reflect a more current view of the field.
-However, given its considerable influence, a description of computer science, as it exists today, must also consider interactions with other fields.
-An easy way to map scientific publications, especially interdisciplinary articles or those from adjacent fields, to the CCS classification does not exist, however.
-Other classification systems exist such as the NSF\\
+This classification addresses relationships with other fields under Applied Computing.
+However, an easy way to map scientific publications, especially interdisciplinary articles or those from adjacent fields, to the CCS classification does not exist.
+Other classification systems exist such as the All Science Journal Classification (ASJC) developed and maintained by Scopus.
+the Web of Science Subject Classification System, and the NSF classification system.
+All three rely on applying one or more journal-derived labels to articles.
+Limitations of journal based classification have stimulated efforts to use article level clusters using citations and text similarity for links.
+\emph{cite Boyack, Small, Waltman, etc,}.
+These limitations are well known~\emph{wang and waltman; lariviere paper} and efforts have been made to instead build article level clusters using citations or other criteria for assembly .
 \emph{https://www.nsf.gov/statistics/nsf13327/pdf/tabb1.pdf}, WoS \\ 
-\emph{https://bit.ly/2NBRqaH}, and the All Science Journal Classification (ASJC) developed and maintained by Scopus 
+\emph{https://bit.ly/2NBRqaH}, and the  
 \\ \emph{insert url} are based on journals that rely on assigning journal-level labels to articles.
-The limitations of journal-based annotations are well known~\emph{wang and waltman; lariviere paper} and efforts have been made to instead build article level clusters using citations or other criteria for assembly \emph{cite Boyack, Small, Waltman, etc,}.
 
-In this article, we attempt to provide new insights into computer science by matching records from two major data sources.
-(i) the dblp bibliography- a reference bibliography for computer science\emph{cite} (ii) the Scopus bibliography.
-which covers the physical science, life sciences, social sciences, and health sciences.
-Using direct citations and co-citations, we construct clusters of articles that are drawn from both journals and conference proceedings  and reconcile them with the All Science Journal Classification (ASJC) developed and maintained by Scopus.
+In this article, we attempt to provide explore the structure of computer science through matching records from two major data sources.
+(i) the dblp bibliography- a reference bibliography for computer science\emph{cite} (ii) the Scopus bibliography, which covers the physical science, life sciences, social sciences, and health sciences.
+Using direct citations and co-citations as links, we construct clusters of articles that are drawn from journals and conference proceedings  and reconcile them with the All Science Journal Classification (ASJC) developed and maintained by Scopus.
 
@@
 
-\emph{Data} The dblp computer science bibliography consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz from  `https://dblp.uni-trier.de/xml/`.
+\emph{Data} The dblp computer science bibliography consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz from  `https://dblp.uni-trier.de/xml/'.
 Publications were parsed from the xml source file and loaded into a PostgreSQL database.
-The Scopus dataset of over 72,000,000 publications was previously parsed into a custom schema as part of the comnstruction of a larger data platform for research evaluation~\cite{Korobskiy_2019}.
+We have previously parsed, the Scopus dataset of over 72,000,000 publications into a custom schema as part of the construction of a larger data platform for research evaluation~\cite{Korobskiy_2019}.
 Records in the dblp dataset, were matched to Scopus identifiers using PostgreSQL's full text search feature applied to document titles.
-The process involves parsing Scopus document titles into tokens, reducing the tokens into lexemes and returning a ts\_vector which lists the lexemes together with their positions.
+The process involves parsing all Scopus document titles into tokens, reducing the tokens into lexemes and returning a ts\_vector which lists the lexemes together with their positions.
 The ts\_vector is then matched with DBLP document titles.
@@
 Only records in dblp with DOIs (4,291,130) were considered and only matches with a rank of $>$ 0.99 were accepted.
-This procedure resulted in a dataset of 634,100 publications.
-Cited references for these were extracted from Scopus, resulting in a total of 3,960,503 nodes (publications and references) and 11,992,387 edges that represents citations of these references and publications within the dataset.
-This dataset was labelled \emph{comp}.\par \emph{Clustering by Direct Citation} Graclus software was downloaded from \\`http://www.cs.utexas.edu/users/dml/Software/graclus.html'.
-The \emph{comp} dataset was cast as an undirected graph and stored in a file with a header line indicating the number of nodes and edges.
-Graclus accepts the number of clusters required as a parameter, so we used 10,15, 20, 25, 30, 40, and 50 as this parameter and  \emph{comp} as input.
-Based on criteria articulated in the Louvain and Leiden clustering algorithms, we chose 20 clusters as the number of output clusters.
-\par \emph{Clustering by Co-Citation} To build clusters using co-citations, we slightly modified the approach of Small and Sweeney (1985) as follows.
+This procedure resulted in a dataset of 634,100 publications with Scopus identifiers.
+Cited references for these were extracted from Scopus, resulting in a total of 3,960,503 nodes (publications and references) and 11,992,387 edges that represent citations of these references and publications within the dataset.
+This dataset was labelled \emph{comp}.\par
+
+\emph{Clustering by Direct Citation} Graclus software was downloaded from \\`http://www.cs.utexas.edu/users/dml/Software/graclus.html'.
+The \emph{comp} dataset was formatted as an undirected graph and stored in a file with a header line indicating the number of nodes and edges.
+Graclus requires the number of clusters to be formed as a parameter, so we varied the parameter between 10 and 50 clusters and \emph{comp}.
+Using Graclus at 20 clusters, resulted in a set of clusters that were roughly matched for size wit the largest cluster approximately containing no more than 10 times the number of nodes in the smallest one~\cite{traag_louvain_2019}.
+
+\emph{Clustering by Co-Citation} To build clusters using co-citations, we used the approach of Small and Sweeney (1985)~\cite{small_clustering_1985}, with minor modifications.
 We first calculated the number of citations accumulated across Scopus for all 634,100 articles in \emph{comp}.
-After discarding those publications that had not been cited at all, we restricted further analysis to the those in the 90th percentile or higher resulting in a dataset of size 50,869.
+After discarding those publications without any citations, we restricted further analysis to those in the 90th percentile of citations or higher resulting in a dataset of size 50,869.
 We then identified 897,407 publications in Scopus that cite the 50,869 previously selected papers from \emph{comp}.
 The cited references in these papers were restricted to those in the set of 50,869 highly cited papers previously identified.
-For each publication in turn, all possible reference pairs were generated.
+For each of the 897,407 citing publications in turn, all possible reference pairs were generated.
 The frequency of these co-cited pairs was then computed across the dataset  and normalized using Salton's cosine formula~\cite{salton_citation_1979}.
 A total of 2,208,135 unique co-cited pairs were thus obtained.
-These data were represented in an edge list where each node was a publication and the weighted edge between the pair was the normalized co-citation frequency.
-Variable level clustering involves iteratively selecting the edges with the highest normalized co-citation value and extracting connected components from the graph.
+These data were represented in a graph where each node was a publication and the weighted edge between the pair was the normalized co-citation frequency.
+\par
+
+Variable level clustering involves applying a threshold below which all edges are dissolved then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn.
+An issue is the generation of very large clusters by chaining through low edge weights.At this point, three parameters are needed (i) a threshold or starting level based on a quantile of normalized co-citation frequency (ii) a level increment (iii) a maximum cluster size.
+Thus, any cluster exceeding the maximum cluster size is then put back into the process and a higher threshold applied.
 \begin{figure}[ht]
@@
 The cascade continues to completion, which is defined by all clusters being of size less than or equal to the $mcs$.
-In this schematic, five rounds are adequate.}
+In this schematic, five rounds are adequate for the process to run to completion.}
 \label{vlc_process}       % Give a unique label
@@
 
-An issue is the generation of very large clusters by chaining through low edge weights.
-To address this, we used Small and Sweeney's variable clustering approach~\cite{small_clustering_1985} with initial parameters of threshold ($t$) = 0.5 (median normalized co-citation frequency), increment $i = 0.1$, and maximum cluster size, $mcs = 100$.
+We variable clustering approach~\cite{small_clustering_1985} with initial parameters of threshold ($t$) = 0.5 (median normalized co-citation frequency), increment $i = 0.1$, and maximum cluster size, $mcs = 100$.
 Thus, at start, all edges below the median normalized co-citation frequency are dissolved.
@@
 Pairwise clustering was then performed on these clusters to generate super-clusters.
-After 9 rounds of pairwise clustering, 12 clusters were generated resulting from agglomeration of the original 3,851 clusters
+After 9 rounds of pairwise clustering, 13 clusters were generated resulting from agglomeration of 3,851 clusters
 

### 2019-11-13 Scientometrics/comp.tex
update

@@
 Other classification systems exist such as the All Science Journal Classification (ASJC) developed and maintained by Scopus.
-the Web of Science Subject Classification System, and the NSF classification system.
+the Web of Science classification of research areas, and the NSF classification system.
 All three rely on applying one or more journal-derived labels to articles.
@@
 
-In this article, we attempt to provide explore the structure of computer science through matching records from two major data sources.
+In this article, we explore the structure of computer science through matching records from two major data sources.
 (i) the dblp bibliography- a reference bibliography for computer science\emph{cite} (ii) the Scopus bibliography, which covers the physical science, life sciences, social sciences, and health sciences.
-Using direct citations and co-citations as links, we construct clusters of articles that are drawn from journals and conference proceedings  and reconcile them with the All Science Journal Classification (ASJC) developed and maintained by Scopus.
+Using direct citations and co-citations as links, we then construct clusters of articles that are drawn from journals and conference proceedings  and reconcile them with the All Science Journal Classification (ASJC) developed and maintained by Scopus.
 
@@
 Overall strategy:
+
+\begin{figure}[ht]
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.5]{scopus_dblp_graclus2.pdf}
+% figure caption is below the figure
+\caption{insert caption}
+\label{heatmap}       % Give a unique label
+\end{figure}
 

### 2019-11-15 Scientometrics/comp.tex
Edited the full text data search section

@@
 Records in the dblp dataset, were matched to Scopus identifiers using PostgreSQL's full text search feature applied to document titles.
-The process involves parsing all Scopus document titles into tokens, reducing the tokens into lexemes and returning a ts\_vector which lists the lexemes together with their positions.
-The ts\_vector is then matched with DBLP document titles.
-A ts\_rank is returned based on the frequency of matching lexemes.
-Only records in dblp with DOIs (4,291,130) were considered and only matches with a rank of $>$ 0.99 were accepted.
+The process involves parsing all Scopus document titles into tokens, reducing the tokens into lexemes and returning a text search vector which lists the lexemes.
+The vectors are then matched with corresponding text search vectors extracted from DBLP document titles.
+A rank is returned based on the frequency of matching lexemes.
+Only records in dblp with DOIs (4,291,130) were considered and only matches with a Postgres ts\_rank of $>$ 0.99 were accepted.
 This procedure resulted in a dataset of 634,100 publications with Scopus identifiers.

### 2019-11-16 Scientometrics/comp.tex
updates

--- 2019-11-13 Scientometrics/comp.tex
@@
 
-%
 Computer science, and its applications, has experienced dramatic growth and diversification over the last twenty years.
@@
 Related areas discussed were  (a) mathematics of computing, e.g., numerical analysis (b) special software topics, e.g., operating systems (c) data management and database systems (d) methodologies valid for multiple applications, e.g., algebraic manipulation (e) computer applications, e.g., computer graphics (f) nontechnical aspects, e.g., computer education.
-In presenting this work, Salton and Bergmark made the key point that the scientific literature serves a rich source of information to study the structure and historical development of a field and reference relevant work in bibliometrics.
+In presenting this work, Salton and Bergmark made the key point that the scientific literature serves a rich source of information to study the structure and historical development of a field and cite similar ideas.
 
-Progressing beyond the triad of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS) published by the Association for Computing Machinery (ACM) now consists of 13 top-level areas.
-https://dl.acm.org/ccs/ccs.cfm \emph{need to figure out to put this in BibTeX} that reflect a more current view of the field.
-This classification addresses relationships with other fields under Applied Computing.
+Progressing beyond this historical triad consisting of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS)~\cite{acm_ref} published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field.
+This classification also addresses relationships with other fields under Applied Computing.
 However, an easy way to map scientific publications, especially interdisciplinary articles or those from adjacent fields, to the CCS classification does not exist.
 Other classification systems exist such as the All Science Journal Classification (ASJC) developed and maintained by Scopus.
-the Web of Science classification of research areas, and the NSF classification system.
+the Web of Science research and categorical classifications, and the NSF classification system.
 All three rely on applying one or more journal-derived labels to articles.
-Limitations of journal based classification have stimulated efforts to use article level clusters using citations and text similarity for links.
-\emph{cite Boyack, Small, Waltman, etc,}.
-These limitations are well known~\emph{wang and waltman; lariviere paper} and efforts have been made to instead build article level clusters using citations or other criteria for assembly .
-\emph{https://www.nsf.gov/statistics/nsf13327/pdf/tabb1.pdf}, WoS \\ 
-\emph{https://bit.ly/2NBRqaH}, and the  
-\\ \emph{insert url} are based on journals that rely on assigning journal-level labels to articles.
+Classification systems that use articles directly have also been developed~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012}, which escape some of the criticisms of journal-based classification~\cite{wang_large-scale_2016,shu_comparing_2019}.
 
 In this article, we explore the structure of computer science through matching records from two major data sources.
-(i) the dblp bibliography- a reference bibliography for computer science\emph{cite} (ii) the Scopus bibliography, which covers the physical science, life sciences, social sciences, and health sciences.
+(i) the dblp bibliography- a reference bibliography for computer science~\cite{dblp_ref} (ii) the Scopus bibliography, which covers the physical science, life sciences, social sciences, and health sciences.
 Using direct citations and co-citations as links, we then construct clusters of articles that are drawn from journals and conference proceedings  and reconcile them with the All Science Journal Classification (ASJC) developed and maintained by Scopus.
@@
 
-\emph{Data} The dblp computer science bibliography consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz from  `https://dblp.uni-trier.de/xml/'.
+\emph{Data} A stable release of the dblp computer science bibliography~\cite{dblp_ref} consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz.
 Publications were parsed from the xml source file and loaded into a PostgreSQL database.

### 2019-11-16 Scientometrics/comp.tex

@@
 Records in the dblp dataset, were matched to Scopus identifiers using PostgreSQL's full text search feature applied to document titles.
-The process involves parsing all Scopus document titles into tokens, reducing the tokens into lexemes and returning a ts\_vector which lists the lexemes together with their positions.
-The ts\_vector is then matched with DBLP document titles.
-A ts\_rank is returned based on the frequency of matching lexemes.
+The process involves parsing all Scopus document titles into tokens, reducing the tokens into lexemes and returning a ts\_vector which lists the lexemes.
+The vectors are then matched with corresponding text search vectors extracted from DBLP document titles.
+A rank is returned based on the frequency of matching lexemes.
 Only records in dblp with DOIs (4,291,130) were considered and only matches with a rank of $>$ 0.99 were accepted.
@@
 This dataset was labelled \emph{comp}.\par
+=======
 

### 2019-11-16 Scientometrics/comp.tex
update

@@
 
-Computer science, and its applications, has experienced dramatic growth and diversification over the last twenty years.
+Computer science, and its applications, has experienced rapid growth and diversification over the last twenty years.
 As noted in a 2017 US National Academies Report~\cite{nas_2017}, ``A wide range of jobs in virtually all sectors demand computing skills to an unprecedented extent.
 And every academic discipline finds itself incorporating computing into its research and educational mission".
-Additionally, the collective influence of the Internet of Things, `big' data, accessible cloud computing, and advances in artificial intelligence have been postulated as a recent driver for growth and evolution~\cite{siebel2019_digital}.
+The collective influence of the Internet of Things (IoT), `big' data, accessible cloud computing, and advances in artificial intelligence have been postulated as a recent driver for growth and evolution~\cite{siebel2019_digital} of computing.
 
-In a historical study of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles), Salton and Bergmark described the global structure of computer science as consisting of three main subareas (i) theoretical foundations, e.g., theory of computation (ii) hardware and computer systems, e.g., architecture (iii) software, e.g, programming systems~\cite{salton_citation_1979}.
-Related areas discussed were  (a) mathematics of computing, e.g., numerical analysis (b) special software topics, e.g., operating systems (c) data management and database systems (d) methodologies valid for multiple applications, e.g., algebraic manipulation (e) computer applications, e.g., computer graphics (f) nontechnical aspects, e.g., computer education.
-In presenting this work, Salton and Bergmark made the key point that the scientific literature serves a rich source of information to study the structure and historical development of a field and cite similar ideas.
+In a historical study of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles), Salton and Bergmark made the key point that the scientific literature serves a rich source of information to study the structure and historical development of a field~\cite{salton_citation_1979}.
+They described the global structure of computer science as consisting of three main subareas (i) theoretical foundations, e.g., theory of computation (ii) hardware and computer systems, e.g., architecture (iii) software, e.g, programming systems.
+Related areas acknowledged were  (a) mathematics of computing, e.g., numerical analysis (b) special software topics, e.g., operating systems (c) data management and database systems (d) methodologies valid for multiple applications, e.g., algebraic manipulation (e) computer applications, e.g., computer graphics (f) nontechnical aspects, e.g., computer education.
 
-Progressing beyond this historical triad consisting of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS)~\cite{acm_ref} published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field.
-This classification also addresses relationships with other fields under Applied Computing.
+Obviousy, much in the way of growth and evolution of computing has occurred since 1974.
+Progressing beyond the historical triad of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS)~\cite{acm_ref} published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field.
+This classification does address relationships with other fields under Applied Computing.
 However, an easy way to map scientific publications, especially interdisciplinary articles or those from adjacent fields, to the CCS classification does not exist.
-Other classification systems exist such as the All Science Journal Classification (ASJC) developed and maintained by Scopus.
-the Web of Science research and categorical classifications, and the NSF classification system.
+
+ \emph{I'd like to see some text about (i) limited funding resources (ii) efficient use of existing resources (iiii) informing policy at multiple levels -- all directed at justifying our study.
+I'm not sure where to put it though.
+George look at Daniel Sarewitz' papers.
+This could be moved to the Discussion.Porter and colleagues in a study on measuring interdisciplinarity~\cite{porter_measuring_2007} observe that 'The discrepancies between disciplinary roots and research realities loom large', a reference to the challenges associated with knowledge diffusing across researchers who tend to be focused in their own areas.
+This concern may be especially relevant for computer science given the ubiquity of computing today and limited public funding for research.
+}
+
+Other classification systems are available such as the All Science Journal Classification (ASJC) developed and maintained by Scopus.
+the Web of Science research and categorical classifications, the NSF classification system~\cite{nsf_classification}.
 All three rely on applying one or more journal-derived labels to articles.
-Classification systems that use articles directly have also been developed~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012}, which escape some of the criticisms of journal-based classification~\cite{wang_large-scale_2016,shu_comparing_2019}.
+Disciplinary assignments using journal based classifications have been extensively discussed and critiqued~\cite{wang_large-scale_2016} [need comprehensive list of citations] with Shu and colleagues recently noting from a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
+Accordingly, article classification systems have also been developed~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012}, which escape some of the criticisms of journal-based classification.
 
-In this article, we explore the structure of computer science through matching records from two major data sources.
-(i) the dblp bibliography- a reference bibliography for computer science~\cite{dblp_ref} (ii) the Scopus bibliography, which covers the physical science, life sciences, social sciences, and health sciences.
-Using direct citations and co-citations as links, we then construct clusters of articles that are drawn from journals and conference proceedings  and reconcile them with the All Science Journal Classification (ASJC) developed and maintained by Scopus.
+In extending the work of Salton and Bergmark to the 21st century, we sought to combine journal and article based classifications in a scalable manner.
+Accordingly, we used a whole text search method to match records from two major data sources.
+(i) the dblp bibliography- a reference bibliography for computer science~\cite{dblp_ref}.
+We assumed that a record in dblp qualifies for a computer science label (ii) the journal based Scopus bibliography, which more comprehensively covers the physical sciences, life sciences, social sciences, and health sciences and enables easy identification of publications linked by citations.
 
-We observe that....[what do we observe?]
+Using both direct citations and co-citations as the basis for clustering, we used articles from from journals and conference proceedings for the period 1996-2015.
+We reconciled these clusters with the the All Science Journal Classification (ASJC) developed and maintained by Scopus as well as to the CCS classification through a combination of automated and manual procedures.
+We describe high-level interactions of computer science within the Physical Sciences as well as with the Social Sciences, and Life Sciences.
 
@@
 Publications were parsed from the xml source file and loaded into a PostgreSQL database.
-We have previously parsed, the Scopus dataset of over 72,000,000 publications into a custom schema as part of the construction of a larger data platform for research evaluation~\cite{Korobskiy_2019}.
+We have previously parsed, the Scopus dataset of over 72,000,000 publications into a custom schema as part of a larger data platform for research evaluation~\cite{GithubERNIE2019}.
 Records in the dblp dataset, were matched to Scopus identifiers using PostgreSQL's full text search feature applied to document titles.
-The process involves parsing all Scopus document titles into tokens, reducing the tokens into lexemes and returning a ts\_vector which lists the lexemes.
+The process involves parsing all Scopus document titles into tokens, reducing the tokens into lexemes and returning vectors, which lists these lexemes.
 The vectors are then matched with corresponding text search vectors extracted from DBLP document titles.
@@
 Cited references for these were extracted from Scopus, resulting in a total of 3,960,503 nodes (publications and references) and 11,992,387 edges that represent citations of these references and publications within the dataset.
-This dataset was labelled \emph{comp}.\par
-=======
+This dataset is referred to as \emph{comp}.\par
 
-\emph{Clustering by Direct Citation} Graclus software was downloaded from \\`http://www.cs.utexas.edu/users/dml/Software/graclus.html'.
-The \emph{comp} dataset was formatted as an undirected graph and stored in a file with a header line indicating the number of nodes and edges.
-Graclus requires the number of clusters to be formed as a parameter, so we varied the parameter between 10 and 50 clusters and \emph{comp}.
-Using Graclus at 20 clusters, resulted in a set of clusters that were roughly matched for size wit the largest cluster approximately containing no more than 10 times the number of nodes in the smallest one~\cite{traag_louvain_2019}.
+\emph{Clustering by Direct Citation} Graclus is a spectral graph clustering package that computes normalized cut and ratio association for a given undirected graph~\cite{graclus_2007}.
+We downloaded v1.2 from the authors' website at `cs.utexas.edu'.
+The \emph{comp} dataset was used as input to Graclus, formatted as an undirected graph and stored in a file with a header line indicating the number of nodes and edges.
+Graclus requires, as a parameter, the number of clusters to be formed and we varied this parameter between 10 and 50 clusters.
+Using Graclus to generate 20 clusters, resulted in a set with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{traag_louvain_2019}.
+[@sitaram please add the number of nodes in the Graclus 20 clusters].
 
-\emph{Clustering by Co-Citation} To build clusters using co-citations, we used the approach of Small and Sweeney (1985)~\cite{small_clustering_1985}, with minor modifications.
-We first calculated the number of citations accumulated across Scopus for all 634,100 articles in \emph{comp}.
+\emph{Clustering by Co-Citation} To build clusters using co-citations, we used variable level clustering, an approach developed by Small and Sweeney (1985)~\cite{small_clustering_1985}, with minor modifications.
+Variable level clustering involves applying a threshold below which all edges are dissolved then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn.
+Three parameters are needed (i) a threshold or starting level based on a quantile of normalized co-citation frequency (ii) a level increment (iii) a maximum cluster size.
+An issue is the generation of very large clusters by chaining through low edge weights.
+Thus, at each iteration, any cluster exceeding the maximum cluster size is put back into the process and a higher threshold applied.
+
+In our implementation of variable level clustering, we first calculated the number of citations accumulated across Scopus for all 634,100 articles in \emph{comp}.
 After discarding those publications without any citations, we restricted further analysis to those in the 90th percentile of citations or higher resulting in a dataset of size 50,869.
@@
 The cited references in these papers were restricted to those in the set of 50,869 highly cited papers previously identified.
-For each of the 897,407 citing publications in turn, all possible reference pairs were generated.
+For each of the 897,407 citing publications in turn, all possible reference pairs were generated ${n \choose x}$ where $n$ is the number of references in a publication and $x=2$.
 The frequency of these co-cited pairs was then computed across the dataset  and normalized using Salton's cosine formula~\cite{salton_citation_1979}.
@@
 
-Variable level clustering involves applying a threshold below which all edges are dissolved then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn.
-An issue is the generation of very large clusters by chaining through low edge weights.At this point, three parameters are needed (i) a threshold or starting level based on a quantile of normalized co-citation frequency (ii) a level increment (iii) a maximum cluster size.
-Thus, any cluster exceeding the maximum cluster size is then put back into the process and a higher threshold applied.
 \begin{figure}[ht]
@@
 
-We variable clustering approach~\cite{small_clustering_1985} with initial parameters of threshold ($t$) = 0.5 (median normalized co-citation frequency), increment $i = 0.1$, and maximum cluster size, $mcs = 100$.
+We applied variable clustering with initial parameters of threshold ($t$) = 0.5 (median normalized co-citation frequency), increment $i = 0.1$, and maximum cluster size, $mcs = 100$.
 Thus, at start, all edges below the median normalized co-citation frequency are dissolved.

### 2019-11-17 Scientometrics/comp.tex
udpate

@@
 Computer science, and its applications, has experienced rapid growth and diversification over the last twenty years.
-As noted in a 2017 US National Academies Report~\cite{nas_2017}, ``A wide range of jobs in virtually all sectors demand computing skills to an unprecedented extent.
+The collective influence of the Internet of Things (IoT), `big' data, accessible cloud computing, and advances in artificial intelligence have further been postulated as a recent driver for its growth and evolution~\cite{siebel2019_digital}.
+As also noted in a 2017 US National Academies Report~\cite{nas_2017}, ``A wide range of jobs in virtually all sectors demand computing skills to an unprecedented extent.
 And every academic discipline finds itself incorporating computing into its research and educational mission".
-The collective influence of the Internet of Things (IoT), `big' data, accessible cloud computing, and advances in artificial intelligence have been postulated as a recent driver for growth and evolution~\cite{siebel2019_digital} of computing.
+
+Given this powerful influence of computer science in research, some understanding its present state, structure, and relationship to other fields that goes beyond satisfying mere interest seems warranted since it would inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy.
+In using the term inform, we are mindful of (i) Greenhalgh (ii) Sarewitz and Pielke.
+\emph{I think that I want to cite these two without really knowing how.
+Greenhalgh for the limitations of positivism.
+Sarewitz for the limitations of allowing science to do whatever it wants to.
+I'd also like to see some text about (i) limited funding resources (ii) efficient use of existing resources (iiii) informing policy at multiple levels -- all directed at justifying our study.
+I'm not sure where to put it though.
+CS can also be an excellent model system for studying interdisciplinarity cite Porter and colleagues in a study on measuring interdisciplinarity~\cite{porter_measuring_2007 } observe that 'The discrepancies between disciplinary roots and research realities loom large', a reference to the challenges associated with knowledge diffusing across researchers who tend to be focused in their own areas.
+This concern may be especially relevant for computer science given the ubiquity of computing today and limited public funding for research.
+Maybe squeeze in Tandy's NAS report on interdisciplinarity.
+I should ping Ohid Yaqub about this too- science policy is his area.}
 
@@
 
-Obviousy, much in the way of growth and evolution of computing has occurred since 1974.
+Much in the way of growth and evolution of computing has occurred since 1974.
 Progressing beyond the historical triad of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS)~\cite{acm_ref} published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field.
@@
 However, an easy way to map scientific publications, especially interdisciplinary articles or those from adjacent fields, to the CCS classification does not exist.
-
- \emph{I'd like to see some text about (i) limited funding resources (ii) efficient use of existing resources (iiii) informing policy at multiple levels -- all directed at justifying our study.
-I'm not sure where to put it though.
-George look at Daniel Sarewitz' papers.
-This could be moved to the Discussion.Porter and colleagues in a study on measuring interdisciplinarity~\cite{porter_measuring_2007} observe that 'The discrepancies between disciplinary roots and research realities loom large', a reference to the challenges associated with knowledge diffusing across researchers who tend to be focused in their own areas.
-This concern may be especially relevant for computer science given the ubiquity of computing today and limited public funding for research.
-}
 
@@
 
-%%%%%%%%%%%%%%%
 \section{Materials and Methods}
@@
 After 9 rounds of pairwise clustering, 13 clusters were generated resulting from agglomeration of 3,851 clusters
+
+\emph{need to cite Granovetter somewhere for definition of strong and weak ties that Small refers to}
 

### 2019-11-17 Scientometrics/comp.tex
wrote up results for Fig 1

@@
 \usepackage{graphicx}
+\usepackage{xcolor}
 %
@@
 Disciplinary assignments using journal based classifications have been extensively discussed and critiqued~\cite{wang_large-scale_2016} [need comprehensive list of citations] with Shu and colleagues recently noting from a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
-Accordingly, article classification systems have also been developed~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012}, which escape some of the criticisms of journal-based classification.
+Article classification systems have also been developed, however~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012}, which escape some of the criticisms of journal-based classification.
 
 In extending the work of Salton and Bergmark to the 21st century, we sought to combine journal and article based classifications in a scalable manner.
-Accordingly, we used a whole text search method to match records from two major data sources.
-(i) the dblp bibliography- a reference bibliography for computer science~\cite{dblp_ref}.
-We assumed that a record in dblp qualifies for a computer science label (ii) the journal based Scopus bibliography, which more comprehensively covers the physical sciences, life sciences, social sciences, and health sciences and enables easy identification of publications linked by citations.
+Consequently, we used a whole text search method to match records from two major data sources.
+(i) the dblp bibliography- a reference bibliography for computer science~\cite{dblp_ref} (ii) the journal based Scopus bibliography, which more comprehensively covers the physical sciences, life sciences, social sciences, and health sciences.
+We assumed that a record in dblp qualifies for a computer science label and cross-matched dblp publications to Scopus to  enable identification of citing and cited publications across multiple disciplines.
 
@@
 We reconciled these clusters with the the All Science Journal Classification (ASJC) developed and maintained by Scopus as well as to the CCS classification through a combination of automated and manual procedures.
-We describe high-level interactions of computer science within the Physical Sciences as well as with the Social Sciences, and Life Sciences.
+We describe below, high-level interactions of computer science within the Physical Sciences as well as with the Social Sciences, and Life Sciences.
 
@@
 We downloaded v1.2 from the authors' website at `cs.utexas.edu'.
-The \emph{comp} dataset was used as input to Graclus, formatted as an undirected graph and stored in a file with a header line indicating the number of nodes and edges.
-Graclus requires, as a parameter, the number of clusters to be formed and we varied this parameter between 10 and 50 clusters.
-Using Graclus to generate 20 clusters, resulted in a set with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{traag_louvain_2019}.
+The \emph{comp} dataset was formatted as an undirected graph, stored in a file with a header line indicating the number of nodes and edges, and used as input to Graclus,  The number of clusters to be formed is required by Graclus, and we varied this parameter between 10 and 50 clusters.
+Using Graclus to generate 20 clusters, resulted in an evenly distributed set of clusters with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{traag_louvain_2019}.
 [@sitaram please add the number of nodes in the Graclus 20 clusters].
@@
 An issue is the generation of very large clusters by chaining through low edge weights.
-Thus, at each iteration, any cluster exceeding the maximum cluster size is put back into the process and a higher threshold applied.
+Thus, at each iteration, any cluster exceeding the maximum cluster size is put back into the process and a higher threshold applied to break such clusters.
 
@@
 The cited references in these papers were restricted to those in the set of 50,869 highly cited papers previously identified.
-For each of the 897,407 citing publications in turn, all possible reference pairs were generated ${n \choose x}$ where $n$ is the number of references in a publication and $x=2$.
+For each of the 897,407 citing publications in turn, all possible reference pairs, ${n \choose 2}$, were generated where $n$ is the number of references in a publication.
 The frequency of these co-cited pairs was then computed across the dataset  and normalized using Salton's cosine formula~\cite{salton_citation_1979}.
@@
 
-We applied variable clustering with initial parameters of threshold ($t$) = 0.5 (median normalized co-citation frequency), increment $i = 0.1$, and maximum cluster size, $mcs = 100$.
+We applied variable clustering with initial parameters of threshold ($t$) = 0.5 (normalized co-citation frequency, see Methods), increment $i = 0.1$, and maximum cluster size, $mcs = 100$.
 Thus, at start, all edges below the median normalized co-citation frequency are dissolved.
@@
 The threshold, $t$, was then incremented by 0.1 and the process repeated while progressively incrementing $t$.
-We used a bi-phasic approach where in which $t$ ranged from 0.5-0.9, after which $i$ was reduced to 0.01 for the range $0.9 <= t <= 0.99$.
+We used a bi-phasic approach where in which $t$ ranged from 0.5-0.9, after which $i$ was reduced to 0.01 for the range $0.9<= t<= 0.99$.
 A final threshold of $t$=0.999 was applied to break the single remaining large cluster.
@@
 
-\emph{need to cite Granovetter somewhere for definition of strong and weak ties that Small refers to}
-
 \label{sec:1}
@@
 \label{sec:2}
+
+For the purpose of this study, we defined, the computer science literature as a working set of all articles in the dblp bibliography published in 1996-2015, that had a digital object identifier (DOI), and could be matched to article identifiers in the Scopus bibliography.
+The process of selection and matching resulted in a dataset of 634,100 publications (Materials and Methods).
+We constructed article level clusters of the computer science literature for the years 1996-2015, at a sufficiently high level of aggregation to support cognitive ease.
+Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation with an argument being made for direct citation as the best approach to concentrate citation links~\cite{klavans_which_2017}.
+Accordingly, we first used direct citation links as the basis for cluster formation.
+A set of 20 clusters was generated using a spectral clustering technique, Graclus, that has previously been applied to citation data~\cite{graclus_2007, subelj_clustering_2016}.
+\emph{@sitaram please confirm the number of pubs that went into Graclus.
+I'm assuming it was 634,100?}.
+To place these clusters in context, we identified that accounted for at least 10\% of the publications in each cluster and observed 31 of the 334 minor subject areas in the Scopus ASJC classification.
+(which consists of 5 subject areas, 27 major subject areas, and 334 minor subject areas).
+
+Unsurprisingly, the broad category Computer Science Applications was present in 17 of 20 clusters, followed by  Electrical and Electronic Engineering in 12 clusters.
+
+At the other extreme, 16 minor subject areas were limited to a single cluster, viz.,
+Atomic and Molecular Physics and Optics; 
+Biochemistry; 
+Chemistry (all); 
+Cognitive Neuroscience; 
+Computer Vision and Pattern Recognition;
+Computers in Earth Sciences;
+Earth and Planetary Sciences; 
+Education; 
+Electronic Optical and Magnetic Materials; 
+Information Systems; 
+Information Systems and Management;  
+Management Science and Operations Research;
+Molecular Biology;
+Neurology; 
+Physics and Astronomy (miscellaneous); 
+and Radiology Nuclear Medicine and Imaging.
+These 16 areas can be described are peripheral, to various degrees, to computer science.
+The picture that emerges is that areas central to computer science are likely to be found in multiple clusters.
+
+\color{blue} \emph{need Tandy's input on the paragraph below.
+Also, do we need a table summarizing the paragraph above as a supplement Fig.1?
+I've stared at these data for so long that I'm burned out so please could you rewrite first, second, third, and fourth points.
+A fifth if you like} \color{black}
+
+Examining these data from the perspective of the generated clusters (Fig.
+1 abscissa), interactions with the Life Sciences were evident in cluster 17 (Biochemistry, Computational Mathematics, Computational Theory and Mathematics, Computer Science Applications, and Molecular Biology) and cluster 10 (Artificial Intelligence, Biomedical Engineering, Cognitive Neuroscience, Computer Science Applications, and Neurology).
+While acknowledging previously reported inaccuracies in journal-based classification\emph{vide supra}, these results strongly suggest that the actual structure of communication within the broad area of computer science is at variance with journal-based classification, also noted by Waltman and van Eck, to wit, "...an indication that traditional disciplines such as those just mentioned only partly reflect the actual organization of today’s scientific research."~\cite{waltman_new_2012}.
+The aphorism of Porter, Cohen, Roessner, and Perreault (2007), `The discrepancies between disciplinary roots and research realities loom large'~\cite{porter_measuring_2007} also invokes ityself.
+Secondly, that a correlation exists between broad journal-based classification and article clusters in terms of subject matter.
+Thirdly, that some areas of computer science are relatively ubiquitous.
+Fourth that interactions with fields outside computer science tend to be restricted to a single cluster or small numbers of clusters.
 
@@
 
-Text with citations \cite{RefB} and \cite{RefJ}.
+\emph{need to cite Granovetter somewhere for definition of strong and weak ties that Small refers to}
 

### 2019-11-17 Scientometrics/comp.tex
wrote up results for Fig 1

@@
 \usepackage{xcolor}
+\usepackage{listings}
 %
@@
 Records in the dblp dataset, were matched to Scopus identifiers using PostgreSQL's full text search feature applied to document titles.
-The process involves parsing all Scopus document titles into tokens, reducing the tokens into lexemes and returning vectors, which lists these lexemes.
+The process involves parsing all Scopus document titles into tokens, reducing the tokens into lexemes and returning vectors, containing these lexemes.
 The vectors are then matched with corresponding text search vectors extracted from DBLP document titles.
 A rank is returned based on the frequency of matching lexemes.
-Only records in dblp with DOIs (4,291,130) were considered and only matches with a rank of $>$ 0.99 were accepted.
-This procedure resulted in a dataset of 634,100 publications with Scopus identifiers.
+Only recordxs in dblp with DOIs (4,291,130) were considered and only matches with a normalized rank of $>$ 0.99 were accepted, roughly equivalent to `at least 11 matching lexemes independent of order and vector length'.
+As an example, the following query returns a normalized rank of 0.994.
+\begin{lstlisting}
+SELECT ts_rank(to_tsvector(`english', `one two three 
+four five six seven eight nine ten eleven'), 
+plainto_tsquery(`english', `one four three two five 
+six seven eight nine ten eleven')); 
+\end{lstlisting}
+
+ This procedure resulted in a dataset of 634,100 dblp publications with Scopus identifiers.
 Cited references for these were extracted from Scopus, resulting in a total of 3,960,503 nodes (publications and references) and 11,992,387 edges that represent citations of these references and publications within the dataset.
@@
 The \emph{comp} dataset was formatted as an undirected graph, stored in a file with a header line indicating the number of nodes and edges, and used as input to Graclus,  The number of clusters to be formed is required by Graclus, and we varied this parameter between 10 and 50 clusters.
-Using Graclus to generate 20 clusters, resulted in an evenly distributed set of clusters with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{traag_louvain_2019}.
+At a setting of 20, the most evenly sized set of clusters resulted with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{traag_louvain_2019}.
 [@sitaram please add the number of nodes in the Graclus 20 clusters].
@@
 \emph{Clustering by Co-Citation} To build clusters using co-citations, we used variable level clustering, an approach developed by Small and Sweeney (1985)~\cite{small_clustering_1985}, with minor modifications.
-Variable level clustering involves applying a threshold below which all edges are dissolved then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn.
+Variable level clustering involves applying a threshold (below which all edges are dissolved) then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn.
 Three parameters are needed (i) a threshold or starting level based on a quantile of normalized co-citation frequency (ii) a level increment (iii) a maximum cluster size.

### 2019-11-17 Scientometrics/comp.tex
wrote up results for Fig 1

@@
 (i) the dblp bibliography- a reference bibliography for computer science~\cite{dblp_ref} (ii) the journal based Scopus bibliography, which more comprehensively covers the physical sciences, life sciences, social sciences, and health sciences.
-We assumed that a record in dblp qualifies for a computer science label and cross-matched dblp publications to Scopus to  enable identification of citing and cited publications across multiple disciplines.
+The underlying assumption is that a record in dblp qualifies as computer science.
+Therefore, we cross-matched dblp publications to Scopus to  enable identification of linked publications across multiple disciplines.
 
@@
 Records in the dblp dataset, were matched to Scopus identifiers using PostgreSQL's full text search feature applied to document titles.
-The process involves parsing all Scopus document titles into tokens, reducing the tokens into lexemes and returning vectors, containing these lexemes.
+The process involves parsing all Scopus document titles into tokens, reducing the tokens into lexemes and returning vectors containing these lexemes.
 The vectors are then matched with corresponding text search vectors extracted from DBLP document titles.
@@
 This procedure resulted in a dataset of 634,100 dblp publications with Scopus identifiers.
-Cited references for these were extracted from Scopus, resulting in a total of 3,960,503 nodes (publications and references) and 11,992,387 edges that represent citations of these references and publications within the dataset.
+Cited references were extracted from Scopus, resulting in a total of 3,960,503 nodes (publications and references) and 11,992,387 edges that represent citations of these references and publications within the dataset.
 This dataset is referred to as \emph{comp}.\par
@@
 We downloaded v1.2 from the authors' website at `cs.utexas.edu'.
-The \emph{comp} dataset was formatted as an undirected graph, stored in a file with a header line indicating the number of nodes and edges, and used as input to Graclus,  The number of clusters to be formed is required by Graclus, and we varied this parameter between 10 and 50 clusters.
-At a setting of 20, the most evenly sized set of clusters resulted with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{traag_louvain_2019}.
+The \emph{comp} dataset was formatted as an undirected graph, stored in a file with a header line indicating the number of nodes and edges, and used as input to Graclus,  We varied the number of clusters to be formed between 10 and 50 clusters.
+At 20 clusters, the most evenly sized set of clusters resulted with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{traag_louvain_2019}.
 [@sitaram please add the number of nodes in the Graclus 20 clusters].
@@
 The process of selection and matching resulted in a dataset of 634,100 publications (Materials and Methods).
-We constructed article level clusters of the computer science literature for the years 1996-2015, at a sufficiently high level of aggregation to support cognitive ease.
+We constructed article level clusters of the computer science literature for the years 1996-2015, at a sufficiently high level of aggregation to be comparable to disciplinary classfication by journal.
 Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation with an argument being made for direct citation as the best approach to concentrate citation links~\cite{klavans_which_2017}.

### 2019-11-18 Scientometrics/comp.tex
edits to latex and bibtex, mainly focusing on low-level writing and text formtting

@@
 In a historical study of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles), Salton and Bergmark made the key point that the scientific literature serves a rich source of information to study the structure and historical development of a field~\cite{salton_citation_1979}.
-They described the global structure of computer science as consisting of three main subareas (i) theoretical foundations, e.g., theory of computation (ii) hardware and computer systems, e.g., architecture (iii) software, e.g, programming systems.
-Related areas acknowledged were  (a) mathematics of computing, e.g., numerical analysis (b) special software topics, e.g., operating systems (c) data management and database systems (d) methodologies valid for multiple applications, e.g., algebraic manipulation (e) computer applications, e.g., computer graphics (f) nontechnical aspects, e.g., computer education.
+They described the global structure of computer science as consisting of three main subareas
+(i) theoretical foundations, such as theory of computation, (ii) hardware and computer systems, such as architecture,  and (iii) software, such as programming systems.
+Related areas acknowledged were  (a) mathematics of computing, such as numerical analysis, (b) special software topics, such as operating systems, (c) data management and database systems, (d) methodologies valid for multiple applications, such as algebraic manipulation, (e) computer applications, such as computer graphics, (f) non-technical aspects, such as computer education.
 
@@
 Consequently, we used a whole text search method to match records from two major data sources.
-(i) the dblp bibliography- a reference bibliography for computer science~\cite{dblp_ref} (ii) the journal based Scopus bibliography, which more comprehensively covers the physical sciences, life sciences, social sciences, and health sciences.
-The underlying assumption is that a record in dblp qualifies as computer science.
-Therefore, we cross-matched dblp publications to Scopus to  enable identification of linked publications across multiple disciplines.
+(i) the DBLP bibliography- a reference bibliography for computer science~\cite{dblp_ref} and  (ii) the journal-based Scopus bibliography, which more comprehensively covers the physical sciences, life sciences, social sciences, and health sciences.
+The underlying assumption is that a record in DBLP qualifies as computer science.
+Therefore, we cross-matched DBLP publications to Scopus to  enable identification of linked publications across multiple disciplines.
 
@@
 We reconciled these clusters with the the All Science Journal Classification (ASJC) developed and maintained by Scopus as well as to the CCS classification through a combination of automated and manual procedures.
-We describe below, high-level interactions of computer science within the Physical Sciences as well as with the Social Sciences, and Life Sciences.
+We describe below the high-level interactions of computer science within the Physical Sciences as well as with the Social Sciences and Life Sciences.
 
 \section{Materials and Methods}
+\label{sec:methods}
 
-\emph{Data} A stable release of the dblp computer science bibliography~\cite{dblp_ref} consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz.
+\subsection{Data}
+ A stable release of the DBLP computer science bibliography~\cite{dblp_ref} consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz.
 Publications were parsed from the xml source file and loaded into a PostgreSQL database.
 We have previously parsed, the Scopus dataset of over 72,000,000 publications into a custom schema as part of a larger data platform for research evaluation~\cite{GithubERNIE2019}.
-Records in the dblp dataset, were matched to Scopus identifiers using PostgreSQL's full text search feature applied to document titles.
+Records in the DBLP dataset, were matched to Scopus identifiers using PostgreSQL's full text search feature applied to document titles.
 The process involves parsing all Scopus document titles into tokens, reducing the tokens into lexemes and returning vectors containing these lexemes.
@@
 A rank is returned based on the frequency of matching lexemes.
-Only recordxs in dblp with DOIs (4,291,130) were considered and only matches with a normalized rank of $>$ 0.99 were accepted, roughly equivalent to `at least 11 matching lexemes independent of order and vector length'.
+Only records in DBLP with DOIs (4,291,130) were considered and only matches with a normalized rank of greater than 0.99 were accepted, roughly equivalent to `at least 11 matching lexemes independent of order and vector length'.
 As an example, the following query returns a normalized rank of 0.994.
@@
 
-This procedure resulted in a dataset of 634,100 dblp publications with Scopus identifiers.
+This procedure resulted in a dataset of 634,100 DBLP publications with Scopus identifiers.
 Cited references were extracted from Scopus, resulting in a total of 3,960,503 nodes (publications and references) and 11,992,387 edges that represent citations of these references and publications within the dataset.
@@
 
-\emph{Clustering by Direct Citation} Graclus is a spectral graph clustering package that computes normalized cut and ratio association for a given undirected graph~\cite{graclus_2007}.
+\subsection{Clustering methods}
+
+\paragraph{Clustering by Direct Citation} Graclus is a spectral graph clustering package that computes normalized cut and ratio association for a given undirected graph~\cite{graclus_2007}. 
+\textcolor{blue}{Let's provide the exact URL as a citation}
 We downloaded v1.2 from the authors' website at `cs.utexas.edu'. 
@@
 
-\emph{Clustering by Co-Citation} To build clusters using co-citations, we used variable level clustering, an approach developed by Small and Sweeney (1985)~\cite{small_clustering_1985}, with minor modifications.
+\paragraph{Clustering by Co-Citation} To build clusters using co-citations, we used variable level clustering, an approach developed by Small and Sweeney (1985)~\cite{small_clustering_1985}, with minor modifications.
 Variable level clustering involves applying a threshold (below which all edges are dissolved) then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn.
@@
 The threshold, $t$, was then incremented by 0.1 and the process repeated while progressively incrementing $t$.
-We used a bi-phasic approach where in which $t$ ranged from 0.5-0.9, after which $i$ was reduced to 0.01 for the range $0.9<= t<= 0.99$.
+We used a bi-phasic approach where in which $t$ ranged from 0.5-0.9, after which $i$ was reduced to 0.01 for the range $0.9 \leq t \leq 0.99$.
 A final threshold of $t$=0.999 was applied to break the single remaining large cluster.
@@
 
-\label{sec:1}
-Text with citations \cite{RefB} and \cite{RefJ}.
+\section{Results}
+\label{sec:results}
 
-\section{Results}
-\label{sec:2}
-
-For the purpose of this study, we defined, the computer science literature as a working set of all articles in the dblp bibliography published in 1996-2015, that had a digital object identifier (DOI), and could be matched to article identifiers in the Scopus bibliography.
+For the purpose of this study, we defined, the computer science literature as a working set of all articles in the DBLP bibliography published in 1996-2015, that had a digital object identifier (DOI), and could be matched to article identifiers in the Scopus bibliography.
 The process of selection and matching resulted in a dataset of 634,100 publications (Materials and Methods).
-We constructed article level clusters of the computer science literature for the years 1996-2015, at a sufficiently high level of aggregation to be comparable to disciplinary classfication by journal.
+We constructed article level clusters of the computer science literature for the years 1996-2015, at a sufficiently high level of aggregation to be comparable to disciplinary classification by journal.
 Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation with an argument being made for direct citation as the best approach to concentrate citation links~\cite{klavans_which_2017}.
@@
 1 abscissa), interactions with the Life Sciences were evident in cluster 17 (Biochemistry, Computational Mathematics, Computational Theory and Mathematics, Computer Science Applications, and Molecular Biology) and cluster 10 (Artificial Intelligence, Biomedical Engineering, Cognitive Neuroscience, Computer Science Applications, and Neurology).
-While acknowledging previously reported inaccuracies in journal-based classification\emph{vide supra}, these results strongly suggest that the actual structure of communication within the broad area of computer science is at variance with journal-based classification, also noted by Waltman and van Eck, to wit, "...an indication that traditional disciplines such as those just mentioned only partly reflect the actual organization of today’s scientific research."~\cite{waltman_new_2012}.
-The aphorism of Porter, Cohen, Roessner, and Perreault (2007), `The discrepancies between disciplinary roots and research realities loom large'~\cite{porter_measuring_2007} also invokes ityself.
+While acknowledging previously reported inaccuracies in journal-based classification \emph{vide supra}, these results strongly suggest that the actual structure of communication within the broad area of computer science is at variance with journal-based classification, also noted by Waltman and van Eck, to wit, ``...an indication that traditional disciplines such as those just mentioned only partly reflect the actual organization of today's scientific research."~\cite{waltman_new_2012}.
+The aphorism of Porter, Cohen, Roessner, and Perreault (2007), `The discrepancies between disciplinary roots and research realities loom large'~\cite{porter_measuring_2007} also invokes itself.
 Secondly, that a correlation exists between broad journal-based classification and article clusters in terms of subject matter.
@@
 Crossref
-Overall strategy:
 
+\textcolor{blue}{George, the rest needs to go into methods}
+
+\paragraph{Overall strategy}
+
+Here we describe the overall strategy used for the two clustering methods.\\
 \begin{figure}[ht]
@@
 
-\begin{itemize}
-\item Spectral clustering
+\noindent
+ Spectral clustering:
 \begin{enumerate}
 \item Subset Scopus by COMP
-\item Match COMP to dblp at high stringency -> reduced number of scps
+\item Match COMP to DBLP at high stringency -> reduced number of scps
  \item Harvest cited references  from Scopus
@@
 \end{enumerate}
-\item Co-citation based clustering
+
+\noindent
+Co-citation based clustering:
 \begin{enumerate}
@@
 \end{enumerate}
-\end{itemize}
 
 \emph{need to cite Granovetter somewhere for definition of strong and weak ties that Small refers to}
+
+%\begin{acknowledgements}
+%If you'd like to thank anyone, place your comments here
+%and remove the percent signs.
+%\end{acknowledgements}
+
+% Authors must disclose all relationships or interests that 
+% could have direct or potential influence or impart bias on 
+% the work: 
+%
+% \section*{Conflict of interest}
+%
+% The authors declare that they have no conflict of interest.
+
+% BibTeX users please use one of
+%\bibliographystyle{spbasic}      % basic style, author-year citations
+\bibliographystyle{spmpsci}      % mathematics and physical sciences
+%\bibliographystyle{spphys}       % APS-like style for physics
+\bibliography{comp}   % name your BibTeX data base
+
+% Non-BibTeX users please use
+
+\clearpage
 
@@
 
-%\begin{acknowledgements}
-%If you'd like to thank anyone, place your comments here
-%and remove the percent signs.
-%\end{acknowledgements}
-
-% Authors must disclose all relationships or interests that 
-% could have direct or potential influence or impart bias on 
-% the work: 
-%
-% \section*{Conflict of interest}
-%
-% The authors declare that they have no conflict of interest.
-
-% BibTeX users please use one of
-%\bibliographystyle{spbasic}      % basic style, author-year citations
-\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
-\bibliography{comp}   % name your BibTeX data base
-
-% Non-BibTeX users please use
-\begin{thebibliography}{}
-%
-% and use \bibitem to create references. Consult the Instructions
-% for authors for reference list style.
-%
-\bibitem{RefJ}
-% Format for Journal Reference
-Author, Article title, Journal, Volume, page numbers (year)
-% Format for books
-\bibitem{RefB}
-Author, Book title, page numbers. Publisher, place (year)
-% etc
-\end{thebibliography}
-
 \end{document}

### 2019-11-18 Scientometrics/comp.tex
edits to latex and bibtex, mainly focusing on low-level writing and text formtting

@@
 I'm not sure where to put it though.
-CS can also be an excellent model system for studying interdisciplinarity cite Porter and colleagues in a study on measuring interdisciplinarity~\cite{porter_measuring_2007 } observe that 'The discrepancies between disciplinary roots and research realities loom large', a reference to the challenges associated with knowledge diffusing across researchers who tend to be focused in their own areas.
+CS can also be an excellent model system for studying interdisciplinarity cite Porter and colleagues in a study on measuring interdisciplinarity~\cite{porter_measuring_2007} observe that 'The discrepancies between disciplinary roots and research realities loom large', a reference to the challenges associated with knowledge diffusing across researchers who tend to be focused in their own areas.
 This concern may be especially relevant for computer science given the ubiquity of computing today and limited public funding for research.
@@
 In extending the work of Salton and Bergmark to the 21st century, we sought to combine journal and article based classifications in a scalable manner.
-Consequently, we used a whole text search method to match records from two major data sources.
-(i) the DBLP bibliography- a reference bibliography for computer science~\cite{dblp_ref} and  (ii) the journal-based Scopus bibliography, which more comprehensively covers the physical sciences, life sciences, social sciences, and health sciences.
+Consequently, we used a whole text search method to match records from two major data sources: (i) the DBLP bibliography--a reference bibliography for computer science~\cite{dblp_ref} and  (ii) the journal-based Scopus bibliography, which more comprehensively covers the physical sciences, life sciences, social sciences, and health sciences.
+\textcolor{blue}{Do we need to cite Scopus?}
 The underlying assumption is that a record in DBLP qualifies as computer science.
@@
 \begin{figure}[ht]
+\centering
 % Use the relevant command to insert your figure file.
@@
 Accordingly, we first used direct citation links as the basis for cluster formation.
-A set of 20 clusters was generated using a spectral clustering technique, Graclus, that has previously been applied to citation data~\cite{graclus_2007, subelj_clustering_2016}.
-\emph{@sitaram please confirm the number of pubs that went into Graclus.
-I'm assuming it was 634,100?}.
-To place these clusters in context, we identified that accounted for at least 10\% of the publications in each cluster and observed 31 of the 334 minor subject areas in the Scopus ASJC classification.
+A set of 20 clusters was generated using a spectral clustering technique, Graclus, that has previously been applied to citation data~\cite{graclus_2007,subelj_clustering_2016}.
+\textcolor{blue}{
+ \emph{@sitaram please confirm the number of pubs that went into Graclus. I'm assuming it was 634,100?}. 
+ }To place these clusters in context, we identified that accounted for at least 10\% of the publications in each cluster and observed 31 of the 334 minor subject areas in the Scopus ASJC classification.
 (which consists of 5 subject areas, 27 major subject areas, and 334 minor subject areas).
@@
 as required. Don't forget to give each section
-and subsection a unique label (see Sect.~\ref{sec:1}).
+and subsection a unique label.
 \paragraph{Paragraph headings} Use paragraph headings as needed.

### 2019-11-18 Scientometrics/comp.tex
update

@@
 And every academic discipline finds itself incorporating computing into its research and educational mission".
-
-Given this powerful influence of computer science in research, some understanding its present state, structure, and relationship to other fields that goes beyond satisfying mere interest seems warranted since it would inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy.
-In using the term inform, we are mindful of (i) Greenhalgh (ii) Sarewitz and Pielke.
-\emph{I think that I want to cite these two without really knowing how.
-Greenhalgh for the limitations of positivism.
-Sarewitz for the limitations of allowing science to do whatever it wants to.
-I'd also like to see some text about (i) limited funding resources (ii) efficient use of existing resources (iiii) informing policy at multiple levels -- all directed at justifying our study.
-I'm not sure where to put it though.
-CS can also be an excellent model system for studying interdisciplinarity cite Porter and colleagues in a study on measuring interdisciplinarity~\cite{porter_measuring_2007} observe that 'The discrepancies between disciplinary roots and research realities loom large', a reference to the challenges associated with knowledge diffusing across researchers who tend to be focused in their own areas.
-This concern may be especially relevant for computer science given the ubiquity of computing today and limited public funding for research.
-Maybe squeeze in Tandy's NAS report on interdisciplinarity.
-I should ping Ohid Yaqub about this too- science policy is his area.}
-
-In a historical study of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles), Salton and Bergmark made the key point that the scientific literature serves a rich source of information to study the structure and historical development of a field~\cite{salton_citation_1979}.
-They described the global structure of computer science as consisting of three main subareas
-(i) theoretical foundations, such as theory of computation, (ii) hardware and computer systems, such as architecture,  and (iii) software, such as programming systems.
+Given this powerful influence of computer science in research, some understanding of its present state, structure, and relationship to other fields that seems warranted since it can inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy.
+For the same reason of its broad influence, computer science can also be an excellent model system for studying interdisciplinarity.
+These are not novel ideas, however, as far back as 1979, Salton and Bergmark conducted a historical study of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles) in which they made the key point that the scientific literature serves a rich source of information to study the structure and historical development of a field~\cite{salton_citation_1979}.
+These authors described the global structure of computer science as comprising three main subareas (i) theoretical foundations, such as theory of computation, (ii) hardware and computer systems, such as architecture,  and (iii) software, such as programming systems.
 Related areas acknowledged were  (a) mathematics of computing, such as numerical analysis, (b) special software topics, such as operating systems, (c) data management and database systems, (d) methodologies valid for multiple applications, such as algebraic manipulation, (e) computer applications, such as computer graphics, (f) non-technical aspects, such as computer education.
@@
 Disciplinary assignments using journal based classifications have been extensively discussed and critiqued~\cite{wang_large-scale_2016} [need comprehensive list of citations] with Shu and colleagues recently noting from a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
-Article classification systems have also been developed, however~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012}, which escape some of the criticisms of journal-based classification.
+Article classification systems have been developed, however~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012} that escape some of the criticisms of journal-based classification.
 
@@
 We describe below the high-level interactions of computer science within the Physical Sciences as well as with the Social Sciences and Life Sciences.
+
+\emph{misc stuff:  In using the term inform, we are mindful of (i) Greenhalgh (ii) Sarewitz and Pielke.
+I think that I want to cite these two without really knowing how.
+Greenhalgh for the limitations of positivism.
+Sarewitz for the limitations of allowing science to do whatever it wants to.
+I'd also like to see some text about (i) limited funding resources (ii) efficient use of existing resources (iiii) informing policy at multiple levels -- all directed at justifying our study.
+I'm not sure where to put it though.
+CS can also be an excellent model system for studying interdisciplinarity cite Porter and colleagues in a study on measuring interdisciplinarity~\cite{porter_measuring_2007} observe that 'The discrepancies between disciplinary roots and research realities loom large', a reference to the challenges associated with knowledge diffusing across researchers who tend to be focused in their own areas.
+This concern may be especially relevant for computer science given the ubiquity of computing today and limited public funding for research.
+Maybe squeeze in Tandy's NAS report on interdisciplinarity.
+I should ping Ohid Yaqub about this too- science policy is his area.}
 
@@
 Only records in DBLP with DOIs (4,291,130) were considered and only matches with a normalized rank of greater than 0.99 were accepted, roughly equivalent to `at least 11 matching lexemes independent of order and vector length'.
-As an example, the following query returns a normalized rank of 0.994.
-\begin{lstlisting}
-SELECT ts_rank(to_tsvector(`english', `one two three 
-four five six seven eight nine ten eleven'), 
-plainto_tsquery(`english', `one four three two five 
-six seven eight nine ten eleven')); 
-\end{lstlisting}
-
 This procedure resulted in a dataset of 634,100 DBLP publications with Scopus identifiers.
@@
 \paragraph{Clustering by Direct Citation} Graclus is a spectral graph clustering package that computes normalized cut and ratio association for a given undirected graph~\cite{graclus_2007}.
-\textcolor{blue}{Let's provide the exact URL as a citation}
-We downloaded v1.2 from the authors' website at `cs.utexas.edu'. 
-The \emph{comp} dataset was formatted as an undirected graph, stored in a file with a header line indicating the number of nodes and edges, and used as input to Graclus,  We varied the number of clusters to be formed between 10 and 50 clusters.
+We used v1.2 in our experiments.
+The \emph{comp} dataset was formatted as an undirected graph, stored in a file with a header line indicating the number of nodes and edges, and used as input to Graclus.
+We varied the number of clusters to be formed between 10 and 50 clusters.
 At 20 clusters, the most evenly sized set of clusters resulted with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{traag_louvain_2019}.

### 2019-11-19 Scientometrics/comp.tex
update

@@
 At 20 clusters, the most evenly sized set of clusters resulted with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{traag_louvain_2019}.
-[@sitaram please add the number of nodes in the Graclus 20 clusters].
+Consequently, we generated 20 clusters using Graclus, which were labelled 0-19 (Fig 2).
 
@@
 % For example, with the graphicx package use
-  \includegraphics[scale=0.2]{vlc.pdf}
+  \includegraphics[scale=0.3]{vlc.pdf}
 % figure caption is below the figure
@@
 A set of 20 clusters was generated using a spectral clustering technique, Graclus, that has previously been applied to citation data~\cite{graclus_2007,subelj_clustering_2016}.
-\textcolor{blue}{
- \emph{@sitaram please confirm the number of pubs that went into Graclus. I'm assuming it was 634,100?}. 
- }To place these clusters in context, we identified that accounted for at least 10\% of the publications in each cluster and observed 31 of the 334 minor subject areas in the Scopus ASJC classification.
+To place these clusters in context, we identified that accounted for at least 10\% of the publications in each cluster and observed 31 of the 334 minor subject areas in the Scopus ASJC classification.
 (which consists of 5 subject areas, 27 major subject areas, and 334 minor subject areas).
@@
 and Radiology Nuclear Medicine and Imaging.
-These 16 areas can be described are peripheral, to various degrees, to computer science.
+These 16 areas can be described as peripheral, in various degrees, to computer science.
 The picture that emerges is that areas central to computer science are likely to be found in multiple clusters.
+\textcolor{blue} {Can we match these clusters and areas's to Salton's classification?}
 
-\color{blue} \emph{need Tandy's input on the paragraph below.
+\textcolor{blue}{we need Tandy's input on the paragraph below.
 Also, do we need a table summarizing the paragraph above as a supplement Fig.1?
 I've stared at these data for so long that I'm burned out so please could you rewrite first, second, third, and fourth points.
-A fifth if you like} \color{black}
+A fifth if you like}
 
@@
 Fourth that interactions with fields outside computer science tend to be restricted to a single cluster or small numbers of clusters.
+We also attempted to map these 20 clusters assembled through direct citation to the CCS classification by manually matching the top 25-50 most heavily cited publications in each cluster to corresponidng categories in the CCS.
+This was feasible in some cases, clusters 0 and 1 mapped reasonably well to the top level categories Hardware and Computer Systems Organization but less so in the cases of other clusters.
+Further, the top cited papers often derived from biology and we were concerned that this small sample (top cited papers) were not representative of the cluster.
 

### 2019-11-20 Scientometrics/comp.tex
update

@@
 
+ \textcolor{blue}{need to add discussion of other clustering techniques, Newman, Kajikawa, Glanzel etc.}
+
 In extending the work of Salton and Bergmark to the 21st century, we sought to combine journal and article based classifications in a scalable manner.
@@
 A set of 20 clusters was generated using a spectral clustering technique, Graclus, that has previously been applied to citation data~\cite{graclus_2007,subelj_clustering_2016}.
-To place these clusters in context, we identified that accounted for at least 10\% of the publications in each cluster and observed 31 of the 334 minor subject areas in the Scopus ASJC classification.
+To place these clusters in context, we identified ASJC categories that accounted for at least 10\% of the publications in each cluster and observed 31 of the 334 minor subject areas in the Scopus ASJC classification.
 (which consists of 5 subject areas, 27 major subject areas, and 334 minor subject areas).
@@
 % figure caption is below the figure
-\caption{insert caption}
+\caption{caption will be inserted I just haven't been able to overcome the threshold to avoid boring tasks}
 \label{heatmap}       % Give a unique label

### 2019-11-21 Scientometrics/comp.tex
added a new figure

@@
 These authors described the global structure of computer science as comprising three main subareas (i) theoretical foundations, such as theory of computation, (ii) hardware and computer systems, such as architecture,  and (iii) software, such as programming systems.
-Related areas acknowledged were  (a) mathematics of computing, such as numerical analysis, (b) special software topics, such as operating systems, (c) data management and database systems, (d) methodologies valid for multiple applications, such as algebraic manipulation, (e) computer applications, such as computer graphics, (f) non-technical aspects, such as computer education.
+Related areas described were  (a) mathematics of computing, such as numerical analysis, (b) special software topics, such as operating systems, (c) data management and database systems, (d) methodologies valid for multiple applications, such as algebraic manipulation, (e) computer applications, such as computer graphics, (f) non-technical aspects, such as computer education.
 
-Much in the way of growth and evolution of computing has occurred since 1974.
-Progressing beyond the historical triad of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS)~\cite{acm_ref} published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field.
+Computing has grown and evolved significantly since 1974.
+Progressing beyond the historical triad of theoretical foundations; hardware and computer systems; and software\cite{salton_citation_1979}, the Computing Classification System (CCS)~\cite{acm_ref} published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field.
 This classification does address relationships with other fields under Applied Computing.
@@
 the Web of Science research and categorical classifications, the NSF classification system~\cite{nsf_classification}.
+Of these three, Scopus and the Web of Science make also contain citation data and proprietary unique identifiers for publications that can be matched, in some cases, to digital object identifiers (DOIs).
 All three rely on applying one or more journal-derived labels to articles.
-Disciplinary assignments using journal based classifications have been extensively discussed and critiqued~\cite{wang_large-scale_2016} [need comprehensive list of citations] with Shu and colleagues recently noting from a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
-Article classification systems have been developed, however~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012} that escape some of the criticisms of journal-based classification.
+Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
+Others have also discussed and critiqued disciplinary assignments using journal based classifications~\cite{wang_large-scale_2016} \textcolor{blue}{need comprehensive list of citations}.
+Article classification systems have been explored~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012}, which escape some of the criticisms of journal-based classification.
 
@@
 
-In extending the work of Salton and Bergmark to the 21st century, we sought to combine journal and article based classifications in a scalable manner.
-Consequently, we used a whole text search method to match records from two major data sources: (i) the DBLP bibliography--a reference bibliography for computer science~\cite{dblp_ref} and  (ii) the journal-based Scopus bibliography, which more comprehensively covers the physical sciences, life sciences, social sciences, and health sciences.
-\textcolor{blue}{Do we need to cite Scopus?}
-The underlying assumption is that a record in DBLP qualifies as computer science.
-Therefore, we cross-matched DBLP publications to Scopus to  enable identification of linked publications across multiple disciplines.
-
+In extending the work of Salton and Bergmark to the 21st century, we were also interested in connections between computer science and other fields.
+As a source of computer science literature, we used DBLP, a reference bibliography for computer science~\cite{dblp_ref}.
+The DBLP bibliography covers publications from computer science and includes publications from hybrid fields in cases they are considered pertinent to computer science research.
+The underlying assumption is that records in DBLP are greatly enriched for computer science even while recognizing that coverage is incomplete and possibly biased.
+Cross-matching DBLP publications to Scopus records using whole text searches applied to titles, enabled harvesting citation data as well as publications from other disciplines.
+This cross-matching also allows the use of both journal and article based classifications when clustering documents.
 Using both direct citations and co-citations as the basis for clustering, we used articles from from journals and conference proceedings for the period 1996-2015.
@@
 Only records in DBLP with DOIs (4,291,130) were considered and only matches with a normalized rank of greater than 0.99 were accepted, roughly equivalent to `at least 11 matching lexemes independent of order and vector length'.
-This procedure resulted in a dataset of 634,100 DBLP publications with Scopus identifiers.
-Cited references were extracted from Scopus, resulting in a total of 3,960,503 nodes (publications and references) and 11,992,387 edges that represent citations of these references and publications within the dataset.
+This procedure resulted in a dataset of 634,100 DBLP publications with Scopus identifiers where 49.6\% were labeled as article and 48.8\% as conference proceeding.
+Cited references were extracted from Scopus, resulting in a total of 3,960,503 nodes (publications and references) and 11,992,387 edges that represent citations within the dataset.
 This dataset is referred to as \emph{comp}.\par
+
+ \begin{figure}[ht]
+\centering
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.5]{ar_cp_ratio.pdf}
+% figure caption is below the figure
+\caption{Summary of DBLP data cross-matched with Scopus.
+634,100 publications from DBLP were cross-matched with Scopus and then matched to the 27 major subject areas in the ASJC (Scopus) classifications.
+The largest number of publications are contributed by Computer Science; Mathematics; and Engineering and then by Social Sciences; Physics and Astronomy; and Biochemistry, Genetics, and Molecular Biology.
+Publications were further annotated with respect to being either articles or conference proceedings and ordered on the abscissa by the ratio of conference proceedings to articles within a major subject area (cp\_count/ar\_count).
+For this dataset, the major subject areas of Energy; Computer Science; Medicine; Mathematics; and Engineering had the highest ratio of conference proceedings to articles while Immunology and Microbiology; Chemistry; General (multidisciplinary); Pharmacology, Toxicology, and Pharmaceutics; and Agricultural and Biological Sciences had the lowest ratio.
+}
+\label{ar_cp_annotation}       % Give a unique label
+\end{figure}
 
@@
 An issue is the generation of very large clusters by chaining through low edge weights.
-Thus, at each iteration, any cluster exceeding the maximum cluster size is put back into the process and a higher threshold applied to break such clusters.
+Thus, at each iteration, any cluster exceeding the maximum cluster size returned to the process and a higher threshold applied to break such clusters.
 
@@
 
-\begin{figure}[ht]
-\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=0.3]{vlc.pdf}
-% figure caption is below the figure
-\caption{Schematic representation of variable clustering protocol modified from Small and Sweeney (1985).
-Three parameters are specified (i) a threshold or starting level based on a quantile of normalized co-citation frequency (ii) a level increment (iii) a maximum cluster size.
-Input data is a set of co-cited publications with edge-weight defined by normalized co-citation frequencies.
-Green clusters are within the max cluster size.
-At the initial threshold, $t1$, a single cluster below the maximum cluster size, $mcs$ (green), along with one large cluster above it (red) are generated.
-As the threshold is incremented to $t2$, additional clusters of acceptable size is generated.
-The cascade continues to completion, which is defined by all clusters being of size less than or equal to the $mcs$.
-In this schematic, five rounds are adequate for the process to run to completion.}
-\label{vlc_process}       % Give a unique label
-\end{figure}
-
 We applied variable clustering with initial parameters of threshold ($t$) = 0.5 (normalized co-citation frequency, see Methods), increment $i = 0.1$, and maximum cluster size, $mcs = 100$.
@@
 Clusters containing only 2 nodes were then discarded bringing the total number of clusters down to 3,851.
-Pairwise clustering was then performed on these clusters to generate super-clusters.
+Pairwise clustering was then performed on these clusters to generate higher-order clusters.
 After 9 rounds of pairwise clustering, 13 clusters were generated resulting from agglomeration of 3,851 clusters
@@
 
+\begin{figure}[ht]
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.5]{scopus_dblp_graclus2.pdf}
+% figure caption is below the figure
+\caption{caption will be inserted I just haven't been able to overcome the threshold to avoid boring tasks}
+\label{heatmap}       % Give a unique label
+\end{figure}
 For the purpose of this study, we defined, the computer science literature as a working set of all articles in the DBLP bibliography published in 1996-2015, that had a digital object identifier (DOI), and could be matched to article identifiers in the Scopus bibliography.
@@
 Here we describe the overall strategy used for the two clustering methods.\\
-\begin{figure}[ht]
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=0.5]{scopus_dblp_graclus2.pdf}
-% figure caption is below the figure
-\caption{caption will be inserted I just haven't been able to overcome the threshold to avoid boring tasks}
-\label{heatmap}       % Give a unique label
-\end{figure}
 
@@
 \end{enumerate}
+
+\begin{figure}[ht]
+\centering
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.3]{vlc.pdf}
+% figure caption is below the figure
+\caption{Schematic representation of variable clustering protocol modified from Small and Sweeney (1985).
+Three parameters are specified (i) a threshold or starting level based on a quantile of normalized co-citation frequency (ii) a level increment (iii) a maximum cluster size.
+Input data is a set of co-cited publications with edge-weight defined by normalized co-citation frequencies.
+Green clusters are within the max cluster size.
+At the initial threshold, $t1$, a single cluster below the maximum cluster size, $mcs$ (green), along with one large cluster above it (red) are generated.
+As the threshold is incremented to $t2$, additional clusters of acceptable size is generated.
+The cascade continues to completion, which is defined by all clusters being of size less than or equal to the $mcs$.
+In this schematic, five rounds are adequate for the process to run to completion.}
+\label{vlc_process}       % Give a unique label
+\end{figure}
 

### 2019-11-21 Scientometrics/comp.tex
update

@@
 
-\emph{misc stuff:  In using the term inform, we are mindful of (i) Greenhalgh (ii) Sarewitz and Pielke.
-I think that I want to cite these two without really knowing how.
-Greenhalgh for the limitations of positivism.
-Sarewitz for the limitations of allowing science to do whatever it wants to.
-I'd also like to see some text about (i) limited funding resources (ii) efficient use of existing resources (iiii) informing policy at multiple levels -- all directed at justifying our study.
-I'm not sure where to put it though.
-CS can also be an excellent model system for studying interdisciplinarity cite Porter and colleagues in a study on measuring interdisciplinarity~\cite{porter_measuring_2007} observe that 'The discrepancies between disciplinary roots and research realities loom large', a reference to the challenges associated with knowledge diffusing across researchers who tend to be focused in their own areas.
-This concern may be especially relevant for computer science given the ubiquity of computing today and limited public funding for research.
-Maybe squeeze in Tandy's NAS report on interdisciplinarity.
-I should ping Ohid Yaqub about this too- science policy is his area.}
-
 \section{Materials and Methods}
@@
 Only records in DBLP with DOIs (4,291,130) were considered and only matches with a normalized rank of greater than 0.99 were accepted, roughly equivalent to `at least 11 matching lexemes independent of order and vector length'.
-This procedure resulted in a dataset of 634,100 DBLP publications with Scopus identifiers where 49.6\% were labeled as article and 48.8\% as conference proceeding.
+This procedure resulted in a dataset of 634,100 DBLP publications with Scopus identifiers where 49.6\% were labeled as article and 48.8\% as conference proceeding (Fig~\ref{fig:ar_cp_annotation}).
 Cited references were extracted from Scopus, resulting in a total of 3,960,503 nodes (publications and references) and 11,992,387 edges that represent citations within the dataset.
@@
 }
-\label{ar_cp_annotation}       % Give a unique label
+\label{fig:ar_cp_annotation}       % Give a unique label
 \end{figure}
@@
 At 20 clusters, the most evenly sized set of clusters resulted with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{traag_louvain_2019}.
-Consequently, we generated 20 clusters using Graclus, which were labelled 0-19 (Fig 2).
+Consequently, we generated 20 clusters using Graclus, which were labeled 0-19 (Fig~\ref{fig:heatmap}).
 
@@
 \caption{caption will be inserted I just haven't been able to overcome the threshold to avoid boring tasks}
-\label{heatmap}       % Give a unique label
+\label{fig:heatmap}       % Give a unique label
 \end{figure}
-For the purpose of this study, we defined, the computer science literature as a working set of all articles in the DBLP bibliography published in 1996-2015, that had a digital object identifier (DOI), and could be matched to article identifiers in the Scopus bibliography.
+For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography published in the years 1996-2015, that had a digital object identifier (DOI), and could also be matched to article identifiers in the Scopus bibliography.
 The process of selection and matching resulted in a dataset of 634,100 publications (Materials and Methods).
-We constructed article level clusters of the computer science literature for the years 1996-2015, at a sufficiently high level of aggregation to be comparable to disciplinary classification by journal.
+INSERT sentence about why one should cluster this dataset.
 Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation with an argument being made for direct citation as the best approach to concentrate citation links~\cite{klavans_which_2017}.
@@
 A set of 20 clusters was generated using a spectral clustering technique, Graclus, that has previously been applied to citation data~\cite{graclus_2007,subelj_clustering_2016}.
-To place these clusters in context, we identified ASJC categories that accounted for at least 10\% of the publications in each cluster and observed 31 of the 334 minor subject areas in the Scopus ASJC classification.
-(which consists of 5 subject areas, 27 major subject areas, and 334 minor subject areas).
+We constructed article level clusters of this computer science dataset at a sufficiently high level of aggregation to avoid cognitive challenge and cross-matched them to disciplinary classification by journal, the Scopus ASJC classification.
+We identified ASJC categories that accounted for at least 10\% of the publications in each cluster and observed 31 of the 334 minor subject areas in the Scopus ASJC classification, which consists of 5 subject areas, 27 major subject areas, and 334 minor subject areas (Fig~\ref{fig:heatmap}).
 
-Unsurprisingly, the broad category Computer Science Applications was present in 17 of 20 clusters, followed by  Electrical and Electronic Engineering in 12 clusters.
-
+Unsurprisingly, the category Computer Science Applications was present in 17 of 20 clusters, followed by  Electrical and Electronic Engineering in 12 clusters.
 At the other extreme, 16 minor subject areas were limited to a single cluster, viz.,
@@
 The picture that emerges is that areas central to computer science are likely to be found in multiple clusters.
-\textcolor{blue} {Can we match these clusters and areas's to Salton's classification?}
-
-\textcolor{blue}{we need Tandy's input on the paragraph below.
-Also, do we need a table summarizing the paragraph above as a supplement Fig.1?
-I've stared at these data for so long that I'm burned out so please could you rewrite first, second, third, and fourth points.
-A fifth if you like}
+We did not attempt to map these clusters to Salton and Bergmark's classification.
 
@@
 Fourth that interactions with fields outside computer science tend to be restricted to a single cluster or small numbers of clusters.
-We also attempted to map these 20 clusters assembled through direct citation to the CCS classification by manually matching the top 25-50 most heavily cited publications in each cluster to corresponidng categories in the CCS.
+We also attempted to map these 20 clusters assembled through direct citation to the CCS classification by manually matching the top 25-50 most heavily cited publications in each cluster to corresponding categories in the CCS.
 This was feasible in some cases, clusters 0 and 1 mapped reasonably well to the top level categories Hardware and Computer Systems Organization but less so in the cases of other clusters.
 Further, the top cited papers often derived from biology and we were concerned that this small sample (top cited papers) were not representative of the cluster.
-
-Cite Alan Porter on expanding universe versus myopic focus.
-Cite Traag, Waltman, Lariviere papers.
-Peter Sjögårde and Per Ahlgren, Loet Leydesdorff, Caroline S.
-Wagner and Lutz Bornmann, Discontinuities in citation relations among journals: self-organized criticality as a model of scientific revolutions and change, Scientometrics, 10.1007/s11192-018-2734-6, 116, 1, (623-644), (2018).
-Antonio Perianes-Rodriguez and Javier Ruiz-Castillo, A comparison of the Web of Science and publication-level classification systems of science, Journal of Informetrics, 10.1016/j.joi.2016.10.007, 11, 1, (32-45), (2017).
-Qi Wang and Ludo Waltman, Large-scale analysis of the accuracy of the journal classification systems of Web of Science and Scopus, Journal of Informetrics, 10.1016/j.joi.2016.02.003, 10, 2, (347-364), (2016).
-Henry Small, Kevin W.
-Boyack and Richard Klavans, Identifying emerging topics in science and technology,
-Crossref
-
-\textcolor{blue}{George, the rest needs to go into methods}
-
-\paragraph{Overall strategy}
-
-Here we describe the overall strategy used for the two clustering methods.\\
-
-\noindent
- Spectral clustering:
-\begin{enumerate}
-\item Subset Scopus by COMP
-\item Match COMP to DBLP at high stringency -> reduced number of scps
- \item Harvest cited references  from Scopus
- \item Cluster articles by direct citation using Graclus to a number that meets simple optimality criteria and does not impose cognitive challenges
- \item Reconcile cluster contents to journal classification for the purpose of referencing
- \item Infer inter-cluster relationships using direct citations, co-citations, and bibliographic coupling
-\end{enumerate}
 
@@
 
+\section{Garbage}
+
+Cite Alan Porter on expanding universe versus myopic focus.
+Cite Traag, Waltman, Lariviere papers.
+Peter Sjögårde and Per Ahlgren, Loet Leydesdorff, Caroline S.
+Wagner and Lutz Bornmann, Discontinuities in citation relations among journals: self-organized criticality as a model of scientific revolutions and change, Scientometrics, 10.1007/s11192-018-2734-6, 116, 1, (623-644), (2018).
+Antonio Perianes-Rodriguez and Javier Ruiz-Castillo, A comparison of the Web of Science and publication-level classification systems of science, Journal of Informetrics, 10.1016/j.joi.2016.10.007, 11, 1, (32-45), (2017).
+Qi Wang and Ludo Waltman, Large-scale analysis of the accuracy of the journal classification systems of Web of Science and Scopus, Journal of Informetrics, 10.1016/j.joi.2016.02.003, 10, 2, (347-364), (2016).
+Henry Small, Kevin W.
+Boyack and Richard Klavans, Identifying emerging topics in science and technology,
+Crossref
+
+\textcolor{blue}{George, the rest needs to go into methods}
+
+\paragraph{Overall strategy}
+
+Here we describe the overall strategy used for the two clustering methods.\\
+
+\emph{misc stuff:  In using the term inform, we are mindful of (i) Greenhalgh (ii) Sarewitz and Pielke.
+I think that I want to cite these two without really knowing how.
+Greenhalgh for the limitations of positivism.
+Sarewitz for the limitations of allowing science to do whatever it wants to.
+I'd also like to see some text about (i) limited funding resources (ii) efficient use of existing resources (iiii) informing policy at multiple levels -- all directed at justifying our study.
+I'm not sure where to put it though.
+CS can also be an excellent model system for studying interdisciplinarity cite Porter and colleagues in a study on measuring interdisciplinarity~\cite{porter_measuring_2007} observe that 'The discrepancies between disciplinary roots and research realities loom large', a reference to the challenges associated with knowledge diffusing across researchers who tend to be focused in their own areas.
+This concern may be especially relevant for computer science given the ubiquity of computing today and limited public funding for research.
+Maybe squeeze in Tandy's NAS report on interdisciplinarity.
+I should ping Ohid Yaqub about this too- science policy is his area.}
+
+\noindent
+ Spectral clustering:
+\begin{enumerate}
+\item Subset Scopus by COMP
+\item Match COMP to DBLP at high stringency -> reduced number of scps
+ \item Harvest cited references  from Scopus
+ \item Cluster articles by direct citation using Graclus to a number that meets simple optimality criteria and does not impose cognitive challenges
+ \item Reconcile cluster contents to journal classification for the purpose of referencing
+ \item Infer inter-cluster relationships using direct citations, co-citations, and bibliographic coupling
+\end{enumerate}
+
 \end{document}

### 2019-11-24 Scientometrics/comp.tex
updated

@@
 
-\title{Citation Analysis of Computer Science%\thanks{Grants or other notes
+\title{Citation Analysis of Computer Science Publications%\thanks{Grants or other notes
 %about the article that should go on the front page should be
@@
 }
-\subtitle{Relationship With Other Fields}
+\subtitle{Relationship To Other Fields}
 
@@
 Computer science as a field has experienced dramatic growth and diversification over the last twenty years.
-Towards an improved understanding of the structure of the field, we analyze a cohort of the computer science literature using a historiographic approach.
-For further insight on the features of this cohort and the flow of information within its components, we construct article level clusters whose elements are linked by citations or co-citations, and reconcile them with subject categories in the All Science Journal Classification (Scopus).
+Towards an improved understanding of the structure of the field, we analyze a cohort of the computer science literature.
+For insight on the features of this cohort and the flow of information within its components, we construct article level clusters whose elements are linked by citations or co-citations, and reconcile them with subject categories in the All Science Journal Classification (Scopus).
 [abstract is feeble and needs to be rewritten]
@@
 
-In extending the work of Salton and Bergmark to the 21st century, we were also interested in connections between computer science and other fields.
+Thus, we sought to extend the work of Salton and Bergmark to reflect a more current reality while also considering connections between computer science and other fields.
 As a source of computer science literature, we used DBLP, a reference bibliography for computer science~\cite{dblp_ref}.
-The DBLP bibliography covers publications from computer science and includes publications from hybrid fields in cases they are considered pertinent to computer science research.
+The DBLP bibliography covers publications from computer science and includes publications from hybrid fields, where they are considered pertinent to computer science research.
 The underlying assumption is that records in DBLP are greatly enriched for computer science even while recognizing that coverage is incomplete and possibly biased.
@@
 Using both direct citations and co-citations as the basis for clustering, we used articles from from journals and conference proceedings for the period 1996-2015.
-We reconciled these clusters with the the All Science Journal Classification (ASJC) developed and maintained by Scopus as well as to the CCS classification through a combination of automated and manual procedures.
+We reconciled these clusters with the All Science Journal Classification (ASJC) developed and maintained by Scopus as well as to the CCS classification through a combination of automated and manual procedures.
 We describe below the high-level interactions of computer science within the Physical Sciences as well as with the Social Sciences and Life Sciences.
@@
 We have previously parsed, the Scopus dataset of over 72,000,000 publications into a custom schema as part of a larger data platform for research evaluation~\cite{GithubERNIE2019}.
-Records in the DBLP dataset, were matched to Scopus identifiers using PostgreSQL's full text search feature applied to document titles.
-The process involves parsing all Scopus document titles into tokens, reducing the tokens into lexemes and returning vectors containing these lexemes.
-The vectors are then matched with corresponding text search vectors extracted from DBLP document titles.
-A rank is returned based on the frequency of matching lexemes.
-Only records in DBLP with DOIs (4,291,130) were considered and only matches with a normalized rank of greater than 0.99 were accepted, roughly equivalent to `at least 11 matching lexemes independent of order and vector length'.
-This procedure resulted in a dataset of 634,100 DBLP publications with Scopus identifiers where 49.6\% were labeled as article and 48.8\% as conference proceeding (Fig~\ref{fig:ar_cp_annotation}).
-Cited references were extracted from Scopus, resulting in a total of 3,960,503 nodes (publications and references) and 11,992,387 edges that represent citations within the dataset.
+Records in the DBLP dataset, were matched to Scopus identifiers using digital object identifiers (DOIs).
+This procedure resulted in a dataset of 2,685,356 DBLP publications with Scopus identifiers where 1,278,322 (47.6\%) were labeled as article and 1,407,034 (52.4\%) as conference proceeding (Fig~\ref{fig:ar_cp_annotation}).
+References cited by these publications were then extracted from Scopus (7,129,006), resulting in a total of 8,000,411 nodes (publications and references) and  44,296,381 edges that represent citations within the dataset.
 This dataset is referred to as \emph{comp}.\par
@@
 \caption{Summary of DBLP data cross-matched with Scopus.
-634,100 publications from DBLP were cross-matched with Scopus and then matched to the 27 major subject areas in the ASJC (Scopus) classifications.
+2,685,356 publications from DBLP were cross-matched with Scopus and then grouped by the 27 major subject areas in the ASJC (Scopus) classification.
 The largest number of publications are contributed by Computer Science; Mathematics; and Engineering and then by Social Sciences; Physics and Astronomy; and Biochemistry, Genetics, and Molecular Biology.
-Publications were further annotated with respect to being either articles or conference proceedings and ordered on the abscissa by the ratio of conference proceedings to articles within a major subject area (cp\_count/ar\_count).
-For this dataset, the major subject areas of Energy; Computer Science; Medicine; Mathematics; and Engineering had the highest ratio of conference proceedings to articles while Immunology and Microbiology; Chemistry; General (multidisciplinary); Pharmacology, Toxicology, and Pharmaceutics; and Agricultural and Biological Sciences had the lowest ratio.
-}
+Publications were further annotated with respect to being either articles \emph{(ar)} or conference proceedings \emph{(cp)}.
+For this dataset, the major subject areas of Computer Science; Engineering; and Mathematics contributed the most publications while Pharmacology, Toxicology, and Pharmaceutics; Nursing, Veterinary and Dentistry contributed the least.}
 \label{fig:ar_cp_annotation}       % Give a unique label
@@
 At 20 clusters, the most evenly sized set of clusters resulted with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{traag_louvain_2019}.
-Consequently, we generated 20 clusters using Graclus, which were labeled 0-19 (Fig~\ref{fig:heatmap}).
+Consequently, we generated 20 clusters using Graclus, which were labeled 0-19 (Fig~\ref{fig:heatmap})
+
+\begin{table}
+% table caption is above the table
+\caption{\emph{2685021 is because of inner joins on ASJC Explain conductance calculations~\cite{shun_parallel_2016}}}
+\label{tab:1}       % Give a unique label
+% For LaTeX tables use
+\begin{tabular}{lllll}
+\hline\noalign{\smallskip}
+Cluster & Publications & Conductance & ASJC Labels & Unique Labels\\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+0 & 111,294 & 0.12 & 265,664 & 142 \\ 
+1 & 117,057 & 0.14 & 246,960 & 166 \\ 
+2 & 116,251 & 0.11 & 280,602 & 165 \\ 
+3 & 353,366 & 0.15 & 881,693 & 200 \\ 
+4 & 145,081 & 0.09 & 349,020 & 154 \\ 
+5 & 92,097 & 0.17 & 248,168 & 186 \\ 
+6 & 71,865 & 0.15 & 199,681 & 163 \\ 
+7 & 179,927 & 0.18 & 465,181 & 202 \\ 
+8 & 302,656 & 0.18 & 760,117 & 214 \\ 
+9 & 69,520 & 0.19 & 197,031 & 174 \\ 
+10 & 42,462 & 0.10 & 102,838 & 141 \\ 
+11 & 448,030 & 0.25 & 1,229,061 & 224 \\ 
+12 & 70,738 & 0.21 & 216,546 & 179 \\ 
+13 & 105,232 & 0.17 & 289,318 & 187 \\ 
+14 & 199,176 & 0.15 & 551,657 & 208 \\ 
+15 & 64,384 & 0.17 & 195,679 & 167 \\ 
+16 & 89,340 & 0.11 & 240,157 & 158 \\ 
+17 & 50,817 & 0.14 & 181,531 & 179 \\ 
+18 & 43,113 & 0.20 & 108,518 & 177 \\ 
+19 & 12,615 & 0.80 & 36,583 & 229 \\ \noalign{\smallskip}\hline
+\end{tabular}
+\end{table}
 
@@
 % For example, with the graphicx package use
-  \includegraphics[scale=0.5]{scopus_dblp_graclus2.pdf}
+  \includegraphics[scale=0.5]{scopus_dblp_graclus3.pdf}
 % figure caption is below the figure
@@
 % For tables use
-\begin{table}
-% table caption is above the table
-\caption{Please write your table caption here}
-\label{tab:1}       % Give a unique label
-% For LaTeX tables use
-\begin{tabular}{lll}
-\hline\noalign{\smallskip}
-first & second & third  \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-number & number & number \\
-number & number & number \\
-\noalign{\smallskip}\hline
-\end{tabular}
-\end{table}
 

### 2019-12-04 Scientometrics/comp.tex
update

@@
 Towards an improved understanding of the structure of the field, we analyze a cohort of the computer science literature.
-For insight on the features of this cohort and the flow of information within its components, we construct article level clusters whose elements are linked by citations or co-citations, and reconcile them with subject categories in the All Science Journal Classification (Scopus).
+For insight on the features of this cohort and the flow of information within its components, we construct article level clusters whose elements are linked by citations or co-citations, and reconcile them with major and minor subject categories in the All Science Journal Classification (Scopus).
 [abstract is feeble and needs to be rewritten]
@@
 Computer science, and its applications, has experienced rapid growth and diversification over the last twenty years.
-The collective influence of the Internet of Things (IoT), `big' data, accessible cloud computing, and advances in artificial intelligence have further been postulated as a recent driver for its growth and evolution~\cite{siebel2019_digital}.
-As also noted in a 2017 US National Academies Report~\cite{nas_2017}, ``A wide range of jobs in virtually all sectors demand computing skills to an unprecedented extent.
+More recently, the collective influence of the Internet of Things (IoT), `big' data, accessible cloud computing, and advances in artificial intelligence have been postulated as a recent driver for growth and evolution~\cite{siebel2019_digital}.
+As noted in a 2017 US National Academies Report~\cite{nas_2017}, ``A wide range of jobs in virtually all sectors demand computing skills to an unprecedented extent.
 And every academic discipline finds itself incorporating computing into its research and educational mission".
-Given this powerful influence of computer science in research, some understanding of its present state, structure, and relationship to other fields that seems warranted since it can inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy.
-For the same reason of its broad influence, computer science can also be an excellent model system for studying interdisciplinarity.
-These are not novel ideas, however, as far back as 1979, Salton and Bergmark conducted a historical study of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles) in which they made the key point that the scientific literature serves a rich source of information to study the structure and historical development of a field~\cite{salton_citation_1979}.
+Given the powerful influence of computer science in research, some understanding of its present state, structure, and relationship to other fields that seems warranted since it can inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy.
+For the same reason of broad influence, computer science can also be an excellent model system for studying interdisciplinarity.
+
+These are not novel ideas however, as far back as 1979, Salton and Bergmark conducted a historical study of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles) in which they made the key point that the scientific literature serves a rich source of information to study the structure and historical development of a field~\cite{salton_citation_1979}.
 These authors described the global structure of computer science as comprising three main subareas (i) theoretical foundations, such as theory of computation, (ii) hardware and computer systems, such as architecture,  and (iii) software, such as programming systems.
-Related areas described were  (a) mathematics of computing, such as numerical analysis, (b) special software topics, such as operating systems, (c) data management and database systems, (d) methodologies valid for multiple applications, such as algebraic manipulation, (e) computer applications, such as computer graphics, (f) non-technical aspects, such as computer education.
+Related areas noted were  (a) mathematics of computing, such as numerical analysis, (b) special software topics, such as operating systems, (c) data management and database systems, (d) methodologies valid for multiple applications, such as algebraic manipulation, (e) computer applications, such as computer graphics, (f) non-technical aspects, such as computer education.
 
@@
 the Web of Science research and categorical classifications, the NSF classification system~\cite{nsf_classification}.
-Of these three, Scopus and the Web of Science make also contain citation data and proprietary unique identifiers for publications that can be matched, in some cases, to digital object identifiers (DOIs).
+Of these, Scopus and the Web of Science also contain citation links and proprietary unique identifiers for publications that can be matched, in some cases, to digital object identifiers (DOIs).
 All three rely on applying one or more journal-derived labels to articles.
-Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
+However, Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
 Others have also discussed and critiqued disciplinary assignments using journal based classifications~\cite{wang_large-scale_2016} \textcolor{blue}{need comprehensive list of citations}.
@@
 
-Thus, we sought to extend the work of Salton and Bergmark to reflect a more current reality while also considering connections between computer science and other fields.
+We sought to extend the work of Salton and Bergmark to reflect a more current reality while also considering connections between computer science and other fields.
 As a source of computer science literature, we used DBLP, a reference bibliography for computer science~\cite{dblp_ref}.
@@
 The underlying assumption is that records in DBLP are greatly enriched for computer science even while recognizing that coverage is incomplete and possibly biased.
-Cross-matching DBLP publications to Scopus records using whole text searches applied to titles, enabled harvesting citation data as well as publications from other disciplines.
+Cross-matching DBLP publications to Scopus records using DOIs, enabled of harvesting citation data as well as links to publications from other disciplines.
 This cross-matching also allows the use of both journal and article based classifications when clustering documents.
 Using both direct citations and co-citations as the basis for clustering, we used articles from from journals and conference proceedings for the period 1996-2015.
-We reconciled these clusters with the All Science Journal Classification (ASJC) developed and maintained by Scopus as well as to the CCS classification through a combination of automated and manual procedures.
+We reconciled these clusters with the All Science Journal Classification (ASJC) developed and maintained by Scopus through a combination of automated and manual procedures.
 We describe below the high-level interactions of computer science within the Physical Sciences as well as with the Social Sciences and Life Sciences.
@@
 At 20 clusters, the most evenly sized set of clusters resulted with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{traag_louvain_2019}.
-Consequently, we generated 20 clusters using Graclus, which were labeled 0-19 (Fig~\ref{fig:heatmap})
+Consequently, we generated 20 clusters, labeled 0-19, using Graclus (Fig~\ref{fig:heatmap}).
+The quality of clustering was evaluated by measuring conductance [add citations] as defined by Shun.
 
@@
 
-\paragraph{Clustering by Co-Citation} To build clusters using co-citations, we used variable level clustering, an approach developed by Small and Sweeney (1985)~\cite{small_clustering_1985}, with minor modifications.
+\paragraph{Clustering by Co-Citation} To build clusters using co-citations, we first implemented variable level clustering, an approach developed by Small and Sweeney (1985)~\cite{small_clustering_1985}, with minor modifications.
 Variable level clustering involves applying a threshold (below which all edges are dissolved) then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn.
@@
 
-In our implementation of variable level clustering, we first calculated the number of citations accumulated across Scopus for all 634,100 articles in \emph{comp}.
-After discarding those publications without any citations, we restricted further analysis to those in the 90th percentile of citations or higher resulting in a dataset of size 50,869.
-We then identified 897,407 publications in Scopus that cite the 50,869 previously selected papers from \emph{comp}.
-The cited references in these papers were restricted to those in the set of 50,869 highly cited papers previously identified.
-For each of the 897,407 citing publications in turn, all possible reference pairs, ${n \choose 2}$, were generated where $n$ is the number of references in a publication.
+In our implementation of variable level clustering, we first calculated the number of citations accumulated across Scopus for all 2,685,356 articles in \emph{comp}.
+After discarding those publications without any citations, we restricted further analysis to those in the 90th percentile of citations or higher resulting in a dataset of size 212,311.
+We then identified 4,318,305 publications in Scopus that cite the 212,311 previously selected papers from \emph{comp}.
+The cited references in these papers were restricted to those in the set of 212,311 highly cited papers previously identified.
+For each of the 4,318,305 citing publications in turn, all possible reference pairs, ${n \choose 2}$, were generated where $n$ is the number of references in a publication.
 The frequency of these co-cited pairs was then computed across the dataset  and normalized using Salton's cosine formula~\cite{salton_citation_1979}.
-A total of 2,208,135 unique co-cited pairs were thus obtained.
+A total of 46,463,117 unique co-cited pairs were thus obtained.
 These data were represented in a graph where each node was a publication and the weighted edge between the pair was the normalized co-citation frequency.
@@
 
-We applied variable clustering with initial parameters of threshold ($t$) = 0.5 (normalized co-citation frequency, see Methods), increment $i = 0.1$, and maximum cluster size, $mcs = 100$.
+We applied variable clustering with initial parameters of threshold ($t$) = median normalized co-citation frequency (quantile=0.5), increment $i = 0.1$, and maximum cluster size, $mcs = 200$.
 Thus, at start, all edges below the median normalized co-citation frequency are dissolved.
@@
 All clusters generated thus, contained  less than 100 nodes.
-Using this approach, 6,822 clusters containing 35,485 nodes were generated.
-Clusters containing only 2 nodes were then discarded bringing the total number of clusters down to 3,851.
-Pairwise clustering was then performed on these clusters to generate higher-order clusters.
-After 9 rounds of pairwise clustering, 13 clusters were generated resulting from agglomeration of 3,851 clusters
+Using this approach, 22,232 clusters containing 84,591 nodes were generated.
+Clusters containing only 2 nodes were then discarded bringing the total number of clusters down to 10,298.
+
+Agglomerative clustering was then performed on these clusters to generate higher-order clusters.
+Briefly, the edge weight between two clusters was assigned as the maximum edge weight of all edges between these two clusters.
+Edges were arranged in descending order and the first pair of clusters were merged and its edge weight with other interacting clusters was recalculated.
+The edges were then re-ordered as before and the next pair of clusters was merged.
+The process was halted after 600 rounds to prevent single large clusters being generated (figure), and resulted in 665 clusters.
+The top 20 clusters were used for further analysis and comparison with clusters generated by direct citation.
+The largest of these 20 clusters contained 1,276 nodes and the smallest contained 136.
 
@@
 \end{figure}
-For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography published in the years 1996-2015, that had a digital object identifier (DOI), and could also be matched to article identifiers in the Scopus bibliography.
-The process of selection and matching resulted in a dataset of 634,100 publications (Materials and Methods).
-INSERT sentence about why one should cluster this dataset.
+For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography published in the years 1996-2015, that had (i) a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography.
+The process of selection and matching resulted in a dataset of 2,685,356 publications (Materials and Methods).
+
+[Need justification for why 20 article level clusters- may be in Waltman's article]
+
 Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation with an argument being made for direct citation as the best approach to concentrate citation links~\cite{klavans_which_2017}.
 Accordingly, we first used direct citation links as the basis for cluster formation.
-A set of 20 clusters was generated using a spectral clustering technique, Graclus, that has previously been applied to citation data~\cite{graclus_2007,subelj_clustering_2016}.
+A set of 20 clusters was generated using Graclus, a spectral clustering technique that has previously been applied to citation data~\cite{graclus_2007,subelj_clustering_2016}.
 We constructed article level clusters of this computer science dataset at a sufficiently high level of aggregation to avoid cognitive challenge and cross-matched them to disciplinary classification by journal, the Scopus ASJC classification.
-We identified ASJC categories that accounted for at least 10\% of the publications in each cluster and observed 31 of the 334 minor subject areas in the Scopus ASJC classification, which consists of 5 subject areas, 27 major subject areas, and 334 minor subject areas (Fig~\ref{fig:heatmap}).
+We considered Scopus ASJC minor subject area categories that accounted for at least 10\% of the publications in each cluster and observed 31 of the 334 ASJC minor subject areas, suggesting some selectivity in these results.
 
-Unsurprisingly, the category Computer Science Applications was present in 17 of 20 clusters, followed by  Electrical and Electronic Engineering in 12 clusters.
-At the other extreme, 16 minor subject areas were limited to a single cluster, viz.,
-Atomic and Molecular Physics and Optics; 
-Biochemistry; 
-Chemistry (all); 
-Cognitive Neuroscience; 
-Computer Vision and Pattern Recognition;
-Computers in Earth Sciences;
-Earth and Planetary Sciences; 
-Education; 
-Electronic Optical and Magnetic Materials; 
-Information Systems; 
-Information Systems and Management;  
-Management Science and Operations Research;
-Molecular Biology;
-Neurology; 
-Physics and Astronomy (miscellaneous); 
-and Radiology Nuclear Medicine and Imaging.
-These 16 areas can be described as peripheral, in various degrees, to computer science.
-The picture that emerges is that areas central to computer science are likely to be found in multiple clusters.
-We did not attempt to map these clusters to Salton and Bergmark's classification.
+(Fig~\ref{fig:heatmap}) permits examination of these data from two perspectives (i) the clusters that map to a given ASJC minor subject area (ii) ASJC minor subject areas that comprised at least 10\% of the publication in a cluster.
+Unsurprisingly, the broad category Computer Science Applications was present in 16 of 20 clusters, followed by Software in 12 clusters, and Electrical and Electronic Engineering in 10 clusters.
 
-Examining these data from the perspective of the generated clusters (Fig.
-1 abscissa), interactions with the Life Sciences were evident in cluster 17 (Biochemistry, Computational Mathematics, Computational Theory and Mathematics, Computer Science Applications, and Molecular Biology) and cluster 10 (Artificial Intelligence, Biomedical Engineering, Cognitive Neuroscience, Computer Science Applications, and Neurology).
-While acknowledging previously reported inaccuracies in journal-based classification \emph{vide supra}, these results strongly suggest that the actual structure of communication within the broad area of computer science is at variance with journal-based classification, also noted by Waltman and van Eck, to wit, ``...an indication that traditional disciplines such as those just mentioned only partly reflect the actual organization of today's scientific research."~\cite{waltman_new_2012}.
+From the other perspective, cluster 17 was the most diverse and contained publications annotated with 8 minor subject area labels, of which Biochemistry, Chemistry(all), Genetics, and Molecular Biology were the most distant from computer science while Statistics \& Probability, Computational Theory \& Mathematics, and Computational Mathematics are closer.
+It is important to be reminded of the caveats associated with (i) the limitations of the DBLP dataset (ii) the limitations of cross-matching to Scopus (iii) the limitations of journal based classification (iv) the limitations of clustering by direct citation.
+Even so, a picture that emerges is that areas central to computer science in 2019 are more likely to be found in multiple clusters (hardware, software, and theory) and that biology, chemistry, and statistics are proximal.
+These results strongly suggest that the actual structure of communication within the broad field of computer science may be at variance with journal-based classification, also noted by Waltman and van Eck, ``...an indication that traditional disciplines such as those just mentioned only partly reflect the actual organization of today's scientific research."~\cite{waltman_new_2012}.
 The aphorism of Porter, Cohen, Roessner, and Perreault (2007), `The discrepancies between disciplinary roots and research realities loom large'~\cite{porter_measuring_2007} also invokes itself.
-Secondly, that a correlation exists between broad journal-based classification and article clusters in terms of subject matter.
+A second inference is that a correlation appears between broad journal-based classification and article clusters in terms of subject matter.
 Thirdly, that some areas of computer science are relatively ubiquitous.
-Fourth that interactions with fields outside computer science tend to be restricted to a single cluster or small numbers of clusters.
+Fourth that interactions with fields outside computer science are restricted to a single cluster or small numbers of clusters.
+
 We also attempted to map these 20 clusters assembled through direct citation to the CCS classification by manually matching the top 25-50 most heavily cited publications in each cluster to corresponding categories in the CCS.
@@
 % For example, with the graphicx package use
-  \includegraphics[scale=0.3]{vlc.pdf}
+  \includegraphics[scale=0.25]{vlc.pdf}
 % figure caption is below the figure

### 2019-12-05 Scientometrics/comp.tex
added new figures

@@
 We used v1.2 in our experiments.
-The \emph{comp} dataset was formatted as an undirected graph, stored in a file with a header line indicating the number of nodes and edges, and used as input to Graclus.
-We varied the number of clusters to be formed between 10 and 50 clusters.
+The \emph{comp} dataset was formatted as an undirected graph, stored in a file with a header line indicating the number of nodes and edges, and used as input to Graclus, which requires the number of clusters to be formed as an input parameter.
+In preliminary experiments, we varied the number of clusters to be formed between 10 and 50 clusters (data not shown).
 At 20 clusters, the most evenly sized set of clusters resulted with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{traag_louvain_2019}.
 Consequently, we generated 20 clusters, labeled 0-19, using Graclus (Fig~\ref{fig:heatmap}).
-The quality of clustering was evaluated by measuring conductance [add citations] as defined by Shun.
+The quality of clustering was evaluated by measuring conductance as defined in Shun et al.~\cite{shun_parallel_2016}.
+Data in \emph{comp} were clustered into 18, 20, or 22 clusters and in each case the last cluster (17, 19, 21) had the highest conductance value and the smallest number of nodes suggesting that it effectively served as a container for `left over publications' during the Graclus process.
+Thus, we did not consider cluster 19 (the 20th cluster) when interpreting our results.
+The remaining 19 clusters had conductance values ranging from 0.09 to 0.25 with a median conductance of 0.15.
+
+ \begin{figure}[ht]
+\centering
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.3]{graclus_comparison.pdf}
+% figure caption is below the figure
+\caption{Summary of DBLP data cross-matched with Scopus.
+2,685,356 publications from DBLP were cross-matched with Scopus and then grouped by the 27 major subject areas in the ASJC (Scopus) classification.
+The largest number of publications are contributed by Computer Science; Mathematics; and Engineering and then by Social Sciences; Physics and Astronomy; and Biochemistry, Genetics, and Molecular Biology.
+Publications were further annotated with respect to being either articles \emph{(ar)} or conference proceedings \emph{(cp)}.
+For this dataset, the major subject areas of Computer Science; Engineering; and Mathematics contributed the most publications while Pharmacology, Toxicology, and Pharmaceutics; Nursing, Veterinary and Dentistry contributed the least.}
+\label{fig:graclus_comparison}       % Give a unique label
+\end{figure}
 
@@
 \hline\noalign{\smallskip}
-Cluster & Publications & Conductance & ASJC Labels & Unique Labels\\
+Cluster & Publications & Conductance & Total ASJC Labels & Unique ASJC Labels\\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 \end{figure}
+
 For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography published in the years 1996-2015, that had (i) a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography.
@@
 
+Co-citation, the frequency with which a pair of articles is cited by other articles, was first described independently by Small and Marshakova in 1973~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973} provides insight into the emergence of new ideas derived from the association of previously independent ones.
+Co-citation, thus provides some degree of evolutionary insight across disciplines and sub-disciplines and has been used for clustering publications~\cite{boyack_co-citation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
+To provide an alternate view of these DBLP data we also constructed clusters using co-citation as below and as described in Methods.
+
 \begin{figure}[ht]
@@
 
-\noindent
+%\noindent
 Co-citation based clustering:
@@
 \end{enumerate}
+
+ \begin{figure}[ht]
+\centering
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.3]{cocitr2_venn.pdf}
+% figure caption is below the figure
+\caption{Summary of DBLP data cross-matched with Scopus.
+2,685,356 publications from DBLP were cross-matched with Scopus and then grouped by the 27 major subject areas in the ASJC (Scopus) classification.
+The largest number of publications are contributed by Computer Science; Mathematics; and Engineering and then by Social Sciences; Physics and Astronomy; and Biochemistry, Genetics, and Molecular Biology.
+Publications were further annotated with respect to being either articles \emph{(ar)} or conference proceedings \emph{(cp)}.
+For this dataset, the major subject areas of Computer Science; Engineering; and Mathematics contributed the most publications while Pharmacology, Toxicology, and Pharmaceutics; Nursing, Veterinary and Dentistry contributed the least.}
+\label{fig:cocitr_venn2}       % Give a unique label
+\end{figure}
 

### 2019-12-05 Scientometrics/comp.tex
updated Venn diagram

@@
 And every academic discipline finds itself incorporating computing into its research and educational mission".
-Given the powerful influence of computer science in research, some understanding of its present state, structure, and relationship to other fields that seems warranted since it can inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy.
-For the same reason of broad influence, computer science can also be an excellent model system for studying interdisciplinarity.
+Given this powerful influence some understanding of the present state and structure of computer science and its relationship to other fields would inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy.
+For the same reason of broad influence, computer science can also serve as a model system for studying interdisciplinarity.
 
-These are not novel ideas however, as far back as 1979, Salton and Bergmark conducted a historical study of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles) in which they made the key point that the scientific literature serves a rich source of information to study the structure and historical development of a field~\cite{salton_citation_1979}.
+As far back as 1979, Salton and Bergmark conducted a historical study of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles) in which they made the point that the scientific literature serves a rich source of information to study the structure and historical development of a field~\cite{salton_citation_1979}.
 These authors described the global structure of computer science as comprising three main subareas (i) theoretical foundations, such as theory of computation, (ii) hardware and computer systems, such as architecture,  and (iii) software, such as programming systems.
@@
 Computing has grown and evolved significantly since 1974.
-Progressing beyond the historical triad of theoretical foundations; hardware and computer systems; and software\cite{salton_citation_1979}, the Computing Classification System (CCS)~\cite{acm_ref} published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field.
+Progressing beyond Salton and Bergmark's historical triad of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS)~\cite{acm_ref} published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field.
 This classification does address relationships with other fields under Applied Computing.
@@
 Other classification systems are available such as the All Science Journal Classification (ASJC) developed and maintained by Scopus.
-the Web of Science research and categorical classifications, the NSF classification system~\cite{nsf_classification}.
-Of these, Scopus and the Web of Science also contain citation links and proprietary unique identifiers for publications that can be matched, in some cases, to digital object identifiers (DOIs).
+the Web of Science research and categorical classifications from Clarivate Analytics, and the NSF classification system~\cite{nsf_classification}.
+Of these, Scopus and the Web of Science also include global bibliographies with citation links and proprietary unique identifiers for publications that can be matched, in some cases, to digital object identifiers (DOIs).
 All three rely on applying one or more journal-derived labels to articles.
-However, Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
+The inheritance, by articles, of labels meant to describe journals can be problematic in fields that evolve faster than their journal classifications.
+Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science, that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
 Others have also discussed and critiqued disciplinary assignments using journal based classifications~\cite{wang_large-scale_2016} \textcolor{blue}{need comprehensive list of citations}.
-Article classification systems have been explored~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012}, which escape some of the criticisms of journal-based classification.
+Article classification systems have been constructed, however, which escape some of the criticisms of journal-based classification~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012}.
 
- \textcolor{blue}{need to add discussion of other clustering techniques, Newman, Kajikawa, Glanzel etc.}
-
-We sought to extend the work of Salton and Bergmark to reflect a more current reality while also considering connections between computer science and other fields.
+In this study, we sought to extend the work of Salton and Bergmark to reflect a more current reality while also considering connections between computer science and other fields.
 As a source of computer science literature, we used DBLP, a reference bibliography for computer science~\cite{dblp_ref}.
 The DBLP bibliography covers publications from computer science and includes publications from hybrid fields, where they are considered pertinent to computer science research.
-The underlying assumption is that records in DBLP are greatly enriched for computer science even while recognizing that coverage is incomplete and possibly biased.
-Cross-matching DBLP publications to Scopus records using DOIs, enabled of harvesting citation data as well as links to publications from other disciplines.
+The underlying assumption is that records in DBLP are greatly enriched for computer science even while recognizing that coverage may be incomplete and possibly biased.
+Cross-matching DBLP publications to Scopus records enabled us to harvest the richer citation data in Scopus, as well as extract links to publications from other disciplines.
 This cross-matching also allows the use of both journal and article based classifications when clustering documents.
-Using both direct citations and co-citations as the basis for clustering, we used articles from from journals and conference proceedings for the period 1996-2015.
+Using both direct citations and co-citations as the basis for clustering, we used DBLP articles from journals and conference proceedings for the period 1996-2015.
 We reconciled these clusters with the All Science Journal Classification (ASJC) developed and maintained by Scopus through a combination of automated and manual procedures.
@@
 Records in the DBLP dataset, were matched to Scopus identifiers using digital object identifiers (DOIs).
-This procedure resulted in a dataset of 2,685,356 DBLP publications with Scopus identifiers where 1,278,322 (47.6\%) were labeled as article and 1,407,034 (52.4\%) as conference proceeding (Fig~\ref{fig:ar_cp_annotation}).
+This procedure resulted in a dataset of 2,685,356 DBLP publications with Scopus identifiers where 1,278,322 (47.6\%) were labeled as article and 1,407,034 (52.4\%) as conference proceedings.
 References cited by these publications were then extracted from Scopus (7,129,006), resulting in a total of 8,000,411 nodes (publications and references) and  44,296,381 edges that represent citations within the dataset.
-This dataset is referred to as \emph{comp}.\par
+This dataset is referred to as \emph{comp} (see Fig~\ref{fig:ar_cp_annotation}).
 
@@
 Publications were further annotated with respect to being either articles \emph{(ar)} or conference proceedings \emph{(cp)}.
-For this dataset, the major subject areas of Computer Science; Engineering; and Mathematics contributed the most publications while Pharmacology, Toxicology, and Pharmaceutics; Nursing, Veterinary and Dentistry contributed the least.}
+For this dataset, the major subject areas of Computer Science (2,059,120 (cp), 1,576,691 (ar); Engineering; and Mathematics contributed the most publications while Pharmacology, Toxicology, and Pharmaceutics; Nursing, Veterinary and Dentistry (1 ar) contributed the least.}
 \label{fig:ar_cp_annotation}       % Give a unique label
@@
 The quality of clustering was evaluated by measuring conductance as defined in Shun et al.~\cite{shun_parallel_2016}.
-Data in \emph{comp} were clustered into 18, 20, or 22 clusters and in each case the last cluster (17, 19, 21) had the highest conductance value and the smallest number of nodes suggesting that it effectively served as a container for `left over publications' during the Graclus process.
+Data in \emph{comp} were clustered into 18, 20, or 22 clusters and in each case the highest numbered cluster (17, 19, or 21) had the greatest conductance value and the smallest number of nodes suggesting that it effectively served as a container for `left over publications' during the Graclus process.
 Thus, we did not consider cluster 19 (the 20th cluster) when interpreting our results.
@@
 \paragraph{Clustering by Co-Citation} To build clusters using co-citations, we first implemented variable level clustering, an approach developed by Small and Sweeney (1985)~\cite{small_clustering_1985}, with minor modifications.
-Variable level clustering involves applying a threshold (below which all edges are dissolved) then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn.
+Variable level clustering involves applying a threshold (below which all edges in a graph are dissolved) then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn.
 Three parameters are needed (i) a threshold or starting level based on a quantile of normalized co-citation frequency (ii) a level increment (iii) a maximum cluster size.
@@
 In our implementation of variable level clustering, we first calculated the number of citations accumulated across Scopus for all 2,685,356 articles in \emph{comp}.
-After discarding those publications without any citations, we restricted further analysis to those in the 90th percentile of citations or higher resulting in a dataset of size 212,311.
-We then identified 4,318,305 publications in Scopus that cite the 212,311 previously selected papers from \emph{comp}.
-The cited references in these papers were restricted to those in the set of 212,311 highly cited papers previously identified.
+After discarding those publications without any citations, \textcolor{blue}{Sitaram please confirm}, we restricted further analysis to those in the 90th percentile of citations or higher resulting in a dataset of size 212,311.
+We then identified 4,318,305 publications in Scopus that cite these 212,311 articles from \emph{comp}.
 For each of the 4,318,305 citing publications in turn, all possible reference pairs, ${n \choose 2}$, were generated where $n$ is the number of references in a publication.
-The frequency of these co-cited pairs was then computed across the dataset  and normalized using Salton's cosine formula~\cite{salton_citation_1979}.
+The cited reference pairs were restricted to those in the set of 212,311 highly cited papers previously identified.The frequency of these co-cited pairs was then computed across the dataset  and normalized using Salton's cosine formula~\cite{salton_citation_1979}.
 A total of 46,463,117 unique co-cited pairs were thus obtained.
@@
 
-Agglomerative clustering was then performed on these clusters to generate higher-order clusters.
-Briefly, the edge weight between two clusters was assigned as the maximum edge weight of all edges between these two clusters.
-Edges were arranged in descending order and the first pair of clusters were merged and its edge weight with other interacting clusters was recalculated.
-The edges were then re-ordered as before and the next pair of clusters was merged.
+Agglomerative clustering was then performed on these 10,298 clusters to generate higher-order clusters.
+Briefly, each cluster was now treated as a node and the edge weight between two clusters was assigned as the maximum edge weight of all edges between the nodes in these two clusters.
+Edges were arranged in descending order.
+The first pair of clusters were merged and its edge weight with other interacting clusters was recalculated.
+All edges were then re-ordered as before and the next pair of clusters was merged.
 The process was halted after 600 rounds to prevent single large clusters being generated (figure), and resulted in 665 clusters.
@@
 The largest of these 20 clusters contained 1,276 nodes and the smallest contained 136.
+
+\begin{figure}[ht]
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.5]{merge_select.pdf}
+% figure caption is below the figure
+\caption{caption will be inserted I just haven't been able to overcome the threshold to avoid boring tasks}
+\label{fig:merge_select}       % Give a unique label
+\end{figure}
 
@@
 
-[Need justification for why 20 article level clusters- may be in Waltman's article]
-
 Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation with an argument being made for direct citation as the best approach to concentrate citation links~\cite{klavans_which_2017}.
@@
 A set of 20 clusters was generated using Graclus, a spectral clustering technique that has previously been applied to citation data~\cite{graclus_2007,subelj_clustering_2016}.
-We constructed article level clusters of this computer science dataset at a sufficiently high level of aggregation to avoid cognitive challenge and cross-matched them to disciplinary classification by journal, the Scopus ASJC classification.
-We considered Scopus ASJC minor subject area categories that accounted for at least 10\% of the publications in each cluster and observed 31 of the 334 ASJC minor subject areas, suggesting some selectivity in these results.
+Considering the caveats associated with generating \emph{comp}, namely, the coverage limitations of the DBLP dataset (ii) cross-matching to Scopus (iii) journal based classification (iv) clustering, we constructed article level clusters of this computer science dataset at a sufficiently high level of aggregation to avoid cognitive challenge and cross-matched them to disciplinary classification by journal, the Scopus ASJC classification.
+We only considered Scopus ASJC minor subject area categories that accounted for at least 10\% of the publications in each cluster.
 
 (Fig~\ref{fig:heatmap}) permits examination of these data from two perspectives (i) the clusters that map to a given ASJC minor subject area (ii) ASJC minor subject areas that comprised at least 10\% of the publication in a cluster.
+Under these conditions, 31 of the 334 ASJC minor subject areas are represented.
 Unsurprisingly, the broad category Computer Science Applications was present in 16 of 20 clusters, followed by Software in 12 clusters, and Electrical and Electronic Engineering in 10 clusters.
@@
 From the other perspective, cluster 17 was the most diverse and contained publications annotated with 8 minor subject area labels, of which Biochemistry, Chemistry(all), Genetics, and Molecular Biology were the most distant from computer science while Statistics \& Probability, Computational Theory \& Mathematics, and Computational Mathematics are closer.
-It is important to be reminded of the caveats associated with (i) the limitations of the DBLP dataset (ii) the limitations of cross-matching to Scopus (iii) the limitations of journal based classification (iv) the limitations of clustering by direct citation.
-Even so, a picture that emerges is that areas central to computer science in 2019 are more likely to be found in multiple clusters (hardware, software, and theory) and that biology, chemistry, and statistics are proximal.
-These results strongly suggest that the actual structure of communication within the broad field of computer science may be at variance with journal-based classification, also noted by Waltman and van Eck, ``...an indication that traditional disciplines such as those just mentioned only partly reflect the actual organization of today's scientific research."~\cite{waltman_new_2012}.
+These data suggest that areas central to computer science in 2019 (Salton and Bergmark's triad) are more likely to be found in multiple clusters (hardware, software, and theory), and that biology, chemistry, and statistics are the most highly represented fields proximal to computer science.
+These results also suggest that the actual structure of communication is at variance with journal-based classification, also noted by Waltman and van Eck, ``...an indication that traditional disciplines such as those just mentioned only partly reflect the actual organization of today's scientific research."~\cite{waltman_new_2012}.
 The aphorism of Porter, Cohen, Roessner, and Perreault (2007), `The discrepancies between disciplinary roots and research realities loom large'~\cite{porter_measuring_2007} also invokes itself.
-A second inference is that a correlation appears between broad journal-based classification and article clusters in terms of subject matter.
-Thirdly, that some areas of computer science are relatively ubiquitous.
-Fourth that interactions with fields outside computer science are restricted to a single cluster or small numbers of clusters.
+A second inference is that a correlation appears between some cases of journal-based classification and article clusters in terms of subject matter.
+Thirdly, that some areas of computer science are relatively ubiquitous, e.g.
+computer applications.
+Last, that interactions with fields outside computer science are restricted to a single cluster or small numbers of clusters, e.g., cluster 17 (ibid) and cluster 18 (artificial intelligence, cognitive neuroscience, and neurology).
 
@@
 % For example, with the graphicx package use
-  \includegraphics[scale=0.3]{cocitr2_venn.pdf}
+  \includegraphics[scale=0.3]{cocit_venn2.pdf}
 % figure caption is below the figure

### 2019-12-05 Scientometrics/comp.tex
update

@@
 
-\title{Citation Analysis of Computer Science Publications%\thanks{Grants or other notes
+\title{Citation Analysis of Computer Science Publications}
+%\thanks{Grants or other notes
 %about the article that should go on the front page should be
 %placed here. General acknowledgments should be placed at the end of the article.}
-}
+
 \subtitle{Relationship To Other Fields}
@@
 
-As far back as 1979, Salton and Bergmark conducted a historical study of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles) in which they made the point that the scientific literature serves a rich source of information to study the structure and historical development of a field~\cite{salton_citation_1979}.
+Noting that that the scientific literature serves a rich source of information to study the structure and historical development of a field, Salton and Bergmark conducted a historical study  of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles)~\cite{salton_citation_1979}.
 These authors described the global structure of computer science as comprising three main subareas (i) theoretical foundations, such as theory of computation, (ii) hardware and computer systems, such as architecture,  and (iii) software, such as programming systems.
@@
 Progressing beyond Salton and Bergmark's historical triad of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS)~\cite{acm_ref} published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field.
-This classification does address relationships with other fields under Applied Computing.
+This classification also addresses relationships with other fields under the category of Applied Computing.
 However, an easy way to map scientific publications, especially interdisciplinary articles or those from adjacent fields, to the CCS classification does not exist.
@@
 
-We applied variable clustering with initial parameters of threshold ($t$) = median normalized co-citation frequency (quantile=0.5), increment $i = 0.1$, and maximum cluster size, $mcs = 200$.
+We applied variable clustering with initial parameters of threshold ($t$) = median normalized co-citation frequency (quantile=0.5), increment $i = 0.1$, and maximum cluster size, $mcs=200$.
 Thus, at start, all edges below the median normalized co-citation frequency are dissolved.
@@
 All edges were then re-ordered as before and the next pair of clusters was merged.
-The process was halted after 600 rounds to prevent single large clusters being generated (figure), and resulted in 665 clusters.
-The top 20 clusters were used for further analysis and comparison with clusters generated by direct citation.
-The largest of these 20 clusters contained 1,276 nodes and the smallest contained 136.
+The process was halted after 600 rounds to prevent single large clusters being generated (figure).
 
@@
 
-Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation with an argument being made for direct citation as the best approach to concentrate citation links~\cite{klavans_which_2017}.
+\emph{Clustering by Direct Citation.} Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation with an argument being made for direct citation as the best approach to concentrate citation links~\cite{klavans_which_2017}.
 Accordingly, we first used direct citation links as the basis for cluster formation.
@@
 From the other perspective, cluster 17 was the most diverse and contained publications annotated with 8 minor subject area labels, of which Biochemistry, Chemistry(all), Genetics, and Molecular Biology were the most distant from computer science while Statistics \& Probability, Computational Theory \& Mathematics, and Computational Mathematics are closer.
-These data suggest that areas central to computer science in 2019 (Salton and Bergmark's triad) are more likely to be found in multiple clusters (hardware, software, and theory), and that biology, chemistry, and statistics are the most highly represented fields proximal to computer science.
-These results also suggest that the actual structure of communication is at variance with journal-based classification, also noted by Waltman and van Eck, ``...an indication that traditional disciplines such as those just mentioned only partly reflect the actual organization of today's scientific research."~\cite{waltman_new_2012}.
-The aphorism of Porter, Cohen, Roessner, and Perreault (2007), `The discrepancies between disciplinary roots and research realities loom large'~\cite{porter_measuring_2007} also invokes itself.
-A second inference is that a correlation appears between some cases of journal-based classification and article clusters in terms of subject matter.
+These data suggest that areas central to computer science in 2019 (Salton and Bergmark's triad) are more likely to be found in multiple clusters (hardware, software, and theory), and that biology, chemistry, and statistics are the most proximal to computer science.
+[What about mathematics?]  A second inference is that, in a few cases journal-based classification and article clusters are tightly related in terms of article content (Hardware and Architecture).
 Thirdly, that some areas of computer science are relatively ubiquitous, e.g.
@@
 
-Co-citation, the frequency with which a pair of articles is cited by other articles, was first described independently by Small and Marshakova in 1973~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973} provides insight into the emergence of new ideas derived from the association of previously independent ones.
-Co-citation, thus provides some degree of evolutionary insight across disciplines and sub-disciplines and has been used for clustering publications~\cite{boyack_co-citation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
-To provide an alternate view of these DBLP data we also constructed clusters using co-citation as below and as described in Methods.
+\emph{Clustering by Co-citation.} Co-citation, the frequency with which a pair of articles is cited by other articles, was first described independently by Small and Marshakova in 1973~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973} provides insight into the emergence of new ideas derived from the association of previously independent ones.
+Co-citation, thus provides some degree of evolutionary insight across disciplines and sub-disciplines and has been used for clustering publications~\cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
+For an alternate view of these DBLP data we constructed clusters using co-citation by first applying variable level clustering to the 2,685,356 articles in \emph{comp} and then performing top-down agglomerative clustering on the resultant 10,298 (of 22,232 clusters) containing greater than two nodes per cluster.
+(Methods).
+We performed 600 iterations to the 10,298 clusters further limited to clusters containing at least 10 nodes, which resulted in 666 clusters.
+Further agglomeration resulted in the development of a single large cluster (Fig~\ref{fig:merge_select}).
+The 20 largest clusters were used for further analysis and comparison with clusters generated by direct citation.
+The largest of these 20 clusters contained 1,276 nodes and the smallest contained 136.
 
@@
 % For example, with the graphicx package use
-  \includegraphics[scale=0.3]{cocit_venn2.pdf}
+ \includegraphics[scale=0.5]{cocit_venn2.pdf}
 % figure caption is below the figure
-\caption{Summary of DBLP data cross-matched with Scopus.
-2,685,356 publications from DBLP were cross-matched with Scopus and then grouped by the 27 major subject areas in the ASJC (Scopus) classification.
-The largest number of publications are contributed by Computer Science; Mathematics; and Engineering and then by Social Sciences; Physics and Astronomy; and Biochemistry, Genetics, and Molecular Biology.
-Publications were further annotated with respect to being either articles \emph{(ar)} or conference proceedings \emph{(cp)}.
-For this dataset, the major subject areas of Computer Science; Engineering; and Mathematics contributed the most publications while Pharmacology, Toxicology, and Pharmaceutics; Nursing, Veterinary and Dentistry contributed the least.}
+\caption{High Level Disciplinary Composition of Publications in Clusters Generate by Variable Level Clustering. 84,591 nodes from were matched to the 4 subject areas, 
+27 major subject areas, and 334 minor subject areas in the Scopus ASJC classification. Since 82.5\% of these nodes were assigned more to than one minor subject category, 
+we assigned fractional counts for the four subject areas that summed to 1 for each article. The figure shows a four way Venn Diagram~\cite{chen_venn_2011} illustrating the 
+relative frequencies of publications from the Physical Sciences, Social Sciences, Life Sciences, and Health Sciences.}
 \label{fig:cocitr_venn2}       % Give a unique label

### 2019-12-06 Scientometrics/comp.tex
fixed minor punctuation

@@
 Publications were parsed from the xml source file and loaded into a PostgreSQL database.
-We have previously parsed, the Scopus dataset of over 72,000,000 publications into a custom schema as part of a larger data platform for research evaluation~\cite{GithubERNIE2019}.
-Records in the DBLP dataset, were matched to Scopus identifiers using digital object identifiers (DOIs).
+We have previously parsed the Scopus dataset of over 72,000,000 publications into a custom schema as part of a larger data platform for research evaluation~\cite{GithubERNIE2019}.
+Records in the DBLP dataset were matched to Scopus identifiers using digital object identifiers (DOIs).
 This procedure resulted in a dataset of 2,685,356 DBLP publications with Scopus identifiers where 1,278,322 (47.6\%) were labeled as article and 1,407,034 (52.4\%) as conference proceedings.
@@
 The quality of clustering was evaluated by measuring conductance as defined in Shun et al.~\cite{shun_parallel_2016}.
-Data in \emph{comp} were clustered into 18, 20, or 22 clusters and in each case the highest numbered cluster (17, 19, or 21) had the greatest conductance value and the smallest number of nodes suggesting that it effectively served as a container for `left over publications' during the Graclus process.
+%George, Tandy - add text about why conductance is good, and that small values are better
+Data in \emph{comp} were clustered into 18, 20, or 22 clusters and in each case the highest numbered cluster (17, 19, or 21) had the greatest conductance value and the smallest number of nodes, suggesting that it effectively served as a container for `left over publications' during the Graclus process.
 Thus, we did not consider cluster 19 (the 20th cluster) when interpreting our results.
@@
 \paragraph{Clustering by Co-Citation} To build clusters using co-citations, we first implemented variable level clustering, an approach developed by Small and Sweeney (1985)~\cite{small_clustering_1985}, with minor modifications.
-Variable level clustering involves applying a threshold (below which all edges in a graph are dissolved) then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn.
-Three parameters are needed (i) a threshold or starting level based on a quantile of normalized co-citation frequency (ii) a level increment (iii) a maximum cluster size.
+Variable level clustering involves applying a threshold (below which all edges in a graph are deleted) then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn.
+Three parameters are needed: (i) a threshold or starting level based on a quantile of normalized co-citation frequency, (ii) a level increment, and (iii) a maximum cluster size.
 An issue is the generation of very large clusters by chaining through low edge weights.
-Thus, at each iteration, any cluster exceeding the maximum cluster size returned to the process and a higher threshold applied to break such clusters.
+Thus, at each iteration, any cluster exceeding the maximum cluster size  is returned to the process and a higher threshold is applied to break such clusters.
 
 In our implementation of variable level clustering, we first calculated the number of citations accumulated across Scopus for all 2,685,356 articles in \emph{comp}.
-After discarding those publications without any citations, \textcolor{blue}{Sitaram please confirm}, we restricted further analysis to those in the 90th percentile of citations or higher resulting in a dataset of size 212,311.
+After discarding those publications without any citations, \textcolor{blue}{Sitaram please confirm}, we restricted further analysis to those in the 90th percentile of citations or higher, resulting in a dataset of size 212,311.
 We then identified 4,318,305 publications in Scopus that cite these 212,311 articles from \emph{comp}.
-For each of the 4,318,305 citing publications in turn, all possible reference pairs, ${n \choose 2}$, were generated where $n$ is the number of references in a publication.
-The cited reference pairs were restricted to those in the set of 212,311 highly cited papers previously identified.The frequency of these co-cited pairs was then computed across the dataset  and normalized using Salton's cosine formula~\cite{salton_citation_1979}.
+For each of the 4,318,305 citing publications in turn, all possible ${n \choose 2}$ reference pairs were generated, where $n$ is the number of references in a publication.
+The cited reference pairs were restricted to those in the set of 212,311 highly cited papers previously identified.
+The frequency of these co-cited pairs was then computed across the dataset  and normalized using Salton's cosine formula~\cite{salton_citation_1979}.
 A total of 46,463,117 unique co-cited pairs were thus obtained.
@@
 We applied variable clustering with initial parameters of threshold ($t$) = median normalized co-citation frequency (quantile=0.5), increment $i = 0.1$, and maximum cluster size, $mcs=200$.
-Thus, at start, all edges below the median normalized co-citation frequency are dissolved.
+Thus, at start, all edges below the median normalized co-citation frequency were deleted.
 Clusters were formed by assembling connected components from each co-cited pair beginning with the heaviest edge weight.
@@
 Agglomerative clustering was then performed on these 10,298 clusters to generate higher-order clusters.
-Briefly, each cluster was now treated as a node and the edge weight between two clusters was assigned as the maximum edge weight of all edges between the nodes in these two clusters.
+Briefly, each cluster was now treated as a node and the edge weight between two clusters was assigned to the maximum edge weight of all edges between the nodes in these two clusters.
 Edges were arranged in descending order.

### 2019-12-06 Scientometrics/comp.tex
cited the Borner paper for why we use conductance, and otherwise just minor edits in the first 6 pages

@@
 Consequently, we generated 20 clusters, labeled 0-19, using Graclus (Fig~\ref{fig:heatmap}).
-The quality of clustering was evaluated by measuring conductance as defined in Shun et al.~\cite{shun_parallel_2016}.
+We used conductance, as defined in Shun et al.~\cite{shun_parallel_2016}, to  evaluate clustering (smaller is better), noting that
+conductance has been found to be ``the stand-alone quality metric that best indicates performance on the information recovery metrics" \cite{emmons2016analysis}.
+% The quality of clustering was evaluated by measuring conductance as defined in Shun et al.~\cite{shun_parallel_2016}. 
 %George, Tandy - add text about why conductance is good, and that small values are better
-Data in \emph{comp} were clustered into 18, 20, or 22 clusters and in each case the highest numbered cluster (17, 19, or 21) had the greatest conductance value and the smallest number of nodes, suggesting that it effectively served as a container for `left over publications' during the Graclus process.
+The data in \emph{comp} were clustered into 18, 20, or 22 clusters and in each case the highest numbered cluster (17, 19, or 21) had the greatest conductance value and the smallest number of nodes, suggesting that it effectively served as a container for `left over publications' during the Graclus process.
 Thus, we did not consider cluster 19 (the 20th cluster) when interpreting our results.
@@
 A final threshold of $t$=0.999 was applied to break the single remaining large cluster.
-All clusters generated thus, contained  less than 100 nodes.
-Using this approach, 22,232 clusters containing 84,591 nodes were generated.
+% All generated clusters  using this process contained  less than 100 nodes.
+Using this approach, 22,232 clusters containing 84,591 nodes were generated, each containing less than 100 nodes.
 Clusters containing only 2 nodes were then discarded bringing the total number of clusters down to 10,298.

### 2019-12-06 Scientometrics/comp.tex
modified results and methods

@@
            Tandy Warnow \at
-              Dept of Computer Science, University of Iliinois Urbana-Champaign, Champaign IL \\
+              Dept of Computer Science, University of Illinois Urbana-Champaign, Champaign IL \\
               \email{warnow@illinois.edu}
@@
 
-\paragraph{Clustering by Co-Citation} To build clusters using co-citations, we first implemented variable level clustering, an approach developed by Small and Sweeney (1985)~\cite{small_clustering_1985}, with minor modifications.
+\paragraph{Clustering by Co-Citation} 
+Co-citation, the frequency with which a pair of articles is cited by other articles,  first described independently by Small and Marshakova in 1973~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973},
+provides insight into the emergence of new ideas derived from the association of previously independent ones. 
+Co-citation, thus provides some degree of evolutionary insight across disciplines and sub-disciplines and has been used for clustering publications~\cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
+For an alternate view of these DBLP data we constructed clusters using co-citation, using a modification of   variable level clustering to the 2,685,356 articles in \emph{comp} and then performing top-down agglomerative clustering on the resultant 10,298 (of 22,232 clusters) containing greater than two nodes per cluster.
+(Methods).
+
+We used variable level clustering, an approach developed in 1985 by Small and Sweeney~\cite{small_clustering_1985}, with minor modifications as follows.
 Variable level clustering involves applying a threshold (below which all edges in a graph are deleted) then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn.
@@
 All edges were then re-ordered as before and the next pair of clusters was merged.
-The process was halted after 600 rounds to prevent single large clusters being generated (figure).
+The process was halted after 600 rounds to prevent single large clusters being generated (Fig.~\ref{fig:merge_select}).
 
@@
 % figure caption is below the figure
-\caption{caption will be inserted I just haven't been able to overcome the threshold to avoid boring tasks}
+\caption{Clustering produced using co-citation. }
 \label{fig:merge_select}       % Give a unique label
@@
 % figure caption is below the figure
-\caption{caption will be inserted I just haven't been able to overcome the threshold to avoid boring tasks}
+\caption{Clustering obtained by direct citation.}
 \label{fig:heatmap}       % Give a unique label
@@
 
-\emph{Clustering by Direct Citation.} Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation with an argument being made for direct citation as the best approach to concentrate citation links~\cite{klavans_which_2017}.
+\subsection{Clustering by Direct Citation} 
+Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation with an argument being made for direct citation as the best approach to concentrate citation links~\cite{klavans_which_2017}.
 Accordingly, we first used direct citation links as the basis for cluster formation.
 A set of 20 clusters was generated using Graclus, a spectral clustering technique that has previously been applied to citation data~\cite{graclus_2007,subelj_clustering_2016}.
-Considering the caveats associated with generating \emph{comp}, namely, the coverage limitations of the DBLP dataset (ii) cross-matching to Scopus (iii) journal based classification (iv) clustering, we constructed article level clusters of this computer science dataset at a sufficiently high level of aggregation to avoid cognitive challenge and cross-matched them to disciplinary classification by journal, the Scopus ASJC classification.
+\textcolor{blue}{
+Considering the caveats associated with generating \emph{comp}, namely, the coverage limitations of the DBLP dataset (ii) cross-matching to Scopus (iii) journal based classification (iv) clustering, }
+we constructed article level clusters of this computer science dataset at a sufficiently high level of aggregation to avoid cognitive challenge and cross-matched them to disciplinary classification by journal, the Scopus ASJC classification.
 We only considered Scopus ASJC minor subject area categories that accounted for at least 10\% of the publications in each cluster.
 
-(Fig~\ref{fig:heatmap}) permits examination of these data from two perspectives (i) the clusters that map to a given ASJC minor subject area (ii) ASJC minor subject areas that comprised at least 10\% of the publication in a cluster.
+Figure~\ref{fig:heatmap} permits examination of these data from two perspectives: (i) the clusters that map to a given ASJC minor subject area and (ii) ASJC minor subject areas that comprised at least 10\% of the publication in a cluster.
 Under these conditions, 31 of the 334 ASJC minor subject areas are represented.
@@
 
-\emph{Clustering by Co-citation.} Co-citation, the frequency with which a pair of articles is cited by other articles, was first described independently by Small and Marshakova in 1973~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973} provides insight into the emergence of new ideas derived from the association of previously independent ones.
-Co-citation, thus provides some degree of evolutionary insight across disciplines and sub-disciplines and has been used for clustering publications~\cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
-For an alternate view of these DBLP data we constructed clusters using co-citation by first applying variable level clustering to the 2,685,356 articles in \emph{comp} and then performing top-down agglomerative clustering on the resultant 10,298 (of 22,232 clusters) containing greater than two nodes per cluster.
-(Methods).
-We performed 600 iterations to the 10,298 clusters further limited to clusters containing at least 10 nodes, which resulted in 666 clusters.
+\subsection{Clustering by Co-citation.}
+
+As described in Methods, we performed 600 iterations to the 10,298 clusters further limited to clusters containing at least 10 nodes, which resulted in 666 clusters.
 Further agglomeration resulted in the development of a single large cluster (Fig~\ref{fig:merge_select}).
-The 20 largest clusters were used for further analysis and comparison with clusters generated by direct citation.
-The largest of these 20 clusters contained 1,276 nodes and the smallest contained 136.
+The 20 largest clusters were used for further analysis and comparison with clusters generated by direct citation. The largest of these 20 clusters contained 1,276 nodes and the smallest contained 136.
+
+\section{Discussion}
+\textcolor{blue}{
+Results obtained using the two different clustering methods produced different but complementary views of the computer
+science literature.
+Discuss: very low conductance values, and the significance of this. 
+Need for additional work. 
+Perhaps value in looking at change over time.
+Emerging interactions of computer science and other disciplines, 
+so papers are related by the communities they impact (co-citation clustering).
+ }
 
@@
 
+\section{Garbage}
+
+Cite Alan Porter on expanding universe versus myopic focus.
+Cite Traag, Waltman, Lariviere papers.
+Peter Sjögårde and Per Ahlgren, Loet Leydesdorff, Caroline S.
+Wagner and Lutz Bornmann, Discontinuities in citation relations among journals: self-organized criticality as a model of scientific revolutions and change, Scientometrics, 10.1007/s11192-018-2734-6, 116, 1, (623-644), (2018).
+Antonio Perianes-Rodriguez and Javier Ruiz-Castillo, A comparison of the Web of Science and publication-level classification systems of science, Journal of Informetrics, 10.1016/j.joi.2016.10.007, 11, 1, (32-45), (2017).
+Qi Wang and Ludo Waltman, Large-scale analysis of the accuracy of the journal classification systems of Web of Science and Scopus, Journal of Informetrics, 10.1016/j.joi.2016.02.003, 10, 2, (347-364), (2016).
+Henry Small, Kevin W.
+Boyack and Richard Klavans, Identifying emerging topics in science and technology,
+Crossref
+
+\paragraph{Overall strategy}
+
+Here we describe the overall strategy used for the two clustering methods.\\
+
+\emph{misc stuff:  In using the term inform, we are mindful of (i) Greenhalgh (ii) Sarewitz and Pielke.
+I think that I want to cite these two without really knowing how.
+Greenhalgh for the limitations of positivism.
+Sarewitz for the limitations of allowing science to do whatever it wants to.
+I'd also like to see some text about (i) limited funding resources (ii) efficient use of existing resources (iiii) informing policy at multiple levels -- all directed at justifying our study.
+I'm not sure where to put it though.
+CS can also be an excellent model system for studying interdisciplinarity cite Porter and colleagues in a study on measuring interdisciplinarity~\cite{porter_measuring_2007} observe that 'The discrepancies between disciplinary roots and research realities loom large', a reference to the challenges associated with knowledge diffusing across researchers who tend to be focused in their own areas.
+This concern may be especially relevant for computer science given the ubiquity of computing today and limited public funding for research.
+Maybe squeeze in Tandy's NAS report on interdisciplinarity.
+I should ping Ohid Yaqub about this too- science policy is his area.}
+
+\noindent
+ Spectral clustering:
+\begin{enumerate}
+\item Subset Scopus by COMP
+\item Match COMP to DBLP at high stringency -> reduced number of scps
+ \item Harvest cited references  from Scopus
+ \item Cluster articles by direct citation using Graclus to a number that meets simple optimality criteria and does not impose cognitive challenges
+ \item Reconcile cluster contents to journal classification for the purpose of referencing
+ \item Infer inter-cluster relationships using direct citations, co-citations, and bibliographic coupling
+\end{enumerate}
+
+\end{document}
+% end of file template.tex
+
 \subsection{Subsection title}
@@
 % For tables use
-
-\section{Garbage}
-
-Cite Alan Porter on expanding universe versus myopic focus.
-Cite Traag, Waltman, Lariviere papers.
-Peter Sjögårde and Per Ahlgren, Loet Leydesdorff, Caroline S.
-Wagner and Lutz Bornmann, Discontinuities in citation relations among journals: self-organized criticality as a model of scientific revolutions and change, Scientometrics, 10.1007/s11192-018-2734-6, 116, 1, (623-644), (2018).
-Antonio Perianes-Rodriguez and Javier Ruiz-Castillo, A comparison of the Web of Science and publication-level classification systems of science, Journal of Informetrics, 10.1016/j.joi.2016.10.007, 11, 1, (32-45), (2017).
-Qi Wang and Ludo Waltman, Large-scale analysis of the accuracy of the journal classification systems of Web of Science and Scopus, Journal of Informetrics, 10.1016/j.joi.2016.02.003, 10, 2, (347-364), (2016).
-Henry Small, Kevin W.
-Boyack and Richard Klavans, Identifying emerging topics in science and technology,
-Crossref
-
-\textcolor{blue}{George, the rest needs to go into methods}
-
-\paragraph{Overall strategy}
-
-Here we describe the overall strategy used for the two clustering methods.\\
-
-\emph{misc stuff:  In using the term inform, we are mindful of (i) Greenhalgh (ii) Sarewitz and Pielke.
-I think that I want to cite these two without really knowing how.
-Greenhalgh for the limitations of positivism.
-Sarewitz for the limitations of allowing science to do whatever it wants to.
-I'd also like to see some text about (i) limited funding resources (ii) efficient use of existing resources (iiii) informing policy at multiple levels -- all directed at justifying our study.
-I'm not sure where to put it though.
-CS can also be an excellent model system for studying interdisciplinarity cite Porter and colleagues in a study on measuring interdisciplinarity~\cite{porter_measuring_2007} observe that 'The discrepancies between disciplinary roots and research realities loom large', a reference to the challenges associated with knowledge diffusing across researchers who tend to be focused in their own areas.
-This concern may be especially relevant for computer science given the ubiquity of computing today and limited public funding for research.
-Maybe squeeze in Tandy's NAS report on interdisciplinarity.
-I should ping Ohid Yaqub about this too- science policy is his area.}
-
-\noindent
- Spectral clustering:
-\begin{enumerate}
-\item Subset Scopus by COMP
-\item Match COMP to DBLP at high stringency -> reduced number of scps
- \item Harvest cited references  from Scopus
- \item Cluster articles by direct citation using Graclus to a number that meets simple optimality criteria and does not impose cognitive challenges
- \item Reconcile cluster contents to journal classification for the purpose of referencing
- \item Infer inter-cluster relationships using direct citations, co-citations, and bibliographic coupling
-\end{enumerate}
-
-\end{document}
-% end of file template.tex

### 2019-12-06 Scientometrics/comp.tex
minor edits to figure captions

@@
 % For example, with the graphicx package use
-  \includegraphics[scale=0.3]{graclus_comparison.pdf}
+  \includegraphics[scale=0.5]{graclus_comparison.pdf}
 % figure caption is below the figure
@@
 % table caption is above the table
-\caption{\emph{2685021 is because of inner joins on ASJC Explain conductance calculations~\cite{shun_parallel_2016}}}
+\caption{\emph{Statistics regarding the 20 clusters produced using direct citation.
+2685021 is because of inner joins on ASJC Explain conductance calculations~\cite{shun_parallel_2016}}}
 \label{tab:1}       % Give a unique label
 % For LaTeX tables use
-\begin{tabular}{lllll}
+\begin{tabular}{lrccc}
 \hline\noalign{\smallskip}
@@
 provides insight into the emergence of new ideas derived from the association of previously independent ones. 
-Co-citation, thus provides some degree of evolutionary insight across disciplines and sub-disciplines and has been used for clustering publications~\cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
+Co-citation thus provides some degree of evolutionary insight across disciplines and sub-disciplines and has been used for clustering publications~\cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
 For an alternate view of these DBLP data we constructed clusters using co-citation, using a modification of   variable level clustering to the 2,685,356 articles in \emph{comp} and then performing top-down agglomerative clustering on the resultant 10,298 (of 22,232 clusters) containing greater than two nodes per cluster.
-(Methods).
 
@@
 % figure caption is below the figure
-\caption{Clustering produced using co-citation. }
+\caption{Clustering produced using co-citation data; the y-axis is the cluster size (given logarithmically), and the x-axis is the number of iterations of the agglomerative clustering technique.
+Note that iterating more than 600 times produces a very large cluster.
+}
 \label{fig:merge_select}       % Give a unique label
@@
 % For example, with the graphicx package use
-  \includegraphics[scale=0.5]{scopus_dblp_graclus3.pdf}
+  \includegraphics[scale=0.45]{scopus_dblp_graclus3.pdf}
 % figure caption is below the figure
-\caption{Clustering obtained by direct citation.}
+\caption{Heat map for the clustering obtained by direct citation. The  y-axis (rows) correspond to topics, defined by Scopus characterizations, and the
+x-axis (columns) represent the 20 different clusters.  
+Each cluster is characterized by topics that label at least 10\% of the publications in the cluster.
+ }
 \label{fig:heatmap}       % Give a unique label
@@
 % figure caption is below the figure
-\caption{Schematic representation of variable clustering protocol modified from Small and Sweeney (1985).
-Three parameters are specified (i) a threshold or starting level based on a quantile of normalized co-citation frequency (ii) a level increment (iii) a maximum cluster size.
+\caption{Schematic representation of variable clustering protocol modified from Small and Sweeney (1985) \cite{small_clustering_1985}.
+Three parameters are specified: (i) a threshold or starting level based on a quantile of normalized co-citation frequency, (ii) a level increment, and  (iii) a maximum cluster size.
 Input data is a set of co-cited publications with edge-weight defined by normalized co-citation frequencies.
@@
 % figure caption is below the figure
-\caption{High Level Disciplinary Composition of Publications in Clusters Generate by Variable Level Clustering. 84,591 nodes from were matched to the 4 subject areas, 
+\caption{High-level disciplinary composition of publications in $\sim$2,000 clusters generated by variable-level clustering  of co-citation data.
+%Variable Level Clustering. 
+84,591 nodes from were matched to the 4 subject areas, 
 27 major subject areas, and 334 minor subject areas in the Scopus ASJC classification. Since 82.5\% of these nodes were assigned more to than one minor subject category, 

### 2019-12-06 Scientometrics/comp.tex
updated ar_cp figure

@@
 Publications were further annotated with respect to being either articles \emph{(ar)} or conference proceedings \emph{(cp)}.
-For this dataset, the major subject areas of Computer Science (2,059,120 (cp), 1,576,691 (ar); Engineering; and Mathematics contributed the most publications while Pharmacology, Toxicology, and Pharmaceutics; Nursing, Veterinary and Dentistry (1 ar) contributed the least.}
+For this dataset, the major subject area of Computer Science (1,194,623(cp), 879,396 (ar) contributed the most publications while Nursing (69 cp,  756 ar) contributed the least.}
 \label{fig:ar_cp_annotation}       % Give a unique label

### 2019-12-06 Scientometrics/comp.tex
updated ar_cp figure

@@
 \begin{figure}[ht]
-\centering
 % Use the relevant command to insert your figure file.
 % For example, with the graphicx package use
-  \includegraphics[scale=0.5]{ar_cp_ratio.pdf}
+  \includegraphics[scale=0.6]{ar_cp_ratio.pdf}
 % figure caption is below the figure
@@
 Publications were further annotated with respect to being either articles \emph{(ar)} or conference proceedings \emph{(cp)}.
-For this dataset, the major subject area of Computer Science (1,194,623(cp), 879,396 (ar) contributed the most publications while Nursing (69 cp,  756 ar) contributed the least.}
+For this dataset, the major subject area of Computer Science with 1,194,623(cp) \& 879,396 contributed the most publications while Nursing with 69 (cp) \& 756 (ar)) contributed the least.}
 \label{fig:ar_cp_annotation}       % Give a unique label

### 2019-12-08 Scientometrics/comp.tex
Minor language / punctuation edits

@@
 
-Other classification systems are available such as the All Science Journal Classification (ASJC) developed and maintained by Scopus.
-the Web of Science research and categorical classifications from Clarivate Analytics, and the NSF classification system~\cite{nsf_classification}.
-Of these, Scopus and the Web of Science also include global bibliographies with citation links and proprietary unique identifiers for publications that can be matched, in some cases, to digital object identifiers (DOIs).
+Other classification systems are available such as the All Science Journal Classification (ASJC) developed and maintained by Scopus, the Web of Science research and categorical classifications from Clarivate Analytics, and the NSF classification system~\cite{nsf_classification}.
+Of these, Scopus and the Web of Science also include global bibliographies with citation links and proprietary unique identifiers for publications, some of which can be matched to digital object identifiers (DOIs).
 All three rely on applying one or more journal-derived labels to articles.
@@
  A stable release of the DBLP computer science bibliography~\cite{dblp_ref} consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz.
-Publications were parsed from the xml source file and loaded into a PostgreSQL database.
-We have previously parsed the Scopus dataset of over 72,000,000 publications into a custom schema as part of a larger data platform for research evaluation~\cite{GithubERNIE2019}.
+Publications were parsed from the XML source file and loaded into a PostgreSQL database.
+We have previously parsed the Scopus dataset of over 72,000,000 publications into a custom schema as part of implementing a larger data platform for research evaluation~\cite{GithubERNIE2019}.
 Records in the DBLP dataset were matched to Scopus identifiers using digital object identifiers (DOIs).
 This procedure resulted in a dataset of 2,685,356 DBLP publications with Scopus identifiers where 1,278,322 (47.6\%) were labeled as article and 1,407,034 (52.4\%) as conference proceedings.
-References cited by these publications were then extracted from Scopus (7,129,006), resulting in a total of 8,000,411 nodes (publications and references) and  44,296,381 edges that represent citations within the dataset.
+References cited by these publications were then extracted from Scopus (7,129,006 records), resulting in a total of 8,000,411 nodes (publications and references) and 44,296,381 edges that represent citations within the dataset.
 This dataset is referred to as \emph{comp} (see Fig~\ref{fig:ar_cp_annotation}).
@@
 
-\paragraph{Clustering by Direct Citation} Graclus is a spectral graph clustering package that computes normalized cut and ratio association for a given undirected graph~\cite{graclus_2007}.
+\paragraph{Clustering by Direct Citation.} Graclus is a spectral graph clustering package that computes normalized cut and ratio association for a given undirected graph~\cite{graclus_2007}.
 We used v1.2 in our experiments.
@@
 
-\paragraph{Clustering by Co-Citation} 
+\paragraph{Clustering by Co-Citation.}
 Co-citation, the frequency with which a pair of articles is cited by other articles,  first described independently by Small and Marshakova in 1973~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973},
@@
 Edges were arranged in descending order.
-The first pair of clusters were merged and its edge weight with other interacting clusters was recalculated.
+The first pair of clusters was merged and its edge weight with other interacting clusters was recalculated.
 All edges were then re-ordered as before and the next pair of clusters was merged.

### 2019-12-10 Scientometrics/comp.tex
added Perianes-Rodriguez

@@
 Computer science as a field has experienced dramatic growth and diversification over the last twenty years.
-Towards an improved understanding of the structure of the field, we analyze a cohort of the computer science literature.
-For insight on the features of this cohort and the flow of information within its components, we construct article level clusters whose elements are linked by citations or co-citations, and reconcile them with major and minor subject categories in the All Science Journal Classification (Scopus).
-[abstract is feeble and needs to be rewritten]
+Towards an current understanding of the structure of the field, we analyze a cohort of the computer science literature.
+For insight on the features of this cohort and the flow of information within its components, we construct article level clusters based on either direct citations or co-citations, and reconcile them with major and minor subject categories in the All Science Journal Classification (Scopus).
+[abstract is feeble and needs to be rewritten].
 
@@
 Computer science, and its applications, has experienced rapid growth and diversification over the last twenty years.
+As observed in a 2017 US National Academies Report, ``A wide range of jobs in virtually all sectors demand computing skills to an unprecedented extent.
+And every academic discipline finds itself incorporating computing into its research and educational mission"~\cite{nas_2017}.
 More recently, the collective influence of the Internet of Things (IoT), `big' data, accessible cloud computing, and advances in artificial intelligence have been postulated as a recent driver for growth and evolution~\cite{siebel2019_digital}.
-As noted in a 2017 US National Academies Report~\cite{nas_2017}, ``A wide range of jobs in virtually all sectors demand computing skills to an unprecedented extent.
-And every academic discipline finds itself incorporating computing into its research and educational mission".
-Given this powerful influence some understanding of the present state and structure of computer science and its relationship to other fields would inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy.
+Given this powerful influence some understanding of the present state and structure of computer science and its relationship to other fields could inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy.
 For the same reason of broad influence, computer science can also serve as a model system for studying interdisciplinarity.
@@
 Noting that that the scientific literature serves a rich source of information to study the structure and historical development of a field, Salton and Bergmark conducted a historical study  of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles)~\cite{salton_citation_1979}.
-These authors described the global structure of computer science as comprising three main subareas (i) theoretical foundations, such as theory of computation, (ii) hardware and computer systems, such as architecture,  and (iii) software, such as programming systems.
+These authors described the global structure of computer science as comprising three main areas (i) theoretical foundations, such as theory of computation, (ii) hardware and computer systems, such as architecture,  and (iii) software, such as programming systems.
 Related areas noted were (a) mathematics of computing, such as numerical analysis, (b) special software topics, such as operating systems, (c) data management and database systems, (d) methodologies valid for multiple applications, such as algebraic manipulation, (e) computer applications, such as computer graphics, (f) non-technical aspects, such as computer education.
 
-Computing has grown and evolved significantly since 1974.
-Progressing beyond Salton and Bergmark's historical triad of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS)~\cite{acm_ref} published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field.
+Progressing beyond 1974-79, and Salton and Bergmark's historical triad of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS)~\cite{acm_ref} published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field.
 This classification also addresses relationships with other fields under the category of Applied Computing.
-However, an easy way to map scientific publications, especially interdisciplinary articles or those from adjacent fields, to the CCS classification does not exist.
+However, an easy way to map scientific publications, especially interdisciplinary articles or those from fields proximal to the CCS classification does not exist.
 
 Other classification systems are available such as the All Science Journal Classification (ASJC) developed and maintained by Scopus, the Web of Science research and categorical classifications from Clarivate Analytics, and the NSF classification system~\cite{nsf_classification}.
+All three rely on applying one or more journal-derived labels to articles.
 Of these, Scopus and the Web of Science also include global bibliographies with citation links and proprietary unique identifiers for publications, some of which can be matched to digital object identifiers (DOIs).
-All three rely on applying one or more journal-derived labels to articles.
-The inheritance, by articles, of labels meant to describe journals can be problematic in fields that evolve faster than their journal classifications.
-Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science, that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
-Others have also discussed and critiqued disciplinary assignments using journal based classifications~\cite{wang_large-scale_2016} \textcolor{blue}{need comprehensive list of citations}.
-Article classification systems have been constructed, however, which escape some of the criticisms of journal-based classification~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012}.
+Applying labels, designed for journals, to articles, of labels meant can be problematic in uterms of accuracy and because fields evolve faster than their journal classifications.
+[should we put in a comment about why article level labels provided by authors have limited use and that enforcement of controlled vocabularies varies by publisher?] Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science, that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
+Others have also discussed and critiqued disciplinary assignments using journal based classifications~\cite{wang_large-scale_2016,perianes-rodriguez_comparison_2017} \textcolor{blue}{need comprehensive list of citations}.
+Article classification systems have been constructed, however, which escape some of the criticisms of journal-based classification~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012} but seem to be in the research domain rather than the domain of practical use [need to check on this].[May need a nother bridging sentence to the next paragraph].
 
@@
 The DBLP bibliography covers publications from computer science and includes publications from hybrid fields, where they are considered pertinent to computer science research.
-The underlying assumption is that records in DBLP are greatly enriched for computer science even while recognizing that coverage may be incomplete and possibly biased.
-Cross-matching DBLP publications to Scopus records enabled us to harvest the richer citation data in Scopus, as well as extract links to publications from other disciplines.
+The underlying assumption we made is that records in DBLP are greatly enriched for computer science even while recognizing that coverage may be incomplete and possibly biased.
+Cross-matching DBLP publications to records in the Scopus, abstract and citation database of peer-reviewed literature, enabled us to harvest the richer links in Scopus as well as extract links to publications from other disciplines.
 This cross-matching also allows the use of both journal and article based classifications when clustering documents.
@@
 We describe below the high-level interactions of computer science within the Physical Sciences as well as with the Social Sciences and Life Sciences.
+[What did we find?
+Some kind of preview sentence!].
 
@@
 conductance has been found to be ``the stand-alone quality metric that best indicates performance on the information recovery metrics" \cite{emmons2016analysis}.
-% The quality of clustering was evaluated by measuring conductance as defined in Shun et al.~\cite{shun_parallel_2016}. 
-%George, Tandy - add text about why conductance is good, and that small values are better
-The data in \emph{comp} were clustered into 18, 20, or 22 clusters and in each case the highest numbered cluster (17, 19, or 21) had the greatest conductance value and the smallest number of nodes, suggesting that it effectively served as a container for `left over publications' during the Graclus process.
+Data from \emph{comp} were clustered into 18, 20, or 22 clusters and in each case the highest numbered cluster (17, 19, or 21) had the greatest conductance value and the smallest number of nodes, suggesting that it effectively served as a container for `left over publications' during the Graclus process.
 Thus, we did not consider cluster 19 (the 20th cluster) when interpreting our results.
 The remaining 19 clusters had conductance values ranging from 0.09 to 0.25 with a median conductance of 0.15.
+[This section on comp and conductneeds to be reasoned and presented better- for example why do we think these are good conductance values?].
 
@@
 For this dataset, the major subject areas of Computer Science; Engineering; and Mathematics contributed the most publications while Pharmacology, Toxicology, and Pharmaceutics; Nursing, Veterinary and Dentistry contributed the least.}
-\label{fig:graclus_comparison}       % Give a unique label
+\label{fig:graclus_comparison}       
 \end{figure}
@@
 \begin{table}
-% table caption is above the table
-\caption{\emph{Statistics regarding the 20 clusters produced using direct citation.
+\caption{\emph{Statistics regarding the 20 clusters produced using direct citation. The \emph{comp} dataset 
 2685021 is because of inner joins on ASJC Explain conductance calculations~\cite{shun_parallel_2016}}}
-\label{tab:1}       % Give a unique label
-% For LaTeX tables use
+\label{tab:1}       
 \begin{tabular}{lrccc}

### 2019-12-10 Scientometrics/comp.tex
rearranged figures

@@
 %placed here. General acknowledgments should be placed at the end of the article.}
-
 \subtitle{Relationship To Other Fields}
-
 %\titlerunning{Short form of title}        % if too long for running head
@@
 
-In this study, we sought to extend the work of Salton and Bergmark to reflect a more current reality while also considering connections between computer science and other fields.
+In this study, we sought to extend the work of Salton and Bergmark to describe current trends while considering connections between computer science and other fields.
 As a source of computer science literature, we used DBLP, a reference bibliography for computer science~\cite{dblp_ref}.
@@
 
-\begin{figure}[ht]
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=0.6]{ar_cp_ratio.pdf}
-% figure caption is below the figure
-\caption{Summary of DBLP data cross-matched with Scopus.
-2,685,356 publications from DBLP were cross-matched with Scopus and then grouped by the 27 major subject areas in the ASJC (Scopus) classification.
-The largest number of publications are contributed by Computer Science; Mathematics; and Engineering and then by Social Sciences; Physics and Astronomy; and Biochemistry, Genetics, and Molecular Biology.
-Publications were further annotated with respect to being either articles \emph{(ar)} or conference proceedings \emph{(cp)}.
-For this dataset, the major subject area of Computer Science with 1,194,623(cp) \& 879,396 contributed the most publications while Nursing with 69 (cp) \& 756 (ar)) contributed the least.}
-\label{fig:ar_cp_annotation}       % Give a unique label
-\end{figure}
-
 \subsection{Clustering methods}
@@
 [This section on comp and conductneeds to be reasoned and presented better- for example why do we think these are good conductance values?].
-
-\begin{figure}[ht]
-\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=0.5]{graclus_comparison.pdf}
-% figure caption is below the figure
-\caption{Summary of DBLP data cross-matched with Scopus.
-2,685,356 publications from DBLP were cross-matched with Scopus and then grouped by the 27 major subject areas in the ASJC (Scopus) classification.
-The largest number of publications are contributed by Computer Science; Mathematics; and Engineering and then by Social Sciences; Physics and Astronomy; and Biochemistry, Genetics, and Molecular Biology.
-Publications were further annotated with respect to being either articles \emph{(ar)} or conference proceedings \emph{(cp)}.
-For this dataset, the major subject areas of Computer Science; Engineering; and Mathematics contributed the most publications while Pharmacology, Toxicology, and Pharmaceutics; Nursing, Veterinary and Dentistry contributed the least.}
-\label{fig:graclus_comparison}       
-\end{figure}
 
@@
 
-\begin{figure}[ht]
-\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=0.5]{merge_select.pdf}
-% figure caption is below the figure
-\caption{Clustering produced using co-citation data; the y-axis is the cluster size (given logarithmically), and the x-axis is the number of iterations of the agglomerative clustering technique.
-Note that iterating more than 600 times produces a very large cluster.
-}
-\label{fig:merge_select}       % Give a unique label
-\end{figure}
-
 \section{Results}
@@
 
-\begin{figure}[ht]
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=0.45]{scopus_dblp_graclus3.pdf}
-% figure caption is below the figure
-\caption{Heat map for the clustering obtained by direct citation. The  y-axis (rows) correspond to topics, defined by Scopus characterizations, and the
-x-axis (columns) represent the 20 different clusters.  
-Each cluster is characterized by topics that label at least 10\% of the publications in the cluster.
- }
-\label{fig:heatmap}       % Give a unique label
-\end{figure}
-
 For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography published in the years 1996-2015, that had (i) a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography.
 The process of selection and matching resulted in a dataset of 2,685,356 publications (Materials and Methods).
+Of these roughly 2.8 million publications, approximately 2.07 million were classified as COMP under subject area and 2.07 million similarly were assigned ASJC codes corresponding to the major subject area, Computer Science with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (1).
+Thus, the sets of computer science publications in DBLP and Scopus are partially overlapping rather than DBLP being a perfect subset of Scopus.
+[the point being that we should justify our use of both journal and article level classifications].
 
@@
 
+%\noindent
+Co-citation based clustering:
+\begin{enumerate}
+\item Stratify by year after subsetting by COMP and restricting to article and cp only
+\item Apply fractional citation counting and identify highly-cited papers
+\item Calculate normalized co-citations
+\item Cluster by variable clustering method of Small
+\item Evaluate major co-cited pairs
+\end{enumerate}
+
+\emph{need to cite Granovetter somewhere for definition of strong and weak ties that Small refers to}
+\clearpage
+
+%%%%%%%%%
+\section{Figures}
+%%%%%%%%%
+
+\begin{figure}[ht]
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.6]{ar_cp_ratio.pdf}
+% figure caption is below the figure
+\caption{Summary of DBLP data cross-matched with Scopus.
+2,685,356 publications from DBLP were cross-matched with Scopus and then grouped by the 27 major subject areas in the ASJC (Scopus) classification.
+The largest number of publications are contributed by Computer Science; Mathematics; and Engineering and then by Social Sciences; Physics and Astronomy; and Biochemistry, Genetics, and Molecular Biology.
+Publications were further annotated with respect to being either articles \emph{(ar)} or conference proceedings \emph{(cp)}.
+For this dataset, the major subject area of Computer Science with 1,194,623(cp) \& 879,396 contributed the most publications while Nursing with 69 (cp) \& 756 (ar)) contributed the least.}
+\label{fig:ar_cp_annotation}       % Give a unique label
+\end{figure}
+
+\newpage
+
+\begin{figure}[ht]
+\centering
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.5]{graclus_comparison.pdf}
+% figure caption is below the figure
+\caption{Summary of DBLP data cross-matched with Scopus.
+2,685,356 publications from DBLP were cross-matched with Scopus and then grouped by the 27 major subject areas in the ASJC (Scopus) classification.
+The largest number of publications are contributed by Computer Science; Mathematics; and Engineering and then by Social Sciences; Physics and Astronomy; and Biochemistry, Genetics, and Molecular Biology.
+Publications were further annotated with respect to being either articles \emph{(ar)} or conference proceedings \emph{(cp)}.
+For this dataset, the major subject areas of Computer Science; Engineering; and Mathematics contributed the most publications while Pharmacology, Toxicology, and Pharmaceutics; Nursing, Veterinary and Dentistry contributed the least.}
+\label{fig:graclus_comparison}       
+\end{figure}
+
+\newpage
+
 \begin{figure}[ht]
@@
 
-%\noindent
-Co-citation based clustering:
-\begin{enumerate}
-\item Stratify by year after subsetting by COMP and restricting to article and cp only
-\item Apply fractional citation counting and identify highly-cited papers
-\item Calculate normalized co-citations
-\item Cluster by variable clustering method of Small
-\item Evaluate major co-cited pairs
-\end{enumerate}
+\newpage
 
+\begin{figure}[ht]
+\centering
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.5]{merge_select.pdf}
+% figure caption is below the figure
+\caption{Clustering produced using co-citation data; the y-axis is the cluster size (given logarithmically), and the x-axis is the number of iterations of the agglomerative clustering technique.
+Note that iterating more than 600 times produces a very large cluster.
+}
+\label{fig:merge_select}       % Give a unique label
+\end{figure}
+
+\newpage
+
+\begin{figure}[ht]
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.45]{scopus_dblp_graclus3.pdf}
+% figure caption is below the figure
+\caption{Heat map for the clustering obtained by direct citation. The  y-axis (rows) correspond to topics, defined by Scopus characterizations, and the
+x-axis (columns) represent the 20 different clusters.  
+Each cluster is characterized by topics that label at least 10\% of the publications in the cluster.
+ }
+\label{fig:heatmap}       % Give a unique label
+\end{figure}
+
+\begin{figure}[ht]
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.45]{scopus_dblp_heatmap3.pdf}
+% figure caption is below the figure
+\caption{Heat map for the clustering obtained by direct citation. The  y-axis (rows) correspond to topics, defined by Scopus characterizations, and the
+x-axis (columns) represent the 20 different clusters.  
+Each cluster is characterized by topics that label at least 10\% of the publications in the cluster.
+ }
+\label{fig:heatmap}       % Give a unique label
+\end{figure}
+
+\newpage
 \begin{figure}[ht]
@@
 
-\emph{need to cite Granovetter somewhere for definition of strong and weak ties that Small refers to}
+\newpage
 

### 2019-12-10 Scientometrics/comp.tex
reordere figures and cleaned up text

@@
 Of these, Scopus and the Web of Science also include global bibliographies with citation links and proprietary unique identifiers for publications, some of which can be matched to digital object identifiers (DOIs).
-Applying labels, designed for journals, to articles, of labels meant can be problematic in uterms of accuracy and because fields evolve faster than their journal classifications.
+Applying labels designed to represent journals, to articles, can be problematic in terms of accuracy given broad scope in some journals,  and also because fields evolve faster than their journal classifications.
 [should we put in a comment about why article level labels provided by authors have limited use and that enforcement of controlled vocabularies varies by publisher?] Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science, that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
@@
 Consequently, we generated 20 clusters, labeled 0-19, using Graclus (Fig~\ref{fig:heatmap}).
+
 We used conductance, as defined in Shun et al.~\cite{shun_parallel_2016}, to  evaluate clustering (smaller is better), noting that
@@
 Data from \emph{comp} were clustered into 18, 20, or 22 clusters and in each case the highest numbered cluster (17, 19, or 21) had the greatest conductance value and the smallest number of nodes, suggesting that it effectively served as a container for `left over publications' during the Graclus process.
-Thus, we did not consider cluster 19 (the 20th cluster) when interpreting our results.
+Thus, we limited our did not consideration of cluster 19 (the 20th cluster) when interpreting results.
 The remaining 19 clusters had conductance values ranging from 0.09 to 0.25 with a median conductance of 0.15.
@@
 
-\begin{table}
-\caption{\emph{Statistics regarding the 20 clusters produced using direct citation. The \emph{comp} dataset 
-2685021 is because of inner joins on ASJC Explain conductance calculations~\cite{shun_parallel_2016}}}
-\label{tab:1}       
-\begin{tabular}{lrccc}
-\hline\noalign{\smallskip}
-Cluster & Publications & Conductance & Total ASJC Labels & Unique ASJC Labels\\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-0 & 111,294 & 0.12 & 265,664 & 142 \\ 
-1 & 117,057 & 0.14 & 246,960 & 166 \\ 
-2 & 116,251 & 0.11 & 280,602 & 165 \\ 
-3 & 353,366 & 0.15 & 881,693 & 200 \\ 
-4 & 145,081 & 0.09 & 349,020 & 154 \\ 
-5 & 92,097 & 0.17 & 248,168 & 186 \\ 
-6 & 71,865 & 0.15 & 199,681 & 163 \\ 
-7 & 179,927 & 0.18 & 465,181 & 202 \\ 
-8 & 302,656 & 0.18 & 760,117 & 214 \\ 
-9 & 69,520 & 0.19 & 197,031 & 174 \\ 
-10 & 42,462 & 0.10 & 102,838 & 141 \\ 
-11 & 448,030 & 0.25 & 1,229,061 & 224 \\ 
-12 & 70,738 & 0.21 & 216,546 & 179 \\ 
-13 & 105,232 & 0.17 & 289,318 & 187 \\ 
-14 & 199,176 & 0.15 & 551,657 & 208 \\ 
-15 & 64,384 & 0.17 & 195,679 & 167 \\ 
-16 & 89,340 & 0.11 & 240,157 & 158 \\ 
-17 & 50,817 & 0.14 & 181,531 & 179 \\ 
-18 & 43,113 & 0.20 & 108,518 & 177 \\ 
-19 & 12,615 & 0.80 & 36,583 & 229 \\ \noalign{\smallskip}\hline
-\end{tabular}
-\end{table}
+\paragraph{Clustering by Co-Citation.}
+For an alternate view of these DBLP data we constructed clusters using co-citation, the frequency with which a pair of articles is cited by other articles.
+Co-citation was first described independently by Small and Marshakova in 1973~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}, and provides insight into the emergence of new ideas derived from the association of previously independent ones.
+Co-citation thus provides some degree of evolutionary insight and has been used for clustering publications~\cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
 
-\paragraph{Clustering by Co-Citation.}
-Co-citation, the frequency with which a pair of articles is cited by other articles,  first described independently by Small and Marshakova in 1973~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973},
-provides insight into the emergence of new ideas derived from the association of previously independent ones. 
-Co-citation thus provides some degree of evolutionary insight across disciplines and sub-disciplines and has been used for clustering publications~\cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
-For an alternate view of these DBLP data we constructed clusters using co-citation, using a modification of   variable level clustering to the 2,685,356 articles in \emph{comp} and then performing top-down agglomerative clustering on the resultant 10,298 (of 22,232 clusters) containing greater than two nodes per cluster.
-
-We used variable level clustering, an approach developed in 1985 by Small and Sweeney~\cite{small_clustering_1985}, with minor modifications as follows.
+To cluster by co-citation, we used a modification of variable level clustering combined with agglomerative clustering, an approach developed in 1985 by Small and Sweeney~\cite{small_clustering_1985}.
 Variable level clustering involves applying a threshold (below which all edges in a graph are deleted) then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn.
@@
 In our implementation of variable level clustering, we first calculated the number of citations accumulated across Scopus for all 2,685,356 articles in \emph{comp}.
-After discarding those publications without any citations, \textcolor{blue}{Sitaram please confirm}, we restricted further analysis to those in the 90th percentile of citations or higher, resulting in a dataset of size 212,311.
+After discarding those publications without any citations, \textcolor{blue}{Sitaram please confirm}, we restricted further analysis to highly cited articles, those in the 90th percentile of citations or higher, resulting in a dataset of size 212,311.
 We then identified 4,318,305 publications in Scopus that cite these 212,311 articles from \emph{comp}.
@@
 A final threshold of $t$=0.999 was applied to break the single remaining large cluster.
-% All generated clusters  using this process contained  less than 100 nodes.
 Using this approach, 22,232 clusters containing 84,591 nodes were generated, each containing less than 100 nodes.
@@
 
-\section{Results}
+\section*{Results}
 \label{sec:results}
@@
 The process of selection and matching resulted in a dataset of 2,685,356 publications (Materials and Methods).
-Of these roughly 2.8 million publications, approximately 2.07 million were classified as COMP under subject area and 2.07 million similarly were assigned ASJC codes corresponding to the major subject area, Computer Science with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (1).
+Of these roughly 2.8 million publications, approximately 2.07 million were classified as COMP under subject area and 2.07 million similarly were assigned ASJC codes corresponding to Computer Science (major subject area), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (1).
 Thus, the sets of computer science publications in DBLP and Scopus are partially overlapping rather than DBLP being a perfect subset of Scopus.
@@
 we constructed article level clusters of this computer science dataset at a sufficiently high level of aggregation to avoid cognitive challenge and cross-matched them to disciplinary classification by journal, the Scopus ASJC classification.
-We only considered Scopus ASJC minor subject area categories that accounted for at least 10\% of the publications in each cluster.
+To focus on relatively high signal, we only considered Scopus ASJC minor subject area categories that accounted for at least 15\% of the publications in each cluster.
 
-Figure~\ref{fig:heatmap} permits examination of these data from two perspectives: (i) the clusters that map to a given ASJC minor subject area and (ii) ASJC minor subject areas that comprised at least 10\% of the publication in a cluster.
+Figure~\ref{fig:heatmap} permits examination of these data from two perspectives: (i) the clusters that map to a given ASJC minor subject area and (ii) ASJC minor subject areas that comprised at least 15\% of the publication in a cluster.
 Under these conditions, 31 of the 334 ASJC minor subject areas are represented.
@@
 \newpage
+\clearpage
+\section*{Tables}
+
+\begin{table}[ht]
+\caption{\emph{Statistics regarding the 20 clusters produced using direct citation. The \emph{comp} dataset 
+2685021 is because of inner joins on ASJC Explain conductance calculations~\cite{shun_parallel_2016}}}
+\label{tab:1}       
+\begin{tabular}{lrccc}
+\hline\noalign{\smallskip}
+Cluster & Publications & Conductance & Total ASJC Labels & Unique ASJC Labels\\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+0 & 111,294 & 0.12 & 265,664 & 142 \\ 
+1 & 117,057 & 0.14 & 246,960 & 166 \\ 
+2 & 116,251 & 0.11 & 280,602 & 165 \\ 
+3 & 353,366 & 0.15 & 881,693 & 200 \\ 
+4 & 145,081 & 0.09 & 349,020 & 154 \\ 
+5 & 92,097 & 0.17 & 248,168 & 186 \\ 
+6 & 71,865 & 0.15 & 199,681 & 163 \\ 
+7 & 179,927 & 0.18 & 465,181 & 202 \\ 
+8 & 302,656 & 0.18 & 760,117 & 214 \\ 
+9 & 69,520 & 0.19 & 197,031 & 174 \\ 
+10 & 42,462 & 0.10 & 102,838 & 141 \\ 
+11 & 448,030 & 0.25 & 1,229,061 & 224 \\ 
+12 & 70,738 & 0.21 & 216,546 & 179 \\ 
+13 & 105,232 & 0.17 & 289,318 & 187 \\ 
+14 & 199,176 & 0.15 & 551,657 & 208 \\ 
+15 & 64,384 & 0.17 & 195,679 & 167 \\ 
+16 & 89,340 & 0.11 & 240,157 & 158 \\ 
+17 & 50,817 & 0.14 & 181,531 & 179 \\ 
+18 & 43,113 & 0.20 & 108,518 & 177 \\ 
+19 & 12,615 & 0.80 & 36,583 & 229 \\ \noalign{\smallskip}\hline
+\end{tabular}
+\end{table}
+\newpage
 
@@
 % Non-BibTeX users please use
-
-\clearpage
-
-\section{Garbage}
-
-Cite Alan Porter on expanding universe versus myopic focus.
-Cite Traag, Waltman, Lariviere papers.
-Peter Sjögårde and Per Ahlgren, Loet Leydesdorff, Caroline S.
-Wagner and Lutz Bornmann, Discontinuities in citation relations among journals: self-organized criticality as a model of scientific revolutions and change, Scientometrics, 10.1007/s11192-018-2734-6, 116, 1, (623-644), (2018).
-Antonio Perianes-Rodriguez and Javier Ruiz-Castillo, A comparison of the Web of Science and publication-level classification systems of science, Journal of Informetrics, 10.1016/j.joi.2016.10.007, 11, 1, (32-45), (2017).
-Qi Wang and Ludo Waltman, Large-scale analysis of the accuracy of the journal classification systems of Web of Science and Scopus, Journal of Informetrics, 10.1016/j.joi.2016.02.003, 10, 2, (347-364), (2016).
-Henry Small, Kevin W.
-Boyack and Richard Klavans, Identifying emerging topics in science and technology,
-Crossref
-
-\paragraph{Overall strategy}
-
-Here we describe the overall strategy used for the two clustering methods.\\
-
-\emph{misc stuff:  In using the term inform, we are mindful of (i) Greenhalgh (ii) Sarewitz and Pielke.
-I think that I want to cite these two without really knowing how.
-Greenhalgh for the limitations of positivism.
-Sarewitz for the limitations of allowing science to do whatever it wants to.
-I'd also like to see some text about (i) limited funding resources (ii) efficient use of existing resources (iiii) informing policy at multiple levels -- all directed at justifying our study.
-I'm not sure where to put it though.
-CS can also be an excellent model system for studying interdisciplinarity cite Porter and colleagues in a study on measuring interdisciplinarity~\cite{porter_measuring_2007} observe that 'The discrepancies between disciplinary roots and research realities loom large', a reference to the challenges associated with knowledge diffusing across researchers who tend to be focused in their own areas.
-This concern may be especially relevant for computer science given the ubiquity of computing today and limited public funding for research.
-Maybe squeeze in Tandy's NAS report on interdisciplinarity.
-I should ping Ohid Yaqub about this too- science policy is his area.}
-
-\noindent
- Spectral clustering:
-\begin{enumerate}
-\item Subset Scopus by COMP
-\item Match COMP to DBLP at high stringency -> reduced number of scps
- \item Harvest cited references  from Scopus
- \item Cluster articles by direct citation using Graclus to a number that meets simple optimality criteria and does not impose cognitive challenges
- \item Reconcile cluster contents to journal classification for the purpose of referencing
- \item Infer inter-cluster relationships using direct citations, co-citations, and bibliographic coupling
-\end{enumerate}
 

### 2019-12-10 Scientometrics/comp.tex
update

@@
               Netelabs, NET ESolutions Corporation, McLean, VA \\
-              \email{netelabs@nete.com}
+              \email{netelabs@nwete.com}
 }
@@
 [should we put in a comment about why article level labels provided by authors have limited use and that enforcement of controlled vocabularies varies by publisher?] Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science, that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
-Others have also discussed and critiqued disciplinary assignments using journal based classifications~\cite{wang_large-scale_2016,perianes-rodriguez_comparison_2017} \textcolor{blue}{need comprehensive list of citations}.
-Article classification systems have been constructed, however, which escape some of the criticisms of journal-based classification~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012} but seem to be in the research domain rather than the domain of practical use [need to check on this].[May need a nother bridging sentence to the next paragraph].
+Others have also discussed and critiqued disciplinary assignments using journal based classifications~\cite{wang_large-scale_2016,perianes-rodriguez_comparison_2017}.
+Article classification systems have been constructed, however, which escape some of the criticisms of journal-based classification~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012} but seem to be in the research domain rather than the domain of practical use [need to check on this].[May need another bridging sentence to the next paragraph].
 
@@
 Publications were parsed from the XML source file and loaded into a PostgreSQL database.
+Just over 95\% of the publications within were published after 1996.
 We have previously parsed the Scopus dataset of over 72,000,000 publications into a custom schema as part of implementing a larger data platform for research evaluation~\cite{GithubERNIE2019}.
@@
 In our implementation of variable level clustering, we first calculated the number of citations accumulated across Scopus for all 2,685,356 articles in \emph{comp}.
-After discarding those publications without any citations, \textcolor{blue}{Sitaram please confirm}, we restricted further analysis to highly cited articles, those in the 90th percentile of citations or higher, resulting in a dataset of size 212,311.
+After discarding those publications without any citations, we restricted further analysis to highly cited articles, those in the 90th percentile of citations or higher, resulting in a dataset of size 212,311.
 We then identified 4,318,305 publications in Scopus that cite these 212,311 articles from \emph{comp}.
@@
 Using this approach, 22,232 clusters containing 84,591 nodes were generated, each containing less than 100 nodes.
-Clusters containing only 2 nodes were then discarded bringing the total number of clusters down to 10,298.
+Clusters containing only 2 nodes were discarded bringing the total number of clusters down to 10,298.
 
 Agglomerative clustering was then performed on these 10,298 clusters to generate higher-order clusters.
-Briefly, each cluster was now treated as a node and the edge weight between two clusters was assigned to the maximum edge weight of all edges between the nodes in these two clusters.
+Briefly, each cluster was now treated as a node and the edge weight between two clusters was assigned to the maximum edge weight of all edges between the nodes in the two precursor clusters.
 Edges were arranged in descending order.
@@
 
-As described in Methods, we performed 600 iterations to the 10,298 clusters further limited to clusters containing at least 10 nodes, which resulted in 666 clusters.
+As described in Methods, we performed 600 iterations of agglomerative clustering to the 10,298 clusters.
+To focus on major clusters, we restricted agglomeration to clusters containing at least 10 nodes, which resulted in 666 clusters.
 Further agglomeration resulted in the development of a single large cluster (Fig~\ref{fig:merge_select}).
-The 20 largest clusters were used for further analysis and comparison with clusters generated by direct citation. The largest of these 20 clusters contained 1,276 nodes and the smallest contained 136.
+Consequently, the 20 largest clusters were used for further analysis and comparison with clusters generated by direct citation.
+The largest of these 20 clusters contained 1,276 nodes and the smallest contained 136.
 
@@
 %%%%%%%%%
-\section{Figures}
+\section*{Figures}
 %%%%%%%%%
@@
 % For example, with the graphicx package use
-  \includegraphics[scale=0.5]{graclus_comparison.pdf}
+  \includegraphics[scale=0.4]{graclus_comparison.pdf}
 % figure caption is below the figure
-\caption{Summary of DBLP data cross-matched with Scopus.
-2,685,356 publications from DBLP were cross-matched with Scopus and then grouped by the 27 major subject areas in the ASJC (Scopus) classification.
-The largest number of publications are contributed by Computer Science; Mathematics; and Engineering and then by Social Sciences; Physics and Astronomy; and Biochemistry, Genetics, and Molecular Biology.
-Publications were further annotated with respect to being either articles \emph{(ar)} or conference proceedings \emph{(cp)}.
-For this dataset, the major subject areas of Computer Science; Engineering; and Mathematics contributed the most publications while Pharmacology, Toxicology, and Pharmaceutics; Nursing, Veterinary and Dentistry contributed the least.}
-\label{fig:graclus_comparison}       
+\caption{Conductance Measurements of Clusters Generated by Graclus.
+2,685,356 DBLP publications, 7,129,006 cited references, and 44,296,381 citations were clustered using Graclus into 18 (grac\_18), 20 (grac\_20), or 22 (grac-22) clusters.
+Conductance, $\phi(S)$, was measured for these clusters considering only the edges between publications using the formula: $\phi(S)=|\partial(S)|/min(vol(S),2m-vol(S)$, where $\partial(S)$ is the boundary (number of edges leaving a set), vol(S) is volume of a set of vertices as the sum of the degrees of the vertices in a set, and $m$ is the number of undirected edges in a set~\cite{shun_parallel_2016}.}
+\label{fig:graclus_comparison_conductance}       
 \end{figure}
@@
 \end{figure}
+
+\begin{figure}[ht]
+\centering
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+ \includegraphics[scale=0.5]{cocit_venn2.pdf}
+% figure caption is below the figure
+\caption{High-level disciplinary composition of publications in $\sim$2,000 clusters generated by variable-level clustering  of co-citation data.
+%Variable Level Clustering. 
+84,591 nodes from were matched to the 4 subject areas, 
+27 major subject areas, and 334 minor subject areas in the Scopus ASJC classification. Since 82.5\% of these nodes were assigned more to than one minor subject category, 
+we assigned fractional counts for the four subject areas that summed to 1 for each article. The figure shows a four way Venn Diagram~\cite{chen_venn_2011} illustrating the 
+relative frequencies of publications from the Physical Sciences, Social Sciences, Life Sciences, and Health Sciences.}
+\label{fig:cocitr_venn2}       % Give a unique label
+\end{figure}
+
+\newpage
 
@@
 \newpage
-\begin{figure}[ht]
-\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
- \includegraphics[scale=0.5]{cocit_venn2.pdf}
-% figure caption is below the figure
-\caption{High-level disciplinary composition of publications in $\sim$2,000 clusters generated by variable-level clustering  of co-citation data.
-%Variable Level Clustering. 
-84,591 nodes from were matched to the 4 subject areas, 
-27 major subject areas, and 334 minor subject areas in the Scopus ASJC classification. Since 82.5\% of these nodes were assigned more to than one minor subject category, 
-we assigned fractional counts for the four subject areas that summed to 1 for each article. The figure shows a four way Venn Diagram~\cite{chen_venn_2011} illustrating the 
-relative frequencies of publications from the Physical Sciences, Social Sciences, Life Sciences, and Health Sciences.}
-\label{fig:cocitr_venn2}       % Give a unique label
-\end{figure}
 

### 2019-12-11 Scientometrics/comp.tex
added cross-match figure

@@
 
-Progressing beyond 1974-79, and Salton and Bergmark's historical triad of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS)~\cite{acm_ref} published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field.
+Beyond Salton and Bergmark's historical triad of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS)~\cite{acm_ref} published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field.
 This classification also addresses relationships with other fields under the category of Applied Computing.
@@
 The process of selection and matching resulted in a dataset of 2,685,356 publications (Materials and Methods).
-Of these roughly 2.8 million publications, approximately 2.07 million were classified as COMP under subject area and 2.07 million similarly were assigned ASJC codes corresponding to Computer Science (major subject area), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (1).
+Of these roughly 2.8 million publications, approximately 2.07 million were classified as COMP under subject area and assigned ASJC codes corresponding to Computer Science (major subject area and 13 minos subject areas), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (1).
+The set of 2.07 million publications classified as COMP in Scopus spanned all 13 minor subject areas with Software 30.3\% being the largest component and Computer Science (miscellaneous) 0.9\% the smallest.
+The number of minor subject areas assigned to a publication averaged to 1.75 with 53\% of the publications being assigned to one minor subject area and 0.0003\% assigned to 7 different minor subject areas (Table 1).
+
 Thus, the sets of computer science publications in DBLP and Scopus are partially overlapping rather than DBLP being a perfect subset of Scopus.
@@
 
-\subsection{Clustering by Direct Citation} 
+\subsection{Clustering by Direct Citation} [Need a sentence about why we're clustering].
 Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation with an argument being made for direct citation as the best approach to concentrate citation links~\cite{klavans_which_2017}.
@@
 Further, the top cited papers often derived from biology and we were concerned that this small sample (top cited papers) were not representative of the cluster.
+[Overall conclusions of Graclus based clustering?]
 
-\subsection{Clustering by Co-citation.}
+\subsection{Clustering by Co-citation.} [Sentence justifying co-citation base clustering]
 
@@
 The largest of these 20 clusters contained 1,276 nodes and the smallest contained 136.
+
+[Overall conclusions of cocitation based clustering]
 
@@
 \end{figure}
+\newpage
 
-\newpage
+\begin{figure}[ht]
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.45]{graclus_cocit_fig.pdf}
+% figure caption is below the figure
+\caption{Heat map for the clustering obtained by direct citation. The  y-axis (rows) correspond to topics, defined by Scopus characterizations, and the
+x-axis (columns) represent the 20 different clusters.  
+Each cluster is characterized by topics that label at least 10\% of the publications in the cluster.
+ }
+\label{fig:heatmap}       % Give a unique label
+\end{figure}
 
@@
 \section*{Tables}
+
+\begin{table}[ht]
+\caption{\emph{Statistics regarding the 20 clusters produced using direct citation. The \emph{comp} dataset 
+2685021 is because of inner joins on ASJC Explain conductance calculations~\cite{shun_parallel_2016}}}
+\label{tab:1}       
+\begin{tabular}{lrccc}
+\hline\noalign{\smallskip}
+minor\_subject\_area & Percent of Publications \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Software & 30.30 \\ 
+Computer Science Applications & 25.20 \\ 
+Computer Networks and Communications & 21.60 \\ 
+Computer Science(all) & 19.60 \\ 
+Artificial Intelligence & 14.30 \\ 
+Information Systems & 11.90 \\ 
+Hardware and Architecture & 11.50 \\ 
+Signal Processing & 9.90 \\ 
+Computer Vision and Pattern Recognition & 9.50 \\ 
+Computational Theory and Mathematics & 8.00 \\ 
+Human-Computer Interaction & 7.50 \\ 
+Computer Graphics and Computer-Aided Design & 5.20 \\ 
+Computer Science (miscellaneous) & 0.90 \\ 
+\noalign{\smallskip}\hline
+\end{tabular}
+\end{table}
+\newpage
 

### 2019-12-13 Scientometrics/comp.tex
update

@@
 \begin{abstract}
-Computer science as a field has experienced dramatic growth and diversification over the last twenty years.
-Towards an current understanding of the structure of the field, we analyze a cohort of the computer science literature.
-For insight on the features of this cohort and the flow of information within its components, we construct article level clusters based on either direct citations or co-citations, and reconcile them with major and minor subject categories in the All Science Journal Classification (Scopus).
-[abstract is feeble and needs to be rewritten].
+Computer science has experienced dramatic growth and diversification over the last twenty years.
+Towards a current understanding of the structure of this discipline, we analyze a cohort of the computer science literature.
+For insight on the features of this cohort and the relationship within its components, we construct article level clusters based on either direct citations or co-citations, and reconcile them with major and minor subject categories in the All Science Journal Classification (Scopus).
+[What do we find?].
 
@@
 
-Beyond Salton and Bergmark's historical triad of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS)~\cite{acm_ref} published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field.
+Looking beyond Salton and Bergmark's historical triad of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS) published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field~\cite{acm_ref}.
 This classification also addresses relationships with other fields under the category of Applied Computing.
-However, an easy way to map scientific publications, especially interdisciplinary articles or those from fields proximal to the CCS classification does not exist.
+However, an easy way to map scientific publications to the CCS, especially interdisciplinary articles or those from proximal fields does not seem to be available.
 
-Other classification systems are available such as the All Science Journal Classification (ASJC) developed and maintained by Scopus, the Web of Science research and categorical classifications from Clarivate Analytics, and the NSF classification system~\cite{nsf_classification}.
+Other classification systems are available such as the All Science Journal Classification (ASJC) developed and maintained by Scopus, the Web of Science research and categorical classifications from Clarivate Analytics, and the NSF classification system~\cite{nsf_classification} [add citations for Scopus and Web of Science].
 All three rely on applying one or more journal-derived labels to articles.
-Of these, Scopus and the Web of Science also include global bibliographies with citation links and proprietary unique identifiers for publications, some of which can be matched to digital object identifiers (DOIs).
-Applying labels designed to represent journals, to articles, can be problematic in terms of accuracy given broad scope in some journals,  and also because fields evolve faster than their journal classifications.
-[should we put in a comment about why article level labels provided by authors have limited use and that enforcement of controlled vocabularies varies by publisher?] Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science, that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
+A natural consequence is limited specificity at the article level.
+
+Scopus and the Web of Science also include comprehensive bibliographies with citation links and proprietary unique identifiers for publications, some of which can be matched to digital object identifiers (DOIs).
+However, Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science, that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
 Others have also discussed and critiqued disciplinary assignments using journal based classifications~\cite{wang_large-scale_2016,perianes-rodriguez_comparison_2017}.
-Article classification systems have been constructed, however, which escape some of the criticisms of journal-based classification~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012} but seem to be in the research domain rather than the domain of practical use [need to check on this].[May need another bridging sentence to the next paragraph].
+Article classification systems have been constructed, which escape some of the criticisms of journal-based classification~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012} but seem to be in the research domain rather than the domain of practical use [need to check on this].[May need another bridging sentence to the next paragraph].
 
-In this study, we sought to extend the work of Salton and Bergmark to describe current trends while considering connections between computer science and other fields.
+In this study, we combine article and journal level approaches to extend the work of Salton and Bergmark to present trends in computer science, while considering connections to other fields.
 As a source of computer science literature, we used DBLP, a reference bibliography for computer science~\cite{dblp_ref}.
 The DBLP bibliography covers publications from computer science and includes publications from hybrid fields, where they are considered pertinent to computer science research.
-The underlying assumption we made is that records in DBLP are greatly enriched for computer science even while recognizing that coverage may be incomplete and possibly biased.
-Cross-matching DBLP publications to records in the Scopus, abstract and citation database of peer-reviewed literature, enabled us to harvest the richer links in Scopus as well as extract links to publications from other disciplines.
-This cross-matching also allows the use of both journal and article based classifications when clustering documents.
-Using both direct citations and co-citations as the basis for clustering, we used DBLP articles from journals and conference proceedings for the period 1996-2015.
-We reconciled these clusters with the All Science Journal Classification (ASJC) developed and maintained by Scopus through a combination of automated and manual procedures.
-We describe below the high-level interactions of computer science within the Physical Sciences as well as with the Social Sciences and Life Sciences.
-[What did we find?
+
+We describe below the high-level interactions of computer science within the Physical Sciences, and with the Social Sciences, Life Sciences, and Health Sciences [What did we find?
 Some kind of preview sentence!].
@@
  A stable release of the DBLP computer science bibliography~\cite{dblp_ref} consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz.
+Just over 95\% of the publications within were published after 1996.
 Publications were parsed from the XML source file and loaded into a PostgreSQL database.
-Just over 95\% of the publications within were published after 1996.
 We have previously parsed the Scopus dataset of over 72,000,000 publications into a custom schema as part of implementing a larger data platform for research evaluation~\cite{GithubERNIE2019}.
@@
 References cited by these publications were then extracted from Scopus (7,129,006 records), resulting in a total of 8,000,411 nodes (publications and references) and 44,296,381 edges that represent citations within the dataset.
-This dataset is referred to as \emph{comp} (see Fig~\ref{fig:ar_cp_annotation}).
+This dataset is referred to as \emph{comp} (Fig~\ref{fig:ar_cp_annotation}, Table~\ref{tab:comp}).
 
-\subsection{Clustering methods}
+\subsection{Clustering methods} In applying both clustering by direct citation and by co-citation, we attempted to consider, wherever possible, the criteria articulated by \v{S}ubelj, van Eck, and Waltman~\cite{subelj_clustering_2016}, of (i) Cluster sizes- the largest cluster should be no more than 10 times the smallest one (ii) Small clusters- should be eliminated (iii) Clustering stability- small changes and replicates should yield similar results (iv) Computing time- minimized where possible (v) Intuitive sensibility- determined by qualitative examination.
 
@@
 In preliminary experiments, we varied the number of clusters to be formed between 10 and 50 clusters (data not shown).
-At 20 clusters, the most evenly sized set of clusters resulted with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{traag_louvain_2019}.
-Consequently, we generated 20 clusters, labeled 0-19, using Graclus (Fig~\ref{fig:heatmap}).
+At around 20 clusters, clusters size was relatively stable with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{subelj_clustering_2016}.
+Consequently, we generated 20 clusters, labeled 0-19, using Graclus (Table~\ref{tab:graclus}).
 
-We used conductance, as defined in Shun et al.~\cite{shun_parallel_2016}, to  evaluate clustering (smaller is better), noting that
-conductance has been found to be ``the stand-alone quality metric that best indicates performance on the information recovery metrics" \cite{emmons2016analysis}.
+We also used conductance, as defined in Shun et al.~\cite{shun_parallel_2016}, to  evaluate clustering (smaller is better), noting that conductance has been found to be ``the stand-alone quality metric that best indicates performance on information recovery metrics" \cite{emmons2016analysis}.
 Data from \emph{comp} were clustered into 18, 20, or 22 clusters and in each case the highest numbered cluster (17, 19, or 21) had the greatest conductance value and the smallest number of nodes, suggesting that it effectively served as a container for `left over publications' during the Graclus process.
-Thus, we limited our did not consideration of cluster 19 (the 20th cluster) when interpreting results.
-The remaining 19 clusters had conductance values ranging from 0.09 to 0.25 with a median conductance of 0.15.
-[This section on comp and conductneeds to be reasoned and presented better- for example why do we think these are good conductance values?].
+Thus, we limited our consideration of cluster 19 (the 20th cluster), also the smallest cluster, when interpreting results.
+The remaining 19 clusters had conductance values ranging from 0.09 to 0.25 with a median conductance of 0.15, Figure~\ref{fig:graclus_comparison_conductance}, Table~\ref{tab:comp}.
 
@@
 For an alternate view of these DBLP data we constructed clusters using co-citation, the frequency with which a pair of articles is cited by other articles.
-Co-citation was first described independently by Small and Marshakova in 1973~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}, and provides insight into the emergence of new ideas derived from the association of previously independent ones.
-Co-citation thus provides some degree of evolutionary insight and has been used for clustering publications~\cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
-
 To cluster by co-citation, we used a modification of variable level clustering combined with agglomerative clustering, an approach developed in 1985 by Small and Sweeney~\cite{small_clustering_1985}.
@@
 Three parameters are needed: (i) a threshold or starting level based on a quantile of normalized co-citation frequency, (ii) a level increment, and (iii) a maximum cluster size.
-An issue is the generation of very large clusters by chaining through low edge weights.
+An issue is the generation of very large clusters by chaining via low edge weights.
 Thus, at each iteration, any cluster exceeding the maximum cluster size  is returned to the process and a higher threshold is applied to break such clusters.
 
-In our implementation of variable level clustering, we first calculated the number of citations accumulated across Scopus for all 2,685,356 articles in \emph{comp}.
+In our implementation of variable level clustering, Figure~\ref{fig:vlc_process}, we first calculated the number of citations accumulated across Scopus for all 2,685,356 articles in \emph{comp}.
 After discarding those publications without any citations, we restricted further analysis to highly cited articles, those in the 90th percentile of citations or higher, resulting in a dataset of size 212,311.
 We then identified 4,318,305 publications in Scopus that cite these 212,311 articles from \emph{comp}.
-For each of the 4,318,305 citing publications in turn, all possible ${n \choose 2}$ reference pairs were generated, where $n$ is the number of references in a publication.
-The cited reference pairs were restricted to those in the set of 212,311 highly cited papers previously identified.
-The frequency of these co-cited pairs was then computed across the dataset  and normalized using Salton's cosine formula~\cite{salton_citation_1979}.
+For each of the 4,318,305 citing publications in turn, all possible ${n \choose 2}$ reference pairs were generated from a publication's cited references, where $n$ is the number of references in a publication.
+The cited reference pairs this generated, were then restricted to those in the set of 212,311 highly cited papers previously identified.
+The frequency of these co-cited pairs was then computed across the \emph{comp} dataset  and normalized using Salton's cosine formula~\cite{salton_citation_1979}.
 A total of 46,463,117 unique co-cited pairs were thus obtained.
@@
 Clusters containing only 2 nodes were discarded bringing the total number of clusters down to 10,298.
+The publications in these 10,298 clusters were overwhelmingly drawn from the Physical Sciences (one of the 4 top level categories in the Scopus ASJC classification), of which computer science is a sub-category, Figure~\ref{fig:cocitr_venn2}.
 
 Agglomerative clustering was then performed on these 10,298 clusters to generate higher-order clusters.
+To focus on larger clusters, only those with at least 10 nodes were used as input.
 Briefly, each cluster was now treated as a node and the edge weight between two clusters was assigned to the maximum edge weight of all edges between the nodes in the two precursor clusters.
 Edges were arranged in descending order.
-The first pair of clusters was merged and its edge weight with other interacting clusters was recalculated.
+The first pair of clusters was merged and its edge weight with other interacting clusters was recalculated, again based on maximum edge weight.
 All edges were then re-ordered as before and the next pair of clusters was merged.
-The process was halted after 600 rounds to prevent single large clusters being generated (Fig.~\ref{fig:merge_select}).
+The process was halted after 600 rounds to prevent a single very large outlier cluster being generated (Fig.~\ref{fig:merge_select}).
 
@@
 
-For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography published in the years 1996-2015, that had (i) a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography.
+In our study of the structure of a twenty year cohort of the computer science literature, we chose to use both traditional journal-based and article-based approaches.
+Considering that traditional disciplines, `may only partly reflect the actual organization of today’s scientific research'~\cite{waltman_new_2012}  we constructed article clusters at high levels of aggregation using citations in two different ways to examine the \emph{comp} dataset and mapped these clusters to journal-based categories.
+
+For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography that (i) had a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography.
+Our underlying assumption is that records in DBLP are greatly enriched for computer science even while recognizing that coverage may be incomplete and possibly biased.
+Cross-matching DBLP publications to records in the Scopus, abstract and citation database of peer-reviewed literature, enabled us to harvest the richer links in Scopus as well as extract links to publications from other disciplines.
+This cross-matching also allows the use of both journal and article based classifications when clustering documents.
+Using both direct citations and co-citations as the basis for clustering, we used DBLP articles from journals and conference proceedings for the period 1996-2015.
+We reconciled these clusters with the All Science Journal Classification (ASJC) developed and maintained by Scopus through a combination of automated and manual procedures.
 The process of selection and matching resulted in a dataset of 2,685,356 publications (Materials and Methods).
-Of these roughly 2.8 million publications, approximately 2.07 million were classified as COMP under subject area and assigned ASJC codes corresponding to Computer Science (major subject area and 13 minos subject areas), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (1).
-The set of 2.07 million publications classified as COMP in Scopus spanned all 13 minor subject areas with Software 30.3\% being the largest component and Computer Science (miscellaneous) 0.9\% the smallest.
-The number of minor subject areas assigned to a publication averaged to 1.75 with 53\% of the publications being assigned to one minor subject area and 0.0003\% assigned to 7 different minor subject areas (Table 1).
+
+Of these roughly 2.8 million publications, approximately 2.07 million were classified as COMP under subject area and assigned ASJC codes corresponding to Computer Science (major subject area with 13 minor subject areas (Table~\ref{tab:comp}), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (Figure~\ref{fig:ar_cp_annotation}).
+
+The set of 2.07 million publications classified as COMP in Scopus spanned all 13 minor subject areas with Software 30.3\% being the largest component and Computer Science (miscellaneous) 0.9\% the smallest (Table~\ref{tab:comp}).
+The number of minor subject areas assigned to a publication averaged to 1.75 with 53\% of the publications being assigned to one minor subject area and 0.0003\% assigned to 7 different minor subject areas.
 
@@
 
-\subsection{Clustering by Direct Citation} [Need a sentence about why we're clustering].
-Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation with an argument being made for direct citation as the best approach to concentrate citation links~\cite{klavans_which_2017}.
+\subsection{Clustering by Direct Citation} Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation with direct citation being proposed as as the best approach to concentrate citation links~\cite{klavans_which_2017}.
 Accordingly, we first used direct citation links as the basis for cluster formation.
 A set of 20 clusters was generated using Graclus, a spectral clustering technique that has previously been applied to citation data~\cite{graclus_2007,subelj_clustering_2016}.
-\textcolor{blue}{
-Considering the caveats associated with generating \emph{comp}, namely, the coverage limitations of the DBLP dataset (ii) cross-matching to Scopus (iii) journal based classification (iv) clustering, }
-we constructed article level clusters of this computer science dataset at a sufficiently high level of aggregation to avoid cognitive challenge and cross-matched them to disciplinary classification by journal, the Scopus ASJC classification.
+We constructed article level clusters of this computer science dataset at a sufficiently high level of aggregation to avoid cognitive challenge and cross-matched them to disciplinary classification by journal, the Scopus ASJC classification.
 To focus on relatively high signal, we only considered Scopus ASJC minor subject area categories that accounted for at least 15\% of the publications in each cluster.
 
-Figure~\ref{fig:heatmap} permits examination of these data from two perspectives: (i) the clusters that map to a given ASJC minor subject area and (ii) ASJC minor subject areas that comprised at least 15\% of the publication in a cluster.
+Figure~\ref{fig:heatmap} permits examination of these data from two perspectives: (i) ASJC minor subject areas that comprised at least 15\% of the publication in a cluster (ii) the clusters that map to a given ASJC minor subject area.
 Under these conditions, 31 of the 334 ASJC minor subject areas are represented.
@@
 From the other perspective, cluster 17 was the most diverse and contained publications annotated with 8 minor subject area labels, of which Biochemistry, Chemistry(all), Genetics, and Molecular Biology were the most distant from computer science while Statistics \& Probability, Computational Theory \& Mathematics, and Computational Mathematics are closer.
-These data suggest that areas central to computer science in 2019 (Salton and Bergmark's triad) are more likely to be found in multiple clusters (hardware, software, and theory), and that biology, chemistry, and statistics are the most proximal to computer science.
-[What about mathematics?]  A second inference is that, in a few cases journal-based classification and article clusters are tightly related in terms of article content (Hardware and Architecture).
+These data suggest that areas central to computer science in 2019 (Salton and Bergmark's historical triad of hardware, software, and theory) are more likely to be found in multiple clusters, whereas, biology, chemistry, and statistics are more restricted in distribution.
+A second inference is that, in a few cases journal-based classification and article clusters are tightly related in terms of article content (Hardware and Architecture).
 Thirdly, that some areas of computer science are relatively ubiquitous, e.g.
@@
 Further, the top cited papers often derived from biology and we were concerned that this small sample (top cited papers) were not representative of the cluster.
-[Overall conclusions of Graclus based clustering?]
+Similar challenges inherent in labeling citation clusters at a high level of aggregation have also been noted~\cite{waltman_new_2012}.
 
-\subsection{Clustering by Co-citation.} [Sentence justifying co-citation base clustering]
-
+\subsection{Clustering by Co-citation.} Co-citation was first described independently by Small and Marshakova in 1973~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}, and provides insight into the emergence of new ideas derived from the association of previously independent ones.
+Co-citation thus provides some degree of evolutionary insight and has been used for clustering publications~\cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
 As described in Methods, we performed 600 iterations of agglomerative clustering to the 10,298 clusters.
@@
 2,685,356 publications from DBLP were cross-matched with Scopus and then grouped by the 27 major subject areas in the ASJC (Scopus) classification.
-The largest number of publications are contributed by Computer Science; Mathematics; and Engineering and then by Social Sciences; Physics and Astronomy; and Biochemistry, Genetics, and Molecular Biology.
+The largest number of publications are contributed by Computer Science; Engineering; Mathematics; and then by Social Sciences; Decision Sciences; Physics and Astronomy; Medicine; and Biochemistry, Genetics, and Molecular Biology.
 Publications were further annotated with respect to being either articles \emph{(ar)} or conference proceedings \emph{(cp)}.
-For this dataset, the major subject area of Computer Science with 1,194,623(cp) \& 879,396 contributed the most publications while Nursing with 69 (cp) \& 756 (ar)) contributed the least.}
+For this dataset, the major subject area of Computer Science with 1,194,623(cp) \& 879,396 contributed the most publications while Dentistry with 0 (cp) \& 1 (ar)) contributed the least.}
 \label{fig:ar_cp_annotation}       % Give a unique label
@@
 In this schematic, five rounds are adequate for the process to run to completion.}
-\label{vlc_process}       % Give a unique label
+\label{fig:vlc_process}       % Give a unique label
 \end{figure}
@@
 2685021 is because of inner joins on ASJC Explain conductance calculations~\cite{shun_parallel_2016}}}
-\label{tab:1}       
+\label{tab:comp}       
 \begin{tabular}{lrccc}
@@
 2685021 is because of inner joins on ASJC Explain conductance calculations~\cite{shun_parallel_2016}}}
-\label{tab:1}       
+\label{tab:graclus}       
 \begin{tabular}{lrccc}

### 2019-12-13 Scientometrics/comp.tex
update
updated script, reordered figures

@@
 
-Figure~\ref{fig:heatmap} permits examination of these data from two perspectives: (i) ASJC minor subject areas that comprised at least 15\% of the publication in a cluster (ii) the clusters that map to a given ASJC minor subject area.
-Under these conditions, 31 of the 334 ASJC minor subject areas are represented.
-Unsurprisingly, the broad category Computer Science Applications was present in 16 of 20 clusters, followed by Software in 12 clusters, and Electrical and Electronic Engineering in 10 clusters.
+Figure~\ref{fig:heatmap} permits examination of these data from two perspectives: (i) rows: the clusters that map to a given ASJC minor subject area (ii) columns: ASJC minor subject areas that comprised at least 15\% of the publication in a cluster.
+Under these conditions of clustering and a threshold of 15\%, 31 of the 334 ASJC minor subject areas are represented.
+Unsurprisingly, the broad categories Computer Science Applications, Software, and Electrical and Electronic Engineering are seen in 17, 12, and 10 clusters respectively while Artificial Intelligence mapped to 7 different clusters.
+At the other end of the range, 12 of the 31 ASJC minor subject areas were each detected in a single cluster.
 
-From the other perspective, cluster 17 was the most diverse and contained publications annotated with 8 minor subject area labels, of which Biochemistry, Chemistry(all), Genetics, and Molecular Biology were the most distant from computer science while Statistics \& Probability, Computational Theory \& Mathematics, and Computational Mathematics are closer.
-These data suggest that areas central to computer science in 2019 (Salton and Bergmark's historical triad of hardware, software, and theory) are more likely to be found in multiple clusters, whereas, biology, chemistry, and statistics are more restricted in distribution.
-A second inference is that, in a few cases journal-based classification and article clusters are tightly related in terms of article content (Hardware and Architecture).
+From the alternate perspective (columns), cluster 17 was the most diverse and contained publications annotated with 8 minor subject area labels: Biochemistry, Chemistry(all), Genetics, Molecular Biology,  Statistics \& Probability, Computational Theory \& Mathematics, and Computational Mathematics.
+Cluster 19 mapped to two areas but was excluded from qualitative analysis because of its high conductance value.
+Of the remaining clusters, the third (Cluster 2) represents interactions between the minor subject areas Theoretical Computer Science, Discrete Mathematics and Combinatorics, and Applied Mathematics as well as the more generic Computer Science (all).
+Clusters 3 and 4 include Computer Networks and Communications and Cluster 18 (Artificial intelligence, Cognitive neuroscience, and Neurology) and clusters 5-9 include Management Science, Operations Research, Information Systems, Modeling and Simulation, and Human Computer Interaction.
+
+To us, these data suggest that areas central to computer science in 2019 (Salton and Bergmark's historical triad of hardware, software, and theory) are more likely to be found in multiple clusters, whereas areas such as biology, chemistry, and statistics are more restricted in distribution.
+A second inference is that, in some cases journal-based classification and our article clusters are similar in terms of article content (Hardware and Architecture).
 Thirdly, that some areas of computer science are relatively ubiquitous, e.g.
 computer applications.
-Last, that interactions with fields outside computer science are restricted to a single cluster or small numbers of clusters, e.g., cluster 17 (ibid) and cluster 18 (artificial intelligence, cognitive neuroscience, and neurology).
+Lastly, that interactions with fields outside computer science are restricted to a single cluster or small numbers of clusters, e.g., cluster 17  and cluster 18.
 
 We also attempted to map these 20 clusters assembled through direct citation to the CCS classification by manually matching the top 25-50 most heavily cited publications in each cluster to corresponding categories in the CCS.
-This was feasible in some cases, clusters 0 and 1 mapped reasonably well to the top level categories Hardware and Computer Systems Organization but less so in the cases of other clusters.
-Further, the top cited papers often derived from biology and we were concerned that this small sample (top cited papers) were not representative of the cluster.
-Similar challenges inherent in labeling citation clusters at a high level of aggregation have also been noted~\cite{waltman_new_2012}.
+This was feasible in some cases, clusters 0 and 1 mapped reasonably well to the top level categories Hardware and Computer Systems Organization but much less so in the cases of other clusters.
+Further, the top cited papers often derived from biology and we were concerned that they were not representative of the cluster.
+The challenges inherent in labeling citation clusters at a high level of aggregation have been previously noted~\cite{waltman_new_2012}.
+
+[closing sentence necessary?]
 
@@
 Co-citation thus provides some degree of evolutionary insight and has been used for clustering publications~\cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
-As described in Methods, we performed 600 iterations of agglomerative clustering to the 10,298 clusters.
-To focus on major clusters, we restricted agglomeration to clusters containing at least 10 nodes, which resulted in 666 clusters.
+Unlike, clustering by direct citation using Graclus, which preserves all publications in \emph{comp}, the process of clustering by co-citation is progressively selective.
+As described in Methods, we first identified the top 10\% most-cited articles in the `\emph{comp} dataset and then documented all co-cited pairs of their cited references that were also elements of \emph{comp}.
+The frequency of co-citation was then computed across Scopus \emph{comp} and normalized using Salton's correction.
+These data were then represented as a graph where each node was a publication and each edge, the normalized co-citation frequency of a co-cited pair.
+To cluster, we performed variable level clustering (VLC) followed by agglomerative clustering of the clusters resultant from VLC.
+To focus on major clusters, we also restricted agglomeration to clusters containing at least 10 nodes, which resulted in 666 clusters.
 Further agglomeration resulted in the development of a single large cluster (Fig~\ref{fig:merge_select}).
 Consequently, the 20 largest clusters were used for further analysis and comparison with clusters generated by direct citation.
-The largest of these 20 clusters contained 1,276 nodes and the smallest contained 136.
+The largest of these 20 clusters contained 1,276 nodes and the smallest contained 136, with total nodes summing to 8,042.
 
@@
 \begin{figure}[ht]
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.45]{scopus_dblp_graclus3.pdf}
+% figure caption is below the figure
+\caption{Heat map for the clustering obtained by direct citation. The  y-axis (rows) correspond to topics, defined by Scopus characterizations, and the
+x-axis (columns) represent the 20 different clusters.  
+Each cluster is characterized by topics that label at least 10\% of the publications in the cluster.
+ }
+\label{fig:heatmap}       % Give a unique label
+\end{figure}
+
+\begin{figure}[ht]
 \centering
@@
 \end{figure}
-
-\newpage
-
 \newpage
@@
 % For example, with the graphicx package use
-  \includegraphics[scale=0.45]{scopus_dblp_graclus3.pdf}
-% figure caption is below the figure
-\caption{Heat map for the clustering obtained by direct citation. The  y-axis (rows) correspond to topics, defined by Scopus characterizations, and the
-x-axis (columns) represent the 20 different clusters.  
-Each cluster is characterized by topics that label at least 10\% of the publications in the cluster.
- }
-\label{fig:heatmap}       % Give a unique label
-\end{figure}
-
-\begin{figure}[ht]
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
   \includegraphics[scale=0.45]{scopus_dblp_heatmap3.pdf}
@@
 \end{figure}
+\newpage
+
 \newpage

### 2019-12-16 Scientometrics/comp.tex
update

@@
 
-\title{Citation Analysis of Computer Science Publications}
+\title{Computer Science, Vignettes, and Citation Analysis}
 %\thanks{Grants or other notes
@@
 %placed here. General acknowledgments should be placed at the end of the article.}
-\subtitle{Relationship To Other Fields}
+\subtitle{Salton and Bergmark Redux}
 %\titlerunning{Short form of title}        % if too long for running head
@@
 
+\begin{itemize}
+\item understanding structure of communications within a field and with adjacent fields
+\item extending Salton and Bergmark and staying high-level
+\item combining article level and journal level 
+\item two clustering methods
+\item Graclus- all inclusive, unweighted edges
+\item Co-citations, highly selective and weighted edges
+\item intersection of Graclus and co-citation
+\item close out
+\end{itemize}
+
 \keywords{Bibliometrics \and Clustering \and Research Evaluation \and Computer Science}
@@
 Other classification systems are available such as the All Science Journal Classification (ASJC) developed and maintained by Scopus, the Web of Science research and categorical classifications from Clarivate Analytics, and the NSF classification system~\cite{nsf_classification} [add citations for Scopus and Web of Science].
-All three rely on applying one or more journal-derived labels to articles.
-A natural consequence is limited specificity at the article level.
-
-Scopus and the Web of Science also include comprehensive bibliographies with citation links and proprietary unique identifiers for publications, some of which can be matched to digital object identifiers (DOIs).
-However, Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science, that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
+Scopus and the Web of Science also include comprehensive bibliographies with citation links and proprietary unique identifiers for publications.
+All three systems rely on applying one or more journal-derived labels to articles.
+A logical prediction, given the diversity of articles within journals, is limited specificity at the article level.
+Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science, that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
 Others have also discussed and critiqued disciplinary assignments using journal based classifications~\cite{wang_large-scale_2016,perianes-rodriguez_comparison_2017}.
@@
 We have previously parsed the Scopus dataset of over 72,000,000 publications into a custom schema as part of implementing a larger data platform for research evaluation~\cite{GithubERNIE2019}.
+The total number of publications in Scopus that are labeled COMP with major subject area of Computer Science is 5,835,160.
 Records in the DBLP dataset were matched to Scopus identifiers using digital object identifiers (DOIs).
@@
 Under these conditions of clustering and a threshold of 15\%, 31 of the 334 ASJC minor subject areas are represented.
-Unsurprisingly, the broad categories Computer Science Applications, Software, and Electrical and Electronic Engineering are seen in 17, 12, and 10 clusters respectively while Artificial Intelligence mapped to 7 different clusters.
+Unsurprisingly, the broad categories Computer Science Applications, Software, and Electrical and Electronic Engineering register in 16, 12, and 10 clusters respectively while Artificial Intelligence mapped to 7 different clusters.
 At the other end of the range, 12 of the 31 ASJC minor subject areas were each detected in a single cluster.
@@
 A second inference is that, in some cases journal-based classification and our article clusters are similar in terms of article content (Hardware and Architecture).
-Thirdly, that some areas of computer science are relatively ubiquitous, e.g.
-computer applications.
-Lastly, that interactions with fields outside computer science are restricted to a single cluster or small numbers of clusters, e.g., cluster 17  and cluster 18.
+Thirdly, that the ASJC minor subject area, computer applications is relatively non-specific, and publications thus labeled are near ubiquitous (16/20).
+Fourthly, that for the DBLP dataset, interactions with fields outside computer science are restricted to a single cluster or small numbers of clusters, e.g., cluster 17  and cluster 18.
 
-We also attempted to map these 20 clusters assembled through direct citation to the CCS classification by manually matching the top 25-50 most heavily cited publications in each cluster to corresponding categories in the CCS.
+We also explored mapping these 20 clusters assembled through direct citation to the CCS classification by manually matching the top 25-50 most heavily cited publications in each cluster to corresponding categories in the CCS.
 This was feasible in some cases, clusters 0 and 1 mapped reasonably well to the top level categories Hardware and Computer Systems Organization but much less so in the cases of other clusters.
@@
 
-\subsection{Clustering by Co-citation.} Co-citation was first described independently by Small and Marshakova in 1973~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}, and provides insight into the emergence of new ideas derived from the association of previously independent ones.
+\subsection{Clustering by Co-citation.} For an alternate examination of the data, we used co-citation frequencies to cluster the DBLP dataset.
+Unlike clustering by direct citation with Graclus, where every input publication is assigned to a cluster and every citation is weighted equally, clustering by co-citation is progressively selective, involves assigning weights to co-citations, and also accounts for weak inter-cluster interactions.
+
+Co-citation was first described independently by Small and Marshakova in 1973~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}, and provides insight into the emergence of new ideas derived from the association of previously independent ones.
 Co-citation thus provides some degree of evolutionary insight and has been used for clustering publications~\cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
-Unlike, clustering by direct citation using Graclus, which preserves all publications in \emph{comp}, the process of clustering by co-citation is progressively selective.
-As described in Methods, we first identified the top 10\% most-cited articles in the `\emph{comp} dataset and then documented all co-cited pairs of their cited references that were also elements of \emph{comp}.
-The frequency of co-citation was then computed across Scopus \emph{comp} and normalized using Salton's correction.
-These data were then represented as a graph where each node was a publication and each edge, the normalized co-citation frequency of a co-cited pair.
-To cluster, we performed variable level clustering (VLC) followed by agglomerative clustering of the clusters resultant from VLC.
-To focus on major clusters, we also restricted agglomeration to clusters containing at least 10 nodes, which resulted in 666 clusters.
-Further agglomeration resulted in the development of a single large cluster (Fig~\ref{fig:merge_select}).
+
+As described in Methods, we first identified the top 10\% most-cited articles in the \emph{comp} dataset and then documented all co-cited pairs of their cited references that were also elements of \emph{comp}.
+The frequency of co-citation was then computed across all records in Scopus and normalized using Salton's correction.
+These co-cited pairs and the normalized co-citation frequencies were then represented as a graph where each node was a publication and each edge represented a co-citation, weighted by the normalized co-citation frequency.
+
+For clustering, we applied variable level clustering (VLC) followed by 600 iterations of agglomeration of the clusters resultant from VLC since further rounds of agglomeration resulted in the development of a single large cluster (Fig~\ref{fig:merge_select}).
+To focus on major clusters, we also restricted agglomeration to clusters containing at least 10 nodes.
 Consequently, the 20 largest clusters were used for further analysis and comparison with clusters generated by direct citation.
@@
 
-[Overall conclusions of cocitation based clustering]
+Fig~\ref{fig:heatmap_cocit} shows a heatmap in which clusters constructed by co-citation are mapped to Scopus ASJC minor subject areas.
+Mappings are only shown if they account for at least 15\% of the publications in a cluster.
+Unlike the earlier figure [insert figure reference] Unlike the case of clustering by direct citation, no cluster maps to more than three ASJC minor subject areas.
+We have to decide what to say about this figure but I think it suggests intra-cluster relationships for the most part.
 
@@
 x-axis (columns) represent the 20 different clusters.  
-Each cluster is characterized by topics that label at least 10\% of the publications in the cluster.
+Each cluster is characterized by topics that label at least 15\% of the publications in the cluster.
  }
@@
 x-axis (columns) represent the 20 different clusters.  
-Each cluster is characterized by topics that label at least 10\% of the publications in the cluster.
+Each cluster is characterized by topics that label at least 15\% of the publications in the cluster.
  }
-\label{fig:heatmap}       % Give a unique label
+\label{fig:heatmap_cocit}       % Give a unique label
 \end{figure}

### 2019-12-16 Scientometrics/comp.tex
lots of changes through results, nothing changed in discussion

@@
 
-Computer science, and its applications, has experienced rapid growth and diversification over the last twenty years.
+Computer science and its applications have experienced rapid growth and diversification over the last twenty years.
 As observed in a 2017 US National Academies Report, ``A wide range of jobs in virtually all sectors demand computing skills to an unprecedented extent.
@@
 
-Noting that that the scientific literature serves a rich source of information to study the structure and historical development of a field, Salton and Bergmark conducted a historical study  of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles)~\cite{salton_citation_1979}.
+Noting that that the scientific literature serves a rich source of information to study the structure and historical development of a field, 
+Salton and Bergmark conducted a historical study  in 1979 of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles)~\cite{salton_citation_1979}.
 These authors described the global structure of computer science as comprising three main areas (i) theoretical foundations, such as theory of computation, (ii) hardware and computer systems, such as architecture,  and (iii) software, such as programming systems.
-Related areas noted were (a) mathematics of computing, such as numerical analysis, (b) special software topics, such as operating systems, (c) data management and database systems, (d) methodologies valid for multiple applications, such as algebraic manipulation, (e) computer applications, such as computer graphics, (f) non-technical aspects, such as computer education.
+Related areas noted were (a) mathematics of computing, such as numerical analysis, (b) special software topics, such as operating systems, (c) data management and database systems, (d) methodologies valid for multiple applications, such as algebraic manipulation, (e) computer applications, such as computer graphics, and  (f) non-technical aspects, such as computer education.
 
@@
 This classification also addresses relationships with other fields under the category of Applied Computing.
-However, an easy way to map scientific publications to the CCS, especially interdisciplinary articles or those from proximal fields does not seem to be available.
+However, an easy way to map scientific publications to the CCS, especially interdisciplinary articles or those from proximal fields, does not seem to be available.
 
@@
 A logical prediction, given the diversity of articles within journals, is limited specificity at the article level. 
-Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science, that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
-Others have also discussed and critiqued disciplinary assignments using journal based classifications~\cite{wang_large-scale_2016,perianes-rodriguez_comparison_2017}.
-Article classification systems have been constructed, which escape some of the criticisms of journal-based classification~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012} but seem to be in the research domain rather than the domain of practical use [need to check on this].[May need another bridging sentence to the next paragraph].
+Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
+Others have also discussed and critiqued disciplinary assignments using journal-based classifications~\cite{wang_large-scale_2016,perianes-rodriguez_comparison_2017}. 
+Article classification systems have been constructed that escape some of the criticisms of journal-based classification~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012}, but seem to be in the research domain rather than the domain of practical use [need to check on this].[May need another bridging sentence to the next paragraph].
 
@@
 \label{sec:methods}
+
+ \subsection{Overview}
+ In our study of the structure of a twenty year cohort of the computer science literature, we chose to use both traditional journal-based and article-based approaches.
+Considering that traditional disciplines `may only partly reflect the actual organization of today's scientific research'~\cite{waltman_new_2012}, we constructed article clusters at high levels of aggregation using citations to examine the \emph{comp} dataset and mapped these clusters to journal-based categories.
+ Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation with direct citation being proposed as as the best approach to concentrate citation links~\cite{klavans_which_2017}.
+Accordingly, we used direct citation links as the basis for cluster formation, and also co-citation to obtain an alternative view.
+
+For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography that (i) had a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography.
+Our underlying assumption is that records in DBLP are greatly enriched for computer science even while recognizing that coverage may be incomplete and possibly biased.
+Cross-matching DBLP publications to records in the Scopus, abstract and citation database of peer-reviewed literature, enabled us to harvest the richer links in Scopus as well as extract links to publications from other disciplines.
+This cross-matching also allows the use of both journal and article based classifications when clustering documents.
+Using both direct citations and co-citations as the basis for clustering, we used DBLP articles from journals and conference proceedings for the period 1996-2015.
+We reconciled these clusters with the All Science Journal Classification (ASJC) developed and maintained by Scopus through a combination of automated and manual procedures, producing a dataset of  2,685,356 publications.
 
@@
 
-\subsection{Clustering methods} In applying both clustering by direct citation and by co-citation, we attempted to consider, wherever possible, the criteria articulated by \v{S}ubelj, van Eck, and Waltman~\cite{subelj_clustering_2016}, of (i) Cluster sizes- the largest cluster should be no more than 10 times the smallest one (ii) Small clusters- should be eliminated (iii) Clustering stability- small changes and replicates should yield similar results (iv) Computing time- minimized where possible (v) Intuitive sensibility- determined by qualitative examination.
+\subsection{Clustering methods} In applying both clustering by direct citation and by co-citation, we attempted to consider, wherever possible, the criteria articulated by \v{S}ubelj, van Eck, and Waltman~\cite{subelj_clustering_2016}, of (i) the largest cluster should be no more than 10 times the smallest one, (ii) small clusters should be eliminated, (iii) small changes and replicates should yield similar results (``stability"),  (iv) computing time should be minimized where possible, and (v) the clustering should seem reasonable on a qualitative level (``intuitive sensibility").
 
-\paragraph{Clustering by Direct Citation.} Graclus is a spectral graph clustering package that computes normalized cut and ratio association for a given undirected graph~\cite{graclus_2007}.
+\paragraph{Clustering by Direct Citation.} Graclus~\cite{graclus_2007} is a spectral graph clustering package that optimizes  various clustering criteria, including normalized cut, ratio cut, and ratio association, that has previously been applied to citation data~\cite{subelj_clustering_2016}.
 We used v1.2 in our experiments. 
@@
 At around 20 clusters, clusters size was relatively stable with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{subelj_clustering_2016}.
-Consequently, we generated 20 clusters, labeled 0-19, using Graclus (Table~\ref{tab:graclus}).
+Consequently, we used Graclus to generate 20 clusters, labeled 0-19 (Table~\ref{tab:graclus}).
 
 We also used conductance, as defined in Shun et al.~\cite{shun_parallel_2016}, to  evaluate clustering (smaller is better), noting that conductance has been found to be ``the stand-alone quality metric that best indicates performance on information recovery metrics" \cite{emmons2016analysis}.
-Data from \emph{comp} were clustered into 18, 20, or 22 clusters and in each case the highest numbered cluster (17, 19, or 21) had the greatest conductance value and the smallest number of nodes, suggesting that it effectively served as a container for `left over publications' during the Graclus process.
-Thus, we limited our consideration of cluster 19 (the 20th cluster), also the smallest cluster, when interpreting results.
-The remaining 19 clusters had conductance values ranging from 0.09 to 0.25 with a median conductance of 0.15, Figure~\ref{fig:graclus_comparison_conductance}, Table~\ref{tab:comp}.
+%Tandy, George - add reference to Zaki paper as well
+In our analysis, we saw that the last cluster (cluster 19) had a much larger conductance value than the other clusters and also had the smallest
+number of nodes.
+We then examined
+results obtained using Graclus with two other numbers of clusters (18 and 22), and
+in each case, the highest numbered cluster  had the greatest conductance value and also the smallest number of nodes.
+These results suggest that Graclus produces a final cluster that effectively serves as a container for `left over publications' during the clustering procedure. 
+Therefore, we limited our consideration of cluster 19 (the final of the twenty clusters)  when interpreting results.
+The remaining 19 clusters had conductance values ranging from 0.09 to 0.25 with a median conductance of 0.15 (Fig.~\ref{fig:graclus_comparison_conductance}, Table~\ref{tab:comp}).
 
 \paragraph{Clustering by Co-Citation.}
+\textcolor{blue}{Check the next paragraphs for repetitiveness.}
+
 For an alternate view of these DBLP data we constructed clusters using co-citation, the frequency with which a pair of articles is cited by other articles. 
-To cluster by co-citation, we used a modification of variable level clustering combined with agglomerative clustering, an approach developed in 1985 by Small and Sweeney~\cite{small_clustering_1985}.
+Unlike clustering by direct citation with Graclus, where every input publication is assigned to a cluster and every citation is weighted equally, clustering by co-citation is progressively selective, involves assigning weights to co-citations, and also accounts for weak inter-cluster interactions.
+
+Co-citation was first described independently by Small and Marshakova in 1973~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}, and provides insight into the emergence of new ideas derived from the association of previously independent ones.
+Co-citation thus provides some degree of evolutionary insight and has been used for clustering publications~\cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
+
+We first identified the top 10\% most-cited articles in the \emph{comp} dataset and then documented all co-cited pairs of their cited references that were also elements of \emph{comp}.
+The frequency of co-citation was then computed across all records in Scopus and normalized using Salton's correction.
+These co-cited pairs and the normalized co-citation frequencies were then represented as a graph where each node was a publication and each edge represented a co-citation, weighted by the normalized co-citation frequency.
+
+%For clustering, we applied a variant of variable level clustering (VLC, described below) followed by 600 iterations of agglomeration of the clusters resultant from VLC since further rounds of agglomeration resulted in the development of a single large cluster (Fig.~\ref{fig:merge_select}).
+To focus on major clusters, we also restricted agglomeration to clusters containing at least 10 nodes.
+Consequently, the 20 largest clusters were used for further analysis and comparison with clusters generated by direct citation.
+The largest of these 20 clusters contained 1,276 nodes and the smallest contained 136, with total nodes summing to 8,042.
+
+We used a modification of variable level clustering combined with agglomerative clustering, an approach developed in 1985 by Small and Sweeney~\cite{small_clustering_1985}.
 Variable level clustering involves applying a threshold (below which all edges in a graph are deleted) then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn.
@@
 
-In our implementation of variable level clustering, Figure~\ref{fig:vlc_process}, we first calculated the number of citations accumulated across Scopus for all 2,685,356 articles in \emph{comp}.
-After discarding those publications without any citations, we restricted further analysis to highly cited articles, those in the 90th percentile of citations or higher, resulting in a dataset of size 212,311.
+In our implementation of variable level clustering (Fig.~\ref{fig:vlc_process}), we first calculated the number of citations accumulated across Scopus for all 2,685,356 articles in \emph{comp}.
+After discarding those publications without any citations, we restricted further analysis to highly cited articles--those in the 90th percentile of citations or higher--resulting in a dataset of size 212,311.
 We then identified 4,318,305 publications in Scopus that cite these 212,311 articles from \emph{comp}.
 For each of the 4,318,305 citing publications in turn, all possible ${n \choose 2}$ reference pairs were generated from a publication's cited references, where $n$ is the number of references in a publication.
-The cited reference pairs this generated, were then restricted to those in the set of 212,311 highly cited papers previously identified.
+The cited reference pairs this generated were then restricted to those in the set of 212,311 highly cited papers previously identified.
 The frequency of these co-cited pairs was then computed across the \emph{comp} dataset  and normalized using Salton's cosine formula~\cite{salton_citation_1979}.
@@
 Clusters containing only 2 nodes were discarded bringing the total number of clusters down to 10,298.
-The publications in these 10,298 clusters were overwhelmingly drawn from the Physical Sciences (one of the 4 top level categories in the Scopus ASJC classification), of which computer science is a sub-category, Figure~\ref{fig:cocitr_venn2}.
+The publications in these 10,298 clusters were overwhelmingly drawn from the Physical Sciences (one of the 4 top level categories in the Scopus ASJC classification), of which computer science is a sub-category (Fig.~\ref{fig:cocitr_venn2}).
 
@@
 
-In our study of the structure of a twenty year cohort of the computer science literature, we chose to use both traditional journal-based and article-based approaches.
-Considering that traditional disciplines, `may only partly reflect the actual organization of today’s scientific research'~\cite{waltman_new_2012}  we constructed article clusters at high levels of aggregation using citations in two different ways to examine the \emph{comp} dataset and mapped these clusters to journal-based categories.
-
-For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography that (i) had a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography.
-Our underlying assumption is that records in DBLP are greatly enriched for computer science even while recognizing that coverage may be incomplete and possibly biased.
-Cross-matching DBLP publications to records in the Scopus, abstract and citation database of peer-reviewed literature, enabled us to harvest the richer links in Scopus as well as extract links to publications from other disciplines.
-This cross-matching also allows the use of both journal and article based classifications when clustering documents.
-Using both direct citations and co-citations as the basis for clustering, we used DBLP articles from journals and conference proceedings for the period 1996-2015.
-We reconciled these clusters with the All Science Journal Classification (ASJC) developed and maintained by Scopus through a combination of automated and manual procedures.
+\subsection{Data}
 The process of selection and matching resulted in a dataset of 2,685,356 publications (Materials and Methods). 
-
-Of these roughly 2.8 million publications, approximately 2.07 million were classified as COMP under subject area and assigned ASJC codes corresponding to Computer Science (major subject area with 13 minor subject areas (Table~\ref{tab:comp}), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (Figure~\ref{fig:ar_cp_annotation}).
+Of these roughly 2.8 million publications, approximately 2.07 million were classified as COMP under subject area and assigned ASJC codes corresponding to Computer Science (major subject area with 13 minor subject areas (Table~\ref{tab:comp}), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (Fig.~\ref{fig:ar_cp_annotation}).
 
@@
 The number of minor subject areas assigned to a publication averaged to 1.75 with 53\% of the publications being assigned to one minor subject area and 0.0003\% assigned to 7 different minor subject areas.
-
-Thus, the sets of computer science publications in DBLP and Scopus are partially overlapping rather than DBLP being a perfect subset of Scopus.
+We note also that  the $4.8x10^6$ DBLP publications are only partially found in Scopus (which had a total of $5.8x10^6$ publications), using our methodology.
+%George, please consider revising this text
+%the sets of computer science publications in DBLP and Scopus are partially overlapping rather than DBLP being a perfect subset of Scopus.
 [the point being that we should justify our use of both journal and article level classifications].
 
-\subsection{Clustering by Direct Citation} Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation with direct citation being proposed as as the best approach to concentrate citation links~\cite{klavans_which_2017}.
-Accordingly, we first used direct citation links as the basis for cluster formation.
-A set of 20 clusters was generated using Graclus, a spectral clustering technique that has previously been applied to citation data~\cite{graclus_2007,subelj_clustering_2016}.
-We constructed article level clusters of this computer science dataset at a sufficiently high level of aggregation to avoid cognitive challenge and cross-matched them to disciplinary classification by journal, the Scopus ASJC classification.
+\subsection{Clustering by Direct Citation}
+
+We constructed article-level clusters of this computer science dataset at a sufficiently high level of aggregation to avoid cognitive challenge and cross-matched them to  the  Scopus ASJC classification.
 To focus on relatively high signal, we only considered Scopus ASJC minor subject area categories that accounted for at least 15\% of the publications in each cluster.
@@
 Under these conditions of clustering and a threshold of 15\%, 31 of the 334 ASJC minor subject areas are represented.
-Unsurprisingly, the broad categories Computer Science Applications, Software, and Electrical and Electronic Engineering register in 16, 12, and 10 clusters respectively while Artificial Intelligence mapped to 7 different clusters.
+Unsurprisingly, the broad categories Computer Science Applications, Software, and Electrical and Electronic Engineering register in 16, 12, and 10 clusters respectively, while Artificial Intelligence mapped to 7 different clusters.
 At the other end of the range, 12 of the 31 ASJC minor subject areas were each detected in a single cluster.
@@
 Of the remaining clusters, the third (Cluster 2) represents interactions between the minor subject areas Theoretical Computer Science, Discrete Mathematics and Combinatorics, and Applied Mathematics as well as the more generic Computer Science (all).
-Clusters 3 and 4 include Computer Networks and Communications and Cluster 18 (Artificial intelligence, Cognitive neuroscience, and Neurology) and clusters 5-9 include Management Science, Operations Research, Information Systems, Modeling and Simulation, and Human Computer Interaction.
+Clusters 3 and 4 include Computer Networks and Communications and Cluster 18 (Artificial Intelligence, Cognitive Neuroscience, and Neurology) and clusters 5--9 include Management Science, Operations Research, Information Systems, Modeling and Simulation, and Human-Computer Interaction.
 
-To us, these data suggest that areas central to computer science in 2019 (Salton and Bergmark's historical triad of hardware, software, and theory) are more likely to be found in multiple clusters, whereas areas such as biology, chemistry, and statistics are more restricted in distribution.
-A second inference is that, in some cases journal-based classification and our article clusters are similar in terms of article content (Hardware and Architecture).
-Thirdly, that the ASJC minor subject area, computer applications is relatively non-specific, and publications thus labeled are near ubiquitous (16/20).
-Fourthly, that for the DBLP dataset, interactions with fields outside computer science are restricted to a single cluster or small numbers of clusters, e.g., cluster 17  and cluster 18.
+These data suggest that areas central to computer science in 2019 (Salton and Bergmark's historical triad of hardware, software, and theory) are more likely to be found in multiple clusters than peripheral topics.
+%, whereas areas such as biology, chemistry, and statistics are more restricted in distribution.  
+A second inference is that, in some cases, journal-based classification and our article clusters are similar in terms of article content (Hardware and Architecture). 
+A third inference is that the ASJC minor subject area ``Computer Applications" is relatively non-specific, and publications thus labeled are nearly ubiquitous (16/20).
+Finally,   for the DBLP dataset, interactions with fields outside computer science (e.g., Biochemistry)  are  typically restricted to a single cluster or found in a small number of clusters.
 
-We also explored mapping these 20 clusters assembled through direct citation to the CCS classification by manually matching the top 25-50 most heavily cited publications in each cluster to corresponding categories in the CCS.
-This was feasible in some cases, clusters 0 and 1 mapped reasonably well to the top level categories Hardware and Computer Systems Organization but much less so in the cases of other clusters.
-Further, the top cited papers often derived from biology and we were concerned that they were not representative of the cluster.
-The challenges inherent in labeling citation clusters at a high level of aggregation have been previously noted~\cite{waltman_new_2012}.
-
-[closing sentence necessary?]
+We also note that these clusters cannot be adequately characterized by using a single CCS classification, a challenge that has been previously noted \cite{waltman_new_2012}.
+For example, we
+manually matched the top 25--50 most heavily cited publications in each cluster to corresponding categories in the CCS.
+This was feasible in some cases, but not in all.
+For example, clusters 0 and 1 mapped reasonably well to the top level categories Hardware and Computer Systems Organization,  but
+the top cited papers often derived from biology and yet biology was clearly not  representative of all of these affected clusters.
 
 \subsection{Clustering by Co-citation.} For an alternate examination of the data, we used co-citation frequencies to cluster the DBLP dataset. 
-Unlike clustering by direct citation with Graclus, where every input publication is assigned to a cluster and every citation is weighted equally, clustering by co-citation is progressively selective, involves assigning weights to co-citations, and also accounts for weak inter-cluster interactions.
-
-Co-citation was first described independently by Small and Marshakova in 1973~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}, and provides insight into the emergence of new ideas derived from the association of previously independent ones.
-Co-citation thus provides some degree of evolutionary insight and has been used for clustering publications~\cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
-
-As described in Methods, we first identified the top 10\% most-cited articles in the \emph{comp} dataset and then documented all co-cited pairs of their cited references that were also elements of \emph{comp}.
-The frequency of co-citation was then computed across all records in Scopus and normalized using Salton's correction.
-These co-cited pairs and the normalized co-citation frequencies were then represented as a graph where each node was a publication and each edge represented a co-citation, weighted by the normalized co-citation frequency.
-
-For clustering, we applied variable level clustering (VLC) followed by 600 iterations of agglomeration of the clusters resultant from VLC since further rounds of agglomeration resulted in the development of a single large cluster (Fig~\ref{fig:merge_select}).
-To focus on major clusters, we also restricted agglomeration to clusters containing at least 10 nodes.
-Consequently, the 20 largest clusters were used for further analysis and comparison with clusters generated by direct citation.
-The largest of these 20 clusters contained 1,276 nodes and the smallest contained 136, with total nodes summing to 8,042.
-
-Fig~\ref{fig:heatmap_cocit} shows a heatmap in which clusters constructed by co-citation are mapped to Scopus ASJC minor subject areas.
+Figure \ref{fig:heatmap_cocit} shows a heatmap in which clusters constructed by co-citation are mapped to Scopus ASJC minor subject areas.
 Mappings are only shown if they account for at least 15\% of the publications in a cluster.
+\textcolor{blue}{
 Unlike the earlier figure [insert figure reference] Unlike the case of clustering by direct citation, no cluster maps to more than three ASJC minor subject areas.
 We have to decide what to say about this figure but I think it suggests intra-cluster relationships for the most part.
+}
 

### 2019-12-17 Scientometrics/comp.tex
added more text

@@
 
-\title{Computer Science, Vignettes, and Citation Analysis}
+\title{A Vignetted View of Computer Science through Citation Analysis}
 %\thanks{Grants or other notes
@@
 Others have also discussed and critiqued disciplinary assignments using journal-based classifications~\cite{wang_large-scale_2016,perianes-rodriguez_comparison_2017}. 
-Article classification systems have been constructed that escape some of the criticisms of journal-based classification~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012}, but seem to be in the research domain rather than the domain of practical use [need to check on this].[May need another bridging sentence to the next paragraph].
+Article classification systems have been constructed that escape some of the criticisms of journal-based classification~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012}, but do not enjoy widespread use.
+[Add reference to Scandinavian paper in QSS].
 
-In this study, we combine article and journal level approaches to extend the work of Salton and Bergmark to present trends in computer science, while considering connections to other fields.
+In this study, we extend the work of Salton and Bergmark by combining article and journal approaches to study trends in computer science, while also considering connections to other fields.
 As a source of computer science literature, we used DBLP, a reference bibliography for computer science~\cite{dblp_ref}.
 The DBLP bibliography covers publications from computer science and includes publications from hybrid fields, where they are considered pertinent to computer science research.
-
 We describe below the high-level interactions of computer science within the Physical Sciences, and with the Social Sciences, Life Sciences, and Health Sciences [What did we find?
@@
 Cross-matching DBLP publications to records in the Scopus, abstract and citation database of peer-reviewed literature, enabled us to harvest the richer links in Scopus as well as extract links to publications from other disciplines.
-This cross-matching also allows the use of both journal and article based classifications when clustering documents.
+This cross-matching to Scopus, also allows the use of both journal and article based classifications when clustering documents.
 Using both direct citations and co-citations as the basis for clustering, we used DBLP articles from journals and conference proceedings for the period 1996-2015.
@@
 Publications were parsed from the XML source file and loaded into a PostgreSQL database.
-We have previously parsed the Scopus dataset of over 72,000,000 publications into a custom schema as part of implementing a larger data platform for research evaluation~\cite{GithubERNIE2019}.
+We have previously parsed the Scopus dataset, presently at over 87.8 million publications, into a custom schema as part of implementing a larger data platform for research evaluation~\cite{GithubERNIE2019}.
 The total number of publications in Scopus that are labeled COMP with major subject area of Computer Science is 5,835,160.
@@
 
-We also used conductance, as defined in Shun et al.~\cite{shun_parallel_2016}, to  evaluate clustering (smaller is better), noting that conductance has been found to be ``the stand-alone quality metric that best indicates performance on information recovery metrics" \cite{emmons2016analysis}.
+We also used conductance, as defined in Shun et al.~\cite{shun_parallel_2016}, to  evaluate clustering by direct citation (smaller is better), noting that conductance has been found to be a good metric for this purpose~\cite{emmons2016analysis,almeida_2012}.
 %Tandy, George - add reference to Zaki paper as well
@@
 \paragraph{Clustering by Co-Citation.}
-\textcolor{blue}{Check the next paragraphs for repetitiveness.}
 
-For an alternate view of these DBLP data we constructed clusters using co-citation, the frequency with which a pair of articles is cited by other articles. 
-Unlike clustering by direct citation with Graclus, where every input publication is assigned to a cluster and every citation is weighted equally, clustering by co-citation is progressively selective, involves assigning weights to co-citations, and also accounts for weak inter-cluster interactions.
-
-Co-citation was first described independently by Small and Marshakova in 1973~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}, and provides insight into the emergence of new ideas derived from the association of previously independent ones.
-Co-citation thus provides some degree of evolutionary insight and has been used for clustering publications~\cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
-
-We first identified the top 10\% most-cited articles in the \emph{comp} dataset and then documented all co-cited pairs of their cited references that were also elements of \emph{comp}.
-The frequency of co-citation was then computed across all records in Scopus and normalized using Salton's correction.
-These co-cited pairs and the normalized co-citation frequencies were then represented as a graph where each node was a publication and each edge represented a co-citation, weighted by the normalized co-citation frequency.
+For an alternate view of these DBLP data we constructed clusters using co-citation, the frequency with which a pair of articles is cited by other articles\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973} and has been used for clustering publications.
+Co-citation, first described independently by Small and Marshakova in 1973, provides insight into the emergence of new ideas derived from the association of previously independent ones.
+Unlike clustering by direct citation with Graclus, where every input publication is assigned to a cluster and every citation is weighted equally, clustering by co-citation is progressively selective, involves assigning weights to co-citations, and also accounts for weak inter-cluster interactions~\cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
 
@@
 To focus on larger clusters, only those with at least 10 nodes were used as input.
-Briefly, each cluster was now treated as a node and the edge weight between two clusters was assigned to the maximum edge weight of all edges between the nodes in the two precursor clusters.
+Briefly, each cluster was now treated as a node and the edge weight between two clusters was assigned to the maximum edge weight of all edges between the nodes in the two clusters.
 Edges were arranged in descending order.
@@
 All edges were then re-ordered as before and the next pair of clusters was merged.
-The process was halted after 600 rounds to prevent a single very large outlier cluster being generated (Fig.~\ref{fig:merge_select}).
+The process was halted after 600 rounds to prevent large outlier clusters being generated (Fig.~\ref{fig:merge_select}).
 
@@
 \subsection{Data}
-The process of selection and matching resulted in a dataset of 2,685,356 publications (Materials and Methods). 
-Of these roughly 2.8 million publications, approximately 2.07 million were classified as COMP under subject area and assigned ASJC codes corresponding to Computer Science (major subject area with 13 minor subject areas (Table~\ref{tab:comp}), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (Fig.~\ref{fig:ar_cp_annotation}).
+The process of selection and matching resulted in a dataset of  publications (Materials and Methods).
+Of 4,291,130 DBLP publications with DOIs, only  2,685,356 are found in Scopus.
+Of these roughly 2.8 million publications, approximately 2.07 million were classified in Scopus as COMP under subject area and assigned ASJC codes corresponding to Computer Science (major subject area with 13 minor subject areas (Table~\ref{tab:comp}), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (Fig.~\ref{fig:ar_cp_annotation}).
+The set of 2.07 million publications classified under the major subject area Computer Science in Scopus spanned all 13 minor subject areas with Software 30.3\% being the largest component and Computer Science (miscellaneous) 0.9\% the smallest (Table~\ref{tab:comp}).
+Another 409,082  publications were labeled Theoretical Computer Science under the major subject area of Mathematics.
+38.86\% of the publications were assigned to one minor subject area, 78.1\% to two minor subject areas, 909.9\% to three minor subject areas, and 0.0003\% assigned to 8 different minor subject areas.
 
-The set of 2.07 million publications classified as COMP in Scopus spanned all 13 minor subject areas with Software 30.3\% being the largest component and Computer Science (miscellaneous) 0.9\% the smallest (Table~\ref{tab:comp}).
-The number of minor subject areas assigned to a publication averaged to 1.75 with 53\% of the publications being assigned to one minor subject area and 0.0003\% assigned to 7 different minor subject areas.
-We note also that  the $4.8x10^6$ DBLP publications are only partially found in Scopus (which had a total of $5.8x10^6$ publications), using our methodology.
 %George, please consider revising this text
@@
 
-\subsection{Clustering by Co-citation.} For an alternate examination of the data, we used co-citation frequencies to cluster the DBLP dataset. 
+\subsection{Clustering by Co-citation.} For an alternate examination of the data, we used co-citation frequencies to cluster the DBLP dataset as described above.
 Figure \ref{fig:heatmap_cocit} shows a heatmap in which clusters constructed by co-citation are mapped to Scopus ASJC minor subject areas.
-Mappings are only shown if they account for at least 15\% of the publications in a cluster.
+Mappings are only shown if they account for at least 15\% of the publications in a cluster (upper panel).
+Under these conditions, only 17 of 20 clusters mapped to minor subject areas where at least 15\% of the nodes in a cluster were labeled with a given subject area.
+When the threshold was reduced to 10\% all 20 clusters indicated at least one mapping to a minor subject area.
+We interpret these data as indicative of two kinds of co-citational linkages (i) intra-cluster (ii) cross cluster.
+The latter predominates and is detected at lower thresholds (lower panel).
+No cluster maps to more than 3 minor subject area at the 15\% threshold in comparison to a maximum of 8 minor subject areas for clustering by direct citation (Fig 3, Cluster 17).
+It should be noted, however, that the size of clusters constructed by co-citation is much smaller than those generated by direct citation through Graclus.
+
 \textcolor{blue}{
@@
 \begin{table}[ht]
-\caption{\emph{Statistics regarding the 20 clusters produced using direct citation. The \emph{comp} dataset 
+\caption{\emph{denominator is 2090947 (some source ids got lost via inner joins and code restrictions) Statistics regarding the 20 clusters produced using direct citation. The \emph{comp} dataset 
 2685021 is because of inner joins on ASJC Explain conductance calculations~\cite{shun_parallel_2016}}}
@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-Software & 30.30 \\ 
-Computer Science Applications & 25.20 \\ 
-Computer Networks and Communications & 21.60 \\ 
-Computer Science(all) & 19.60 \\ 
-Artificial Intelligence & 14.30 \\ 
-Information Systems & 11.90 \\ 
-Hardware and Architecture & 11.50 \\ 
-Signal Processing & 9.90 \\ 
-Computer Vision and Pattern Recognition & 9.50 \\ 
-Computational Theory and Mathematics & 8.00 \\ 
-Human-Computer Interaction & 7.50 \\ 
-Computer Graphics and Computer-Aided Design & 5.20 \\ 
-Computer Science (miscellaneous) & 0.90 \\ 
+Software & 30.1 \\
+Computer Science Applications & 25.0 \\ 
+Computer Networks and Communications & 21.5 \\
+Theoretical Computer Science & 19.6 \\ 
+Computer Science(all) & 19.4 \\ 
+Artificial Intelligence & 14.2 \\ 
+Information Systems & 11.8 \\ 
+Hardware and Architecture & 11.8 \\ 
+Signal Processing & 9.8 \\ 
+Computer Vision and Pattern Recognition & 9.4 \\ 
+Computational Theory and Mathematics & 7.9 \\ 
+Human-Computer Interaction & 7.4 \\ 
+Computer Graphics and Computer-Aided Design & 5.2 \\ 
+Computer Science (miscellaneous) & 0.9 \\ 
 \noalign{\smallskip}\hline

### 2019-12-17 Scientometrics/comp.tex
udpate

@@
 The process of selection and matching resulted in a dataset of  publications (Materials and Methods).
-Of 4,291,130 DBLP publications with DOIs, only  2,685,356 are found in Scopus.
-Of these roughly 2.8 million publications, approximately 2.07 million were classified in Scopus as COMP under subject area and assigned ASJC codes corresponding to Computer Science (major subject area with 13 minor subject areas (Table~\ref{tab:comp}), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (Fig.~\ref{fig:ar_cp_annotation}).
-The set of 2.07 million publications classified under the major subject area Computer Science in Scopus spanned all 13 minor subject areas with Software 30.3\% being the largest component and Computer Science (miscellaneous) 0.9\% the smallest (Table~\ref{tab:comp}).
-Another 409,082  publications were labeled Theoretical Computer Science under the major subject area of Mathematics.
-38.86\% of the publications were assigned to one minor subject area, 78.1\% to two minor subject areas, 909.9\% to three minor subject areas, and 0.0003\% assigned to 8 different minor subject areas.
+Of 4,291,130 DBLP publications with DOIs, only  2,685,356 had corresponding DOIs in Scopus.
+Of these roughly 2.68 million publications, approximately 2.07 million were assigned ASJC codes in Scopus corresponding to Computer Science (major subject area with 13 minor subject areas (Table~\ref{tab:comp}), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (Fig.~\ref{fig:ar_cp_annotation}).
+The set of 2.07 million publications classified under the major subject area Computer Science in Scopus spanned all 13 minor subject areas with Software 30.3\% being the largest component and Computer Science (miscellaneous) 0.9\% the smallest.
+Interestingly, 409,082  publications were labeled Theoretical Computer Science but under the major subject area of Mathematics(Table~\ref{tab:comp}).
+Overall, 38.86\% of the publications were assigned to one minor subject area, 78.1\% to two minor subject areas, 909.9\% to three minor subject areas, and 0.0003\% assigned to 8 different minor subject areas.
 

### 2019-12-17 Scientometrics/comp.tex
added new figure to latex

@@
 \centering
+\includegraphics[width=0.9\textwidth]{quad-chart-narrow.pdf}
+\caption{Co-citation analysis.
+(a) The variable-level clustering technique (adapted from
+Small and Sweeney (1985)).
+(b) The distribution of publications (using fractional counting)
+across four main categories.
+(c) The Venn diagram of the fractional counting given in (b).
+(d) The distribution of cluster sizes (logarithmic y-axis) as
+a function of the number of iterations of the agglomerative
+clustering technique; note that the largest cluster is
+extremely large when the number of iterations exceeds 600.
+}
+\label{fig:quad-chart}
+\end{figure}
+
+\begin{figure}[ht]
+\centering
 % Use the relevant command to insert your figure file.

### 2019-12-18 Scientometrics/comp.tex
began Discussion

@@
 
-In this study, we extend the work of Salton and Bergmark by combining article and journal approaches to study trends in computer science, while also considering connections to other fields.
+In this study, we extend the work of Salton and Bergmark by combining article and journal approaches to study trends in computer science, while also considering connections to other fields, especially biology, which dominates the total number of scientific publications and is citationally active [need to tweak].
 As a source of computer science literature, we used DBLP, a reference bibliography for computer science~\cite{dblp_ref}.
@@
 Considering that traditional disciplines `may only partly reflect the actual organization of today's scientific research'~\cite{waltman_new_2012}, we constructed article clusters at high levels of aggregation using citations to examine the \emph{comp} dataset and mapped these clusters to journal-based categories.
+
  Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation with direct citation being proposed as as the best approach to concentrate citation links~\cite{klavans_which_2017}.
@@
 For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography that (i) had a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography.
-Our underlying assumption is that records in DBLP are greatly enriched for computer science even while recognizing that coverage may be incomplete and possibly biased.
+The underlying assumption is that records in DBLP are greatly enriched for computer science even while recognizing that coverage may be incomplete and possibly biased.
 Cross-matching DBLP publications to records in the Scopus, abstract and citation database of peer-reviewed literature, enabled us to harvest the richer links in Scopus as well as extract links to publications from other disciplines.
@@
 A stable release of the DBLP computer science bibliography~\cite{dblp_ref} consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz.
-Just over 95\% of the publications within were published after 1996.
+Slightly over 95\% of the publications within were published after 1996.
 Publications were parsed from the XML source file and loaded into a PostgreSQL database.
-We have previously parsed the Scopus dataset, presently at over 87.8 million publications, into a custom schema as part of implementing a larger data platform for research evaluation~\cite{GithubERNIE2019}.
-The total number of publications in Scopus that are labeled COMP with major subject area of Computer Science is 5,835,160.
+As part of implementing a larger data platform for research evaluation~\cite{GithubERNIE2019}, we have previously parsed the Scopus dataset, presently at over 87.8 million publications, into a custom schema in a PostgreSQL database.
+The total number of publications in Scopus labeled with major subject area of Computer Science (in turn a subset of the Physical Sciences subject area) is 5,835,160.
 Records in the DBLP dataset were matched to Scopus identifiers using digital object identifiers (DOIs).
@@
 At around 20 clusters, clusters size was relatively stable with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{subelj_clustering_2016}.
-Consequently, we used Graclus to generate 20 clusters, labeled 0-19 (Table~\ref{tab:graclus}).
+Consequently, we used Graclus to generate 20 clusters, labeled 0-19 (Table~\ref{tab:graclus}), analogous to Level 1 of Waltman and van Eck's mapping of nearly 10 million publications~\cite{waltman_new_2012} but focused on the DBLP bibliography.
 
@@
 Clusters containing only 2 nodes were discarded bringing the total number of clusters down to 10,298.
-The publications in these 10,298 clusters were overwhelmingly drawn from the Physical Sciences (one of the 4 top level categories in the Scopus ASJC classification), of which computer science is a sub-category (Fig.~\ref{fig:cocitr_venn2}).
+The publications in these 10,298 clusters were overwhelmingly drawn from the Physical Sciences (one of the 4 top level categories in the Scopus ASJC classification), of which computer science is a sub-category (Fig.~\ref{fig:quad-chart}).
 
@@
 All edges were then re-ordered as before and the next pair of clusters was merged.
-The process was halted after 600 rounds to prevent large outlier clusters being generated (Fig.~\ref{fig:merge_select}).
+The process was halted after 600 rounds to prevent large outlier clusters being generated (Fig.~\ref{fig:quad-chart}).
 
@@
 The set of 2.07 million publications classified under the major subject area Computer Science in Scopus spanned all 13 minor subject areas with Software 30.3\% being the largest component and Computer Science (miscellaneous) 0.9\% the smallest.
-Interestingly, 409,082  publications were labeled Theoretical Computer Science but under the major subject area of Mathematics(Table~\ref{tab:comp}).
-Overall, 38.86\% of the publications were assigned to one minor subject area, 78.1\% to two minor subject areas, 909.9\% to three minor subject areas, and 0.0003\% assigned to 8 different minor subject areas.
+Publications in the \emph{comp} dataset labeled Theoretical Computer Science (409,082) are classified under the the major subject area of Mathematics rather than Computer Science (Table~\ref{tab:comp}).
+Overall, 38.86\% of the publications were assigned to one minor subject area, 78.1\% to two minor subject areas, 90.9\% to three minor subject areas, and 0.0003\% assigned to 8 different minor subject areas.
 
@@
 %, whereas areas such as biology, chemistry, and statistics are more restricted in distribution.  
-A second inference is that, in some cases, journal-based classification and our article clusters are similar in terms of article content (Hardware and Architecture). 
+A second inference is that, in some cases, journal-based classification and our article clusters align fairly well (Hardware and Architecture). 
 A third inference is that the ASJC minor subject area ``Computer Applications" is relatively non-specific, and publications thus labeled are nearly ubiquitous (16/20).
@@
 
-\textcolor{blue}{
-Unlike the earlier figure [insert figure reference] Unlike the case of clustering by direct citation, no cluster maps to more than three ASJC minor subject areas.
-We have to decide what to say about this figure but I think it suggests intra-cluster relationships for the most part.
-}
+We also mapped the contents of clusters generated by direct citation and co-citation to each other, Fig~\ref{fig:graclus_cocit_fig}.
 
-\section{Discussion}
-\textcolor{blue}{
-Results obtained using the two different clustering methods produced different but complementary views of the computer
-science literature.
-Discuss: very low conductance values, and the significance of this. 
-Need for additional work. 
-Perhaps value in looking at change over time.
-Emerging interactions of computer science and other disciplines, 
-so papers are related by the communities they impact (co-citation clustering).
- }
+\section{Discussion} In this article, we have tried to revisit a characterization of computer science from 1979~\cite{salton_citation_1979} in the light of expansion and diversification of this field.
+We analyzed considerably more data, 2.68 million publications versus 391, and leveraged access to two bibliographic databases, DBLP and Scopus.
+The former identifies a sample of the scientific literature that is computer science and the latter (roughly 10 times larger at 87.XX million publications) enabled analyzing citations across the four major groups of Physical Science, Social Sciences, Life Sciences, and Health Sciences in the Scopus ASJC classification.
 
-%\noindent
-Co-citation based clustering:
-\begin{enumerate}
-\item Stratify by year after subsetting by COMP and restricting to article and cp only
-\item Apply fractional citation counting and identify highly-cited papers
-\item Calculate normalized co-citations
-\item Cluster by variable clustering method of Small
-\item Evaluate major co-cited pairs
-\end{enumerate}
+Obvious critiques of our approach are (i) use of the DBLP dataset, which may not capture all aspects of computer science and its interactions with other fields (ii) partitioning DBLP into a weakly justified number of clusters and arbitrarily defined thresholds for detection (iii) mapping the results of this clustering against a classification designed around journals rather than individual articles.
+Our focus on high-level features may mitigate these valid concerns and preference for simplicity and intuitiveness in our choice of methods.
+
+Reconciling direct citation clusters to the Scopus ASJC classification, yielded results that are consistent with the observation of Waltman and van Eck (2012)~\cite{waltman_new_2012}, `that traditional disciplines such as those just mentioned only partly reflect the actual organization of today’s scientific research'.
+Of interest to us, was the single obviously multidisciplinary cluster in which at least 15\% of its component publications were labeled with the ASJC minor subject areas Biochemistry, Chemistry, Computational Mathematics, Computational Theory and Mathematics, Computer Science Applications, Genetics, Molecular Biology, Statistics \& Probability followed by the cluster mapping to Artificial Intelligence, Cognitive Neuroscience, and Neurology.
+Perhaps at the opposite end of this spectrum is the more insular cluster that maps to Hardware and Architecture, Electrical and Electronic Engineering, and Software.
+To us, these data suggest a diverse field of activities [not sure what that means].
+
+Analyzing clusters generated using co-citation links is more challenging.
+The data suggest two patterns that may co-exist.
+One in which the nodes in a co-citation cluster are detected at the threshold applied mostly from a single or two direct citation clusters.
+The second, which may account for more than 50\% of the nodes in a co-citation cluster, in which these nodes are distributed across all 20 direct citation clusters.
+The latter is intriguing in its implications of a web of such citational links gluing the body of scientific literature together.
+
+Emerging interactions of computer science and other disciplines, so papers are related by the communities they impact (co-citation clustering). [Over to Tandy]
 
@@
 \centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=0.25]{vlc.pdf}
-% figure caption is below the figure
-\caption{Schematic representation of variable clustering protocol modified from Small and Sweeney (1985) \cite{small_clustering_1985}.
+\includegraphics[width=0.9\textwidth]{quad-chart-narrow.pdf}
+\caption{Co-citation analysis.
+(a) Schematic representation of variable clustering protocol modified from Small and Sweeney (1985) \cite{small_clustering_1985}.
 Three parameters are specified: (i) a threshold or starting level based on a quantile of normalized co-citation frequency, (ii) a level increment, and  (iii) a maximum cluster size.
@@
 The cascade continues to completion, which is defined by all clusters being of size less than or equal to the $mcs$.
-In this schematic, five rounds are adequate for the process to run to completion.}
-\label{fig:vlc_process}       % Give a unique label
-\end{figure}
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.9\textwidth]{quad-chart-narrow.pdf}
-\caption{Co-citation analysis.
-(a) The variable-level clustering technique (adapted from
-Small and Sweeney (1985)).
-(b) The distribution of publications (using fractional counting)
-across four main categories.
+In this schematic, five rounds are adequate for the process to run to completion.
+(b) The distribution of publications (using fractional counting) across four top-level ASJC subject areas after applying variable level clustering as in a)
 (c) The Venn diagram of the fractional counting given in (b).
-(d) The distribution of cluster sizes (logarithmic y-axis) as
-a function of the number of iterations of the agglomerative
-clustering technique; note that the largest cluster is
-extremely large when the number of iterations exceeds 600.
+(d) The distribution of cluster sizes (logarithmic y-axis) as a function of the number of iterations of the agglomerative clustering technique; note that the largest cluster is extremely large when the number of iterations exceeds 600.
 }
 \label{fig:quad-chart}
-\end{figure}
-
-\begin{figure}[ht]
-\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
- \includegraphics[scale=0.5]{cocit_venn2.pdf}
-% figure caption is below the figure
-\caption{High-level disciplinary composition of publications in $\sim$2,000 clusters generated by variable-level clustering  of co-citation data.
-%Variable Level Clustering. 
-84,591 nodes from were matched to the 4 subject areas, 
-27 major subject areas, and 334 minor subject areas in the Scopus ASJC classification. Since 82.5\% of these nodes were assigned more to than one minor subject category, 
-we assigned fractional counts for the four subject areas that summed to 1 for each article. The figure shows a four way Venn Diagram~\cite{chen_venn_2011} illustrating the 
-relative frequencies of publications from the Physical Sciences, Social Sciences, Life Sciences, and Health Sciences.}
-\label{fig:cocitr_venn2}       % Give a unique label
-\end{figure}
-\newpage
-
-\begin{figure}[ht]
-\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=0.5]{merge_select.pdf}
-% figure caption is below the figure
-\caption{Clustering produced using co-citation data; the y-axis is the cluster size (given logarithmically), and the x-axis is the number of iterations of the agglomerative clustering technique.
-Note that iterating more than 600 times produces a very large cluster.
-}
-\label{fig:merge_select}       % Give a unique label
 \end{figure}
@@
 
-\newpage
-
 \begin{figure}[ht]
@@
 % figure caption is below the figure
-\caption{Heat map for the clustering obtained by direct citation. The  y-axis (rows) correspond to topics, defined by Scopus characterizations, and the
-x-axis (columns) represent the 20 different clusters.  
-Each cluster is characterized by topics that label at least 10\% of the publications in the cluster.
- }
-\label{fig:heatmap}       % Give a unique label
+\caption{Intersections between clusters generated using direct citation and co-citation features.
+x-axis: Clusters generated by Graclus number 0-19.
+y-axis: Cluster generated by variable level clustering and agglomerative clustering using a modification of Small and Sweeney (1985)~\cite{small_clustering_1985}.
+Point size (perc) is the percentage of a co-cited cluster that maps to a corresponding Graclus cluster.
+A minimum threshold of 15\% was set.
+Graclus cluster 19, the 20th cluster, did not map to any cluster on the y:axis.}
+\label{fig:graclus_cocit_fig}       % Give a unique label
 \end{figure}
-
 \newpage
@@
 \end{figure*}
+
+\begin{figure}[ht]
+\centering
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.25]{vlc.pdf}
+% figure caption is below the figure
+\caption{Schematic representation of variable clustering protocol modified from Small and Sweeney (1985) \cite{small_clustering_1985}.
+Three parameters are specified: (i) a threshold or starting level based on a quantile of normalized co-citation frequency, (ii) a level increment, and  (iii) a maximum cluster size.
+Input data is a set of co-cited publications with edge-weight defined by normalized co-citation frequencies.
+Green clusters are within the max cluster size.
+At the initial threshold, $t1$, a single cluster below the maximum cluster size, $mcs$ (green), along with one large cluster above it (red) are generated.
+As the threshold is incremented to $t2$, additional clusters of acceptable size is generated.
+The cascade continues to completion, which is defined by all clusters being of size less than or equal to the $mcs$.
+In this schematic, five rounds are adequate for the process to run to completion.}
+\label{fig:vlc_process}       % Give a unique label
+\end{figure}
+
+\begin{figure}[ht]
+\centering
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+ \includegraphics[scale=0.5]{cocit_venn2.pdf}
+% figure caption is below the figure
+\caption{High-level disciplinary composition of publications in $\sim$2,000 clusters generated by variable-level clustering  of co-citation data.
+%Variable Level Clustering. 
+84,591 nodes from were matched to the 4 subject areas, 
+27 major subject areas, and 334 minor subject areas in the Scopus ASJC classification. Since 82.5\% of these nodes were assigned more to than one minor subject category, 
+we assigned fractional counts for the four subject areas that summed to 1 for each article. The figure shows a four way Venn Diagram~\cite{chen_venn_2011} illustrating the 
+relative frequencies of publications from the Physical Sciences, Social Sciences, Life Sciences, and Health Sciences.}
+\label{fig:cocitr_venn2}       % Give a unique label
+\end{figure}
+\newpage
+
+\begin{figure}[ht]
+\centering
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.5]{merge_select.pdf}
+% figure caption is below the figure
+\caption{Clustering produced using co-citation data; the y-axis is the cluster size (given logarithmically), and the x-axis is the number of iterations of the agglomerative clustering technique.
+Note that iterating more than 600 times produces a very large cluster.
+}
+\label{fig:merge_select}       % Give a unique label
+\end{figure}
+
 %

### 2019-12-18 Scientometrics/comp.tex
lots of edits, look for your name, George

@@
 Salton and Bergmark conducted a historical study  in 1979 of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles)~\cite{salton_citation_1979}.
-These authors described the global structure of computer science as comprising three main areas (i) theoretical foundations, such as theory of computation, (ii) hardware and computer systems, such as architecture,  and (iii) software, such as programming systems.
+These authors described the global structure of computer science as comprising three main areas: (i) theoretical foundations, such as theory of computation, (ii) hardware and computer systems, such as architecture,  and (iii) software, such as programming systems.
 Related areas noted were (a) mathematics of computing, such as numerical analysis, (b) special software topics, such as operating systems, (c) data management and database systems, (d) methodologies valid for multiple applications, such as algebraic manipulation, (e) computer applications, such as computer graphics, and  (f) non-technical aspects, such as computer education.
 
-Looking beyond Salton and Bergmark's historical triad of theoretical foundations; hardware and computer systems; and software, the Computing Classification System (CCS) published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field~\cite{acm_ref}.
+Looking beyond Salton and Bergmark's historical triad of theoretical foundations, hardware and computer systems, and software, the Computing Classification System (CCS) published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field~\cite{acm_ref}.
 This classification also addresses relationships with other fields under the category of Applied Computing.
@@
 
-Other classification systems are available such as the All Science Journal Classification (ASJC) developed and maintained by Scopus, the Web of Science research and categorical classifications from Clarivate Analytics, and the NSF classification system~\cite{nsf_classification} [add citations for Scopus and Web of Science].
+Other classification systems are available, such as the All Science Journal Classification (ASJC) developed and maintained by Scopus, the Web of Science research and categorical classifications from Clarivate Analytics, and the NSF classification system~\cite{nsf_classification} [add citations for Scopus and Web of Science].
 Scopus and the Web of Science also include comprehensive bibliographies with citation links and proprietary unique identifiers for publications.
@@
 A logical prediction, given the diversity of articles within journals, is limited specificity at the article level. 
-Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD) and the Web of Science that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
+Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD) \cite{CSCD} and the Web of Science that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
 Others have also discussed and critiqued disciplinary assignments using journal-based classifications~\cite{wang_large-scale_2016,perianes-rodriguez_comparison_2017}. 
@@
  In our study of the structure of a twenty year cohort of the computer science literature, we chose to use both traditional journal-based and article-based approaches.
-Considering that traditional disciplines `may only partly reflect the actual organization of today's scientific research'~\cite{waltman_new_2012}, we constructed article clusters at high levels of aggregation using citations to examine the \emph{comp} dataset and mapped these clusters to journal-based categories.
+Considering that traditional disciplines `may only partly reflect the actual organization of today's scientific research'~\cite{waltman_new_2012}, we constructed article clusters at high levels of aggregation using citations to examine the  computer science literature (as represented in our \emph{comp} dataset, described below) and mapped these clusters to journal-based categories.
 
- Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation with direct citation being proposed as as the best approach to concentrate citation links~\cite{klavans_which_2017}.
+ Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation, with direct citation being proposed as as the best approach to concentrate citation links~\cite{klavans_which_2017}.
 Accordingly, we used direct citation links as the basis for cluster formation, and also co-citation to obtain an alternative view.
@@
 The underlying assumption is that records in DBLP are greatly enriched for computer science even while recognizing that coverage may be incomplete and possibly biased.
-Cross-matching DBLP publications to records in the Scopus, abstract and citation database of peer-reviewed literature, enabled us to harvest the richer links in Scopus as well as extract links to publications from other disciplines.
-This cross-matching to Scopus, also allows the use of both journal and article based classifications when clustering documents.
+Cross-matching DBLP publications to records in the Scopus abstract and citation database of peer-reviewed literature, enabled us to harvest the richer links in Scopus as well as extract links to publications from other disciplines.
+This cross-matching to Scopus also allows the use of both journal and article based classifications when clustering documents.
 Using both direct citations and co-citations as the basis for clustering, we used DBLP articles from journals and conference proceedings for the period 1996-2015.
@@
 This procedure resulted in a dataset of 2,685,356 DBLP publications with Scopus identifiers where 1,278,322 (47.6\%) were labeled as article and 1,407,034 (52.4\%) as conference proceedings.
-References cited by these publications were then extracted from Scopus (7,129,006 records), resulting in a total of 8,000,411 nodes (publications and references) and 44,296,381 edges that represent citations within the dataset.
-This dataset is referred to as \emph{comp} (Fig~\ref{fig:ar_cp_annotation}, Table~\ref{tab:comp}).
+References cited by these publications were then extracted from Scopus (7,129,006 records), resulting in a total of 8,000,411
+publications and references. 
+We represented these data using a graph where the 8,000,411 nodes represent
+publications and references  and the 44,296,381 undirected edges represent citations within the dataset. 
+We refer to these data as the  \emph{comp} dataset (Fig~\ref{fig:ar_cp_annotation}, Table~\ref{tab:comp}).
 
-\subsection{Clustering methods} In applying both clustering by direct citation and by co-citation, we attempted to consider, wherever possible, the criteria articulated by \v{S}ubelj, van Eck, and Waltman~\cite{subelj_clustering_2016}, of (i) the largest cluster should be no more than 10 times the smallest one, (ii) small clusters should be eliminated, (iii) small changes and replicates should yield similar results (``stability"),  (iv) computing time should be minimized where possible, and (v) the clustering should seem reasonable on a qualitative level (``intuitive sensibility").
+\subsection{Clustering methods} In applying both clustering by direct citation and by co-citation, we attempted to consider, wherever possible, the criteria articulated by \v{S}ubelj, van Eck, and Waltman~\cite{subelj_clustering_2016} that (i) the largest cluster should be no more than 10 times the smallest one, (ii) small clusters should be eliminated, (iii) small changes and replicates should yield similar results (``stability"),  (iv) computing time should be minimized where possible, and (v) the clustering should seem reasonable on a qualitative level (``intuitive sensibility").
 
@@
 
-For an alternate view of these DBLP data we constructed clusters using co-citation, the frequency with which a pair of articles is cited by other articles\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973} and has been used for clustering publications.
-Co-citation, first described independently by Small and Marshakova in 1973, provides insight into the emergence of new ideas derived from the association of previously independent ones.
-Unlike clustering by direct citation with Graclus, where every input publication is assigned to a cluster and every citation is weighted equally, clustering by co-citation is progressively selective, involves assigning weights to co-citations, and also accounts for weak inter-cluster interactions~\cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
+For an alternate view of these DBLP data, we constructed clusters using co-citation, the frequency with which a pair of articles is cited by other articles \cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}.
+% and has been used for clustering publications.
+%George, add citation
+Co-citation, first described independently by Small and Marshakova in 1973 \cite{marshakova-shaikevich_co-citation_1973}, provides insight into the emergence of new ideas derived from the association of previously independent ones.
+Unlike clustering by direct citation, where every input publication is assigned to a cluster and every citation is weighted equally, the co-citation relationship between papers is weighted to represent the strength of the co-citation history.
+Because this produces a weighted graph, clustering methods that address weights are required.
+Furthermore, co-citation produces relatively weak inter-cluster interactions, requiring additional modifications to standard clustering approaches \cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
 
@@
 
-In our implementation of variable level clustering (Fig.~\ref{fig:vlc_process}), we first calculated the number of citations accumulated across Scopus for all 2,685,356 articles in \emph{comp}.
+In our implementation of variable level clustering (Fig.~\ref{fig:quad-chart}(a)), we first calculated the number of citations accumulated across Scopus for all 2,685,356 articles in \emph{comp}.
 After discarding those publications without any citations, we restricted further analysis to highly cited articles--those in the 90th percentile of citations or higher--resulting in a dataset of size 212,311.
@@
 The cited reference pairs this generated were then restricted to those in the set of 212,311 highly cited papers previously identified.
+A total of 46,463,117 unique co-cited pairs were thus obtained.
 The frequency of these co-cited pairs was then computed across the \emph{comp} dataset  and normalized using Salton's cosine formula~\cite{salton_citation_1979}.
-A total of 46,463,117 unique co-cited pairs were thus obtained.
 These data were represented in a graph where each node was a publication and the weighted edge between the pair was the normalized co-citation frequency.
@@
 
-We applied variable clustering with initial parameters of threshold ($t$) = median normalized co-citation frequency (quantile=0.5), increment $i = 0.1$, and maximum cluster size, $mcs=200$.
+We applied variable clustering with initial parameters as follows: the threshold defining the initial median normalized co-citation frequency (quantile) $t=0.5$, increment $i = 0.1$, and maximum cluster size, $mcs=200$.
 Thus, at start, all edges below the median normalized co-citation frequency were deleted.
@@
 Using this approach, 22,232 clusters containing 84,591 nodes were generated, each containing less than 100 nodes.
-Clusters containing only 2 nodes were discarded bringing the total number of clusters down to 10,298.
+Clusters containing only 2 nodes were discarded, bringing the total number of clusters down to 10,298.
 The publications in these 10,298 clusters were overwhelmingly drawn from the Physical Sciences (one of the 4 top level categories in the Scopus ASJC classification), of which computer science is a sub-category (Fig.~\ref{fig:quad-chart}).
@@
 
-From the alternate perspective (columns), cluster 17 was the most diverse and contained publications annotated with 8 minor subject area labels: Biochemistry, Chemistry(all), Genetics, Molecular Biology,  Statistics \& Probability, Computational Theory \& Mathematics, and Computational Mathematics.
+From the alternate perspective (columns), Cluster 17 was the most diverse and contained publications annotated with 8 minor subject area labels: Biochemistry, Chemistry(all), Genetics, Molecular Biology,  Statistics \& Probability, Computational Theory \& Mathematics, and Computational Mathematics.
 Cluster 19 mapped to two areas but was excluded from qualitative analysis because of its high conductance value.
-Of the remaining clusters, the third (Cluster 2) represents interactions between the minor subject areas Theoretical Computer Science, Discrete Mathematics and Combinatorics, and Applied Mathematics as well as the more generic Computer Science (all).
-Clusters 3 and 4 include Computer Networks and Communications and Cluster 18 (Artificial Intelligence, Cognitive Neuroscience, and Neurology) and clusters 5--9 include Management Science, Operations Research, Information Systems, Modeling and Simulation, and Human-Computer Interaction.
+Of the remaining clusters, Cluster 2 represents interactions between the minor subject areas Theoretical Computer Science, Discrete Mathematics and Combinatorics, and Applied Mathematics as well as the more generic Computer Science (all).
+Clusters 3 and 4 include Computer Networks and Communications, and Cluster 18 (Artificial Intelligence, Cognitive Neuroscience, and Neurology) and clusters 5--9 include Management Science, Operations Research, Information Systems, Modeling and Simulation, and Human-Computer Interaction.
 
@@
 A second inference is that, in some cases, journal-based classification and our article clusters align fairly well (Hardware and Architecture). 
-A third inference is that the ASJC minor subject area ``Computer Applications" is relatively non-specific, and publications thus labeled are nearly ubiquitous (16/20).
+A third inference is that the ASJC minor subject area ``Computer Applications" is relatively non-specific, and publications thus labeled are nearly ubiquitous (present in 16 out of 20 clusters).
 Finally,   for the DBLP dataset, interactions with fields outside computer science (e.g., Biochemistry)  are  typically restricted to a single cluster or found in a small number of clusters.
@@
 For example, clusters 0 and 1 mapped reasonably well to the top level categories Hardware and Computer Systems Organization,  but
-the top cited papers often derived from biology and yet biology was clearly not  representative of all of these affected clusters.
+the top cited papers often derived from biology and yet biology was clearly not  representative of any of these affected clusters.
 
-\subsection{Clustering by Co-citation.} For an alternate examination of the data, we used co-citation frequencies to cluster the DBLP dataset as described above.
-Figure \ref{fig:heatmap_cocit} shows a heatmap in which clusters constructed by co-citation are mapped to Scopus ASJC minor subject areas.
-Mappings are only shown if they account for at least 15\% of the publications in a cluster (upper panel).
+\subsection{Clustering by Co-citation.} 
+For an alternate examination of the data, we used co-citation frequencies to cluster the DBLP dataset as described above.
+Figure \ref{fig:heatmap_cocit} shows a heatmap in which clusters constructed by co-citation are mapped to Scopus ASJC minor subject areas, with the top subfigure showing results for those labels that
+account for at least 15\% of the publications in a cluster, and the bottom subfigure showing results for those labels that account for at least 10\% of the publications.
+%Mappings are only shown if they account for at least 15\% of the publications in a cluster (upper panel). 
 Under these conditions, only 17 of 20 clusters mapped to minor subject areas where at least 15\% of the nodes in a cluster were labeled with a given subject area.
-When the threshold was reduced to 10\% all 20 clusters indicated at least one mapping to a minor subject area.
+When the threshold was reduced to 10\%, all 20 clusters indicated at least one mapping to a minor subject area.
 We interpret these data as indicative of two kinds of co-citational linkages (i) intra-cluster (ii) cross cluster.
 The latter predominates and is detected at lower thresholds (lower panel).
-No cluster maps to more than 3 minor subject area at the 15\% threshold in comparison to a maximum of 8 minor subject areas for clustering by direct citation (Fig 3, Cluster 17).
+No cluster maps to more than three minor subject area at the 15\% threshold,  in contrast to a maximum of eight minor subject areas for clustering by direct citation (Fig.
+3, Cluster 17).
 It should be noted, however, that the size of clusters constructed by co-citation is much smaller than those generated by direct citation through Graclus.
+%George, add some comments and discussion
 
@@
 
-\section{Discussion} In this article, we have tried to revisit a characterization of computer science from 1979~\cite{salton_citation_1979} in the light of expansion and diversification of this field.
+\section{Discussion} In this article, we revisited a characterization of computer science from 1979~\cite{salton_citation_1979} in the light of expansion and diversification of this field.
 We analyzed considerably more data, 2.68 million publications versus 391, and leveraged access to two bibliographic databases, DBLP and Scopus.
@@
 
-Obvious critiques of our approach are (i) use of the DBLP dataset, which may not capture all aspects of computer science and its interactions with other fields (ii) partitioning DBLP into a weakly justified number of clusters and arbitrarily defined thresholds for detection (iii) mapping the results of this clustering against a classification designed around journals rather than individual articles.
-Our focus on high-level features may mitigate these valid concerns and preference for simplicity and intuitiveness in our choice of methods.
+Obvious critiques of our approach are: (i) use of the DBLP dataset, which may not capture all aspects of computer science and its interactions with other fields, (ii) partitioning DBLP into a weakly justified number of clusters and arbitrarily defined thresholds for detection, and (iii) mapping the results of this clustering against a classification designed around journals rather than individual articles.
+Our focus on high-level features and preference for simplicity and intuitiveness in our choice of methods may mitigate these concerns.
 
-Reconciling direct citation clusters to the Scopus ASJC classification, yielded results that are consistent with the observation of Waltman and van Eck (2012)~\cite{waltman_new_2012}, `that traditional disciplines such as those just mentioned only partly reflect the actual organization of today’s scientific research'.
-Of interest to us, was the single obviously multidisciplinary cluster in which at least 15\% of its component publications were labeled with the ASJC minor subject areas Biochemistry, Chemistry, Computational Mathematics, Computational Theory and Mathematics, Computer Science Applications, Genetics, Molecular Biology, Statistics \& Probability followed by the cluster mapping to Artificial Intelligence, Cognitive Neuroscience, and Neurology.
+Reconciling direct citation clusters to the Scopus ASJC classification yielded results that are consistent with the observation of Waltman and van Eck (2012)~\cite{waltman_new_2012}, `that traditional disciplines such as those just mentioned only partly reflect the actual organization of today’s scientific research'.
+Of interest to us, was the single obviously multidisciplinary cluster in which at least 15\% of its component publications were labeled with the ASJC minor subject areas Biochemistry, Chemistry, Computational Mathematics, Computational Theory and Mathematics, Computer Science Applications, Genetics, Molecular Biology, Statistics \& Probability, followed by the cluster mapping to Artificial Intelligence, Cognitive Neuroscience, and Neurology.
 Perhaps at the opposite end of this spectrum is the more insular cluster that maps to Hardware and Architecture, Electrical and Electronic Engineering, and Software.
-To us, these data suggest a diverse field of activities [not sure what that means].
+To us, these data suggest that some subfields within computer science are primarily inward looking (remain concerned with fundamental questions in computer science), while others are more actively engaged with fields external to computer science.
 
@@
 % figure caption is below the figure
-\caption{Conductance Measurements of Clusters Generated by Graclus.
+\caption{Conductance Measurements of Clusters Generated by Graclus of the direct citation dataset.
 2,685,356 DBLP publications, 7,129,006 cited references, and 44,296,381 citations were clustered using Graclus into 18 (grac\_18), 20 (grac\_20), or 22 (grac-22) clusters.
@@
 % figure caption is below the figure
-\caption{Heat map for the clustering obtained by direct citation. The  y-axis (rows) correspond to topics, defined by Scopus characterizations, and the
+\caption{Heat map for the clustering obtained by co-citation, using two thresholds for inclusion (top: 15\%, bottom: 10\%).
+The  y-axis (rows) correspond to topics, defined by Scopus characterizations, and the
 x-axis (columns) represent the 20 different clusters.  
-Each cluster is characterized by topics that label at least 15\% of the publications in the cluster.
- }
+Each cluster is characterized by topics that label at least the required minimum percentage of publications in the cluster (top: 15\%, bottom: 10\%).   }
 \label{fig:heatmap_cocit}       % Give a unique label

### 2019-12-19 Scientometrics/comp.tex
small edits

@@
 A logical prediction, given the diversity of articles within journals, is limited specificity at the article level. 
-Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD) \cite{CSCD} and the Web of Science that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
+Shu and colleagues recently noted in a comparative study of the Chinese Science Citation Database (CSCD)  and the Web of Science that 46\% of articles did not belong to the discipline of the journal they were published in~\cite{shu_comparing_2019}.
 Others have also discussed and critiqued disciplinary assignments using journal-based classifications~\cite{wang_large-scale_2016,perianes-rodriguez_comparison_2017}. 
@@
 This cross-matching to Scopus also allows the use of both journal and article based classifications when clustering documents.
-Using both direct citations and co-citations as the basis for clustering, we used DBLP articles from journals and conference proceedings for the period 1996-2015.
+Using both direct citations and co-citations as the basis for clustering, we used DBLP articles from journals and conference proceedings.
 We reconciled these clusters with the All Science Journal Classification (ASJC) developed and maintained by Scopus through a combination of automated and manual procedures, producing a dataset of  2,685,356 publications.
@@
 
-We used a modification of variable level clustering combined with agglomerative clustering, an approach developed in 1985 by Small and Sweeney~\cite{small_clustering_1985}. 
+We used a modification of variable level clustering combined with agglomerative clustering, an approach developed in 1985 by Small and Sweeney~\cite{small_clustering_1985} for co-citation analysis.
 Variable level clustering involves applying a threshold (below which all edges in a graph are deleted) then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn.
@@
 
-We applied variable clustering with initial parameters as follows: the threshold defining the initial median normalized co-citation frequency (quantile) $t=0.5$, increment $i = 0.1$, and maximum cluster size, $mcs=200$.
+We applied variable clustering with initial parameters as follows: the threshold  $t$  is initially set to  the median normalized co-citation frequency (quantile=0.5), increment $i = 0.1$, and maximum cluster size, $mcs=200$.
 Thus, at start, all edges below the median normalized co-citation frequency were deleted.
@@
 The threshold, $t$, was then incremented by 0.1 and the process repeated while progressively incrementing $t$.
-We used a bi-phasic approach where in which $t$ ranged from 0.5-0.9, after which $i$ was reduced to 0.01 for the range $0.9 \leq t \leq 0.99$.
+We used a bi-phasic approach where in which $t$ ranged from 0.5--0.9, after which $i$ was reduced to 0.01 for the range $0.9 \leq t \leq 0.99$.
 A final threshold of $t$=0.999 was applied to break the single remaining large cluster.
@@
 Clusters containing only 2 nodes were discarded, bringing the total number of clusters down to 10,298.
-The publications in these 10,298 clusters were overwhelmingly drawn from the Physical Sciences (one of the 4 top level categories in the Scopus ASJC classification), of which computer science is a sub-category (Fig.~\ref{fig:quad-chart}).
+The publications in these 10,298 clusters were overwhelmingly drawn from the Physical Sciences (one of the four top level categories in the Scopus ASJC classification), of which computer science is a sub-category (Fig.~\ref{fig:quad-chart}).
 

### 2019-12-20 Scientometrics/comp.tex
more tables and text

@@
 \usepackage{listings}
+\usepackage{comment}
 %
@@
 
-Computer science and its applications have experienced rapid growth and diversification over the last twenty years.
+Computer science, and its applications, has experienced rapid growth and diversification over the last twenty years.
 As observed in a 2017 US National Academies Report, ``A wide range of jobs in virtually all sectors demand computing skills to an unprecedented extent.
@@
 More recently, the collective influence of the Internet of Things (IoT), `big' data, accessible cloud computing, and advances in artificial intelligence have been postulated as a recent driver for growth and evolution~\cite{siebel2019_digital}.
-Given this powerful influence some understanding of the present state and structure of computer science and its relationship to other fields could inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy.
-For the same reason of broad influence, computer science can also serve as a model system for studying interdisciplinarity.
+Given this powerful influence, some understanding of the present state and structure of computer science and its relationship to other fields could inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy.
 
-Noting that that the scientific literature serves a rich source of information to study the structure and historical development of a field, 
-Salton and Bergmark conducted a historical study  in 1979 of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles)~\cite{salton_citation_1979}.
-These authors described the global structure of computer science as comprising three main areas: (i) theoretical foundations, such as theory of computation, (ii) hardware and computer systems, such as architecture,  and (iii) software, such as programming systems.
+In terms of historical precedent, Salton and Bergmark conducted a study  in 1979 of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles)~\cite{salton_citation_1979}.
+Noting that that the scientific literature serves a rich source of information to study the structure and historical development of a field, these authors described the global structure of computer science as comprising three main areas: (i) theoretical foundations, such as theory of computation, (ii) hardware and computer systems, such as architecture,  and (iii) software, such as programming systems.
 Related areas noted were (a) mathematics of computing, such as numerical analysis, (b) special software topics, such as operating systems, (c) data management and database systems, (d) methodologies valid for multiple applications, such as algebraic manipulation, (e) computer applications, such as computer graphics, and  (f) non-technical aspects, such as computer education.
 
-Looking beyond Salton and Bergmark's historical triad of theoretical foundations, hardware and computer systems, and software, the Computing Classification System (CCS) published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field~\cite{acm_ref}.
+Looking beyond this historical triad of theoretical foundations, hardware and computer systems, and software, the Computing Classification System (CCS) published by the Association for Computing Machinery now consists of 13 top-level areas that reflect a more current view of the field~\cite{acm_ref}.
 This classification also addresses relationships with other fields under the category of Applied Computing.
@@
 
-Other classification systems are available, such as the All Science Journal Classification (ASJC) developed and maintained by Scopus, the Web of Science research and categorical classifications from Clarivate Analytics, and the NSF classification system~\cite{nsf_classification} [add citations for Scopus and Web of Science].
+Other classification systems are available, such as the All Science Journal Classification (ASJC) developed and maintained by Scopus, the Web of Science research and categorical classifications from Clarivate Analytics, and the National Science Foundation classification system~\cite{nsf_classification,scopus_ref,wos_ref}.
 Scopus and the Web of Science also include comprehensive bibliographies with citation links and proprietary unique identifiers for publications.
+The Scopus All Science Journal Classification (ASJC), which we use in this study is organized under into 4 subject areas, 27 major subject areas, and 334 minor subject areas.
 All three systems rely on applying one or more journal-derived labels to articles.
@@
 Others have also discussed and critiqued disciplinary assignments using journal-based classifications~\cite{wang_large-scale_2016,perianes-rodriguez_comparison_2017}. 
-Article classification systems have been constructed that escape some of the criticisms of journal-based classification~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012}, but do not enjoy widespread use.
-[Add reference to Scandinavian paper in QSS].
+Article classification systems have been constructed that escape some of the criticisms of journal-based classification~\cite{traag_louvain_2019,boyack_classification_2014,waltman_new_2012}, but do not seem to presently enjoy widespread use.
 
-In this study, we extend the work of Salton and Bergmark by combining article and journal approaches to study trends in computer science, while also considering connections to other fields, especially biology, which dominates the total number of scientific publications and is citationally active [need to tweak].
-As a source of computer science literature, we used DBLP, a reference bibliography for computer science~\cite{dblp_ref}.
+In this study, we extend the work of Salton and Bergmark by combining article and journal approaches to study trends in computer science, while also considering connections to other fields, especially biology since approximately 42\% of Scopus is classified under the top level subject areas of Life Sciences and Health Sciences.
+As a source of computer  literature, we used DBLP, a reference bibliography for computer science~\cite{dblp_ref}.
 The DBLP bibliography covers publications from computer science and includes publications from hybrid fields, where they are considered pertinent to computer science research.
-We describe below the high-level interactions of computer science within the Physical Sciences, and with the Social Sciences, Life Sciences, and Health Sciences [What did we find?
-Some kind of preview sentence!].
+We describe below the high-level interactions of computer science within the Physical Sciences, and with the Social Sciences, Life Sciences, and Health Sciences.
 
@@
 
- \subsection{Overview}
- In our study of the structure of a twenty year cohort of the computer science literature, we chose to use both traditional journal-based and article-based approaches.
-Considering that traditional disciplines `may only partly reflect the actual organization of today's scientific research'~\cite{waltman_new_2012}, we constructed article clusters at high levels of aggregation using citations to examine the  computer science literature (as represented in our \emph{comp} dataset, described below) and mapped these clusters to journal-based categories.
-
- Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation, with direct citation being proposed as as the best approach to concentrate citation links~\cite{klavans_which_2017}.
-Accordingly, we used direct citation links as the basis for cluster formation, and also co-citation to obtain an alternative view.
-
-For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography that (i) had a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography.
+ \emph{Overview} For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography that (i) had a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography.
 The underlying assumption is that records in DBLP are greatly enriched for computer science even while recognizing that coverage may be incomplete and possibly biased.
@@
 
-\subsection{Data}
-A stable release of the DBLP computer science bibliography~\cite{dblp_ref} consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz.
+\emph{Data} A stable release of the DBLP computer science bibliography~\cite{dblp_ref} consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz.
 Slightly over 95\% of the publications within were published after 1996.
@@
 
-\subsection{Clustering methods} In applying both clustering by direct citation and by co-citation, we attempted to consider, wherever possible, the criteria articulated by \v{S}ubelj, van Eck, and Waltman~\cite{subelj_clustering_2016} that (i) the largest cluster should be no more than 10 times the smallest one, (ii) small clusters should be eliminated, (iii) small changes and replicates should yield similar results (``stability"),  (iv) computing time should be minimized where possible, and (v) the clustering should seem reasonable on a qualitative level (``intuitive sensibility").
+\emph{Clustering} Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation, with direct citation being proposed as as the best approach to concentrate citation links~\cite{klavans_which_2017}.
+Accordingly, we used direct citation links as the basis for cluster formation, and also co-citation to obtain an alternative view.
+In applying both clustering by direct citation and by co-citation, we attempted to consider, wherever possible, the criteria articulated by \v{S}ubelj, van Eck, and Waltman~\cite{subelj_clustering_2016} that (i) the largest cluster should be no more than 10 times the smallest one, (ii) small clusters should be eliminated, (iii) small changes and replicates should yield similar results (``stability"),  (iv) computing time should be minimized where possible, and (v) the clustering should seem reasonable on a qualitative level (``intuitive sensibility").
 
-\paragraph{Clustering by Direct Citation.} Graclus~\cite{graclus_2007} is a spectral graph clustering package that optimizes  various clustering criteria, including normalized cut, ratio cut, and ratio association, that has previously been applied to citation data~\cite{subelj_clustering_2016}.
+ \emph {Direct Citation} Graclus~\cite{graclus_2007} is a spectral graph clustering package that optimizes  various clustering criteria, including normalized cut, ratio cut, and ratio association, that has previously been applied to citation data~\cite{subelj_clustering_2016}.
 We used v1.2 in our experiments.
@@
 At around 20 clusters, clusters size was relatively stable with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{subelj_clustering_2016}.
-Consequently, we used Graclus to generate 20 clusters, labeled 0-19 (Table~\ref{tab:graclus}), analogous to Level 1 of Waltman and van Eck's mapping of nearly 10 million publications~\cite{waltman_new_2012} but focused on the DBLP bibliography.
+Consequently, we used Graclus to generate 20 clusters, labeled 0-19 (Table~\ref{tab:graclus}), analogous to Level 1 of Waltman and van Eck's mapping of nearly 10 million publications but focused on the DBLP bibliography rather than a broader Web of Science sample~\cite{waltman_new_2012}.
 
 We also used conductance, as defined in Shun et al.~\cite{shun_parallel_2016}, to  evaluate clustering by direct citation (smaller is better), noting that conductance has been found to be a good metric for this purpose~\cite{emmons2016analysis,almeida_2012}.
-%Tandy, George - add reference to Zaki paper as well
-In our analysis, we saw that the last cluster (cluster 19) had a much larger conductance value than the other clusters and also had the smallest
-number of nodes.
-We then examined
-results obtained using Graclus with two other numbers of clusters (18 and 22), and
-in each case, the highest numbered cluster  had the greatest conductance value and also the smallest number of nodes.
+In our analysis, we saw that the last cluster (cluster 19) had a much larger conductance value than the other clusters and also had the smallest number of nodes.
+We then examined results obtained using Graclus with two other numbers of clusters (18 and 22), and in each case, the highest numbered cluster had the greatest conductance value and also the smallest number of nodes.
 These results suggest that Graclus produces a final cluster that effectively serves as a container for `left over publications' during the clustering procedure.
@@
 
-\paragraph{Clustering by Co-Citation.}
-
-For an alternate view of these DBLP data, we constructed clusters using co-citation, the frequency with which a pair of articles is cited by other articles \cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}.
-% and has been used for clustering publications.
-%George, add citation
+\emph{Co-Citation.} For an alternate view of these DBLP data, we constructed clusters using co-citation, the frequency with which a pair of articles is cited by other articles \cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}.
 Co-citation, first described independently by Small and Marshakova in 1973 \cite{marshakova-shaikevich_co-citation_1973}, provides insight into the emergence of new ideas derived from the association of previously independent ones.
@@
 
-%For clustering, we applied a variant of variable level clustering (VLC, described below) followed by 600 iterations of agglomeration of the clusters resultant from VLC since further rounds of agglomeration resulted in the development of a single large cluster (Fig.~\ref{fig:merge_select}).
-To focus on major clusters, we also restricted agglomeration to clusters containing at least 10 nodes.
-Consequently, the 20 largest clusters were used for further analysis and comparison with clusters generated by direct citation.
-The largest of these 20 clusters contained 1,276 nodes and the smallest contained 136, with total nodes summing to 8,042.
-
-We used a modification of variable level clustering combined with agglomerative clustering, an approach developed in 1985 by Small and Sweeney~\cite{small_clustering_1985} for co-citation analysis.
-Variable level clustering involves applying a threshold (below which all edges in a graph are deleted) then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn.
+We used a modification of variable level clustering combined with agglomerative clustering, an approach developed in 1985 by Small and Sweeney~\cite{small_clustering_1985} for co-citation analysis.Variable level clustering involves applying a threshold (below which all edges in a graph are deleted) then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn.
 Three parameters are needed: (i) a threshold or starting level based on a quantile of normalized co-citation frequency, (ii) a level increment, and (iii) a maximum cluster size.
@@
 A total of 46,463,117 unique co-cited pairs were thus obtained.
-The frequency of these co-cited pairs was then computed across the \emph{comp} dataset  and normalized using Salton's cosine formula~\cite{salton_citation_1979}.
+The frequency of these co-cited pairs was then computed across the \emph{comp} dataset  and normalized using Salton's cosine formula~\cite{salton_citation_1979} to limit dominance by areas with high citation activity.
 These data were represented in a graph where each node was a publication and the weighted edge between the pair was the normalized co-citation frequency.
@@
 All edges were then re-ordered as before and the next pair of clusters was merged.
-The process was halted after 600 rounds to prevent large outlier clusters being generated (Fig.~\ref{fig:quad-chart}).
+The process was halted after 600 rounds to prevent large outlier clusters being generated (Fig.~\ref{fig:quad-chart}, panel d).
 
@@
 
-\subsection{Data}
-The process of selection and matching resulted in a dataset of  publications (Materials and Methods).
+ In our high-level study of the structure of a twenty year cohort of the computer science literature, we chose to use both traditional journal-based and article-based approaches.
+Considering that traditional disciplines `may only partly reflect the actual organization of today's scientific research'~\cite{waltman_new_2012}, we constructed article clusters at high levels of aggregation using citations to examine the  computer science literature and mapped these clusters to journal-based categories.
+
+\emph{Data} The process of selection and matching resulted in a dataset of  publications (Materials and Methods).
 Of 4,291,130 DBLP publications with DOIs, only  2,685,356 had corresponding DOIs in Scopus.
@@
 Publications in the \emph{comp} dataset labeled Theoretical Computer Science (409,082) are classified under the the major subject area of Mathematics rather than Computer Science (Table~\ref{tab:comp}).
+
+\iffalse
 Overall, 38.86\% of the publications were assigned to one minor subject area, 78.1\% to two minor subject areas, 90.9\% to three minor subject areas, and 0.0003\% assigned to 8 different minor subject areas.
+\fi
 
-%George, please consider revising this text
-%the sets of computer science publications in DBLP and Scopus are partially overlapping rather than DBLP being a perfect subset of Scopus.
-[the point being that we should justify our use of both journal and article level classifications].
-
-\subsection{Clustering by Direct Citation}
-
-We constructed article-level clusters of this computer science dataset at a sufficiently high level of aggregation to avoid cognitive challenge and cross-matched them to  the  Scopus ASJC classification.
+\emph{Clustering by Direct Citation} We constructed article-level clusters of this computer science dataset at a sufficiently high level of aggregation to avoid cognitive challenge and cross-matched them to the Scopus ASJC classification.
 To focus on relatively high signal, we only considered Scopus ASJC minor subject area categories that accounted for at least 15\% of the publications in each cluster.
@@
 Figure~\ref{fig:heatmap} permits examination of these data from two perspectives: (i) rows: the clusters that map to a given ASJC minor subject area (ii) columns: ASJC minor subject areas that comprised at least 15\% of the publication in a cluster.
-Under these conditions of clustering and a threshold of 15\%, 31 of the 334 ASJC minor subject areas are represented.
+Under these conditions of clustering and this threshold of 15\%, 31 of the 334 ASJC minor subject areas are represented.
 Unsurprisingly, the broad categories Computer Science Applications, Software, and Electrical and Electronic Engineering register in 16, 12, and 10 clusters respectively, while Artificial Intelligence mapped to 7 different clusters.
@@
 These data suggest that areas central to computer science in 2019 (Salton and Bergmark's historical triad of hardware, software, and theory) are more likely to be found in multiple clusters than peripheral topics.
-%, whereas areas such as biology, chemistry, and statistics are more restricted in distribution.  
 A second inference is that, in some cases, journal-based classification and our article clusters align fairly well (Hardware and Architecture).
-A third inference is that the ASJC minor subject area ``Computer Applications" is relatively non-specific, and publications thus labeled are nearly ubiquitous (present in 16 out of 20 clusters).
-Finally,   for the DBLP dataset, interactions with fields outside computer science (e.g., Biochemistry)  are  typically restricted to a single cluster or found in a small number of clusters.
+A third inference is that the ASJC minor subject area ``Computer Applications" is relatively broad, and publications thus labeled are present at the $>=$ 15\% level in 16 out of 20 clusters).
+Finally,   for this DBLP dataset, as we clustered it, interactions with fields outside computer science such as Biology are (Biochemistry, Neurology)  are  detected in two separate clusters.
+The first appears to be the interaction of Biochemistry, Molecular Biology, and Genetics with Statistics, Mathematics, and Computer Science.
+The second is the interaction of Neurology, Cognitive Neuroscience, and Artificial Intelligence.
 
-We also note that these clusters cannot be adequately characterized by using a single CCS classification, a challenge that has been previously noted \cite{waltman_new_2012}.
-For example, we
-manually matched the top 25--50 most heavily cited publications in each cluster to corresponding categories in the CCS.
-This was feasible in some cases, but not in all.
-For example, clusters 0 and 1 mapped reasonably well to the top level categories Hardware and Computer Systems Organization,  but
-the top cited papers often derived from biology and yet biology was clearly not  representative of any of these affected clusters.
+These clusters cannot be easily characterized by using the CCS classification.
+For example, we manually matched the top 25--50 most heavily cited publications in each cluster to corresponding categories in the CCS.
+This was feasible with clusters 0 and 1 mapped reasonably well to the top level categories Hardware and Computer Systems Organization, but in other cases, the top cited papers often derived from biology, yet biology was clearly not  representative of the majority of the nodes in these clusters.
 
-\subsection{Clustering by Co-citation.} 
-For an alternate examination of the data, we used co-citation frequencies to cluster the DBLP dataset as described above.
-Figure \ref{fig:heatmap_cocit} shows a heatmap in which clusters constructed by co-citation are mapped to Scopus ASJC minor subject areas, with the top subfigure showing results for those labels that
-account for at least 15\% of the publications in a cluster, and the bottom subfigure showing results for those labels that account for at least 10\% of the publications.
-%Mappings are only shown if they account for at least 15\% of the publications in a cluster (upper panel). 
-Under these conditions, only 17 of 20 clusters mapped to minor subject areas where at least 15\% of the nodes in a cluster were labeled with a given subject area.
-When the threshold was reduced to 10\%, all 20 clusters indicated at least one mapping to a minor subject area.
-We interpret these data as indicative of two kinds of co-citational linkages (i) intra-cluster (ii) cross cluster.
-The latter predominates and is detected at lower thresholds (lower panel).
-No cluster maps to more than three minor subject area at the 15\% threshold,  in contrast to a maximum of eight minor subject areas for clustering by direct citation (Fig.
-3, Cluster 17).
-It should be noted, however, that the size of clusters constructed by co-citation is much smaller than those generated by direct citation through Graclus.
-%George, add some comments and discussion
+\emph{Clustering by Co-citation.} For an alternate examination of the data, we used co-citation frequencies to cluster the DBLP dataset as described above (Materials and Methods).
+Figure \ref{fig:heatmap_cocit} shows a heatmap in which clusters constructed by co-citation are mapped to Scopus ASJC minor subject area labels, with the top subfigure showing results for those labels that account for at least 15\% of the publications in a cluster, and the bottom subfigure showing results for those labels that account for at least 10\% of the publications.
 
-We also mapped the contents of clusters generated by direct citation and co-citation to each other, Fig~\ref{fig:graclus_cocit_fig}.
+At the threshold of 15\%, only 17 of 20 co-citation clusters mapped to at least one minor subject areas.
+In contrast to a maximum of eight minor subject areas for clustering by direct citation at the 15\% threshold (Fig.
+3, Cluster 17), no co-citation cluster maps to more than three minor subject areas.
+The threshold had to be reduced to 10\%, for all 20 co-citation clusters to map to at least one minor subject area.
+We interpret these data as indicative of broader clusters created by weaker linkages that accumulate during the agglomerative clustering phase~\cite{small_clustering_1985}.
 
-\section{Discussion} In this article, we revisited a characterization of computer science from 1979~\cite{salton_citation_1979} in the light of expansion and diversification of this field.
-We analyzed considerably more data, 2.68 million publications versus 391, and leveraged access to two bibliographic databases, DBLP and Scopus.
-The former identifies a sample of the scientific literature that is computer science and the latter (roughly 10 times larger at 87.XX million publications) enabled analyzing citations across the four major groups of Physical Science, Social Sciences, Life Sciences, and Health Sciences in the Scopus ASJC classification.
+Clustering by co-citation begins, for each cluster, with a pair of nodes that nucleates its subsequent formation.
+Thus, we also designated the pair of nodes in a cluster with the strongest edge as its nucleating cluster and labeled the cluster by inspecting this pair of documents and assigning an intuitive label to it.
+These labels are compared to the minor subject area that accounts for the largest fraction of the nodes in a co-citation cluster (Table~\ref{tab:centroid_reconcile}).
+The extent of correspondence between the manually applied label and the ASJC minor subject area suggest that using the nucleating cluster as the basis for labeling co-citation clusters (as we generated them) may be valid although its usefulness is likely to vary according to the data being examined.
+We provide the DOIs of these nucleating pairs matched to manually assigned labels for independent review (Table~\ref{tab:centroid}.
 
-Obvious critiques of our approach are: (i) use of the DBLP dataset, which may not capture all aspects of computer science and its interactions with other fields, (ii) partitioning DBLP into a weakly justified number of clusters and arbitrarily defined thresholds for detection, and (iii) mapping the results of this clustering against a classification designed around journals rather than individual articles.
-Our focus on high-level features and preference for simplicity and intuitiveness in our choice of methods may mitigate these concerns.
+To examine the correspondence between clusters generated by direct citation vs co-citation, we mapped the contents of these clusters to each other, Fig~\ref{fig:graclus_cocit_fig}.
+At a threshold of 15\%, similar to other cross-matching, 90\% (18/20) of the co-cited clusters mapped to 1 or 2 direct citation clusters.
+This suggests that the majority of co-cited pairs tend to lie within the same cluster of publications linked by citations and by extension, tend towards disciplinarity rather then interdisciplinarity.
 
-Reconciling direct citation clusters to the Scopus ASJC classification yielded results that are consistent with the observation of Waltman and van Eck (2012)~\cite{waltman_new_2012}, `that traditional disciplines such as those just mentioned only partly reflect the actual organization of today’s scientific research'.
-Of interest to us, was the single obviously multidisciplinary cluster in which at least 15\% of its component publications were labeled with the ASJC minor subject areas Biochemistry, Chemistry, Computational Mathematics, Computational Theory and Mathematics, Computer Science Applications, Genetics, Molecular Biology, Statistics \& Probability, followed by the cluster mapping to Artificial Intelligence, Cognitive Neuroscience, and Neurology.
-Perhaps at the opposite end of this spectrum is the more insular cluster that maps to Hardware and Architecture, Electrical and Electronic Engineering, and Software.
-To us, these data suggest that some subfields within computer science are primarily inward looking (remain concerned with fundamental questions in computer science), while others are more actively engaged with fields external to computer science.
+\section{Discussion} Considering expansion and diversification of the field of computer science, we revisited its characterization in 1979~\cite{salton_citation_1979} .
+In comparison to Salton and Bergmark, we analyzed considerably more data, 2.68 million publications versus 391 by using two bibliographic databases, DBLP and Scopus, consisting of  7.1 million and 87.8 million publications respectively.
+By linking the two datasets to harvest citation and metadata, we were able to construct article level clusters in two different ways and reconcile these clusters with the Scopus ASJC classification, which provides a journal level perspective.
+
+Reconciling direct citation clusters to the Scopus ASJC classification yielded partially overlapping results that are consistent with the observation of Waltman and van Eck (2012)~\cite{waltman_new_2012}, `that traditional disciplines such as those just mentioned only partly reflect the actual organization of today’s scientific research'.
+Of interest to us, was the single obviously multidisciplinary cluster in which at least 15\% of its component publications were labeled with the ASJC minor subject areas Biochemistry, Chemistry, Computational Mathematics, Computational Theory and Mathematics, Computer Science Applications, Genetics, Molecular Biology, Statistics \& Probability.
+A second cluster mapped to Artificial Intelligence, Cognitive Neuroscience, and Neurology.
+Both suggest collaboration between computer science and biology.
+At the opposite end of this spectrum is the, perhaps more insular, cluster that maps to Hardware and Architecture, Electrical and Electronic Engineering, and Software.
+These data suggest that, at least from the perspective of a high level of aggregation, some subfields within computer science may be primarily inward looking (remain concerned with fundamental questions in computer science and electrical engineering), while others are more actively engaged with fields external to computer science.
 
 Analyzing clusters generated using co-citation links is more challenging.
-The data suggest two patterns that may co-exist.
-One in which the nodes in a co-citation cluster are detected at the threshold applied mostly from a single or two direct citation clusters.
-The second, which may account for more than 50\% of the nodes in a co-citation cluster, in which these nodes are distributed across all 20 direct citation clusters.
+The data suggest two co-existing patterns.
+One in which the nodes in a co-citation cluster map largely to one or two direct citation clusters.
+The second, which may account for more than 50\% of the nodes in a co-citation cluster, is where the nodes in co-citation cluster are distributed across all 20 direct citation clusters.
 The latter is intriguing in its implications of a web of such citational links gluing the body of scientific literature together.
 
-Emerging interactions of computer science and other disciplines, so papers are related by the communities they impact (co-citation clustering). [Over to Tandy]
+Reasonable critiques of our approach are: (i) use of the DBLP dataset and the efficiency of matching to Scopus, which may not capture all aspects of computer science and its interactions with other fields, (ii) the basis for clustering and (iii) mapping the results of this clustering against a classification designed around journals rather than individual articles.
+Our focus on high-level features and a preference for simplicity and intuitiveness in our choice of methods may mitigate these concerns.
 
-\emph{need to cite Granovetter somewhere for definition of strong and weak ties that Small refers to}
 \clearpage
@@
 18 & 43,113 & 0.20 & 108,518 & 177 \\ 
-19 & 12,615 & 0.80 & 36,583 & 229 \\ \noalign{\smallskip}\hline
+19 & 12,615 & 0.80 & 36,583 & 229 \\ 
+\noalign{\smallskip}\hline
 \end{tabular}
 \end{table}
+\newpage
+
+\begin{table}[ht]
+\caption{\emph{Co-citation Centroid}}
+\label{tab:centroid_reconcile}       
+\begin{tabular}{p{8 mm}p{42 mm}l}
+\hline\noalign{\smallskip}
+Cluster & Label & CC  \\
+\noalign{\smallskip}\hline
+18670 & Dynamical Systems & EEE (14)  \newline Control/Systems Eng (14) \\
+18892 & Operations Research & EEE (24) \\ 
+18918 & Image Processing & EEE (17)  \newline Software (17) \\ 
+18947 & Robotics & Software (12) \\ 
+18956 & Computer Vision & Comp Graphics and Comp-Aided Design (21)\\ 
+18972 & Software & Software (55) \\ 
+18974 & Applied Mathematics & Applied Mathematics (12)\\ 
+18983 & Optimization & EEE (35) \\ 
+18997 & Chaotic Systems & Control/Systems Eng (23)\\ 
+19008 & Hum Comp Interaction & Education (19)\\ 
+19009 & Artificial Intelligence & Computer Vision and Pattern Recognition (32)\\ 
+19013 & Security & Computer Science(all) (29)\\ 
+19026 & Architecture & EEE (35) \\ 
+19027 & Graph algorithms & Computer Networks and Communications (19)\\ 
+19030 & Databases & Software (19)\\ 
+19031 & Networks & EEE (32)\\ 
+19033 & Facial Recognition & Comp Vision and Pattern Recognition (18)\\ 
+19034 & Neurology & Neurology (12)\\ 
+19035 & Intelligent Systems & Artificial Intelligence (17)\\ 
+19036 & Comp Geometry & Software (10)\\ 
+\noalign{\smallskip}\hline
+\end{tabular}
+\end{table}
+
+\begin{table}[ht]
+\caption{\emph{Co-citation Centroid}}
+\label{tab:centroid}       
+\begin{tabular}{p{8 mm}p{42 mm}ll}
+\hline\noalign{\smallskip}
+Cluster & Nucleating Pair & NCF & Label \\
+\noalign{\smallskip}\hline
+18670 & 10.1016/j.cam.2015.03.057 10.1016/j.sigpro.2015.10.009 & 0.92 & Dynamical Systems \\
+18892 & 10.1287/msom.1080.0228 10.1287/msom.1060.0190 & 0.72 & Operations Research\\ 
+18918 & 10.1007/s11128-010-0177-y 10.1007/s11128-013-0567-z & 0.83 & Image Processing\\ 
+18947 & 10.1109/TASE.2011.2160452 10.1109/TASE.2011.2178023 & 0.77 & Robotics\\ 
+18956 & 10.1109/ICCV.2017.32 10.1109/ICCV.2017.31 & 0.84 & Computer Vision\\ 
+18972 & 10.1109/ASE.2013.6693094 10.1145/2568225.2568254 & 0.69 & Software \\ 
+18974 & 10.1016/j.amc.2009.03.023 10.1016/j.amc.2010.07.064 & 0.54 & Applied Mathematics\\ 
+18983 & 10.1137/110848864 10.1137/110848876 & 0.66 & Optimization\\ 
+18997 & 10.1504/IJMIC.2014.065339 10.1504/IJMIC.2015.068871 & 0.91 & Chaotic Systems \\ 
+19008 & 10.1016/j.chb.2008.12.013 10.1016/j.chb.2008.12.012 & 0.63 & Hum Comp Interaction\\ 
+19009 & 10.1109/AVSS.2017.8078491 10.1109/ICCV.2017.206 & 0.78 & Artificial Intelligence\\ 
+19013 & 10.1145/2508859.2516668 10.1007/978-3-642-42045-0\_15 & 0.88 & Security\\ 
+19026 & 10.1145/2541940.2541942 10.1109/HPCA.2014.6835965 & 0.81 & Architecture\\ 
+19027 & 10.1016/S0305-0548(03)00250-8 10.1016/j.ejor.2006.03.013 & 0.82 & Graph algorithms\\ 
+19030 & 10.1109/ICDE.2008.4497474 10.14778/1687627.1687666 & 0.69 & Databases \\ 
+19031 & 10.1109/TMM.2005.843347 10.1109/TCE.2005.1405724 & 0.55 & Networks\\ 
+19033 & 10.1109/TIFS.2014.2327757 10.1109/TCYB.2014.2376934 & 0.78 & Facial Recognition\\ 
+19034 & 10.1016/j.neuroimage.2013.05.018 10.1016/j.neuroimage.2014.06.016 & 0.63 & Neurology\\ 
+19035 & 10.1002/int.21933 10.1002/int.21927 & 1.09 & Intelligent Systems\\ 
+19036 & 10.1006/jsco.2000.0402 10.1006/jsco.2000.0403 & 0.73 & Comp Geometry\\ 
+\noalign{\smallskip}\hline
+\end{tabular}
+\end{table}
+\newpage
+
 \newpage

### 2019-12-20 Scientometrics/comp.tex
minor edits

@@
 Scopus and the Web of Science also include comprehensive bibliographies with citation links and proprietary unique identifiers for publications.
-The Scopus All Science Journal Classification (ASJC), which we use in this study is organized under into 4 subject areas, 27 major subject areas, and 334 minor subject areas.
+The Scopus All Science Journal Classification (ASJC), which we use in this study, is organized  into 4 subject areas, 27 major subject areas, and 334 minor subject areas.
 All three systems rely on applying one or more journal-derived labels to articles.
@@
 
- \emph{Overview} For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography that (i) had a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography.
+ \emph{Overview} For the purpose of this study, our working definition of the computer science literature is all publications in the DBLP bibliography that (i) had a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography.
 The underlying assumption is that records in DBLP are greatly enriched for computer science even while recognizing that coverage may be incomplete and possibly biased.
-Cross-matching DBLP publications to records in the Scopus abstract and citation database of peer-reviewed literature, enabled us to harvest the richer links in Scopus as well as extract links to publications from other disciplines.
+Cross-matching DBLP publications to records in the Scopus abstract and citation database of peer-reviewed literature enabled us to harvest the richer links in Scopus as well as extract links to publications from other disciplines.
 This cross-matching to Scopus also allows the use of both journal and article based classifications when clustering documents.
@@
 As part of implementing a larger data platform for research evaluation~\cite{GithubERNIE2019}, we have previously parsed the Scopus dataset, presently at over 87.8 million publications, into a custom schema in a PostgreSQL database.
-The total number of publications in Scopus labeled with major subject area of Computer Science (in turn a subset of the Physical Sciences subject area) is 5,835,160.
+The total number of publications in Scopus labeled with major subject area Computer Science (in turn a subset of the Physical Sciences subject area) is 5,835,160.
 Records in the DBLP dataset were matched to Scopus identifiers using digital object identifiers (DOIs).
@@
 
- \emph {Direct Citation} Graclus~\cite{graclus_2007} is a spectral graph clustering package that optimizes  various clustering criteria, including normalized cut, ratio cut, and ratio association, that has previously been applied to citation data~\cite{subelj_clustering_2016}.
+ \emph {Direct Citation} Graclus~\cite{graclus_2007} is a spectral graph clustering package that optimizes  various clustering criteria, including normalized cut, ratio cut, and ratio association, and that has previously been applied to citation data~\cite{subelj_clustering_2016}.
 We used v1.2 in our experiments.
@@
 
-We used a modification of variable level clustering combined with agglomerative clustering, an approach developed in 1985 by Small and Sweeney~\cite{small_clustering_1985} for co-citation analysis.Variable level clustering involves applying a threshold (below which all edges in a graph are deleted) then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn.
+We used a modification of variable level clustering combined with agglomerative clustering, an approach developed in 1985 by Small and Sweeney~\cite{small_clustering_1985} for co-citation analysis.
+Variable level clustering involves applying a threshold (below which all edges in a graph are deleted) then iteratively selecting edges with the highest normalized co-citation value and extracting connected components from the graph as clusters for each edge in turn.
 Three parameters are needed: (i) a threshold or starting level based on a quantile of normalized co-citation frequency, (ii) a level increment, and (iii) a maximum cluster size.
@@
 We applied variable clustering with initial parameters as follows: the threshold  $t$  is initially set to  the median normalized co-citation frequency (quantile=0.5), increment $i = 0.1$, and maximum cluster size, $mcs=200$.
-Thus, at start, all edges below the median normalized co-citation frequency were deleted.
+Thus, at the start, all edges below the median normalized co-citation frequency were deleted.
 Clusters were formed by assembling connected components from each co-cited pair beginning with the heaviest edge weight.
@@
 Using this approach, 22,232 clusters containing 84,591 nodes were generated, each containing less than 100 nodes.
-Clusters containing only 2 nodes were discarded, bringing the total number of clusters down to 10,298.
+Clusters containing only two nodes were discarded, bringing the total number of clusters down to 10,298.
 The publications in these 10,298 clusters were overwhelmingly drawn from the Physical Sciences (one of the four top level categories in the Scopus ASJC classification), of which computer science is a sub-category (Fig.~\ref{fig:quad-chart}).
@@
 Of these roughly 2.68 million publications, approximately 2.07 million were assigned ASJC codes in Scopus corresponding to Computer Science (major subject area with 13 minor subject areas (Table~\ref{tab:comp}), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (Fig.~\ref{fig:ar_cp_annotation}).
-The set of 2.07 million publications classified under the major subject area Computer Science in Scopus spanned all 13 minor subject areas with Software 30.3\% being the largest component and Computer Science (miscellaneous) 0.9\% the smallest.
+The set of 2.07 million publications classified under the major subject area Computer Science in Scopus spanned all 13 minor subject areas with Software at 30.3\%  being the largest component and Computer Science (miscellaneous) at 0.9\% the smallest.
 Publications in the \emph{comp} dataset labeled Theoretical Computer Science (409,082) are classified under the the major subject area of Mathematics rather than Computer Science (Table~\ref{tab:comp}).
@@
 
-Figure~\ref{fig:heatmap} permits examination of these data from two perspectives: (i) rows: the clusters that map to a given ASJC minor subject area (ii) columns: ASJC minor subject areas that comprised at least 15\% of the publication in a cluster.
+Figure~\ref{fig:heatmap} permits examination of these data from two perspectives: (i) rows: the clusters that map to a given ASJC minor subject area and (ii) columns: ASJC minor subject areas that comprised at least 15\% of the publication in a cluster.
 Under these conditions of clustering and this threshold of 15\%, 31 of the 334 ASJC minor subject areas are represented.
@@
 Cluster 19 mapped to two areas but was excluded from qualitative analysis because of its high conductance value.
-Of the remaining clusters, Cluster 2 represents interactions between the minor subject areas Theoretical Computer Science, Discrete Mathematics and Combinatorics, and Applied Mathematics as well as the more generic Computer Science (all).
+Of the remaining clusters, Cluster 2 represents interactions between the four minor subject areas Theoretical Computer Science, Discrete Mathematics and Combinatorics, Applied Mathematics,  and the more generic Computer Science (all).
 Clusters 3 and 4 include Computer Networks and Communications, and Cluster 18 (Artificial Intelligence, Cognitive Neuroscience, and Neurology) and clusters 5--9 include Management Science, Operations Research, Information Systems, Modeling and Simulation, and Human-Computer Interaction.
@@
 A second inference is that, in some cases, journal-based classification and our article clusters align fairly well (Hardware and Architecture).
-A third inference is that the ASJC minor subject area ``Computer Applications" is relatively broad, and publications thus labeled are present at the $>=$ 15\% level in 16 out of 20 clusters).
+A third inference is that the ASJC minor subject area ``Computer Applications" is relatively broad, and publications thus labeled are present at the $>=$ 15\% level in 16 out of 20 clusters.
 Finally,   for this DBLP dataset, as we clustered it, interactions with fields outside computer science such as Biology are (Biochemistry, Neurology)  are  detected in two separate clusters.
-The first appears to be the interaction of Biochemistry, Molecular Biology, and Genetics with Statistics, Mathematics, and Computer Science.
-The second is the interaction of Neurology, Cognitive Neuroscience, and Artificial Intelligence.
+The first appears to be the interaction of Biochemistry, Molecular Biology, and Genetics with Statistics, Mathematics, and Computer Science, and the second is the interaction of Neurology, Cognitive Neuroscience, and Artificial Intelligence.
 
@@
 3, Cluster 17), no co-citation cluster maps to more than three minor subject areas.
-The threshold had to be reduced to 10\%, for all 20 co-citation clusters to map to at least one minor subject area.
+The threshold had to be reduced to 10\% for all 20 co-citation clusters to map to at least one minor subject area.
 We interpret these data as indicative of broader clusters created by weaker linkages that accumulate during the agglomerative clustering phase~\cite{small_clustering_1985}.
@@
 Clustering by co-citation begins, for each cluster, with a pair of nodes that nucleates its subsequent formation.
-Thus, we also designated the pair of nodes in a cluster with the strongest edge as its nucleating cluster and labeled the cluster by inspecting this pair of documents and assigning an intuitive label to it.
-These labels are compared to the minor subject area that accounts for the largest fraction of the nodes in a co-citation cluster (Table~\ref{tab:centroid_reconcile}).
-The extent of correspondence between the manually applied label and the ASJC minor subject area suggest that using the nucleating cluster as the basis for labeling co-citation clusters (as we generated them) may be valid although its usefulness is likely to vary according to the data being examined.
+Thus, we also designated the pair of nodes in a cluster with the strongest edge as its nucleating pair and labeled the cluster by inspecting this pair of documents and assigning an intuitive label to it.
+These labels show high degree of correspondence  to the ASJC minor subject area that accounts for the largest fraction of the nodes in a co-citation cluster (Table~\ref{tab:centroid_reconcile}).
+The extent of this correspondence %between the manually applied label and the ASJC minor subject area 
+suggests that using the nucleating cluster as the basis for labeling co-citation clusters (as we generated them) may be valid, although its usefulness is likely to vary according to the data being examined.
 We provide the DOIs of these nucleating pairs matched to manually assigned labels for independent review (Table~\ref{tab:centroid}.
 
-To examine the correspondence between clusters generated by direct citation vs co-citation, we mapped the contents of these clusters to each other, Fig~\ref{fig:graclus_cocit_fig}.
+To examine the correspondence between clusters generated by direct citation vs co-citation, we mapped the contents of these clusters to each other (Fig~\ref{fig:graclus_cocit_fig}).
  At a threshold of 15\%, similar to other cross-matching, 90\% (18/20) of the co-cited clusters mapped to 1 or 2 direct citation clusters.
-This suggests that the majority of co-cited pairs tend to lie within the same cluster of publications linked by citations and by extension, tend towards disciplinarity rather then interdisciplinarity.
+This suggests that the majority of co-cited pairs tend to lie within the same cluster of publications linked by citations and,  by extension, tend towards disciplinarity rather than interdisciplinarity.
 
-\section{Discussion} Considering expansion and diversification of the field of computer science, we revisited its characterization in 1979~\cite{salton_citation_1979} .
+\section{Discussion} Considering expansion and diversification of the field of computer science, we revisited its characterization in 1979~\cite{salton_citation_1979}.
 In comparison to Salton and Bergmark, we analyzed considerably more data, 2.68 million publications versus 391 by using two bibliographic databases, DBLP and Scopus, consisting of  7.1 million and 87.8 million publications respectively.
@@
 
-Reconciling direct citation clusters to the Scopus ASJC classification yielded partially overlapping results that are consistent with the observation of Waltman and van Eck (2012)~\cite{waltman_new_2012}, `that traditional disciplines such as those just mentioned only partly reflect the actual organization of today’s scientific research'.
-Of interest to us, was the single obviously multidisciplinary cluster in which at least 15\% of its component publications were labeled with the ASJC minor subject areas Biochemistry, Chemistry, Computational Mathematics, Computational Theory and Mathematics, Computer Science Applications, Genetics, Molecular Biology, Statistics \& Probability.
+Reconciling direct citation clusters to the Scopus ASJC classification yielded partially overlapping results that are consistent with the observation of Waltman and van Eck (2012)~\cite{waltman_new_2012} `that traditional disciplines such as those just mentioned only partly reflect the actual organization of today’s scientific research'.
+Of interest to us was the single obviously multidisciplinary cluster in which at least 15\% of its component publications were labeled with the ASJC minor subject areas Biochemistry, Chemistry, Computational Mathematics, Computational Theory and Mathematics, Computer Science Applications, Genetics, Molecular Biology, Statistics \& Probability.
 A second cluster mapped to Artificial Intelligence, Cognitive Neuroscience, and Neurology.
 Both suggest collaboration between computer science and biology.
-At the opposite end of this spectrum is the, perhaps more insular, cluster that maps to Hardware and Architecture, Electrical and Electronic Engineering, and Software.
+At the opposite end of this spectrum is the perhaps more insular cluster that maps to Hardware and Architecture, Electrical and Electronic Engineering, and Software.
 These data suggest that, at least from the perspective of a high level of aggregation, some subfields within computer science may be primarily inward looking (remain concerned with fundamental questions in computer science and electrical engineering), while others are more actively engaged with fields external to computer science.
@@
 
-Reasonable critiques of our approach are: (i) use of the DBLP dataset and the efficiency of matching to Scopus, which may not capture all aspects of computer science and its interactions with other fields, (ii) the basis for clustering and (iii) mapping the results of this clustering against a classification designed around journals rather than individual articles.
+Reasonable critiques of our approach are: (i) use of the DBLP dataset and the efficiency of matching to Scopus, which may not capture all aspects of computer science and its interactions with other fields, (ii) the basis for clustering, and (iii) mapping the results of this clustering against a classification designed around journals rather than individual articles.
 Our focus on high-level features and a preference for simplicity and intuitiveness in our choice of methods may mitigate these concerns.

### 2019-12-20 Scientometrics/comp.tex
update

--- 2019-12-20 Scientometrics/comp.tex
@@
 \begin{table}[ht]
-\caption{\emph{denominator is 2090947 (some source ids got lost via inner joins and code restrictions) Statistics regarding the 20 clusters produced using direct citation. The \emph{comp} dataset 
-2685021 is because of inner joins on ASJC Explain conductance calculations~\cite{shun_parallel_2016}}}
+\caption{Characterization of the \emph{comp} dataset relative to Scopus ASJC minor subject areas.}
 \label{tab:comp}       
@@
 \begin{table}[ht]
-\caption{\emph{Statistics regarding the 20 clusters produced using direct citation. The \emph{comp} dataset 
-2685021 is because of inner joins on ASJC Explain conductance calculations~\cite{shun_parallel_2016}}}
+\caption{Descriptive statistics of the 20 clusters produced from the \emph{dataset} using Graclus (direct citation).
+The number of publications in each cluster, the conductance~\cite{shun_parallel_2016} of each cluster, the total number ASJC minor subject area labels assigned to publications in each cluster and the number of
+unique labels in each cluster are shown}
 \label{tab:graclus}       
@@
 \begin{table}[ht]
-\caption{\emph{Co-citation Centroid}}
-\label{tab:centroid_reconcile}       
-\begin{tabular}{p{8 mm}p{42 mm}l}
-\hline\noalign{\smallskip}
-Cluster & Label & CC  \\
-\noalign{\smallskip}\hline
-18670 & Dynamical Systems & EEE (14)  \newline Control/Systems Eng (14) \\
-18892 & Operations Research & EEE (24) \\ 
-18918 & Image Processing & EEE (17)  \newline Software (17) \\ 
-18947 & Robotics & Software (12) \\ 
-18956 & Computer Vision & Comp Graphics and Comp-Aided Design (21)\\ 
-18972 & Software & Software (55) \\ 
-18974 & Applied Mathematics & Applied Mathematics (12)\\ 
-18983 & Optimization & EEE (35) \\ 
-18997 & Chaotic Systems & Control/Systems Eng (23)\\ 
-19008 & Hum Comp Interaction & Education (19)\\ 
-19009 & Artificial Intelligence & Computer Vision and Pattern Recognition (32)\\ 
-19013 & Security & Computer Science(all) (29)\\ 
-19026 & Architecture & EEE (35) \\ 
-19027 & Graph algorithms & Computer Networks and Communications (19)\\ 
-19030 & Databases & Software (19)\\ 
-19031 & Networks & EEE (32)\\ 
-19033 & Facial Recognition & Comp Vision and Pattern Recognition (18)\\ 
-19034 & Neurology & Neurology (12)\\ 
-19035 & Intelligent Systems & Artificial Intelligence (17)\\ 
-19036 & Comp Geometry & Software (10)\\ 
-\noalign{\smallskip}\hline
-\end{tabular}
-\end{table}
-
-\begin{table}[ht]
-\caption{\emph{Co-citation Centroid}}
+\caption{\emph{Nucleating Co-citations.} For each of the 20 co-citation clusters, the pair with the strongest edge (greatest normalized co-citation frequency) is shown below along with a manually assigned label}
 \label{tab:centroid}       
@@
 \hline\noalign{\smallskip}
-Cluster & Nucleating Pair & NCF & Label \\
+Cluster & Nucleating Pair & NCF & Manual Label \\
 \noalign{\smallskip}\hline
@@
 
+\begin{table}[ht]
+\caption{\emph{Nucleating Co-citations} Manually assigned labels for nucleating co-cited pairs (Table~\ref{tab:centroid}) are matched to the ASJC minor subject area that constitutes the largest fraction (shown as percentage in parentheses) of all nodes in the cluster.
+In cases of ties, both minor subject areas are shown.
+Abbreviations: Electrical and Electronic Engineering (EEE); Control and Systems Engineering (CSE)}
+\label{tab:centroid_reconcile}       
+\begin{tabular}{p{8 mm}p{42 mm}l}
+\hline\noalign{\smallskip}
+Cluster & Label & Minor Subject Area \\
+\noalign{\smallskip}\hline
+18670 & Dynamical Systems & (i) EEE (14) (ii) CSE (14) \\
+18892 & Operations Research & EEE (24) \\ 
+18918 & Image Processing & (i) EEE (17) (ii) Software (17) \\ 
+18947 & Robotics & Software (12) \\ 
+18956 & Computer Vision & Computer Graphics and Computer-Aided Design (21)\\ 
+18972 & Software & Software (55) \\ 
+18974 & Applied Mathematics & Applied Mathematics (12)\\ 
+18983 & Optimization & EEE (35) \\ 
+18997 & Chaotic Systems & CSE (23)\\ 
+19008 & Hum Comp Interaction & Education (19)\\ 
+19009 & Artificial Intelligence & Computer Vision and Pattern Recognition (32)\\ 
+19013 & Security & Computer Science(all) (29)\\ 
+19026 & Architecture & EEE (35) \\ 
+19027 & Graph algorithms & Computer Networks and Communications (19)\\ 
+19030 & Databases & Software (19)\\ 
+19031 & Networks & EEE (32)\\ 
+19033 & Facial Recognition & Computer Vision and Pattern Recognition (18)\\ 
+19034 & Neurology & Neurology (12)\\ 
+19035 & Intelligent Systems & Artificial Intelligence (17)\\ 
+19036 & Comp Geometry & Software (10)\\ 
+\noalign{\smallskip}\hline
+\end{tabular}
+\end{table}
 \newpage

### 2019-12-20 Scientometrics/comp.tex
lots of changes

@@
 Computer science has experienced dramatic growth and diversification over the last twenty years.
-Towards a current understanding of the structure of this discipline, we analyze a cohort of the computer science literature.
+Towards a current understanding of the structure of this discipline, we analyze a cohort of the computer science literature using the DBLP database.
 For insight on the features of this cohort and the relationship within its components, we construct article level clusters based on either direct citations or co-citations, and reconcile them with major and minor subject categories in the All Science Journal Classification (Scopus).
-[What do we find?].
+Our study finds complementary insights can be gained by direct citation and co-citation, 
+and both point to the dramatic increase in computer science publications and scope.
+Our analyses show the emergence of new subfields, including ones that interact with external fields, such as the biological sciences, while some subfields
+have remained primarily inward looking.
+Thus,  the  division of computer science into three major subfields (hardware, software, and theory) observed by Salton and Bergmark 40 years ago is no longer
+an appropriate characterization of the computer science field.
 
@@
 
-\keywords{Bibliometrics \and Clustering \and Research Evaluation \and Computer Science}
+\keywords{Bibliometrics \and Clustering \and Research Evaluation \and Computer Science \and DBLP}
 % \PACS{PACS code1 \and PACS code2 \and more}
@@
 publications and references  and the 44,296,381 undirected edges represent citations within the dataset. 
-We refer to these data as the  \emph{comp} dataset (Fig~\ref{fig:ar_cp_annotation}, Table~\ref{tab:comp}).
+We refer to these data as the  \emph{comp} dataset (Fig.~\ref{fig:ar_cp_annotation}, Table~\ref{tab:comp}).
 
@@
 All edges were then re-ordered as before and the next pair of clusters was merged.
-The process was halted after 600 rounds to prevent large outlier clusters being generated (Fig.~\ref{fig:quad-chart}, panel d).
+The process was halted after 600 rounds to prevent large outlier clusters being generated (Fig.~\ref{fig:quad-chart}(d)).
 
@@
 suggests that using the nucleating cluster as the basis for labeling co-citation clusters (as we generated them) may be valid, although its usefulness is likely to vary according to the data being examined.
-We provide the DOIs of these nucleating pairs matched to manually assigned labels for independent review (Table~\ref{tab:centroid}.
+We provide the DOIs of these nucleating pairs matched to manually assigned labels for independent review (Table~\ref{tab:centroid}).
 
-To examine the correspondence between clusters generated by direct citation vs co-citation, we mapped the contents of these clusters to each other (Fig~\ref{fig:graclus_cocit_fig}).
+To examine the correspondence between clusters generated by direct citation vs co-citation, we mapped the contents of these clusters to each other (Fig.~\ref{fig:graclus_cocit_fig}).
  At a threshold of 15\%, similar to other cross-matching, 90\% (18/20) of the co-cited clusters mapped to 1 or 2 direct citation clusters.
@@
 
-Analyzing clusters generated using co-citation links is more challenging.
-The data suggest two co-existing patterns.
-One in which the nodes in a co-citation cluster map largely to one or two direct citation clusters.
-The second, which may account for more than 50\% of the nodes in a co-citation cluster, is where the nodes in co-citation cluster are distributed across all 20 direct citation clusters.
-The latter is intriguing in its implications of a web of such citational links gluing the body of scientific literature together.
+%Analyzing clusters generated using co-citation links is more challenging. 
+A comparison of the clusters generated using direct citation and co-citation show interesting contrasts. 
+In some cases, 
+%The data suggest two co-existing patterns. One in which 
+the nodes in a co-citation cluster map largely to one or two direct citation clusters, but  in some other cases, the nodes in a co-citation cluster are taken from a large number of the direct citation clusters.
+%The second, which may account for more than 50\% of the nodes in a co-citation cluster, is where the nodes in co-citation cluster are distributed across all 20 direct citation clusters. 
+The latter condition is intriguing in its implications of a web of co-citational links gluing the body of scientific literature together.
 
-Reasonable critiques of our approach are: (i) use of the DBLP dataset and the efficiency of matching to Scopus, which may not capture all aspects of computer science and its interactions with other fields, (ii) the basis for clustering, and (iii) mapping the results of this clustering against a classification designed around journals rather than individual articles.
-Our focus on high-level features and a preference for simplicity and intuitiveness in our choice of methods may mitigate these concerns.
-
+Overall we observed that in the 40 years since Salton and Bergmark's landmark paper,
+ the field of computer science has not only expanded in volume, it has expanded in its interactions with other fields, and has
+also resulted in new subfields.
+%Significant interactions with the biological sciences in particular were observed, suggesting that computer science has been stimulated by
+%biology and also impacted biology. 
+The focus of this article was on high-level features, and a preference for simplicity and intuitiveness in the choice of methods.
+This preference may mitigate questions  regarding generalizability and the specific choices we made, such as the
+ (i) use of the DBLP dataset and the efficiency of matching to Scopus, which may not capture all aspects of computer science and its interactions with other fields, (ii) the basis for clustering, and (iii) mapping the results of this clustering against a classification designed around journals rather than individual articles.
+Future research should examine the growth and changes in the field of computer science to investigate the changes at a more detailed
+level.
 \clearpage
@@
 \begin{figure}[ht]
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=0.45]{scopus_dblp_graclus3.pdf}
-% figure caption is below the figure
-\caption{Heat map for the clustering obtained by direct citation. The  y-axis (rows) correspond to topics, defined by Scopus characterizations, and the
-x-axis (columns) represent the 20 different clusters.  
-Each cluster is characterized by topics that label at least 15\% of the publications in the cluster.
- }
-\label{fig:heatmap}       % Give a unique label
-\end{figure}
-
-\begin{figure}[ht]
 \centering
@@
 \begin{figure}[ht]
+\centering
 % Use the relevant command to insert your figure file.
 % For example, with the graphicx package use
-  \includegraphics[scale=0.45]{scopus_dblp_heatmap3.pdf}
+  \includegraphics[scale=0.45]{scopus_dblp_graclus3.pdf}
+% figure caption is below the figure
+\caption{Heat map for the clustering obtained by direct citation. The  y-axis (rows) correspond to topics, defined by Scopus characterizations, and the
+x-axis (columns) represent the 20 different clusters.  
+Each cluster is characterized by topics that label at least 15\% of the publications in the cluster.
+ }
+\label{fig:heatmap}       % Give a unique label
+\end{figure}
+
+\newpage
+
+\begin{figure}[ht]
+\centering
+% Use the relevant command to insert your figure file.
+% For example, with the graphicx package use
+  \includegraphics[scale=0.5]{scopus_dblp_heatmap3.pdf}
 % figure caption is below the figure
@@
 The number of publications in each cluster, the conductance~\cite{shun_parallel_2016} of each cluster, the total number ASJC minor subject area labels assigned to publications in each cluster and the number of
-unique labels in each cluster are shown}
+unique labels in each cluster are shown.}
 \label{tab:graclus}       
@@
 \begin{table}[ht]
-\caption{\emph{Nucleating Co-citations.} For each of the 20 co-citation clusters, the pair with the strongest edge (greatest normalized co-citation frequency) is shown below along with a manually assigned label}
+\caption{\emph{Nucleating Co-citations.} For each of the 20 co-citation clusters, the pair with the strongest edge (greatest normalized co-citation frequency) is shown below along with a manually assigned label.}
 \label{tab:centroid}       
@@
 In cases of ties, both minor subject areas are shown.
-Abbreviations: Electrical and Electronic Engineering (EEE); Control and Systems Engineering (CSE)}
+Abbreviations: Electrical and Electronic Engineering (EEE); Control and Systems Engineering (CSE).}
 \label{tab:centroid_reconcile}       

### 2019-12-20 Scientometrics/comp.tex
update

@@
 
-\title{A Vignetted View of Computer Science through Citation Analysis}
+\title{Viewing Computer Science through Citation Analysis}
 %\thanks{Grants or other notes
@@
 \begin{abstract}
-Computer science has experienced dramatic growth and diversification over the last twenty years.
-Towards a current understanding of the structure of this discipline, we analyze a cohort of the computer science literature using the DBLP database.
-For insight on the features of this cohort and the relationship within its components, we construct article level clusters based on either direct citations or co-citations, and reconcile them with major and minor subject categories in the All Science Journal Classification (Scopus).
-Our study finds complementary insights can be gained by direct citation and co-citation, 
-and both point to the dramatic increase in computer science publications and scope.
-Our analyses show the emergence of new subfields, including ones that interact with external fields, such as the biological sciences, while some subfields
-have remained primarily inward looking.
-Thus,  the  division of computer science into three major subfields (hardware, software, and theory) observed by Salton and Bergmark 40 years ago is no longer
-an appropriate characterization of the computer science field.
-
-\begin{itemize}
-\item understanding structure of communications within a field and with adjacent fields
-\item extending Salton and Bergmark and staying high-level
-\item combining article level and journal level 
-\item two clustering methods
-\item Graclus- all inclusive, unweighted edges
-\item Co-citations, highly selective and weighted edges
-\item intersection of Graclus and co-citation
-\item close out
-\end{itemize}
+Computer science has experienced dramatic growth and diversification over the last twenty years. Towards a current understanding of the structure of this discipline, we analyze 
+a cohort of the computer science literature using the DBLP database. For insight on the features of this cohort and the relationship within its components, we constructed article 
+level clusters based on either direct citations or co-citations, and reconcile them to major and minor subject categories in the All Science Journal Classification (ASJC). 
+We described complementary insights from clustering by direct citation and co-citation, and both point to the increase in computer science publications and their scope.
+Our analysis shows cross-category clusters, some that interact with external fields, such as the biological sciences, while others remain inward looking.
 
@@
 
-In terms of historical precedent, Salton and Bergmark conducted a study  in 1979 of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles)~\cite{salton_citation_1979}.
+In historical precedent, Salton and Bergmark conducted a study  in 1979 of the computer science literature (419 computer articles published in 1974,  and 3,812 references cited in these articles)~\cite{salton_citation_1979}.
 Noting that that the scientific literature serves a rich source of information to study the structure and historical development of a field, these authors described the global structure of computer science as comprising three main areas: (i) theoretical foundations, such as theory of computation, (ii) hardware and computer systems, such as architecture,  and (iii) software, such as programming systems.
@@
 However, an easy way to map scientific publications to the CCS, especially interdisciplinary articles or those from proximal fields, does not seem to be available.
+[Need to add a few more citations].
 
@@
 
-In this study, we extend the work of Salton and Bergmark by combining article and journal approaches to study trends in computer science, while also considering connections to other fields, especially biology since approximately 42\% of Scopus is classified under the top level subject areas of Life Sciences and Health Sciences.
+In this study, we extend the work of Salton and Bergmark through a combination of article and journal approaches to study trends in computer science, while also considering connections to other fields, especially biology since approximately 42\% of Scopus is classified under the top level subject areas of Life Sciences and Health Sciences.
 As a source of computer  literature, we used DBLP, a reference bibliography for computer science~\cite{dblp_ref}.
@@
 This cross-matching to Scopus also allows the use of both journal and article based classifications when clustering documents.
-Using both direct citations and co-citations as the basis for clustering, we used DBLP articles from journals and conference proceedings.
+We used DBLP articles from journals and conference proceedings to construct article clusters by using either direct citations or co-citations as links.
 We reconciled these clusters with the All Science Journal Classification (ASJC) developed and maintained by Scopus through a combination of automated and manual procedures, producing a dataset of  2,685,356 publications.
@@
 Publications were parsed from the XML source file and loaded into a PostgreSQL database.
-As part of implementing a larger data platform for research evaluation~\cite{GithubERNIE2019}, we have previously parsed the Scopus dataset, presently at over 87.8 million publications, into a custom schema in a PostgreSQL database.
+As part of implementing a larger data platform for research evaluation~\cite{GithubERNIE2019}, we have previously parsed the Scopus dataset, presently at over 88 million publications, into a custom schema in a PostgreSQL database.
 The total number of publications in Scopus labeled with major subject area Computer Science (in turn a subset of the Physical Sciences subject area) is 5,835,160.
@@
  In our high-level study of the structure of a twenty year cohort of the computer science literature, we chose to use both traditional journal-based and article-based approaches.
-Considering that traditional disciplines `may only partly reflect the actual organization of today's scientific research'~\cite{waltman_new_2012}, we constructed article clusters at high levels of aggregation using citations to examine the  computer science literature and mapped these clusters to journal-based categories.
+Considering that traditional disciplines `may only partly reflect the actual organization of today's scientific research'~\cite{waltman_new_2012}, we constructed article clusters at high levels of aggregation using citations to examine the  computer science literature and also mapped these clusters to journal-based categories to take advantage of both article level and journal level approaches.
 
@@
 \section{Discussion} Considering expansion and diversification of the field of computer science, we revisited its characterization in 1979~\cite{salton_citation_1979}.
-In comparison to Salton and Bergmark, we analyzed considerably more data, 2.68 million publications versus 391 by using two bibliographic databases, DBLP and Scopus, consisting of  7.1 million and 87.8 million publications respectively.
+In comparison to Salton and Bergmark, we analyzed considerably more data, 2.68 million publications versus 391 by using two bibliographic databases, DBLP and Scopus, consisting of  approximately 7 million and 88 million publications respectively.
 By linking the two datasets to harvest citation and metadata, we were able to construct article level clusters in two different ways and reconcile these clusters with the Scopus ASJC classification, which provides a journal level perspective.
@@
 
-%Analyzing clusters generated using co-citation links is more challenging. 
-A comparison of the clusters generated using direct citation and co-citation show interesting contrasts. 
-In some cases, 
-%The data suggest two co-existing patterns. One in which 
-the nodes in a co-citation cluster map largely to one or two direct citation clusters, but  in some other cases, the nodes in a co-citation cluster are taken from a large number of the direct citation clusters.
-%The second, which may account for more than 50\% of the nodes in a co-citation cluster, is where the nodes in co-citation cluster are distributed across all 20 direct citation clusters. 
-The latter condition is intriguing in its implications of a web of co-citational links gluing the body of scientific literature together.
+A comparison of the clusters generated using direct citation and co-citation shows interesting contrasts.
+The nodes in a co-citation cluster often map largely to one or two direct citation clusters, for example.
+98\% of the nodes in co-citation cluster 19008 map to direct citation cluster 8, which in turn aligns with theory, software, applications, and networks.
+Conversely, co- citation cluster 18947 nucleated by a pair of articles in the Journal of Applied Mathematics and Computation is distributed between direct clusters 11,16, and 17 effectively spanning Artificial Intelligence, Applied Mathematics, Biochemistry, Chemistry, Genetics, Theory, Software, Applications, and Statistics.
 
-Overall we observed that in the 40 years since Salton and Bergmark's landmark paper,
- the field of computer science has not only expanded in volume, it has expanded in its interactions with other fields, and has
-also resulted in new subfields.
-%Significant interactions with the biological sciences in particular were observed, suggesting that computer science has been stimulated by
-%biology and also impacted biology. 
 The focus of this article was on high-level features, and a preference for simplicity and intuitiveness in the choice of methods.
-This preference may mitigate questions  regarding generalizability and the specific choices we made, such as the
- (i) use of the DBLP dataset and the efficiency of matching to Scopus, which may not capture all aspects of computer science and its interactions with other fields, (ii) the basis for clustering, and (iii) mapping the results of this clustering against a classification designed around journals rather than individual articles.
-Future research should examine the growth and changes in the field of computer science to investigate the changes at a more detailed
-level.
+This preference may address questions  regarding generalizability and the specific choices we made, such as the (i) use of the DBLP dataset matched to Scopus, which may not capture all aspects of computer science and its interactions with other fields, (ii) the basis for clustering, and (iii) mapping the results of this clustering against a classification designed around journals rather than individual articles.
+We believe that a journal level combined with article level approach is useful for studies of this kind.
+
+We speculate that biology, often dominant in bibliometric studies, is restricted to two clusters on account of (i) the focus of DBLP (ii) our use of normalized co-citations (ii) the threshold set for detection.
+Future research should, of course, include complementary investigations at finer levels of granularity and sensitivity using article-level approaches that others have developed.
+
+In the 40 years since Salton and Bergmark's landmark paper, the field of computer science has not only expanded in volume, it has expanded in its interactions with other fields, and has
+also resulted in new disciplinary and interdisciplinary subfields.
+
 \clearpage
@@
 
-%\begin{acknowledgements}
-%If you'd like to thank anyone, place your comments here
-%and remove the percent signs.
-%\end{acknowledgements}
+\begin{acknowledgements}
+Research and development reported in this publication was partially supported by funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract No HHSN271201800040C (N44DA-18-1216).
+TW is supported by the Grainger Foundation.
+\end{acknowledgements}
 
@@
 %
-% \section*{Conflict of interest}
-%
-% The authors declare that they have no conflict of interest.
+ \section*{Conflict of interest}
+The authors declare that they have no conflicts of interest.
+Citation data used in this paper relied on Scopus (Elsevier Inc.) as implemented in the ERNIE project (Korobskiy et al., 2019), which is collaborative between NET ESolutions Corporation and Elsevier Inc.
+The content of this publication is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health, NET ESolutions Corporation, or Elsevier Inc.
 

### 2019-12-20 Scientometrics/comp.tex
minor edits, but look at the last paragraph

@@
 a cohort of the computer science literature using the DBLP database. For insight on the features of this cohort and the relationship within its components, we constructed article 
-level clusters based on either direct citations or co-citations, and reconcile them to major and minor subject categories in the All Science Journal Classification (ASJC). 
+level clusters based on either direct citations or co-citations, and reconciled them to major and minor subject categories in the All Science Journal Classification (ASJC). 
 We described complementary insights from clustering by direct citation and co-citation, and both point to the increase in computer science publications and their scope.
@@
 
- \emph{Overview} For the purpose of this study, our working definition of the computer science literature is all publications in the DBLP bibliography that (i) had a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography.
+ \emph{Overview} For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography that (i) had a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography.
 The underlying assumption is that records in DBLP are greatly enriched for computer science even while recognizing that coverage may be incomplete and possibly biased.
 Cross-matching DBLP publications to records in the Scopus abstract and citation database of peer-reviewed literature enabled us to harvest the richer links in Scopus as well as extract links to publications from other disciplines.
-This cross-matching to Scopus also allows the use of both journal and article based classifications when clustering documents.
+This cross-matching to Scopus also allowed the use of both journal- and article-based classifications when clustering documents.
 We used DBLP articles from journals and conference proceedings to construct article clusters by using either direct citations or co-citations as links.
@@
 In preliminary experiments, we varied the number of clusters to be formed between 10 and 50 clusters (data not shown).
-At around 20 clusters, clusters size was relatively stable with the largest cluster containing roughly 10 times the number of nodes in the smallest one~\cite{subelj_clustering_2016}.
+At around 20 clusters, clusters size was relatively stable with the largest cluster containing roughly 10 times the number of nodes in the smallest one,
+so that 20 clusters is a good choice with respect to the criteria specified in~\cite{subelj_clustering_2016}.
 Consequently, we used Graclus to generate 20 clusters, labeled 0-19 (Table~\ref{tab:graclus}), analogous to Level 1 of Waltman and van Eck's mapping of nearly 10 million publications but focused on the DBLP bibliography rather than a broader Web of Science sample~\cite{waltman_new_2012}.
@@
 
-In our implementation of variable level clustering (Fig.~\ref{fig:quad-chart}(a)), we first calculated the number of citations accumulated across Scopus for all 2,685,356 articles in \emph{comp}.
+We first calculated the number of citations accumulated across Scopus for all 2,685,356 articles in \emph{comp}.
 After discarding those publications without any citations, we restricted further analysis to highly cited articles--those in the 90th percentile of citations or higher--resulting in a dataset of size 212,311.
@@
 
-We applied variable clustering with initial parameters as follows: the threshold  $t$  is initially set to  the median normalized co-citation frequency (quantile=0.5), increment $i = 0.1$, and maximum cluster size, $mcs=200$.
+In our implementation of variable level clustering (Fig.~\ref{fig:quad-chart}(a)), 
+we set initial parameter values as follows: the threshold  $t$  is initially set to  the median normalized co-citation frequency (quantile=0.5), increment $i = 0.1$, and maximum cluster size, $mcs=200$.
 Thus, at the start, all edges below the median normalized co-citation frequency were deleted.
@@
 
-These data suggest that areas central to computer science in 2019 (Salton and Bergmark's historical triad of hardware, software, and theory) are more likely to be found in multiple clusters than peripheral topics.
+These data suggest that fields central to computer science in 2019 (Salton and Bergmark's historical triad of hardware, software, and theory) are more likely to be found in multiple clusters than peripheral fields.
 A second inference is that, in some cases, journal-based classification and our article clusters align fairly well (Hardware and Architecture).
 A third inference is that the ASJC minor subject area ``Computer Applications" is relatively broad, and publications thus labeled are present at the $>=$ 15\% level in 16 out of 20 clusters.
-Finally,   for this DBLP dataset, as we clustered it, interactions with fields outside computer science such as Biology are (Biochemistry, Neurology)  are  detected in two separate clusters.
+Finally,   for this DBLP dataset, as we clustered it, interactions with fields outside computer science such as Biology  (i.e., Biochemistry, Neurology)  are  detected in two separate clusters.
 The first appears to be the interaction of Biochemistry, Molecular Biology, and Genetics with Statistics, Mathematics, and Computer Science, and the second is the interaction of Neurology, Cognitive Neuroscience, and Artificial Intelligence.
@@
 Clustering by co-citation begins, for each cluster, with a pair of nodes that nucleates its subsequent formation.
-Thus, we also designated the pair of nodes in a cluster with the strongest edge as its nucleating pair and labeled the cluster by inspecting this pair of documents and assigning an intuitive label to it.
-These labels show high degree of correspondence  to the ASJC minor subject area that accounts for the largest fraction of the nodes in a co-citation cluster (Table~\ref{tab:centroid_reconcile}).
-The extent of this correspondence %between the manually applied label and the ASJC minor subject area 
-suggests that using the nucleating cluster as the basis for labeling co-citation clusters (as we generated them) may be valid, although its usefulness is likely to vary according to the data being examined.
+Thus, we also designated the pair of nodes in a cluster with the strongest edge as its nucleating pair and labeled the cluster by manually labeling the nucleating pair of documents.
+These labels show a high degree of correspondence  to the ASJC minor subject area that accounts for the largest fraction of the nodes in a co-citation cluster (Table~\ref{tab:centroid_reconcile}). 
+%The extent of this correspondence %between the manually applied label and the ASJC minor subject area 
+Thus, using the nucleating pair as the basis for labeling co-citation clusters (as we generated them) may be valid, although its usefulness is likely to vary according to the data being examined; we also note that manual annotation (although beneficial) is not scalable.
 We provide the DOIs of these nucleating pairs matched to manually assigned labels for independent review (Table~\ref{tab:centroid}).
@@
 
-\section{Discussion} Considering expansion and diversification of the field of computer science, we revisited its characterization in 1979~\cite{salton_citation_1979}.
-In comparison to Salton and Bergmark, we analyzed considerably more data, 2.68 million publications versus 391 by using two bibliographic databases, DBLP and Scopus, consisting of  approximately 7 million and 88 million publications respectively.
+\section{Discussion} 
+Considering expansion and diversification of the field of computer science, we revisited its characterization by Salton and Bergmark in 1979~\cite{salton_citation_1979}.
+In comparison to \cite{salton_citation_1979}, we analyzed considerably more data, 2.68 million publications versus 391 by using two bibliographic databases, DBLP and Scopus, consisting of  approximately 7 million and 88 million publications respectively.
 By linking the two datasets to harvest citation and metadata, we were able to construct article level clusters in two different ways and reconcile these clusters with the Scopus ASJC classification, which provides a journal level perspective.
@@
 A comparison of the clusters generated using direct citation and co-citation shows interesting contrasts. 
-The nodes in a co-citation cluster often map largely to one or two direct citation clusters, for example.
-98\% of the nodes in co-citation cluster 19008 map to direct citation cluster 8, which in turn aligns with theory, software, applications, and networks.
-Conversely, co- citation cluster 18947 nucleated by a pair of articles in the Journal of Applied Mathematics and Computation is distributed between direct clusters 11,16, and 17 effectively spanning Artificial Intelligence, Applied Mathematics, Biochemistry, Chemistry, Genetics, Theory, Software, Applications, and Statistics.
+The nodes in a co-citation cluster often map largely to one or two direct citation clusters: for example, 98\% of the nodes in co-citation cluster 19008 map to direct citation cluster 8, which in turn aligns with theory, software, applications, and networks.
+Conversely, co-citation cluster 18947 nucleated by a pair of articles in the Journal of Applied Mathematics and Computation is distributed between direct citation clusters 11, 16, and 17, effectively spanning Artificial Intelligence, Applied Mathematics, Biochemistry, Chemistry, Genetics, Theory, Software, Applications, and Statistics.
 
@@
 This preference may address questions  regarding generalizability and the specific choices we made, such as the (i) use of the DBLP dataset matched to Scopus, which may not capture all aspects of computer science and its interactions with other fields, (ii) the basis for clustering, and (iii) mapping the results of this clustering against a classification designed around journals rather than individual articles.
-We believe that a journal level combined with article level approach is useful for studies of this kind.
+We believe that an approach that combines journal-level  with article-level analyses is useful for studies of this kind.
 
-We speculate that biology, often dominant in bibliometric studies, is restricted to two clusters on account of (i) the focus of DBLP (ii) our use of normalized co-citations (ii) the threshold set for detection.
+We speculate that biology, often dominant in bibliometric studies, is restricted to two clusters on account of (i) the focus of DBLP,  (ii) our use of normalized co-citations, and (ii) the threshold set for detection.
 Future research should, of course, include complementary investigations at finer levels of granularity and sensitivity using article-level approaches that others have developed.
@@
 also resulted in new disciplinary and interdisciplinary subfields. 
+Furthermore, machine learning and data science, which build off computer science and statistics, 
+are emerging as major fields that are driving innovation in industry and science, and research in these areas is increasingly being performed in
+fields external to computer science.
+While DBLP provides an insight into what is commonly accepted as computer science, additional evaluation of the broader literature that
+uses and develops computer science is needed to better assess the impact of computer science.
 

### 2019-12-20 Scientometrics/comp.tex
update

@@
 Because this produces a weighted graph, clustering methods that address weights are required.
-Furthermore, co-citation produces relatively weak inter-cluster interactions, requiring additional modifications to standard clustering approaches \cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
+Clustering by co-citation also considers weak inter-cluster interactions that involve modifications to standard clustering approaches.
+\cite{boyack_cocitation_2010,boyack_improving_2013,small_structure_1974,small_clustering_1985}.
 
@@
 Unsurprisingly, the broad categories Computer Science Applications, Software, and Electrical and Electronic Engineering register in 16, 12, and 10 clusters respectively, while Artificial Intelligence mapped to 7 different clusters.
-At the other end of the range, 12 of the 31 ASJC minor subject areas were each detected in a single cluster.
+At the other end of the range, 12 of the 31 ASJC minor subject areas were each detected only in a single cluster.
 
@@
 At the threshold of 15\%, only 17 of 20 co-citation clusters mapped to at least one minor subject areas.
-In contrast to a maximum of eight minor subject areas for clustering by direct citation at the 15\% threshold (Fig.
-3, Cluster 17), no co-citation cluster maps to more than three minor subject areas.
+At the 15\% threshold, no co-citation cluster maps to more than three minor subject areas, in contrast to a maximum of eight minor subject areas for clustering by direct citation (Fig.
+3, Cluster 17), .
 The threshold had to be reduced to 10\% for all 20 co-citation clusters to map to at least one minor subject area.
@@
 Both suggest collaboration between computer science and biology.
-At the opposite end of this spectrum is the perhaps more insular cluster that maps to Hardware and Architecture, Electrical and Electronic Engineering, and Software.
+At the opposite end of this spectrum is the cluster that maps to Hardware and Architecture, Electrical and Electronic Engineering, and Software.
 These data suggest that, at least from the perspective of a high level of aggregation, some subfields within computer science may be primarily inward looking (remain concerned with fundamental questions in computer science and electrical engineering), while others are more actively engaged with fields external to computer science.
@@
 
-In the 40 years since Salton and Bergmark's landmark paper, the field of computer science has not only expanded in volume, it has expanded in its interactions with other fields, and has
-also resulted in new disciplinary and interdisciplinary subfields. 
-Furthermore, machine learning and data science, which build off computer science and statistics, 
-are emerging as major fields that are driving innovation in industry and science, and research in these areas is increasingly being performed in
-fields external to computer science.
-While DBLP provides an insight into what is commonly accepted as computer science, additional evaluation of the broader literature that
+In the 40 years since Salton and Bergmark's landmark paper, the field of computer science has not only expanded in volume, it has expanded in its interactions with other fields, and has also resulted in new disciplinary and interdisciplinary subfields.
+Furthermore, machine learning and data science, which build off computer science and statistics, are emerging as major fields that are driving innovation in industry and science, and research in these areas is increasingly being performed in fields external to computer science.While DBLP provides an insight into what is commonly accepted as computer science, additional evaluation of the broader literature that
 uses and develops computer science is needed to better assess the impact of computer science.

### 2019-12-20 Scientometrics/comp.tex
near final

@@
 \usepackage{comment}
+\usepackage{hyperref}
 %
@@
 
-\emph{Clustering} Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation, with direct citation being proposed as as the best approach to concentrate citation links~\cite{klavans_which_2017}.
+\emph{Clustering} Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation, with direct citation being proposed as as the best approach to concentrate citation links~\cite{kessler_comparison_1965,klavans_which_2017}.
 Accordingly, we used direct citation links as the basis for cluster formation, and also co-citation to obtain an alternative view.
@@
 We speculate that biology, often dominant in bibliometric studies, is restricted to two clusters on account of (i) the focus of DBLP,  (ii) our use of normalized co-citations, and (ii) the threshold set for detection.
-Future research should, of course, include complementary investigations at finer levels of granularity and sensitivity using article-level approaches that others have developed.
+Future research should, of course, include complementary investigations at finer levels of granularity and sensitivity using article-level and topic approaches that others have developed~\cite{glanzel_using_2017,boyack_clustering_2011,boyack_investigating_2017,boyack_classification_2014,sjogarde_granularity_2019,traag_louvain_2019}.
+We also refer readers to a related study of the computer science literature~\cite{chakraborty_role_2018} that is focused on evolving interdisciplinarity in computer science using data from Microsoft Academic Research and a 24 category classification of Computer Science.
 
 In the 40 years since Salton and Bergmark's landmark paper, the field of computer science has not only expanded in volume, it has expanded in its interactions with other fields, and has also resulted in new disciplinary and interdisciplinary subfields.
-Furthermore, machine learning and data science, which build off computer science and statistics, are emerging as major fields that are driving innovation in industry and science, and research in these areas is increasingly being performed in fields external to computer science.While DBLP provides an insight into what is commonly accepted as computer science, additional evaluation of the broader literature that
-uses and develops computer science is needed to better assess the impact of computer science.
+Furthermore, machine learning and data science, which build off computer science and statistics, are emerging as major fields that are driving innovation in industry and science, and research in these areas is increasingly being performed in fields external to computer science.While DBLP provides an insight into what is commonly accepted as computer science, additional evaluation of the broader literature that uses and develops computer science is needed to better assess the impact of computer science.
 

### 2019-12-20 Scientometrics/comp.tex
Scientometrics Submission

@@
 \title{Viewing Computer Science through Citation Analysis}
-%\thanks{Grants or other notes
-%about the article that should go on the front page should be
-%placed here. General acknowledgments should be placed at the end of the article.}
+
+\thanks{Research and development reported in this publication was partially supported by funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract No HHSN271201800040C (N44DA-18-1216).
+TW is supported by the Grainger Foundation.}
 \subtitle{Salton and Bergmark Redux}
@@
 
-\begin{acknowledgements}
-Research and development reported in this publication was partially supported by funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract No HHSN271201800040C (N44DA-18-1216).
-TW is supported by the Grainger Foundation.
+\begin{acknowledgements} The authors thank Henry Small for very helpful discussions.
 \end{acknowledgements}

### 2020-03-30 Scientometrics/rebuttal/rebuttal_letter.tex
updated source files

\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
%SetFonts

\title{SCIM-D-19-01397: Response to Initial Critique}
\author{George Chacko}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}

\vspace{30 mm}
\noindent Dear Dr. Gl{\"a}nzel:\\

Thank you very much for your message of March 6, 2020 in which it was communicated that the manuscript would benefit from major revisions.  We agree with this assessment and thank the reviewers for their constructive critique. Accordingly, I am (also on behalf of my co-authors) resubmitting (i) a revised manuscript with markup (ii) a clean copy with only the revisions. Lastly, I have addressed the comments of the reviewers in the remainder of this document.

I hope you will find that our revisions improve the manuscript. We would have responded sooner but the distractions of COVID-19 manifested themselves in a number of ways that impacted normal function. I also hope that you and your colleagues are safe and healthy.\\

\noindent Sincerely

\vspace{8 mm}

\noindent George Chacko, PhD

\newpage

\section*{Reviewer 1} The authors have extended the works of Salton and Bergmark on the computer science research. This study has potential. However, there are several concerns which reviewer wants to mention as follows:

\begin{enumerate}

\item Section 2 is really overwhelming with numerical values. Sometimes, its difficult to follow up the discussion. It would be easy for the reader if authors can make unique way of explaining the cleaning and merging they have done. May be in the form of a table to mention the numerical values and a flow chart to explain the flow of the process till the agglomerative clustering.

\emph{The reviewer makes a good point. We rewritten Section 2 (Materials and Methods) to include a paragraph that emphasizes flow while not eliminating any of the details we think are necessary. We think it's more readable now.}

\item Section-wise brief discussion is missing at the end of Introduction.

\emph{We have revised the Introduction to better track the flow of information through the document}

\item Quality of some images is really poor. Please improve them to make it much more visible.

\emph {We are a little puzzled by this comment, since the pdfs generated on our machines show acceptable image quality. However, we have regenerated all the images in pdf (and TIFF @600 dpi). In some cases, modified axis labels to make them more readable. Thank you for flagging this defect. In the event that the manuscript is accepted for publication, we will certainly work closely with journal staff to generate even higher resolution figures.}

\item Why is "Results" not a separate section?

\emph{This has been corrected, thank you. The error was on account of LaTeX formatting.}

\item Overall, the paper is interesting covering the field of computer science, which actually needs a separate attention, considering a lot of inter-disciplinary works fading away the actual computer science contribution. However, the presentation of this paper could be simplified for the broader audience.

\emph{Thank you for this comment, which is also raised by Reviewer 2. We have broadened the outreach in this revision.}
\end{enumerate}
\clearpage

\section*{Reviewer 2}

This manuscript overview the fields of computer science by the means of clustering for networks of direct citation or co-citation. Its originality is using DBLP bibliography, and I understand that the authors worked hard to process big data. As a result, I judge that this manuscript should be accepted. However, there are some points to be revised. (C01 - C05 are mandatory to be revised.)

\emph{Thank you for these comments. We would add respectfully that in terms of originality, our implementation of co-citation based clustering builds on rather than simply reproduces Small and Sweeney's approach.}

\begin{itemize}    
\item C01. The header ``Results" has a lack of numbering, and ``3 Discussion" will be ``4 Discussion".

\emph{Thank you for pointing this out. Our apologies, this has been fixed}

\item    C02. Some second-level headers in the sections ``2 Materials and Methods" and "Results" don't have period, so add period like "Overview.".

\emph{ Again, our thanks. We have corrected our previously sloppy editing for which we apologize}

\item C03. Update: "(Fig. 3, Cluster 17), ." $->$ "(Fig. 3, Cluster 17)."

\emph{A correction has been made}

\item C04. For the section ``1 Introduction," what is the purpose of this research, or what is this research aiming at? Ultimately, it is estimated that the part "we extend the work of Salton and Bergmark" will be the purpose. 
However, readers cannot understand the originality or significance of this research, because it seems to simply apply an existing methodology to current data. Thus, you should describe what you want to know from your 
results using the work of Salton and Bergmark. First, you should make the purpose specific in the section "1 Introduction". Second, answer to your new purpose in the section ``3 Discussion" or others (i.g. "Conclusion" if you add).
I recommend that you write an outspoken expression using "purpose" or "aim at" about your purpose for appealing your research's value to roughly-looking readers.

\emph{We interpret this comment from the reviewer as noting a lack of communication of purpose in the manuscript. We agree that in trying to reach out to multiple readerships with sometimes thinly overlapping interests, we have 
presented a broad sense of purpose. Therefore, we have tried to clarify purpose in the revision.}

\emph{Regarding `existing methodology to current data.', we will also offer that while we use Graclus, an existing methodology, for clustering by direct citation, it has not been used exhaustively in citation analysis as far as we can tell, and this is consistent with text in \v{S}ubelj, van Eck, and Waltman (2016). Further, we have modified co-citation based clustering as described by Small and Sweeney (1985). Lastly, that clustering methods tend to display sensitivity to input data such that every case has to be carefully evaluated. However, it is our responsibility to communicate this to the reader, so the reviewer's point is very well taken}

\item C05. How do the authors identify the field labels? The existing field labels would not be able to used, because your new borders by clustering and those of the exisiting field are different.

\emph{We are sorry that this was not clear. Yes, the new borders are different. Therefore, in each case we we only considered `Scopus ASJC minor subject area categories that accounted for at least 15\% of the publications in each cluster'. Thus, a cluster could map to multiple subject areas if at least 15\% of its content matched to each of them. We had to try setting different thresholds, indeed we show the heatmap for co-citation is shown at two different thresholds.}

\item C06. [Optional] In the section ``3 Discussion,"  you had better to write a limitation by excluding small fields, which may include innovative seeds. In order to use this research for the purpose of promoting academic-industry collaboration, you can also describe it as your future work. I like Fig.3 (c), because I'm excited to low score areas that may be new opportunities. Meanwhile, currently, agricultural IT is emerging and fishery starts to use IT. You may be able to provide information of new opportunities with your cutoff small fields by using figures like Fig.3 (c)

\emph{For reasons of scope and feasibility, we restricted ourselves to interpreting strong signals from a measurement at a single point in time. Further, `To focus on relatively high signal, we only considered Scopus ASJC minor subject area categories that accounted for at least 15\% of the publications in each cluster', but we have added a sentence to the Discussion about excluding small fields, which may (or may not) include innovative seeds}

\item C07. [Optional] As a significance of your research, the authors can suggest the academic about a question if some current systems that a paper connects to one field are outdated.

\emph{Even though we find the idea attractive, we are hesitant to verge into speculation. We do make the point that contextualized interpretation of these results is important and will address the suggestion to a greater extent in the revision}

\item I'm looking forward to reviewing the updated manuscript again.

\emph{Thank you!}

\end{itemize}

\end{document}

### 2020-03-30 Scientometrics/rebuttal/comp_revised.tex
updated source files

--- 2019-12-20 Scientometrics/comp.tex
@@
 \usepackage{listings}
-\usepackage{comment}
+%\usepackage{comment}
 \usepackage{hyperref}
+\usepackage{changes}
+\definechangesauthor[name={George Chacko}, color=orange]{gc}
+%\setremarkmarkup{(#2)}
+%\usepackage[firstpage]{draftwatermark}
+
+%\usepackage{draftwatermark}
+%\SetWatermarkText{Confidential Draft}
+%\SetWatermarkScale{0.5}
+%\SetWatermarkColor[gray]{0.5}
+
 %
@@
 % \journalname{myjournal}
-%
+
+% examples of changes syntax
+%This is \added[id=per,remark={we need this}]{new} text.
+% This is \added[id=per,remark={has to be in it}]{new} text.
+% This is \deleted[id=per,remark=obsolete]{unnecessary}text.
+% This is \replaced[id=per]{nice}{bad} text.
+% This is \added[remark={we need this}]{new} text.
+% This is \added[remark={has to be in it}]{new} text.
+% This is \deleted[remark=obsolete]{unnecessary}text.
+% This is \replaced{nice}{bad} text.
+% to generate a clean copy edit the \usepackage{changes} above to \usepackage[final]{changes}
+
 \begin{document}
@@
               %Fax: +123-45-678910\\
-              \email{sitaram@nete.com}           %  \\
-%             \emph{Present address:} of F. Author  %  if needed
+              \email{sitaramssd@gmail.com}           %  \\
+              \emph{Present address: Randstad USA, Atlanta, GA} 
            \and
@@
               Netelabs, NET ESolutions Corporation, McLean, VA \\
-              \email{netelabs@nwete.com}
+              \email{netelabs@nete.com}
 }
@@
 
-\begin{abstract}
+\begin{abstract}w
 Computer science has experienced dramatic growth and diversification over the last twenty years. Towards a current understanding of the structure of this discipline, we analyze 
-a cohort of the computer science literature using the DBLP database. For insight on the features of this cohort and the relationship within its components, we constructed article 
-level clusters based on either direct citations or co-citations, and reconciled them to major and minor subject categories in the All Science Journal Classification (ASJC). 
-We described complementary insights from clustering by direct citation and co-citation, and both point to the increase in computer science publications and their scope.
-Our analysis shows cross-category clusters, some that interact with external fields, such as the biological sciences, while others remain inward looking.
+a \replaced{large sample}{cohort} of the computer science literature from the DBLP database.
+For insight on the features of this cohort and the relationship within its components, we have constructed article
+level clusters based on either direct citations or co-citations, and reconciled them \replaced{with}{to} major and minor subject categories in the All Science Journal Classification (ASJC). 
+We describe complementary insights from clustering by direct citation and co-citation. \deleted[remark=repositioned]{, and both point to the increase in computer science publications and their scope}.
+Our analysis \replaced{reveals}{shows} cross-category clusters, some that interact with external fields, such as the biological sciences, while others remain inward looking.\added{Overall, we document an increase in computer science publications and their scope.}
 
@@
 And every academic discipline finds itself incorporating computing into its research and educational mission"~\cite{nas_2017}.
-More recently, the collective influence of the Internet of Things (IoT), `big' data, accessible cloud computing, and advances in artificial intelligence have been postulated as a recent driver for growth and evolution~\cite{siebel2019_digital}.
-Given this powerful influence, some understanding of the present state and structure of computer science and its relationship to other fields could inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy.
+More recently, the collective influence of the Internet of Things (IoT), `big' data, accessible cloud computing, and advances in artificial intelligence have been \replaced{presented as a driver for digital transformation}{postulated as a recent driver for growth and evolution}~\cite{siebel2019_digital}.
+Given this \replaced{rapid growth and expansion}{powerful influence}, an updated understanding of the present state and structure of computer science and its relationship to other fields \replaced{can only inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy.}{could inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy.}
 
@@
 However, an easy way to map scientific publications to the CCS, especially interdisciplinary articles or those from proximal fields, does not seem to be available.
-[Need to add a few more citations].
 
@@
 
-In this study, we extend the work of Salton and Bergmark through a combination of article and journal approaches to study trends in computer science, while also considering connections to other fields, especially biology since approximately 42\% of Scopus is classified under the top level subject areas of Life Sciences and Health Sciences.
+\replaced{The purpose of this study is to develop an improved understanding of the structure of the field of computer science relative to the landmark study of Salton and Bergmark forty years ago.
+We extend their work by takimg advantage of modern bibliographic resources and clustering technologies and using a combination of article and journal approaches to study trends in the computer science literature.
+We also consider connections to other fields, especially biology, since approximately 42\% of Scopus is classified under the top level subject areas of Life Sciences and Health Sciences.
+As a source of computer  literature, we use DBLP, a reference bibliography for computer science~\cite{dblp_ref}.
+The DBLP bibliography covers publications from computer science and includes publications from hybrid fields, where they are considered pertinent to computer science research.} {In this study, we extend the work of Salton and Bergmark through a combination of article and journal approaches to study trends in computer science, while also considering connections to other fields, especially biology since approximately 42\% of Scopus is classified under the top level subject areas of Life Sciences and Health Sciences.
 As a source of computer  literature, we used DBLP, a reference bibliography for computer science~\cite{dblp_ref}.
 The DBLP bibliography covers publications from computer science and includes publications from hybrid fields, where they are considered pertinent to computer science research.
-We describe below the high-level interactions of computer science within the Physical Sciences, and with the Social Sciences, Life Sciences, and Health Sciences.
+We describe below the high-level interactions of computer science within the Physical Sciences, and with the Social Sciences, Life Sciences, and Health Sciences.}
+
+We XXX XXXX XXXXX
 
@@
 
- \emph{Overview} For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography that (i) had a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography.
-The underlying assumption is that records in DBLP are greatly enriched for computer science even while recognizing that coverage may be incomplete and possibly biased.
-Cross-matching DBLP publications to records in the Scopus abstract and citation database of peer-reviewed literature enabled us to harvest the richer links in Scopus as well as extract links to publications from other disciplines.
-This cross-matching to Scopus also allowed the use of both journal- and article-based classifications when clustering documents.
+\emph{Overview} \added[id=gc,{remark=Reviewer 1}]{The underlying assumption is that, notwithstanding incomplete coverage, records in DBLP are greatly enriched for computer science~\cite{dblp_ref}.
+Therefore, the contents of DBLP are an excellent sample of the computer science literature to analyze.
+The workflow described in the following paragraphs of Materials and Methods, consists at a high-level of (i) merging the DBLP and Scopus datasets using digital object identifiers(DOIs) (ii) extracting cited references for the articles common to DBLP and Scopus (iii) clustering by direct citation and by our modification of co-citation based clustering.
+The outcome was a dataset of 8,000,411 publications.}
+
+\replaced{Our working definition of the computer science literature, for the purpose of this study, was all publications in the DBLP bibliography that (i) had a digital object identifier DOI, and (ii) could also be matched to article identifiers in the Scopus bibliography.}{For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography that (i) had a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography.} Cross-matching DBLP publications to records in the Scopus abstract and citation database of peer-reviewed literature enables us to harvest the richer links in Scopus, as well as \added{to} extract links to publications from other disciplines.
+Cross-matching to Scopus also allows the use of journal-\added{based} classifications when clustering documents at the article-level.
 We used DBLP articles from journals and conference proceedings to construct article clusters by using either direct citations or co-citations as links.
-We reconciled these clusters with the All Science Journal Classification (ASJC) developed and maintained by Scopus through a combination of automated and manual procedures, producing a dataset of  2,685,356 publications.
+We reconciled these clusters with the All Science Journal Classification (ASJC) developed and maintained by Scopus through a combination of automated and manual procedures, producing a dataset of  2,685,356 publications, which when combined with cited references extracted from Scopus grew to 8,000,411 publications.
 
-\emph{Data} A stable release of the DBLP computer science bibliography~\cite{dblp_ref} consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz. 
+\added{\emph{DBLP data}}A stable release of the DBLP computer science bibliography~\cite{dblp_ref} consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz.
 Slightly over 95\% of the publications within were published after 1996.
 Publications were parsed from the XML source file and loaded into a PostgreSQL database.
-As part of implementing a larger data platform for research evaluation~\cite{GithubERNIE2019}, we have previously parsed the Scopus dataset, presently at over 88 million publications, into a custom schema in a PostgreSQL database.
+
+\added{\emph{Scopus data}} As part of implementing a larger data platform for research evaluation~\cite{GithubERNIE2019}, we have previously parsed the Scopus dataset, presently at over 88 million publications, into a custom schema in a PostgreSQL database.
 The total number of publications in Scopus labeled with major subject area Computer Science (in turn a subset of the Physical Sciences subject area) is 5,835,160.
-Records in the DBLP dataset were matched to Scopus identifiers using digital object identifiers (DOIs).
+
+\added{Merging and graph construction} Records in the DBLP dataset were matched to Scopus identifiers using digital object identifiers (DOIs).
 This procedure resulted in a dataset of 2,685,356 DBLP publications with Scopus identifiers where 1,278,322 (47.6\%) were labeled as article and 1,407,034 (52.4\%) as conference proceedings.
-References cited by these publications were then extracted from Scopus (7,129,006 records), resulting in a total of 8,000,411
-publications and references. 
-We represented these data using a graph where the 8,000,411 nodes represent
-publications and references  and the 44,296,381 undirected edges represent citations within the dataset. 
-We refer to these data as the  \emph{comp} dataset (Fig.~\ref{fig:ar_cp_annotation}, Table~\ref{tab:comp}).
+References cited by these publications were then extracted from Scopus (7,129,006 records), resulting in a total of 8,000,411 publications and references.
+
+\added{We represented these  8,000,411 records, referred to as the  \emph{comp} dataset (Fig.~\ref{fig:ar_cp_annotation}, Table~\ref{tab:comp}), as a graph where the 8,000,411 nodes represent publications and references  and the 44,296,381 undirected edges represent citations within the dataset.}
 
@@
 
-We first calculated the number of citations accumulated across Scopus for all 2,685,356 articles in \emph{comp}.
-After discarding those publications without any citations, we restricted further analysis to highly cited articles--those in the 90th percentile of citations or higher--resulting in a dataset of size 212,311.
-We then identified 4,318,305 publications in Scopus that cite these 212,311 articles from \emph{comp}.
-For each of the 4,318,305 citing publications in turn, all possible ${n \choose 2}$ reference pairs were generated from a publication's cited references, where $n$ is the number of references in a publication.
-The cited reference pairs this generated were then restricted to those in the set of 212,311 highly cited papers previously identified.
+\added{We began by identifying highly cited articles in \emph{comp} and selected those in the 90th percentile (212,311 articles).
+We then identified ~4.3 million publications in Scopus that cite these 212,311 articles.
+For each of the 4.3 million citing publications in turn, all possible ${n \choose 2}$ reference pairs were generated from a publication's cited references, where $n$ is the number of references in a publication.
+The cited reference pairs this generated were then restricted to those where both members of a pair were in the set of 212,311 highly cited papers previously identified.
 A total of 46,463,117 unique co-cited pairs were thus obtained.
@@
 These data were represented in a graph where each node was a publication and the weighted edge between the pair was the normalized co-citation frequency.
-\par
+\par }
 
@@
 
-\section*{Results}
+\section{Results}
 \label{sec:results}
 
- In our high-level study of the structure of a twenty year cohort of the computer science literature, we chose to use both traditional journal-based and article-based approaches.
+ In our high-level study of the structure of a twenty year sample of the computer science literature, we chose to use both traditional journal-based and article-based approaches.
 Considering that traditional disciplines `may only partly reflect the actual organization of today's scientific research'~\cite{waltman_new_2012}, we constructed article clusters at high levels of aggregation using citations to examine the  computer science literature and also mapped these clusters to journal-based categories to take advantage of both article level and journal level approaches.
 
-\emph{Data} The process of selection and matching resulted in a dataset of  publications (Materials and Methods).
-Of 4,291,130 DBLP publications with DOIs, only  2,685,356 had corresponding DOIs in Scopus.
-Of these roughly 2.68 million publications, approximately 2.07 million were assigned ASJC codes in Scopus corresponding to Computer Science (major subject area with 13 minor subject areas (Table~\ref{tab:comp}), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (Fig.~\ref{fig:ar_cp_annotation}).
+\deleted{\emph{Data}The process of selection and matching resulted in a dataset of  publications (Materials and Methods).
+Of 4,291,130 DBLP publications with DOIs, only  2,685,356 had corresponding DOIs in Scopus.} Of 2.68 million publications in \emph{comp}, approximately 2.07 million were assigned ASJC codes in Scopus corresponding to Computer Science (major subject area with 13 minor subject areas (Table~\ref{tab:comp}), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (Fig.~\ref{fig:ar_cp_annotation}).
 The set of 2.07 million publications classified under the major subject area Computer Science in Scopus spanned all 13 minor subject areas with Software at 30.3\%  being the largest component and Computer Science (miscellaneous) at 0.9\% the smallest.
@@
 At the 15\% threshold, no co-citation cluster maps to more than three minor subject areas, in contrast to a maximum of eight minor subject areas for clustering by direct citation (Fig.
-3, Cluster 17), .
+3, Cluster 17).
 The threshold had to be reduced to 10\% for all 20 co-citation clusters to map to at least one minor subject area.
-We interpret these data as indicative of broader clusters created by weaker linkages that accumulate during the agglomerative clustering phase~\cite{small_clustering_1985}.
+We interpret these results as indicative of broader clusters created by weaker linkages that accumulate during the agglomerative clustering phase~\cite{small_clustering_1985}.
 
@@
 \section{Discussion} 
-Considering expansion and diversification of the field of computer science, we revisited its characterization by Salton and Bergmark in 1979~\cite{salton_citation_1979}.
+\added{Considering expansion and diversification of the field of computer science, we revisited its characterization by Salton and Bergmark in 1979~\cite{salton_citation_1979}.
 In comparison to \cite{salton_citation_1979}, we analyzed considerably more data, 2.68 million publications versus 391 by using two bibliographic databases, DBLP and Scopus, consisting of  approximately 7 million and 88 million publications respectively.
-By linking the two datasets to harvest citation and metadata, we were able to construct article level clusters in two different ways and reconcile these clusters with the Scopus ASJC classification, which provides a journal level perspective.
+By linking the two datasets, we were able to harvest citation data as well as other metadata that enabled theo construct article level clusters in two different ways and reconciliation with the Scopus ASJC classification, for a journal level perspective.}
 
@@
 We believe that an approach that combines journal-level  with article-level analyses is useful for studies of this kind.
+\added{However, we acknowledge that our approach would not detect emerging fields with few publications that could be important signs of innovation.}
 
-We speculate that biology, often dominant in bibliometric studies, is restricted to two clusters on account of (i) the focus of DBLP,  (ii) our use of normalized co-citations, and (ii) the threshold set for detection.
+We speculate that biology, often dominant in bibliometric studies, is restricted to two clusters on account of (i) the focus of DBLP,  (ii) our use of normalized co-citations, and (iii) the threshold set for detection.
 Future research should, of course, include complementary investigations at finer levels of granularity and sensitivity using article-level and topic approaches that others have developed~\cite{glanzel_using_2017,boyack_clustering_2011,boyack_investigating_2017,boyack_classification_2014,sjogarde_granularity_2019,traag_louvain_2019}.
-We also refer readers to a related study of the computer science literature~\cite{chakraborty_role_2018} that is focused on evolving interdisciplinarity in computer science using data from Microsoft Academic Research and a 24 category classification of Computer Science.
+We also refer readers to a related study of the computer science literature~\cite{chakraborty_role_2018} that is focused on evolving interdisciplinarity in computer science using data from Microsoft Academic Research and a classification of Computer Science into 24 categories.
 
@@
 %%%%%%%%%
-\section*{Figures}
+\section{Figures}
+{Figures}
 %%%%%%%%%
@@
 % For example, with the graphicx package use
-  \includegraphics[scale=0.6]{ar_cp_ratio.pdf}
+\includegraphics[scale=0.75]{ar_cp_ratio.pdf}
+% generated by ar_cp_ratio.R
 % figure caption is below the figure
@@
 % For example, with the graphicx package use
-  \includegraphics[scale=0.4]{graclus_comparison.pdf}
+\includegraphics[scale=0.6]{graclus_comparison.pdf}
+% generated by conductance.R script
 % figure caption is below the figure
@@
 \centering
-\includegraphics[width=0.9\textwidth]{quad-chart-narrow.pdf}
+\includegraphics[width=0.85\textwidth]{quad_plot.pdf}
+%\includegraphics[width=0.9\textwidth]{quad-chart-narrow.pdf}
 \caption{Co-citation analysis.
@@
 % For example, with the graphicx package use
-  \includegraphics[scale=0.45]{scopus_dblp_graclus3.pdf}
+\includegraphics[scale=0.6]{scopus_dblp_graclus3.pdf}
+% generated by scopus_dblp_graclus2.R
 % figure caption is below the figure
@@
 % For example, with the graphicx package use
-  \includegraphics[scale=0.5]{scopus_dblp_heatmap3.pdf}
+\includegraphics[scale=0.6]{scopus_dblp_heatmap3.pdf}
+% generated by scopus_cocit_heatmap.R
 % figure caption is below the figure
@@
 % For example, with the graphicx package use
-  \includegraphics[scale=0.45]{graclus_cocit_fig.pdf}
+  \includegraphics[scale=0.6]{graclus_cocit_fig.pdf}
 % figure caption is below the figure
@@
 \begin{acknowledgements} The authors thank Henry Small for very helpful discussions.
+Research and development reported in this publication was partially supported by funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract No HHSN271201800040C (N44DA-18-1216).
+TW is supported by the Grainger Foundation.
+Citation data used in this paper relied on Scopus (Elsevier Inc.) as implemented in the ERNIE project (Korobskiy et al., 2019), which is collaborative between NET ESolutions Corporation and Elsevier Inc.
+We thank our Elsevier colleagues for their support of the ERNIE project.
 \end{acknowledgements}
@@
 The authors declare that they have no conflicts of interest.
-Citation data used in this paper relied on Scopus (Elsevier Inc.) as implemented in the ERNIE project (Korobskiy et al., 2019), which is collaborative between NET ESolutions Corporation and Elsevier Inc.
 The content of this publication is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health, NET ESolutions Corporation, or Elsevier Inc.
+
+\bibliographystyle{spmpsci}      % mathematics and physical sciences
+%\bibliographystyle{spphys}       % APS-like style for physics
+\bibliography{comp}   % name your BibTeX data base
+
+% Non-BibTeX users please use
+
+\end{document}
 
@@
 % Non-BibTeX users please use
-
+\listofchanges
 \end{document}

### 2020-03-30 Scientometrics/rebuttal/comp_revised.tex
resubmit

@@
 \usepackage{hyperref}
-\usepackage{changes}
+\usepackage[final]{changes}
+%\usepackage{changes}
 \definechangesauthor[name={George Chacko}, color=orange]{gc}
@@
 
-\begin{abstract}w
+\begin{abstract}
 Computer science has experienced dramatic growth and diversification over the last twenty years. Towards a current understanding of the structure of this discipline, we analyze 
@@
 
-We XXX XXXX XXXXX
+\added{We constructed clusters of articles using either direct citation or co-citations and match these clusters to ASJC categories to place them in context.
+We also align clusters from direct citations to those from co-citations and discuss our findings, Overall, we note cross category clusters with different degrees of interaction with fields outside computer science.}
 
@@
 For each of the 4.3 million citing publications in turn, all possible ${n \choose 2}$ reference pairs were generated from a publication's cited references, where $n$ is the number of references in a publication.
-The cited reference pairs this generated were then restricted to those where both members of a pair were in the set of 212,311 highly cited papers previously identified.
+The cited reference pairs generated were then restricted to those where both members of a pair were in the set of 212,311 highly cited papers previously identified.
 A total of 46,463,117 unique co-cited pairs were thus obtained.
@@
  In our high-level study of the structure of a twenty year sample of the computer science literature, we chose to use both traditional journal-based and article-based approaches.
-Considering that traditional disciplines `may only partly reflect the actual organization of today's scientific research'~\cite{waltman_new_2012}, we constructed article clusters at high levels of aggregation using citations to examine the  computer science literature and also mapped these clusters to journal-based categories to take advantage of both article level and journal level approaches.
+Considering that traditional disciplinary categories `may only partly reflect the actual organization of today's scientific research'~\cite{waltman_new_2012}, we constructed article clusters at high levels of aggregation using citations to examine the  computer science literature and also mapped these clusters to journal-based categories to take advantage of both article level and journal level approaches.
 
@@
 At the threshold of 15\%, only 17 of 20 co-citation clusters mapped to at least one minor subject areas.
-At the 15\% threshold, no co-citation cluster maps to more than three minor subject areas, in contrast to a maximum of eight minor subject areas for clustering by direct citation (Fig.
-3, Cluster 17).
-The threshold had to be reduced to 10\% for all 20 co-citation clusters to map to at least one minor subject area.
+At the 15\% threshold, no co-citation cluster maps to more than three minor subject areas, in contrast to a maximum of eight minor subject areas for clustering by direct citation \added{(Fig.
+3, Cluster 17).} The threshold had to be reduced to 10\% for all 20 co-citation clusters to map to at least one minor subject area.
 We interpret these results as indicative of broader clusters created by weaker linkages that accumulate during the agglomerative clustering phase~\cite{small_clustering_1985}.
@@
 These labels show a high degree of correspondence  to the ASJC minor subject area that accounts for the largest fraction of the nodes in a co-citation cluster (Table~\ref{tab:centroid_reconcile}).
-%The extent of this correspondence %between the manually applied label and the ASJC minor subject area 
-Thus, using the nucleating pair as the basis for labeling co-citation clusters (as we generated them) may be valid, although its usefulness is likely to vary according to the data being examined; we also note that manual annotation (although beneficial) is not scalable.
+While using the nucleating pair as the basis for labeling co-citation clusters (as we generated them) may be valid, its usefulness is likely to vary according to the data being examined; we also note that manual annotation (although beneficial) is not scalable.
 We provide the DOIs of these nucleating pairs matched to manually assigned labels for independent review (Table~\ref{tab:centroid}).
@@
 The focus of this article was on high-level features, and a preference for simplicity and intuitiveness in the choice of methods.
-This preference may address questions  regarding generalizability and the specific choices we made, such as the (i) use of the DBLP dataset matched to Scopus, which may not capture all aspects of computer science and its interactions with other fields, (ii) the basis for clustering, and (iii) mapping the results of this clustering against a classification designed around journals rather than individual articles.
+This preference influences the specific choices we made, such as the (i) use of the DBLP dataset matched to Scopus, which may not capture all aspects of computer science and its interactions with other fields, (ii) the basis for clustering, and (iii) mapping the results of this clustering against a classification designed around journals rather than individual articles.
 We believe that an approach that combines journal-level  with article-level analyses is useful for studies of this kind.
-\added{However, we acknowledge that our approach would not detect emerging fields with few publications that could be important signs of innovation.}
+\added{However, we acknowledge that our approach would not detect emerging fields with few publications that could be important signs of innovation.
+We also feel strongly that contextualized interpretation by domain experts should be performed on results generated by such approaches.}
 
@@
 \clearpage
-\section*{Tables}
+\section{Tables}
 
 \begin{table}[ht]
-\caption{Characterization of the \emph{comp} dataset relative to Scopus ASJC minor subject areas.}
+\caption{Characterization of the \emph{comp} dataset relative to Scopus ASJC minor subject areas under computer science.}
 \label{tab:comp}       
@@
 \hline\noalign{\smallskip}
-Cluster & Nucleating Pair & NCF & Manual Label \\
+Cluster & Nucleating Pair & NCF & Label \\
 \noalign{\smallskip}\hline

### 2020-05-11 Scientometrics/rebuttal2/rebuttal_letter.tex
R2

--- 2020-03-30 Scientometrics/rebuttal/rebuttal_letter.tex
@@
 \emph {We are a little puzzled by this comment, since the pdfs generated on our machines show acceptable image quality.
-However, we have regenerated all the images in pdf (and TIFF @600 dpi).
-In some cases, modified axis labels to make them more readable.
+However, we have regenerated all the images in pdf (and TIFF @600 dpi as supplementary images for the journal).
+In some cases, we also modified axis labels to make them more readable.
 Thank you for flagging this defect.
@@
 
-\emph{Regarding `existing methodology to current data.', we will also offer that while we use Graclus, an existing methodology, for clustering by direct citation, it has not been used exhaustively in citation analysis as far as we can tell, and this is consistent with text in \v{S}ubelj, van Eck, and Waltman (2016).
+\emph{Regarding `existing methodology to current data.', we would say that the purpose of this paper was discovery.
+However, we will also offer that while we use Graclus, an existing methodology, for clustering by direct citation, it has not been used exhaustively in citation analysis as far as we can tell, and this is consistent with text in \v{S}ubelj, van Eck, and Waltman (2016).
 Further, we have modified co-citation based clustering as described by Small and Sweeney (1985).
 Lastly, that clustering methods tend to display sensitivity to input data such that every case has to be carefully evaluated.
-However, it is our responsibility to communicate this to the reader, so the reviewer's point is very well taken}
+However, it is our responsibility to communicate all this to the reader, so the reviewer's point is very well taken and we thank her/him for it}
 
@@
 
-\emph{Even though we find the idea attractive, we are hesitant to verge into speculation.
+\emph{Even though we find the idea attractive, we are hesitant to verge into excessive speculation.
 We do make the point that contextualized interpretation of these results is important and will address the suggestion to a greater extent in the revision}

### 2020-05-11 Scientometrics/rebuttal2/rebuttal_letter_2.tex
R2

\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
%SetFonts

\title{SCIM-D-19-01397: Response to Review of R1}
\author{George Chacko}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}

\vspace{30 mm}
\noindent Dear Dr. Gl{\"a}nzel:\\

Thank you very much for your message of May 11, 2020 in which it was communicated that our manuscript could be considered for publication `after you have carried out the corrections 
suggested by reviewer(s)'. Accordingly, I am (also on behalf of my co-authors) resubmitting a revised manuscript. I have addressed the comments  of the reviewers below. For the second time, 
we thank the reviewers for their constructive critique and timely reviews. If our views diverge from those of the reviewers, we do so respectfully.

\vspace{8 mm}

\noindent Sincerely

\vspace{8 mm}

\noindent George Chacko, PhD

\newpage

\section*{Reviewer 1} 1. By visibility of the images Reviewer means that Fig. 3 (especially a \& b) labels on x and y axis are of very small font. 2. After the revision, paper is better understandable then before. Also, Since authors have 
used DBLP and Scopus, Reviewer would like authors to add  some discussion in the introduction about other two widely used bibliometric sources i.e google scholar and web of science and mention pros and cons of why they have used 
the said two and why not these two. Authors may take hint of such discussion from papers like: Zavadskas, E. K., Skibniewski, M. J., \& Antucheviciene, J. (2014). Performance analysis of Civil Engineering Journals based on the Web of Science® 
database. Archives of Civil and Mechanical Engineering, 14(4), 519-527. Shukla, A. K., Janmaijaya, M., Abraham, A., \& Muhuri, P. K. (2019). Engineering applications of artificial intelligence: A bibliometric analysis of 30 years (1988-2018). 
Engineering Applications of Artificial Intelligence, 85, 517-532.ienc

\subsection*{Response}
\begin{enumerate}
\item Fig 3 has been revised to increase the size of x-axis and y-axis labels and scaled by placing it in landscape mode. Thank you for clarifying our question.
\item We have carefully considered the suggestion to expand the introduction to discuss Google Scholar and Web of Science as alternatives to Scopus. This suggestion is appreciated. 
However, we believe that an expanded discussion of the perceived relative merits of these commercial databases is distracting since the reasons advanced in the literature to recommend one 
over the other are contextual, disciplinary, and often subjective. We have added a sentence, however, mentioning Scopus and Web of Science and citing Archambault 2009 (below).

Our use of DBLP is justified in the Introduction as a `reference bibliography for computer science'. We also mention the limitations of ASJC and other journal based classifications to identify 
disciplines, hence our reliance on article level clusters. In the course of responding to this point. we found a conference paper by Pham and Klamma, that also identifies DBLP as important 
to the field of computer science, and we have included it in our bibliography.

In terms of Scopus, the choice was simple. Our implementation of Scopus is full-featured (all ~90 million records and associated metadata are resident on our servers). Thus, we do not need to scrape 
data or use a throttled API to access information. We also chose Scopus over Web of Science because of its its well designed XML structure. We previously used Web of Science (also as resident on 
our servers) and our experience is that the two are comparable in terms of coverage but clearly not identical. This is consistent with Eric Archambault's observations.  Lastly, our budget does not permit us to afford two subscriptions.

Google Scholar is a non-starter as far as we are concerned. It suffers from false positives, duplicates, includes grey literature, and does not allow large scale analysis. As mentioned by Martin-Martin et al. (2019),
`Google Scholar, Web of Science, and Scopus: Which is best for me?' on the London School of Economics website, \emph{``The question, as our colleague Professor Harzing put it, is whether 
we are ready to accept a trade-off: going beyond the comfortable and orderly borders of curated databases in exchange for more diverse coverage.''} We do not consider this trade-off useful for 
our purposes. Accordingly, we find value in the orderly borders of the Scopus and DBLP curated databases over the use of Google Scholar for this study.

We examined the references suggested by the reviewer; Zavadskas et al. (2014) and Shukla et al. (2019). The text within is not inconsistent with the points we make in our first paragraph but did not 
provide additional insight that would persuade us to expand the Introduction further. For example, Shukla et al. state that.``WoS is the first multidisciplinary bibliographic index of journal publications designed. 
It is considered a standard data source for bibliometrics. Other databases such as Scopus by Elsevier are also used by bibliometricians." and ``A comparison with other indexing platforms such as Scopus, 
Google Scholar can be a good future scope of this study.''

To examine the issue raised by the reviewer, we read some comprehensive comparisons of these databases but did not find compelling reasons to further expand the Introduction. We have listed a few 
of these sources below. Archambault's paper is relevant (or at least consistent with) our comment that the choice of either Web of Science or Scopus is contextual and can be subjective. 
MacRoberts and MacRoberts assert that all bibliographic databases have limitations and we agree.

\begin{itemize}
\item Yang and Meho (2007) Citation Analysis: A Comparison of Google Scholar, Scopus, and Web of Science JASIST 10.1002/meet.14504301185
\item Falagas et al. (2007) Comparison of PubMed, Scopus, Web of Science, and Google Scholar: Strengths and Weaknesses FASEB J. 10.1096/fj.07-9492LSF
\item Archambault et al. (2009)  Comparing bibliometric statistics obtained from the Web of Science and Scopus. JASIST  10.1002/asi.21062
\item Harzing and Alakangas (2016) Google Scholar, Scopus and the Web of Science: a longitudinal and cross-disciplinary comparison Scientometrics 10.1007/s11192-015-1798-9
\item MacRoberts and MacRoberts (2018) JASIST 10.1002/asi.23970
\end{itemize}
\end{enumerate}

\section*{Reviewer 2}

This manuscript overviews the fields of computer science by the means of clustering for networks of direct citation or co-citation. Comparing with the previous version, the manuscript 
becomes easy for readers to understand the content along the purpose. However, there are some mis-spelligs or mis-formattings.
- Please search "co-citation. .", and delete one of these periods.
- Please search "by takimg advantage of modern bibliographic resources", and change "takimg" to "taking".
- Please search "discuss our findings, Overall", and change from comma to period.
- Please search "y:axis", and change to "y-axis".

The formats of second-level headings are mixed like "Co-Citation." and "Scopus data", whose difference is to finish with a period or without it. Please unify the format, and the reviewer recommends 
the italic (and bold) "Co-Citation:", refering to\\ http://journals.ieeeauthorcenter.ieee.org/wp-content/uploads/sites/7/IEEE-Editorial-Style-Manual.pdf.
- "DBLP dataA" must be "DBLP data A".
- I guess that "Merging and graph construction" is also one of the second-level headings.
I have judged that these are proofreading tasks, but the number of these is large. Thus, please check your manuscript to repair careless mistakes by yourself. I expect I cannot find all.
As a result, I recommend minor revision close to proofreading-level. About the content, there is no problem

\subsection*{Response}

We thank the reviewer for these comments. We have corrected all the typographic errors noted and made further corrections at the proofreading level. Some of them seem to have been generated by 
the \emph{changes} package juxtaposing sections of text when run in clean mode. We have constructed a clean copy.

\end{document}

### 2020-05-11 Scientometrics/rebuttal2/comp_revised_2.tex
R2

--- 2020-03-30 Scientometrics/rebuttal/comp_revised.tex
@@
 %\SetWatermarkColor[gray]{0.5}
+
+\usepackage{rotating}
+\usepackage{pdflscape}
 
@@
 level clusters based on either direct citations or co-citations, and reconciled them \replaced{with}{to} major and minor subject categories in the All Science Journal Classification (ASJC). 
-We describe complementary insights from clustering by direct citation and co-citation. \deleted[remark=repositioned]{, and both point to the increase in computer science publications and their scope}.
-Our analysis \replaced{reveals}{shows} cross-category clusters, some that interact with external fields, such as the biological sciences, while others remain inward looking.\added{Overall, we document an increase in computer science publications and their scope.}
+We describe complementary insights from clustering by direct citation and co-citation, and both point to the increase in computer science publications and their scope.
+Our analysis \replaced{reveals}{shows} cross-category clusters, some that interact with external fields, such as the biological sciences, while others remain inward looking.
+\added{Overall, we document an increase in computer science publications and their scope.}
 
@@
 And every academic discipline finds itself incorporating computing into its research and educational mission"~\cite{nas_2017}.
-More recently, the collective influence of the Internet of Things (IoT), `big' data, accessible cloud computing, and advances in artificial intelligence have been \replaced{presented as a driver for digital transformation}{postulated as a recent driver for growth and evolution}~\cite{siebel2019_digital}.
-Given this \replaced{rapid growth and expansion}{powerful influence}, an updated understanding of the present state and structure of computer science and its relationship to other fields \replaced{can only inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy.}{could inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy.}
+More recently, the collective influence of the Internet of Things (IoT), `big' data, accessible cloud computing, and advances in artificial intelligence have been presented as a driver for digital transformation~\cite{siebel2019_digital}.
+Given this rapid growth and expansion, an updated understanding of the present state and structure of computer science and its relationship to other fields can inform planning and policy making at multiple levels from national level funding all the way down to faculty hiring strategy.
 
@@
 
-Other classification systems are available, such as the All Science Journal Classification (ASJC) developed and maintained by Scopus, the Web of Science research and categorical classifications from Clarivate Analytics, and the National Science Foundation classification system~\cite{nsf_classification,scopus_ref,wos_ref}.
-Scopus and the Web of Science also include comprehensive bibliographies with citation links and proprietary unique identifiers for publications.
-The Scopus All Science Journal Classification (ASJC), which we use in this study, is organized  into 4 subject areas, 27 major subject areas, and 334 minor subject areas.
+Other classification systems are available, such as the All Science Journal Classification (ASJC) developed and maintained by Scopus, the Web of Science research and categorical classifications from Clarivate Analytics, and the National Science Foundation classification system respectively~\cite{nsf_classification,scopus_ref,wos_ref}.
+Scopus and the Web of Science are commercially available databases with comprehensive, though not identical coverage~\cite{archambault_2009}, that can be used to conduct large scale analyses.
+The All Science Journal Classification (ASJC), maintained by Scopus, which we use in this study, is organized  into 4 subject areas, 27 major subject areas, and 334 minor subject areas.
 All three systems rely on applying one or more journal-derived labels to articles.
+
 A logical prediction, given the diversity of articles within journals, is limited specificity at the article level.
@@
 
-\replaced{The purpose of this study is to develop an improved understanding of the structure of the field of computer science relative to the landmark study of Salton and Bergmark forty years ago.
-We extend their work by takimg advantage of modern bibliographic resources and clustering technologies and using a combination of article and journal approaches to study trends in the computer science literature.
+The purpose of this study is to develop an improved understanding of the structure of the field of computer science relative to the landmark study of Salton and Bergmark forty years ago.
+We extend their work by taking advantage of modern bibliographic resources and clustering technologies and using a combination of article and journal approaches to study trends in the computer science literature.
 We also consider connections to other fields, especially biology, since approximately 42\% of Scopus is classified under the top level subject areas of Life Sciences and Health Sciences.
-As a source of computer  literature, we use DBLP, a reference bibliography for computer science~\cite{dblp_ref}.
-The DBLP bibliography covers publications from computer science and includes publications from hybrid fields, where they are considered pertinent to computer science research.} {In this study, we extend the work of Salton and Bergmark through a combination of article and journal approaches to study trends in computer science, while also considering connections to other fields, especially biology since approximately 42\% of Scopus is classified under the top level subject areas of Life Sciences and Health Sciences.
-As a source of computer  literature, we used DBLP, a reference bibliography for computer science~\cite{dblp_ref}.
+As a source of computer  literature, we use DBLP, a reference bibliography for computer science~\cite{dblp_ref,pham_2010}.
 The DBLP bibliography covers publications from computer science and includes publications from hybrid fields, where they are considered pertinent to computer science research.
-We describe below the high-level interactions of computer science within the Physical Sciences, and with the Social Sciences, Life Sciences, and Health Sciences.}
-
-\added{We constructed clusters of articles using either direct citation or co-citations and match these clusters to ASJC categories to place them in context.
-We also align clusters from direct citations to those from co-citations and discuss our findings, Overall, we note cross category clusters with different degrees of interaction with fields outside computer science.}
+We construct clusters of articles using either direct citation or co-citations and match these clusters to ASJC categories to place them in context.
+We also aligned clusters from direct citations to those from co-citations and discuss our findings.
+Overall, we note cross category clusters with different degrees of interaction with fields outside computer science.
 
@@
 
-\emph{Overview} \added[id=gc,{remark=Reviewer 1}]{The underlying assumption is that, notwithstanding incomplete coverage, records in DBLP are greatly enriched for computer science~\cite{dblp_ref}.
+\emph{Overview} Our underlying assumption is that, notwithstanding incomplete coverage, records in DBLP are greatly enriched for computer science~\cite{dblp_ref,pham_2010}.
 Therefore, the contents of DBLP are an excellent sample of the computer science literature to analyze.
 The workflow described in the following paragraphs of Materials and Methods, consists at a high-level of (i) merging the DBLP and Scopus datasets using digital object identifiers(DOIs) (ii) extracting cited references for the articles common to DBLP and Scopus (iii) clustering by direct citation and by our modification of co-citation based clustering.
-The outcome was a dataset of 8,000,411 publications.}
+The outcome was a dataset of 8,000,411 publications.
 
-\replaced{Our working definition of the computer science literature, for the purpose of this study, was all publications in the DBLP bibliography that (i) had a digital object identifier DOI, and (ii) could also be matched to article identifiers in the Scopus bibliography.}{For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography that (i) had a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography.} Cross-matching DBLP publications to records in the Scopus abstract and citation database of peer-reviewed literature enables us to harvest the richer links in Scopus, as well as \added{to} extract links to publications from other disciplines.
+Our working definition of the computer science literature, for the purpose of this study, was all publications in the DBLP bibliography that (i) had a digital object identifier DOI, and (ii) could also be matched to article identifiers in the Scopus bibliography.
+Cross-matching DBLP publications to records in the Scopus abstract and citation database of peer-reviewed literature enables us to harvest the richer links in Scopus, as well as extract links to publications from other disciplines.
 Cross-matching to Scopus also allows the use of journal-\added{based} classifications when clustering documents at the article-level.
-We used DBLP articles from journals and conference proceedings to construct article clusters by using either direct citations or co-citations as links.
+We used DBLP articles from journals and conference proceedings to construct article clusters using either direct citations or co-citations as links.
 We reconciled these clusters with the All Science Journal Classification (ASJC) developed and maintained by Scopus through a combination of automated and manual procedures, producing a dataset of  2,685,356 publications, which when combined with cited references extracted from Scopus grew to 8,000,411 publications.
 
-\added{\emph{DBLP data}}A stable release of the DBLP computer science bibliography~\cite{dblp_ref} consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz.
+\emph{DBLP data.} A stable release of the DBLP computer science bibliography~\cite{dblp_ref} consisting of 7,079,994 records was downloaded as dblp-2018-08-01.xml.gz.
 Slightly over 95\% of the publications within were published after 1996.
@@
 
-\added{\emph{Scopus data}} As part of implementing a larger data platform for research evaluation~\cite{GithubERNIE2019}, we have previously parsed the Scopus dataset, presently at over 88 million publications, into a custom schema in a PostgreSQL database.
+\emph{Scopus data.} As part of implementing a larger data platform for research evaluation~\cite{GithubERNIE2019}, we have previously parsed the Scopus dataset, presently at over 88 million publications, into a custom schema in a PostgreSQL database.
 The total number of publications in Scopus labeled with major subject area Computer Science (in turn a subset of the Physical Sciences subject area) is 5,835,160.
 
-\added{Merging and graph construction} Records in the DBLP dataset were matched to Scopus identifiers using digital object identifiers (DOIs).
+\emph{Merging and graph construction.} Records in the DBLP dataset were matched to Scopus identifiers using digital object identifiers (DOIs).
 This procedure resulted in a dataset of 2,685,356 DBLP publications with Scopus identifiers where 1,278,322 (47.6\%) were labeled as article and 1,407,034 (52.4\%) as conference proceedings.
@@
 
-\added{We represented these  8,000,411 records, referred to as the  \emph{comp} dataset (Fig.~\ref{fig:ar_cp_annotation}, Table~\ref{tab:comp}), as a graph where the 8,000,411 nodes represent publications and references  and the 44,296,381 undirected edges represent citations within the dataset.}
+We represented these  8,000,411 records, referred to as the  \emph{comp} dataset (Fig.~\ref{fig:ar_cp_annotation}, Table~\ref{tab:comp}), as a graph where the 8,000,411 nodes represent publications and references  and the 44,296,381 undirected edges represent citations within the dataset.
 
-\emph{Clustering} Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation, with direct citation being proposed as as the best approach to concentrate citation links~\cite{kessler_comparison_1965,klavans_which_2017}.
+\emph{Clustering.} Clustering of publications is commonly accomplished through direct citation, bibliographic coupling, and co-citation, with direct citation being proposed as as the best approach to concentrate citation links~\cite{kessler_comparison_1965,klavans_which_2017}.
 Accordingly, we used direct citation links as the basis for cluster formation, and also co-citation to obtain an alternative view.
@@
 
- \emph {Direct Citation} Graclus~\cite{graclus_2007} is a spectral graph clustering package that optimizes  various clustering criteria, including normalized cut, ratio cut, and ratio association, and that has previously been applied to citation data~\cite{subelj_clustering_2016}.
+\emph {Direct Citation.} Graclus~\cite{graclus_2007} is a spectral graph clustering package that optimizes  various clustering criteria, including normalized cut, ratio cut, and ratio association, and that has previously been applied to citation data~\cite{subelj_clustering_2016}.
 We used v1.2 in our experiments.
@@
 These results suggest that Graclus produces a final cluster that effectively serves as a container for `left over publications' during the clustering procedure.
-Therefore, we limited our consideration of cluster 19 (the final of the twenty clusters)  when interpreting results.
+Therefore, we limited our consideration of cluster 19 (the last of the twenty clusters)  when interpreting our results.
 The remaining 19 clusters had conductance values ranging from 0.09 to 0.25 with a median conductance of 0.15 (Fig.~\ref{fig:graclus_comparison_conductance}, Table~\ref{tab:comp}).
@@
 
-\added{We began by identifying highly cited articles in \emph{comp} and selected those in the 90th percentile (212,311 articles).
+We began by identifying highly cited articles in \emph{comp} and selected those in the 90th percentile (212,311 articles).
 We then identified ~4.3 million publications in Scopus that cite these 212,311 articles.
@@
 These data were represented in a graph where each node was a publication and the weighted edge between the pair was the normalized co-citation frequency.
-\par }
+\par
 
-In our implementation of variable level clustering (Fig.~\ref{fig:quad-chart}(a)), 
-we set initial parameter values as follows: the threshold  $t$  is initially set to  the median normalized co-citation frequency (quantile=0.5), increment $i = 0.1$, and maximum cluster size, $mcs=200$.
+In our implementation of variable level clustering (Fig.~\ref{fig:quad-chart}(a)), we set initial parameter values as follows: the threshold  $t$  is initially set to  the median normalized co-citation frequency (quantile=0.5), increment $i = 0.1$, and maximum cluster size, $mcs=200$.
 Thus, at the start, all edges below the median normalized co-citation frequency were deleted.
@@
 
-\deleted{\emph{Data}The process of selection and matching resulted in a dataset of  publications (Materials and Methods).
-Of 4,291,130 DBLP publications with DOIs, only  2,685,356 had corresponding DOIs in Scopus.} Of 2.68 million publications in \emph{comp}, approximately 2.07 million were assigned ASJC codes in Scopus corresponding to Computer Science (major subject area with 13 minor subject areas (Table~\ref{tab:comp}), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (Fig.~\ref{fig:ar_cp_annotation}).
+Of 2.68 million publications in \emph{comp}, approximately 2.07 million were assigned ASJC codes in Scopus corresponding to Computer Science (major subject area with 13 minor subject areas (Table~\ref{tab:comp}), with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (Fig.~\ref{fig:ar_cp_annotation}).
 The set of 2.07 million publications classified under the major subject area Computer Science in Scopus spanned all 13 minor subject areas with Software at 30.3\%  being the largest component and Computer Science (miscellaneous) at 0.9\% the smallest.
@@
 
-\iffalse
-Overall, 38.86\% of the publications were assigned to one minor subject area, 78.1\% to two minor subject areas, 90.9\% to three minor subject areas, and 0.0003\% assigned to 8 different minor subject areas.
-\fi
-
-\emph{Clustering by Direct Citation} We constructed article-level clusters of this computer science dataset at a sufficiently high level of aggregation to avoid cognitive challenge and cross-matched them to the Scopus ASJC classification.
+\emph{Clustering by Direct Citation.} We constructed article-level clusters of this computer science dataset at a sufficiently high level of aggregation to avoid cognitive challenge and cross-matched them to the Scopus ASJC classification.
 To focus on relatively high signal, we only considered Scopus ASJC minor subject area categories that accounted for at least 15\% of the publications in each cluster.
@@
 \section{Discussion} 
-\added{Considering expansion and diversification of the field of computer science, we revisited its characterization by Salton and Bergmark in 1979~\cite{salton_citation_1979}.
+Considering expansion and diversification of the field of computer science, we revisited its characterization by Salton and Bergmark in 1979~\cite{salton_citation_1979}.
 In comparison to \cite{salton_citation_1979}, we analyzed considerably more data, 2.68 million publications versus 391 by using two bibliographic databases, DBLP and Scopus, consisting of  approximately 7 million and 88 million publications respectively.
-By linking the two datasets, we were able to harvest citation data as well as other metadata that enabled theo construct article level clusters in two different ways and reconciliation with the Scopus ASJC classification, for a journal level perspective.}
+By linking the two datasets, we were able to harvest citation data as well as other metadata that enabled theo construct article level clusters in two different ways and reconciliation with the Scopus ASJC classification, for a journal level perspective.
 
@@
 We believe that an approach that combines journal-level  with article-level analyses is useful for studies of this kind.
-\added{However, we acknowledge that our approach would not detect emerging fields with few publications that could be important signs of innovation.
-We also feel strongly that contextualized interpretation by domain experts should be performed on results generated by such approaches.}
+However, we acknowledge that our approach would not detect emerging fields with few publications that could be important signs of innovation.
+We also feel strongly that contextualized interpretation by domain experts should be performed on results generated by such approaches.
 
@@
 Future research should, of course, include complementary investigations at finer levels of granularity and sensitivity using article-level and topic approaches that others have developed~\cite{glanzel_using_2017,boyack_clustering_2011,boyack_investigating_2017,boyack_classification_2014,sjogarde_granularity_2019,traag_louvain_2019}.
-We also refer readers to a related study of the computer science literature~\cite{chakraborty_role_2018} that is focused on evolving interdisciplinarity in computer science using data from Microsoft Academic Research and a classification of Computer Science into 24 categories.
+We also refer readers to related studies of the computer science literature~\cite{chakraborty_role_2018} that are focused on (i) evolving interdisciplinarity in computer science using data from Microsoft Academic Research and a classification of Computer Science into 24 categories (ii) combining the DBLP and CiteSeerX libraries to generate a knowledge network~\cite{pham_2010}.
 
@@
 \newpage
-
+\begin{landscape}
 \begin{figure}[ht]
 \centering
-\includegraphics[width=0.85\textwidth]{quad_plot.pdf}
+\includegraphics[width=1.4\textwidth]{vlc_thrice.pdf}
+%\includegraphics[width=0.9\textwidth]{quad_plot.pdf}
 %\includegraphics[width=0.9\textwidth]{quad-chart-narrow.pdf}
@@
 \end{figure}
-
+\end{landscape}
 \newpage
@@
 A minimum threshold of 15\% was set.
-Graclus cluster 19, the 20th cluster, did not map to any cluster on the y:axis.}
+Graclus cluster 19, the 20th cluster, did not map to any cluster on the y-axis.}
 \label{fig:graclus_cocit_fig}       % Give a unique label
@@
 TW is supported by the Grainger Foundation.
-Citation data used in this paper relied on Scopus (Elsevier Inc.) as implemented in the ERNIE project (Korobskiy et al., 2019), which is collaborative between NET ESolutions Corporation and Elsevier Inc.
+Citation data used in this paper relied on Scopus data as implemented in the ERNIE project (Korobskiy et al., 2019), which is collaborative between NET ESolutions Corporation and Elsevier Inc.
 We thank our Elsevier colleagues for their support of the ERNIE project.
@@
 The authors declare that they have no conflicts of interest.
+Elsevier personnel played no role in conceptualization, experimental design, review of results, or conclusions presented.
 The content of this publication is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health, NET ESolutions Corporation, or Elsevier Inc.

### 2020-05-11 Scientometrics/rebuttal2/comp_revised_2.tex
R2

@@
 % end of file template.tex
-
-\subsection{Subsection title}
-\label{sec:2}
-as required. Don't forget to give each section
-and subsection a unique label.
-\paragraph{Paragraph headings} Use paragraph headings as needed.
-\begin{equation}
-a^2+b^2=c^2
-\end{equation}
-
-% For one-column wide figures use
-\begin{figure}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics{example.eps}
-% figure caption is below the figure
-\caption{Please write your figure caption here}
-\label{fig:1}       % Give a unique label
-\end{figure}
-%
-% For two-column wide figures use
-\begin{figure*}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[width=0.75\textwidth]{example.eps}
-% figure caption is below the figure
-\caption{Please write your figure caption here}
-\label{fig:2}       % Give a unique label
-\end{figure*}
-
-\begin{figure}[ht]
-\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=0.25]{vlc.pdf}
-% figure caption is below the figure
-\caption{Schematic representation of variable clustering protocol modified from Small and Sweeney (1985) \cite{small_clustering_1985}.
-Three parameters are specified: (i) a threshold or starting level based on a quantile of normalized co-citation frequency, (ii) a level increment, and  (iii) a maximum cluster size.
-Input data is a set of co-cited publications with edge-weight defined by normalized co-citation frequencies.
-Green clusters are within the max cluster size.
-At the initial threshold, $t1$, a single cluster below the maximum cluster size, $mcs$ (green), along with one large cluster above it (red) are generated.
-As the threshold is incremented to $t2$, additional clusters of acceptable size is generated.
-The cascade continues to completion, which is defined by all clusters being of size less than or equal to the $mcs$.
-In this schematic, five rounds are adequate for the process to run to completion.}
-\label{fig:vlc_process}       % Give a unique label
-\end{figure}
-
-\begin{figure}[ht]
-\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
- \includegraphics[scale=0.5]{cocit_venn2.pdf}
-% figure caption is below the figure
-\caption{High-level disciplinary composition of publications in $\sim$2,000 clusters generated by variable-level clustering  of co-citation data.
-%Variable Level Clustering. 
-84,591 nodes from were matched to the 4 subject areas, 
-27 major subject areas, and 334 minor subject areas in the Scopus ASJC classification. Since 82.5\% of these nodes were assigned more to than one minor subject category, 
-we assigned fractional counts for the four subject areas that summed to 1 for each article. The figure shows a four way Venn Diagram~\cite{chen_venn_2011} illustrating the 
-relative frequencies of publications from the Physical Sciences, Social Sciences, Life Sciences, and Health Sciences.}
-\label{fig:cocitr_venn2}       % Give a unique label
-\end{figure}
-\newpage
-
-\begin{figure}[ht]
-\centering
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[scale=0.5]{merge_select.pdf}
-% figure caption is below the figure
-\caption{Clustering produced using co-citation data; the y-axis is the cluster size (given logarithmically), and the x-axis is the number of iterations of the agglomerative clustering technique.
-Note that iterating more than 600 times produces a very large cluster.
-}
-\label{fig:merge_select}       % Give a unique label
-\end{figure}
-
-%
-% For tables use

### 2020-05-11 Scientometrics/rebuttal2/rebuttal_letter_2.tex
R2

@@
 \item Fig 3 has been revised to increase the size of x-axis and y-axis labels and scaled by placing it in landscape mode. Thank you for clarifying our question.
-\item We have carefully considered the suggestion to expand the introduction to discuss Google Scholar and Web of Science as alternatives to Scopus. This suggestion is appreciated. 
+\item We have carefully considered the suggestion, which we appreciate, to expand the introduction to discuss Google Scholar and Web of Science as alternatives to Scopus. 
 However, we believe that an expanded discussion of the perceived relative merits of these commercial databases is distracting since the reasons advanced in the literature to recommend one 
@@
 data or use a throttled API to access information. We also chose Scopus over Web of Science because of its its well designed XML structure. We previously used Web of Science (also as resident on 
-our servers) and our experience is that the two are comparable in terms of coverage but clearly not identical.
-This is consistent with Eric Archambault's observations.
+our servers) and our experience is that the two are comprehensive in terms of coverage but clearly not identical.
+This is consistent with Archambault's observations.
 Lastly, our budget does not permit us to afford two subscriptions.
@@
 
-To examine the issue raised by the reviewer, we read some comprehensive comparisons of these databases but did not find compelling reasons to further expand the Introduction. We have listed a few 
-of these sources below. Archambault's paper is relevant (or at least consistent with) our comment that the choice of either Web of Science or Scopus is contextual and can be subjective. 
+To examine the issue raised by the reviewer, we read some comprehensive comparisons of these databases (below) but did not find compelling reasons to further expand the Introduction. Archambault's 
+paper is relevant (or at least consistent with) our comment that the choice of either Web of Science or Scopus is contextual and can be subjective. 
 MacRoberts and MacRoberts assert that all bibliographic databases have limitations and we agree.
@@
 
-We thank the reviewer for these comments. We have corrected all the typographic errors noted and made further corrections at the proofreading level. Some of them seem to have been generated by 
-the \emph{changes} package juxtaposing sections of text when run in clean mode. We have constructed a clean copy.
+We thank the reviewer for these comments. We have corrected all the typographic errors noted and made further corrections at the proofreading level to try and ensure consistency. Some of these errors 
+seem to have been generated by the \emph{changes} package juxtaposing sections of text when run in clean mode. We have constructed a clean copy.
 

### 2020-05-11 Scientometrics/rebuttal2/comp_revised_2.tex
R2

@@
 Overall, we note cross category clusters with different degrees of interaction with fields outside computer science.
-
+\clearpage
 \section{Materials and Methods}
@@
 
-\emph{Overview} Our underlying assumption is that, notwithstanding incomplete coverage, records in DBLP are greatly enriched for computer science~\cite{dblp_ref,pham_2010}.
+\emph{Overview.} Our underlying assumption is that, notwithstanding incomplete coverage, records in DBLP are greatly enriched for computer science~\cite{dblp_ref,pham_2010}.
 Therefore, the contents of DBLP are an excellent sample of the computer science literature to analyze.
@@
 
-\emph {Direct Citation.} Graclus~\cite{graclus_2007} is a spectral graph clustering package that optimizes  various clustering criteria, including normalized cut, ratio cut, and ratio association, and that has previously been applied to citation data~\cite{subelj_clustering_2016}.
+\emph{Direct Citation.} Graclus~\cite{graclus_2007} is a spectral graph clustering package that optimizes  various clustering criteria, including normalized cut, ratio cut, and ratio association, and that has previously been applied to citation data~\cite{subelj_clustering_2016}.
 We used v1.2 in our experiments.
@@
 
-\emph{Co-Citation.} For an alternate view of these DBLP data, we constructed clusters using co-citation, the frequency with which a pair of articles is cited by other articles \cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}.
+\emph{Co-citation.} For an alternate view of these DBLP data, we constructed clusters using co-citation, the frequency with which a pair of articles is cited by other articles \cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}.
 Co-citation, first described independently by Small and Marshakova in 1973 \cite{marshakova-shaikevich_co-citation_1973}, provides insight into the emergence of new ideas derived from the association of previously independent ones.
@@
 We then identified ~4.3 million publications in Scopus that cite these 212,311 articles.
-For each of the 4.3 million citing publications in turn, all possible ${n \choose 2}$ reference pairs were generated from a publication's cited references, where $n$ is the number of references in a publication.
-The cited reference pairs generated were then restricted to those where both members of a pair were in the set of 212,311 highly cited papers previously identified.
+For each of the 4.3 million citing publications in turn,
+all possible ${n \choose 2}$ reference pairs were generated from a publication's cited references, where $n$ is the number of references in a publication.
+The cited reference pairs generated were then restricted to those where both members of a pair were in the
+set of 212,311 highly cited papers previously identified.
 A total of 46,463,117 unique co-cited pairs were thus obtained.
-The frequency of these co-cited pairs was then computed across the \emph{comp} dataset  and normalized using Salton's cosine formula~\cite{salton_citation_1979} to limit dominance by areas with high citation activity.
+The frequency of these co-cited pairs was then computed across the \emph{comp} dataset  and normalized using Salton's cosine
+formula~\cite{salton_citation_1979} to limit dominance by areas with high citation activity.
 These data were represented in a graph where each node was a publication and the weighted edge between the pair was the normalized co-citation frequency.
-\par
 
@@
 
+\clearpage
 \section{Results}
@@
 This suggests that the majority of co-cited pairs tend to lie within the same cluster of publications linked by citations and,  by extension, tend towards disciplinarity rather than interdisciplinarity.
-
+\clearpage
 \section{Discussion} 
@@
 % figure caption is below the figure
-\caption{Conductance Measurements of Clusters Generated by Graclus of the direct citation dataset.
+\caption{Conductance measurements of clusters generated by Graclus of the direct citation dataset.
 2,685,356 DBLP publications, 7,129,006 cited references, and 44,296,381 citations were clustered using Graclus into 18 (grac\_18), 20 (grac\_20), or 22 (grac-22) clusters.
@@
 \begin{table}[ht]
-\caption{Descriptive statistics of the 20 clusters produced from the \emph{dataset} using Graclus (direct citation).
+\caption{Descriptive statistics of the 20 clusters produced from the \emph{comp} dataset using Graclus (direct citation).
 The number of publications in each cluster, the conductance~\cite{shun_parallel_2016} of each cluster, the total number ASJC minor subject area labels assigned to publications in each cluster and the number of
@@
 \begin{table}[ht]
-\caption{\emph{Nucleating Co-citations.} For each of the 20 co-citation clusters, the pair with the strongest edge (greatest normalized co-citation frequency) is shown below along with a manually assigned label.}
+\caption{Nucleating co-citations.
+For each of the 20 co-citation clusters, the pair with the strongest edge (greatest normalized co-citation frequency) is shown below along with a manually assigned label.}
 \label{tab:centroid}       
@@
 \begin{table}[ht]
-\caption{\emph{Nucleating Co-citations} Manually assigned labels for nucleating co-cited pairs (Table~\ref{tab:centroid}) are matched to the ASJC minor subject area that constitutes the largest fraction (shown as percentage in parentheses) of all nodes in the cluster.
+\caption{Nucleating co-citations.
+Manually assigned labels for nucleating co-cited pairs (Table~\ref{tab:centroid}) are matched to the ASJC minor subject area that constitutes the largest fraction (shown as percentage in parentheses) of all nodes in the cluster.
 In cases of ties, both minor subject areas are shown.
